### 2013-12-12 ms.tex
initial

\documentclass{emulateapj}

\usepackage[dvipdf]{epsfig} 
\usepackage[dvips]{rotating}
\usepackage{subfigure}

\newcommand{\IRAS}{{\it IRAS}}
\newcommand{\HERSCHEL}{{\it Herschel}}
\newcommand{\SPITZER}{{\it Spitzer}}

\bibpunct{(}{)}{;}{a}{}{,}

\shorttitle{Planck Dust Model}

\shortauthors{Meisner \& Finkbeiner}

\begin{document}

\title{Two-component thermal dust emission model: application to the Planck HFI maps}
\author{Aaron M. Meisner\altaffilmark{1,2}}
\author{Douglas P. Finkbeiner\altaffilmark{1,2}}
\altaffiltext{1}{Department of Physics, Harvard University, 17 Oxford Street, 
Cambridge, MA 02138, USA; ameisner@fas.harvard.edu}
\altaffiltext{2}{Harvard-Smithsonian Center for Astrophysics, 60 Garden St, 
Cambridge, MA 02138, USA; dfinkbeiner@cfa.harvard.edu}

\begin{abstract}
We have fit the FDS99 two-component dust emission model over
the full sky, based on dust SEDs comprised of  Planck HFI and IRAS 100$\mu$m. 
As a result, we have obtained maps of optical depth $\tau_{545}$ and dust 
temperatures $T_1$ and $T_2$,  with angular resolution  $\sim$6$'$. These maps 
serve as an interesting comparison to alternative models, for example 
one-component models with varying $T$ and $\beta$. We also expect the derived 
optical depth to be useful as a cross-check for other extinction estimates, 
such as the SFD98 map, which assumed $\beta = 2$ single-component dust 
emission, as well as forthcoming dust maps based on observations of stars in 
the optical rather than infrared emission.
\end{abstract}

\section{Introduction}

\section{Data}

We have made use of the Planck 2013 data release, specifically the 217 GHz, 
353 GHz, 545 GHz and 857 GHz channels Planck Collaboration (2013a). We use the 
versions of these maps which have been corrected for zodiacal light by the 
Planck team, using the zodiacal light model described in Planck Collaboration 
(2013b). For each pixel on the sky, Planck thus provides us with four data 
points of the dust emission SED. The angular resolution of these maps is 
$5.5$. TODO: actually smooth all of the maps to a common PSF of XX arcmin.

To add information about the dust emission on the Wien side of its spectrum,
we include IRAS 100$\mu$m. We use the SFD reprocessing of IRAS 100$\mu$m, which
we will refer to as \verb|i100| (Schegel et al. 1998). \verb|i100|
\section{Pre-processing}

\subsection{Unit Conversions}

Some of the maps in native format are provided in thermodynamic $\delta T$, 
while others are provided in units of MJy/sr. Before performing any fits, 
we convert all measurements to MJy/sr following the guidelines of the document
``HFI-unit conversion and colour correction instructions v1.2''.

\subsection{Zodiacal Light Removal}
Cite the appropriate reference for the Planck ZL model.

\subsection{Smoothing to common resolution}

\subsection{CMB Subtraction}
The CMB is effectively imperceptible at 857 GHz, but can be noticed at a 
low level at 545 GHz, and is extremely bright at 217 GHz and 353 GHz relative 
to the diffuse Galactic emission we wish to characterize.

\subsection{Finite Bandpass Correction}

\subsection{Correlation against HI}
The raw Planck maps we have downloaded show offsets relative to HI, in the
sense that the FIR emission does not go to zero when HI emission goes to
zero. Since HI correlates linearly with far-IR emission in the diffuse ISM, 
when the optical depth is low and molecular effects are negligible, we modeled
far IR emission as a constant times HI emission, plus some offset. We then
subtracted the best-fit offset such that

\subsection{Molecular Emission}

\section{Model}
Our model is that of FDS99, which consists of two populations of dust 
grain emitting as modified blackbodies, but with different temperatures
and different power law emissivities $\beta$.

\subsection{Fitting Methodology}

\begin{figure*}[ht]
\begin{center}
\epsfig{file=t2_0128.eps, width=7.0in}
\caption{Our best-fit $T_2$, binned to 27.5$'$ resolution}
\end{center}
\end{figure*}

\end{document}

### 2013-12-12 ms.tex
more sub-sections added to outline, bibliography included, other clean-up

@@
 \begin{abstract}
-We have fit the FDS99 two-component dust emission model over
-the full sky, based on dust SEDs comprised of  Planck HFI and IRAS 100$\mu$m. 
-As a result, we have obtained maps of optical depth $\tau_{545}$ and dust 
-temperatures $T_1$ and $T_2$,  with angular resolution  $\sim$6$'$. These maps 
+We have fit the \cite{FDS99} two-component dust emission model over
+the full sky, based on Galactic dust SEDs composed of  Planck HFI and \cite{SFD} 
+\IRAS~100$\mu$m. As a result, we have obtained maps of dust optical depth $\tau_{545}$ 
+and temperatures $T_1$ and $T_2$,  with angular resolution  $\sim$6$'$. These maps 
 serve as an interesting comparison to alternative models, for example 
@@
 emission, as well as forthcoming dust maps based on observations of stars in 
-the optical rather than infrared emission.
+the optical rather than infrared emission. %mention the enhanced temperature resolution relative
+% to SFD
 \end{abstract}
@@
 we will refer to as \verb|i100| (Schegel et al. 1998). \verb|i100|
+
 \section{Pre-processing}
@@
 
+\subsection{Point Sources}
+
 \section{Model}
@@
 grain emitting as modified blackbodies, but with different temperatures
-and different power law emissivities $\beta$.
+and different emissivity power law indices $\beta$.
 
@@
 
+\section{Conclusion}
+
+Based on observations obtained with Planck (http://www.esa.int/Planck), 
+an ESA science mission with instruments and contributions directly funded 
+by ESA Member States, NASA, and Canada.
+
+\bibliographystyle{apj}
+\bibliography{twocomp.bib}
+
 \end{document}

### 2013-12-13 ms.tex
more text, more references

@@
 \newcommand{\SPITZER}{{\it Spitzer}}
+\newcommand{\PLANCK}{{\it Planck}}
 
@@
 
-\shorttitle{Planck Dust Model}
+\shorttitle{\PLANCK~Dust Model}
 
@@
 
-\title{Two-component thermal dust emission model: application to the Planck HFI maps}
+\title{Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps}
 \author{Aaron M. Meisner\altaffilmark{1,2}}
@@
 \begin{abstract}
-We have fit the \cite{FDS99} two-component dust emission model over
-the full sky, based on Galactic dust SEDs composed of  Planck HFI and \cite{SFD} 
-\IRAS~100$\mu$m. As a result, we have obtained maps of dust optical depth $\tau_{545}$ 
-and temperatures $T_1$ and $T_2$,  with angular resolution  $\sim$6$'$. These maps 
-serve as an interesting comparison to alternative models, for example 
-one-component models with varying $T$ and $\beta$. We also expect the derived 
-optical depth to be useful as a cross-check for other extinction estimates, 
-such as the SFD98 map, which assumed $\beta = 2$ single-component dust 
-emission, as well as forthcoming dust maps based on observations of stars in 
-the optical rather than infrared emission. %mention the enhanced temperature resolution relative
-% to SFD
+We present full-sky maps of dust optical depth and temperature derived from 
+the \cite{FDS99} two-component dust emission model fitted to \PLANCK~217, 353, 
+545, 857 GHz and \cite{SFD} \IRAS~100$\mu$m data. Both the optical 
+depth and temperature maps have angular resolution of $6.1'$. Such maps serve 
+as an important alternative to and comparison for other dust 
+emission models, especially the single modified blackbody model in which 
+$\beta$ and $T$ both vary spatially. We also expect the derived optical 
+depth to provide valuable cross-checks for other dust-column related data 
+products, specifically the \cite{SFD} map, which assumed 
+$\beta = 2$ single-component dust emission and included a temperature map of 
+inferior $\sim$$1.3^{\circ}$ resolution. We briefly compare our 
+best-fit two-component spectral energy distributions to those of the 
+\cite{planckdust} single-component parametrization.
+%mention the enhanced temperature resolution relative to SFD
+%Our optical depth map will also provide a useful reference for dust maps 
+%based on stellar colors rather than infrared emission.
 \end{abstract}
@@
 \section{Introduction}
+%why dust important in astronomy/astrophysics
+The presence of Galactic interstellar dust affects
+astronomical observations over a wide range of wavelengths. At mid-infrared
+and far-infrared wavelengths, Galactic dust emission is a major contributor
+to the observed sky intensity. In the optical and ultraviolet, extinction
+by foreground dust grains attenuates the signal from extragalactic sources
+over the entire sky. Understanding the properties of dust in the interstellar 
+medium (ISM) is valuable in its own right, as the ISM is the site of star 
+formation, thereby playing a crucial role in galaxy evolution. Equally if not 
+more important to the practice of astronomy, however, is accounting for dust 
+as a foreground which reddens optical/UV observations and superimposes 
+Galactic emission on low-frequency observations of the 
+cosmic microwave background (CMB). %specify ``low frequency more precisely eventually
+
+%basic background about interstellar dust emission
+
+%maybe say instead ``over the past 30/40 years...''
+%Barnard first recognized evidence for dust in astronomical observations, and
+%ever since it has been mapped in increasing detail. 
+Over the past decades, satellite observations have dramatically enhanced our
+knowledge about infrared emission from the ISM. High-latitude complexes of 
+resolved infrared sources were first identified by \cite{low84} using 
+\IRAS~60$\mu$m and 100$\mu$m observations \citep{wheelock94}. This so-called 
+``infrared cirrus,'' attributable to thermal emission from large dust grains in
+the interstellar medium, has since been probed in greater detail by a variety 
+of instruments and detected over virtually the entire sky. Beginning in 1989, 
+DIRBE  mapped the full sky at ten infrared wavelengths from 1.25$\mu$m to 
+240$\mu$m with a reliable zero point, but inferior 0.7$^{\circ}$ angular 
+resolution \citep{boggess92}.mention FIRAS specifically, since it is important 
+to FDS99.
+
+FDS99 used FIRAS to make a globally best-fit model of dust emission 
+appropriate over a very broad range of frequencies. They showed that a 
+model consisting of a single modified blackbody with power law index $\beta$ 
+could not fit the IRAS/FIRAS/DIRBE spectrum at both the Wien and 
+Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 proposed
+a spectrum consisting of two modified black bodies, each with a different
+temperature and power law index. Physically, these two components
+represent distinct dust grain species within the ISM, specifically 
+silicates and carbonaceous grains.
+
+%how what we're doing fits in
+%     where FDS99 fit in
+%     Planck data qualities that improve on data used in FDS99
+%     benefits of using Planck + FDS99 model
+%utility/applications of what we're doing
+
+%list of figures : 
+% posterior surface for some pixel, with samples from markov chain overplotted
+%    --> also overplot output best-fit (T,I545) and unctertainty estimate
+% plot for some set of pixels of SED overlaid with best-fit two-component model
+%    --> done in Python instead of IDL
+%    --> overlay 
+% plot of resulting T2 and tau
+% plots of full-sky residuals relative to our model ?
+%  ---> and for lower-frequency bands to emphasize that FDS99 is better for
+%       extrapolating towards mm wavelengths
 
@@
 
-We have made use of the Planck 2013 data release, specifically the 217 GHz, 
-353 GHz, 545 GHz and 857 GHz channels Planck Collaboration (2013a). We use the 
-versions of these maps which have been corrected for zodiacal light by the 
-Planck team, using the zodiacal light model described in Planck Collaboration 
-(2013b). For each pixel on the sky, Planck thus provides us with four data 
-points of the dust emission SED. The angular resolution of these maps is 
-$5.5$. TODO: actually smooth all of the maps to a common PSF of XX arcmin.
+All \PLANCK~data products utilized throughout this work are drawn from the\PLANCK~2013 data release \citep{planck2013}. Specifically, we have made use of the
+the 217 GHz, 353 GHz, 545 GHz and 857 GHz intensity maps. We use the 
+versions of these maps which have been corrected for zodiacal light 
+\citep[\texttt{R1.10\_nominal\_ZodiCorrected},][]{planckzodi}.
 
-To add information about the dust emission on the Wien side of its spectrum,
-we include IRAS 100$\mu$m. We use the SFD reprocessing of IRAS 100$\mu$m, which
-we will refer to as \verb|i100| (Schegel et al. 1998). \verb|i100|
+%For each pixel on the sky, Planck thus provides us with four data points of 
+%the dust emission SED. The angular resolution of these maps is $5.5$.
+
+%TODO: actually smooth all of the maps to a common PSF of 6.1 arcmin.
+
+To incorporate information about the dust emission on the Wien side of its 
+spectrum, we make use of 100$\mu$m data. In particular, we use the SFD 
+reprocessing of IRAS 100$\mu$m, which we will refer to as \verb|i100| (Schegel et al. 1998). \verb|i100| has angular resolution of $6.1'$. %list other
+%important characteristics of i100 e.g. that it has been zodi-corrected
+% and relies on dirbe on scales larger than ???
 
 \section{Pre-processing}
+
+\subsection{Smoothing}
 
@@
 
-\subsection{Zodiacal Light Removal}
-Cite the appropriate reference for the Planck ZL model.
+%\subsection{Zodiacal Light}
+%As mentioned above, we rely upon the \cite{planckzodi} zodiacal light 
+%correction.
 
-\subsection{Smoothing to common resolution}
-
-\subsection{CMB Subtraction}
+\subsection{CMB Removal}
 The CMB is effectively imperceptible at 857 GHz, but can be noticed at a 
-low level at 545 GHz, and is extremely bright at 217 GHz and 353 GHz relative 
-to the diffuse Galactic emission we wish to characterize.
+low level at 545 GHz, and is prominent at 217 GHz and 353 GHz relative 
+to the diffuse Galactic emission we wish to characterize, especially at high
+latitudes. To remove the CMB anisotropies, we have subtracted the SMICA model
+from each of our Planck maps \citep{smica}, after appropriate unit conversions.
 
@@
 \subsection{Correlation against HI}
-The raw Planck maps we have downloaded show offsets relative to HI, in the
+The raw \PLANCK~maps we have downloaded show offsets relative to HI, in the
 sense that the FIR emission does not go to zero when HI emission goes to
@@
 
-\section{Model}
+\section{Dust Emission Model}
 Our model is that of FDS99, which consists of two populations of dust 
-grain emitting as modified blackbodies, but with different temperatures
-and different emissivity power law indices $\beta$.
+grains emitting as modified blackbodies, but with different temperatures
+and different emissivity power law indices $\beta$. The shape of this spectrum 
+is given by:
+
+\begin{equation}
+I_{\nu} \propto f_{1}q_{1}(\nu/\nu_{0})^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}(\nu/\nu_0)^{\beta_2}B_{\nu}(T_2)
+\end{equation}
+
+With $\nu_0$ = 3000 GHz, $f_{1}$ = 0.0363, $\beta_1$ = 1.67, $\beta_2$ = 2.70, 
+and $q_1/q_2$ = 13.0. For the parameters thus far specified, the two dust temperatures are further related by:
+
+\begin{equation}
+T_1 = 0.352T_2^{1.18}
+\end{equation}
+
+At each sky location, we have five independent intensity 
+measurements (four ) FDS99 found typical values for T2 and
 
@@
 
-\begin{figure*}[ht]
+\section{Pixelization}
+For the purpose of fitting, we break the sky into independent pixels of 
+angular diameter $\sim$, defined by the HEALPix pixelization with nside=2048. 
+This is convenient because the Planck maps are provided in this format and 
+this pixelization adequately samples the $6.1'$ resolution maps under 
+consideration. We reiterate that each pixel is fit independently of 
+neighboring pixels.
+
+\section{Markov Chains}
+As explained in $\S$ %need to label ``model'' section so i can reference it
+
+\section{Results}
+
+\subsection{Calculating $\tau$}
+
+\subsection{Data Release}
+We are releasing nside=2048 HEALPix maps in Galactic coordinates summarizing 
+the results of of our two-component dust fits.
+
+\begin{figure*}
 \begin{center}
-\epsfig{file=t2_0128.eps, width=7.0in}
+\epsfig{file=results.eps, width=7.0in}
 \caption{Our best-fit $T_2$, binned to 27.5$'$ resolution}

### 2013-12-13 ms.tex
more text and equations

@@
 \section{Dust Emission Model}
+\label{sec:modeling}
 Our model is that of FDS99, which consists of two populations of dust 
@@
 \section{Markov Chains}
-As explained in $\S$ %need to label ``model'' section so i can reference it
+As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
+per-pixel dust emission SED are the hot dust temperature $T_2$, which 
+determinesthe shape of the SED, and the spectrum normalization. In practice,
+the normalization is controlled via $I^{*}_{545}$, the amplitude of the SED
+in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a Metropolis-Hastings 
+Markov chain sampling the posterior probability as a function of the two parameters $T_2$ and $I^{*}_{545}$. To be clear, we are sampling the posterior
+given by:
+
+\begin{equation}
+P(I^{*}_{545}, T_2) \propto L({I_i}|I^{*}_{545}, T_2)P(T_2)
+\end{equation}
+
+The likelihood function is given by:
+
+Where the errors on each intensity measurement, $\sigma_{\nu}$ are given by:
+
+In order to obtain reasonable fitting results at high latitude where the
+data is noisy, we include a prior on $T_2$
 

### 2013-12-13 ms.tex
added HEALPix reference

@@
 For the purpose of fitting, we break the sky into independent pixels of 
-angular diameter $\sim$, defined by the HEALPix pixelization with nside=2048. 
+angular diameter $\sim$, defined by the HEALPix pixelization with nside=2048 \citep{healpix}. 
 This is convenient because the Planck maps are provided in this format and 
@@
 
-\subsection{Calculating $\tau$}
-
-\subsection{Data Release}
-We are releasing nside=2048 HEALPix maps in Galactic coordinates summarizing 
-the results of of our two-component dust fits.
-
 \begin{figure*}
@@
 \end{figure*}
+
+\subsection{Calculating $\tau$}
+
+\subsection{Data Release}
+We are releasing nside=2048 HEALPix maps in Galactic coordinates summarizing 
+the results of of our two-component dust fits.
 

### 2013-12-13 ms.tex
more text

--- 2013-12-13 ms.tex
@@
 \subsection{Molecular Emission}
+One advantage of the FIRAS data used by FDS99 was its many narrow bins in 
+frequency, which allowed those frequency ranges contaminated by strong 
+molecular line emission to be discarded from the analysis. Unfortunately, with 
+the broad \PLANCK~and \IRAS~bandpasses we do not have such a luxury. This means
+ that we cannot truly separate out the thermal continuum of dust emission we 
+wish to study from the molecular line emission. The most prominent molecular 
+line emission in the Planck bands of interest arises from CO lines in the XX, 
+YY bands. We investigated the possibility of subtracting out CO emission based 
+on the template of
 
-\subsection{Point Sources}
+\subsection{Compact Sources}
+To mask compact sources, we use the SFD compact source mask, which was 
+originally constructed to mask point sources and resolved compact objects
+that are not part of the Galactic cirrus at 3000 GHz. Given our pixelization 
+(see $\S$\ref{sec:pix}), 1.56\% of pixels are masked. We have inspected all of 
+the maps used in this analysis and do not see any evidence that this compact 
+source mask fails to adequately mask compact sources in the \PLANCK~data. In 
+practice, we perform our dust SED fits in all pixels, even those flagged by 
+the point source mask. Compact source affected pixels can be ignored or 
+interpolated over downstream.
+%maybe say that we're releasing a version of the map with point sources
+%interpolated over by us as well
 
@@
 At each sky location, we have five independent intensity 
-measurements (four ) FDS99 found typical values for T2 and
+measurements (four ) FDS99 found typical values for $T_2$ and
 
@@
 \section{Pixelization}
+\label{sec:pix}
 For the purpose of fitting, we break the sky into independent pixels of 
-angular diameter $\sim$, defined by the HEALPix pixelization with nside=2048. 
+angular size $\sim$1.72$'$, defined by the HEALPix pixelization with nside=2048 \citep{healpix}. 
 This is convenient because the Planck maps are provided in this format and 
@@
 \begin{equation}
-P(I^{*}_{545}, T_2) \propto L({I_i}|I^{*}_{545}, T_2)P(T_2)
+P(I^{*}_{545}, T_2) \propto \mathcal{L}(\{I_i\}|I^{*}_{545}, T_2)P(T_2)
 \end{equation}
@@
 
+%mention something about the proposal distribution at some point?
+
 \section{Results}
-
-\subsection{Calculating $\tau$}
-
-\subsection{Data Release}
-We are releasing nside=2048 HEALPix maps in Galactic coordinates summarizing 
-the results of of our two-component dust fits.
 
@@
 
+\subsection{Calculating $\tau$}
+
+\subsection{Data Release}
+We are releasing nside=2048 HEALPix maps in Galactic coordinates summarizing 
+the results of of our two-component dust fits.
+
 \section{Conclusion}
 
-Based on observations obtained with Planck (http://www.esa.int/Planck), 
-an ESA science mission with instruments and contributions directly funded 
-by ESA Member States, NASA, and Canada.
+This material is based upon work supported by the National Science Foundation 
+Graduate Research Fellowship under Grant No.Based on observations obtained with
+ Planck (http://www.esa.int/Planck), an ESA science mission with instruments 
+and contributions directly funded by ESA Member States, NASA, and Canada. This 
+research made use of the NASA Astrophysics Data System (ADS) and the IDL 
+Astronomy User's Library at Goddard. \footnote{Available at 
+\texttt{http://idlastro.gsfc.nasa.gov}}
 

### 2013-12-13 ms.tex
CO reference, more text and clean-up

@@
 
-All \PLANCK~data products utilized throughout this work are drawn from the\PLANCK~2013 data release \citep{planck2013}. Specifically, we have made use of the
-the 217 GHz, 353 GHz, 545 GHz and 857 GHz intensity maps. We use the 
+All \PLANCK~data products utilized throughout this work are drawn from the 
+\PLANCK~2013 data release \citep{planck2013}. Specifically, we have made use 
+of the the 217 GHz, 353 GHz, 545 GHz and 857 GHz intensity maps. We use the 
 versions of these maps which have been corrected for zodiacal light 
@@
 spectrum, we make use of 100$\mu$m data. In particular, we use the SFD 
-reprocessing of IRAS 100$\mu$m, which we will refer to as \verb|i100| (Schegel et al. 1998). \verb|i100| has angular resolution of $6.1'$. %list other
+reprocessing of IRAS 100$\mu$m, which we will refer to as \verb|i100|. \verb|i100| has angular resolution of $6.1'$. %list other
 %important characteristics of i100 e.g. that it has been zodi-corrected
@@
 
-\subsection{Correlation against HI}
+\subsection{Correlation versus HI}
 The raw \PLANCK~maps we have downloaded show offsets relative to HI, in the
@@
 YY bands. We investigated the possibility of subtracting out CO emission based 
-on the template of
+on the template of \cite{planckco}. However, we found that the CO emission
+rarely amounted to more than XX\% of the total intensity, and following
+the treatment of \cite{planckdust}, $\S$2.1, we do not attempt to remove CO
+emission.
 
@@
 determinesthe shape of the SED, and the spectrum normalization. In practice,
-the normalization is controlled via $I^{*}_{545}$, the amplitude of the SED
-in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a Metropolis-Hastings 
-Markov chain sampling the posterior probability as a function of the two parameters $T_2$ and $I^{*}_{545}$. To be clear, we are sampling the posterior
+the normalization is controlled via $\tilde{I}_{545}$, the amplitude of the 
+model SED in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a 
+Metropolis-Hastings Markov chain sampling the posterior probability as a function of the two parameters $T_2$ and $\tilde{I}_{545}$. To be clear, we are sampling the posterior
 given by:
@@
 \begin{equation}
-P(I^{*}_{545}, T_2) \propto \mathcal{L}(\{I_i\}|I^{*}_{545}, T_2)P(T_2)
+P(\tilde{I}_{545}, T_2) \propto \mathcal{L}(\{I_i\}|\tilde{I}_{545}, T_2)P(T_2)
 \end{equation}

### 2013-12-14 ms.tex
more text, another Planck paper in references

@@
 Galactic emission on low-frequency observations of the 
-cosmic microwave background (CMB). %specify ``low frequency more precisely eventually
+cosmic microwave background (CMB). 
+%specify ``low frequency more precisely eventually
 
@@
 \subsection{Smoothing}
+We wish to simultaneously fit \verb|i100| along with four \PLANCK~bands. To 
+properly combine these maps, they must have the same PSF. \verb|i100|, with its
+$6.1'$ symmetric Gaussian PSF, is the lowest-resolution map we have included. 
+To match PSFs, we have therefore smoothed each of the \PLANCK~maps under 
+consideration to $6.1'$ resolution by considering each native map to have
+a symmetric Gaussian beam and smoothing by the appropriate symmetric Gaussian
+such that the resulting map has a FWHM of $6.1'$. The FWHM we assign to the 
+native \PLANCK~maps is taken from \cite{planckbeam}, specifically $5.01'$ for
+217 GHz, $4.86'$ for 353 GHz, $4.84'$ for 545 GHz, and $4.63'$ for 857 GHz.
 
@@
 \begin{equation}
-I_{\nu} \propto f_{1}q_{1}(\nu/\nu_{0})^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}(\nu/\nu_0)^{\beta_2}B_{\nu}(T_2)
+M_{\nu} \propto f_{1}q_{1}(\nu/\nu_{0})^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}(\nu/\nu_0)^{\beta_2}B_{\nu}(T_2)
 \end{equation}
@@
 With $\nu_0$ = 3000 GHz, $f_{1}$ = 0.0363, $\beta_1$ = 1.67, $\beta_2$ = 2.70, 
-and $q_1/q_2$ = 13.0. For the parameters thus far specified, the two dust temperatures are further related by:
+and $q_1/q_2$ = 13.0. For the parameters thus far specified, the two dust 
+temperatures are further related by:
 
@@
 
-At each sky location, we have five independent intensity 
-measurements (four ) FDS99 found typical values for $T_2$ and
+At each sky location, we have five independent intensity measurements (four ) 
+FDS99 found typical values for $T_2$ and
 
@@
 For the purpose of fitting, we break the sky into independent pixels of 
-angular size $\sim$1.72$'$, defined by the HEALPix pixelization with nside=2048 \citep{healpix}. 
-This is convenient because the Planck maps are provided in this format and 
-this pixelization adequately samples the $6.1'$ resolution maps under 
-consideration. We reiterate that each pixel is fit independently of 
+angular size $\sim$1.72$'$, defined by the HEALPix pixelization with nside=2048
+\citep{healpix}. This is convenient because the Planck maps are provided in 
+this format and this pixelization adequately samples the $6.1'$ resolution maps
+under consideration. We reiterate that each pixel is fit independently of 
 neighboring pixels.
@@
 model SED in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a 
-Metropolis-Hastings Markov chain sampling the posterior probability as a function of the two parameters $T_2$ and $\tilde{I}_{545}$. To be clear, we are sampling the posterior
+Metropolis-Hastings Markov chain sampling the posterior probability as a 
+function of the two parameters $T_2$ and $\tilde{I}_{545}$. For each pixel, we 
+are sampling the posterior given by:
+
+\begin{equation}
+P(\tilde{I}_{545}, T_2|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2)P(T_2)
+\end{equation}
+
+The likelihood function is given by:
+\begin{equation}
+\mathcal{L}(\{I\}|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(M_{\nu_{i}}(\tilde{I}_{545}, T_2)|I_{\nu_{i}}, \sigma_{\nu_i})
+\end{equation}
+
+%be more careful about notation re: color corrections
+
+Where the product runs over $\nu_i$ in $\{217,\ 353,\ 545,\ 857,\ 3000\}$ GHz. 
+For each pixel, the errors on each intensity measurement $\sigma_{\nu_i}$ are 
 given by:
@@
 \begin{equation}
-P(\tilde{I}_{545}, T_2) \propto \mathcal{L}(\{I_i\}|\tilde{I}_{545}, T_2)P(T_2)
+\sigma_{\nu_i} = \sqrt{c^2_{\nu_i}I^2_{\nu_i} + c^2_{\nu_i}CMB_{\nu_i} + }
 \end{equation}
 
-The likelihood function is given by:
+This error budget is based on \cite{planckdust} Equation 7. $c_{\nu_i}$ is the 
+multiplicative calibration uncertainty for the intensity in each band, and we 
+have adopted the values listed in \cite{planckdust} Table 1. We have adopted 
+$c_{217 GHz}$ = XX. In order to obtain reasonable fitting results at high 
+latitude where the data is noisy, we include a prior on $T_2$:
 
-Where the errors on each intensity measurement, $\sigma_{\nu}$ are given by:
+\begin{equation}
+P(T_2) = \mathcal{N}(T_2|\bar{T}_2, \sigma_{\bar{T}_2})
+\end{equation}
 
-In order to obtain reasonable fitting results at high latitude where the
-data is noisy, we include a prior on $T_2$
-
+With $\bar{T}_2$ = 16.2 K and $\sigma_{\bar{T}_2}$ = 1.4 K. In practice we 
+always perform computations using the logarithm of relevant probabilities.
 %mention something about the proposal distribution at some point?
@@
 
+%provide maps at multiple different nsides ?
+%   -> if so, actually smooth the maps before rebinning, or leave 
+%      undersampled?
+
+\subsection{Comparison to Planck Collaboration Dust Map}
+
 \section{Conclusion}

### 2013-12-14 ms.tex
more

@@
 %       extrapolating towards mm wavelengths
+% zoom-in of region with interesting dust showing :
+%  SFD T map, two-component T map, Planck team one-component T map
 
@@
 We wish to simultaneously fit \verb|i100| along with four \PLANCK~bands. To 
-properly combine these maps, they must have the same PSF. \verb|i100|, with its
-$6.1'$ symmetric Gaussian PSF, is the lowest-resolution map we have included. 
-To match PSFs, we have therefore smoothed each of the \PLANCK~maps under 
-consideration to $6.1'$ resolution by considering each native map to have
-a symmetric Gaussian beam and smoothing by the appropriate symmetric Gaussian
-such that the resulting map has a FWHM of $6.1'$. The FWHM we assign to the 
-native \PLANCK~maps is taken from \cite{planckbeam}, specifically $5.01'$ for
-217 GHz, $4.86'$ for 353 GHz, $4.84'$ for 545 GHz, and $4.63'$ for 857 GHz.
+properly combine these maps, they must have the same point spread function 
+(PSF). \verb|i100|, with its $6.1'$ symmetric Gaussian PSF, is the 
+lowest-resolution map we have included. To match PSFs, we have therefore 
+smoothed each of the \PLANCK~maps under consideration to $6.1'$ resolution by 
+considering each native map to have a symmetric Gaussian beam and smoothing by 
+the appropriate symmetric Gaussian such that the resulting map has a FWHM of 
+$6.1'$. The FWHM we assign to the native \PLANCK~maps is taken from 
+\cite{planckbeam}, specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, 
+$4.84'$ for 545 GHz, and $4.63'$ for 857 GHz.
 
@@
 \begin{equation}
-\sigma_{\nu_i} = \sqrt{c^2_{\nu_i}I^2_{\nu_i} + c^2_{\nu_i}CMB_{\nu_i} + }
+\sigma_{\nu_i} = \sqrt{c^2_{\nu_i}I^2_{\nu_i} + c^2_{\nu_i}CMB^2_{\nu_i} + (\delta O_{\nu_i})^2 + n^2_{\nu_i}}
 \end{equation}
 
+% what about the instrumental noise n_{\nu_i} ---> can't find anything
+% in planck literature
+
 This error budget is based on \cite{planckdust} Equation 7. $c_{\nu_i}$ is the 
-multiplicative calibration uncertainty for the intensity in each band, and we 
-have adopted the values listed in \cite{planckdust} Table 1. We have adopted 
-$c_{217 GHz}$ = XX. In order to obtain reasonable fitting results at high 
+multiplicative calibration uncertainty for the intensity in each band. We 
+have adopted the $c_{\nu_i}$ values listed in \cite{planckdust} Table 1. For 
+the 217 GHz band, we have assigned $c_{217 GHz}$ = 0.54, from Table 11 of 
+\cite{planckcalib}. In order to obtain reasonable fitting results at high 
 latitude where the data is noisy, we include a prior on $T_2$:
@@
 %      undersampled?
+% provide uncertainty maps for tau and T2 ??
+
+\subsection{Limitations}
+% CIBA !!!
+% IRAS missing so that parts of sky not truly 6.1' resolution map
 

### 2013-12-14 ms.tex
more

@@
 while others are provided in units of MJy/sr. Before performing any fits, 
-we convert all measurements to MJy/sr following the guidelines of the document
-``HFI-unit conversion and colour correction instructions v1.2''.
+we convert all measurements to MJy/sr following the guidelines of \cite{planckresponse} and the document ``HFI-unit conversion and colour correction instructions v1.2''.
+
+%i think it's table 5 that I specifically want to cite within the ``spectral
+%response'' paper, but i need to check that those values are consistent
+% with the ones i actually used from the other document
 
@@
 % what about the instrumental noise n_{\nu_i} ---> can't find anything
-% in planck literature
+% in planck literature ... nevermind n^2 <-> ii_cov in binary tables
 
-This error budget is based on \cite{planckdust} Equation 7. $c_{\nu_i}$ is the 
-multiplicative calibration uncertainty for the intensity in each band. We 
-have adopted the $c_{\nu_i}$ values listed in \cite{planckdust} Table 1. For 
-the 217 GHz band, we have assigned $c_{217 GHz}$ = 0.54, from Table 11 of 
-\cite{planckcalib}. In order to obtain reasonable fitting results at high 
-latitude where the data is noisy, we include a prior on $T_2$:
+This error budget is the same as that of \cite{planckdust} Equation 7. 
+$c_{\nu_i}$ is the multiplicative calibration uncertainty for the intensity in 
+each band. We have adopted the $c_{\nu_i}$ values listed in \cite{planckdust} 
+Table 1. For the 217 GHz band, we have assigned $c_{217 GHz}$ = 0.54, from 
+Table 11 of \cite{planckcalib}. $CMB$ represents the CMB intensity 
+subtracted at the relevant pixel. $\delta0_{\nu_i}$ represents the uncertainty
+in the offset used to tie \PLANCK~intensity to HI. We have adopted the 
+ $\delta0_{\nu_i}$ values of \cite{planckdust} Table 1. $n_{\nu_i}$ represents 
+the instrumental noise in the pixel of interest, and is taken to be the square 
+root of the \verb|ii_cov| parameter that accompanies each \PLANCK~intensity 
+map. In order to obtain reasonable fitting results at high latitude where the 
+data is noisy, we include a prior on $T_2$:
+
+%what about the offset uncertainty for 217 GHz
 
@@
 
+\subsubsection{Ignoring 217 GHz}
+The \cite{planckdust} result used only XX, YY, ZZ, 3000 GHz. When we 
+repeat our analysis ignoring 217 GHz, so that we are using the same
+set of frequencies, we find that no major changes arise. This actually
+should be done/investigated though.
+
 \section{Conclusion}

### 2013-12-14 ms.tex
mainly bandpass correction discussion

@@
 %  SFD T map, two-component T map, Planck team one-component T map
+%      good spot is in polaris, centered on (lgal,bgal) ~ (112, 20)
 
@@
 while others are provided in units of MJy/sr. Before performing any fits, 
-we convert all measurements to MJy/sr following the guidelines of \cite{planckresponse} and the document ``HFI-unit conversion and colour correction instructions v1.2''.
+we convert all measurements to MJy/sr following the guidelines of \cite{planckresponse}.
 
@@
 %response'' paper, but i need to check that those values are consistent
-% with the ones i actually used from the other document
+% with the ones i actually used from the other document ``HFI-unit conversion 
+%and colour correction instructions v1.2''
 
@@
 \subsection{Finite Bandpass Correction}
+The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
+intensity $M_{\nu}$ in MJy/sr for any single frequency $\nu$. But in reality
+we are comparing to broad bands typically hundreds of GHz wide. The shape of 
+model spectrum $M_{\nu}$ is only dependent upon one parameter: the hot
+dust temperature $T_2$. We have therefore computed bandpass correction factors
+$b_{\nu_i}$ such that $M_{\nu_i}b_{\nu_i}$ is the predicted observation for the
+\PLANCK~or \IRAS~band of interest. We have used the \PLANCK~transmission 
+curves provided in the file \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. 
+For 3000 GHz, we have used the \IRAS~bandpass, following the treatment of
+\cite{planckdust}. We note that it is not clear which bandpass should
+properly be considered for the IRAS/DIRBE composite 100$\mu$m maps used in 
+this analysis (here SFD \verb|i100|) and that of \cite{planckdust}.
+
+% check that RIMO file i've used is actually the most up-to-date version
 
@@
 \begin{equation}
-M_{\nu} \propto f_{1}q_{1}(\nu/\nu_{0})^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}(\nu/\nu_0)^{\beta_2}B_{\nu}(T_2)
+M_{\nu} \propto f_{1}q_{1}(\frac{\nu}{\nu_{0}})^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}(\frac{\nu}{\nu_0})^{\beta_2}B_{\nu}(T_2)
 \end{equation}
@@
 
-\subsubsection{Ignoring 217 GHz}
+\subsubsection{Omitting 217 GHz}
 The \cite{planckdust} result used only XX, YY, ZZ, 3000 GHz. When we 

### 2013-12-15 ms.tex
more introduction

@@
 as an important alternative to and comparison for other dust 
-emission models, especially the single modified blackbody model in which 
+emission models, especially the single modified blackbody (MBB) model in which 
 $\beta$ and $T$ both vary spatially. We also expect the derived optical 
@@
 appropriate over a very broad range of frequencies. They showed that a 
-model consisting of a single modified blackbody with power law index $\beta$ 
+model consisting of a single MBB with power law index $\beta$ 
 could not fit the IRAS/FIRAS/DIRBE spectrum at both the Wien and 
 Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 proposed
-a spectrum consisting of two modified black bodies, each with a different
+a spectrum consisting of two MBBs, each with a different
 temperature and power law index. Physically, these two components
@@
 silicates and carbonaceous grains.
+
+\cite{planckdust} has recently conducted a study modeling
+\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
+MBB spectrum.
+
+In $\S$\ref{sec:data} we discuss the data used in throughout this study. In 
+$\S$\ref{sec:prepro} we describe our preprocessing of the data to isolate 
+thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we describe the 
+dust emission model we fit to the \PLANCK and \IRAS~data. In 
+$S$\ref{sec:fitting} we provide details of the Markov Chain Monte Carlo method 
+we use to estimate the parameters of our model. In $\S$\ref{sec:results} we 
+present the full-sky maps of dust temperature and optical depth we have 
+obtained, and conclude and $\S$\ref{sec:conclusion}
 
@@
 \section{Data}
-
+\label{sec:data}
 All \PLANCK~data products utilized throughout this work are drawn from the 
@@
 \section{Pre-processing}
+\label{sec:prepro}
 
@@
 Our model is that of FDS99, which consists of two populations of dust 
-grains emitting as modified blackbodies, but with different temperatures
+grains emitting as MBBs, but with different temperatures
 and different emissivity power law indices $\beta$. The shape of this spectrum 
@@
 
-\subsection{Fitting Methodology}
+\section{Fitting Procedure}
+\label{sec:fitting}
 
-\section{Pixelization}
+\subsection{Pixelization}
 \label{sec:pix}
@@
 
-\section{Markov Chains}
+\subsection{Markov Chains}
 As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
@@
 \section{Results}
+\label{sec:results}
 
@@
 \subsubsection{Omitting 217 GHz}
-The \cite{planckdust} result used only XX, YY, ZZ, 3000 GHz. When we 
+The \cite{planckdust} result used only 353, 545, 857, and 3000 GHz. When we 
 repeat our analysis ignoring 217 GHz, so that we are using the same
@@
 \section{Conclusion}
+\label{sec:conclusion}
 

### 2013-12-15 ms.tex
more introduction

@@
 \PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
-MBB spectrum.
+MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
+as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
+doing so, we obtain $6.1'$ maps of dust temperature and optical depth. Because
+we are using a model that has been validated using FIRAS data down to sub-mm
+wavelengths, this model should be useful in constructing predictions of dust
+emission over a very broad range of wavelengths. This includes low frequencies,
+which \cite{planckdust} admit their model does not adequately fit, and also
+data near the peak of the dust SED, for example Akari. We also anticipate 
+the optical depth map we derive will be useful as a comparison for extinction
+estimates based directly upon optical/NIR observations of stars.
+
+%would be nice if i had a citation here for Eddie/Greg pan-starrs dust stuff
 
@@
 spectrum, we make use of 100$\mu$m data. In particular, we use the SFD 
-reprocessing of IRAS 100$\mu$m, which we will refer to as \verb|i100|. \verb|i100| has angular resolution of $6.1'$. %list other
-%important characteristics of i100 e.g. that it has been zodi-corrected
-% and relies on dirbe on scales larger than ???
+reprocessing of IRAS 100$\mu$m, which we will refer to as \verb|i100|, and at 
+times by frequency as 3000 GHz. \verb|i100| has angular resolution of $6.1'$. 
+%list other %important characteristics of i100 e.g. that it has been 
+%zodi-corrected and relies on dirbe on scales larger than ???
 
@@
 \subsection{Comparison to Planck Collaboration Dust Map}
+%striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping
 

### 2013-12-15 ms.tex
editing intro, adding to intro

@@
 \newcommand{\PLANCK}{{\it Planck}}
+\newcommand{\AKARI}{{\it Akari}}
 
@@
 \begin{abstract}
-We present full-sky maps of dust optical depth and temperature derived from 
-the \cite{FDS99} two-component dust emission model fitted to \PLANCK~217, 353, 
-545, 857 GHz and \cite{SFD} \IRAS~100$\mu$m data. Both the optical 
-depth and temperature maps have angular resolution of $6.1'$. Such maps serve 
-as an important alternative to and comparison for other dust 
+We present full-sky maps of dust optical depth and temperature derived by 
+applying the \cite{FDS99} two-component dust emission model fitted to 
+\PLANCK~217, 353, 545, 857 GHz and \cite{SFD} \IRAS~100$\mu$m data. Both the 
+optical depth and temperature maps have angular resolution of $6.1'$. Such maps
+ serve as an important alternative to and comparison for other dust 
 emission models, especially the single modified blackbody (MBB) model in which 
@@
 medium (ISM) is valuable in its own right, as the ISM is the site of star 
-formation, thereby playing a crucial role in galaxy evolution. Equally if not 
-more important to the practice of astronomy, however, is accounting for dust 
-as a foreground which reddens optical/UV observations and superimposes 
-Galactic emission on low-frequency observations of the 
-cosmic microwave background (CMB). 
+formation, thereby playing a crucial role in galaxy evolution. Equally, or 
+perhaps even more important to the practice of astronomy, however, is 
+accurately accounting for dust as a foreground which reddens optical/UV o
+bservations and superimposes Galactic emission on low-frequency observations 
+of the cosmic microwave background (CMB). 
 %specify ``low frequency more precisely eventually
+% somewhere mention re-radiation
 
@@
 Over the past decades, satellite observations have dramatically enhanced our
-knowledge about infrared emission from the ISM. High-latitude complexes of 
-resolved infrared sources were first identified by \cite{low84} using 
-\IRAS~60$\mu$m and 100$\mu$m observations \citep{wheelock94}. This so-called 
-``infrared cirrus,'' attributable to thermal emission from large dust grains in
-the interstellar medium, has since been probed in greater detail by a variety 
-of instruments and detected over virtually the entire sky. Beginning in 1989, 
-DIRBE  mapped the full sky at ten infrared wavelengths from 1.25$\mu$m to 
-240$\mu$m with a reliable zero point, but inferior 0.7$^{\circ}$ angular 
-resolution \citep{boggess92}.mention FIRAS specifically, since it is important 
-to FDS99.
+knowledge about infrared emission from the ISM. IRAS, with its $\sim$6$'$ 
+resolution, revolutionized the study of Galactic dust emission, first revealing
+ the high-latitude ``infrared cirrus'' using \IRAS~60$\mu$m and 100$\mu$m 
+observations \citep{low84, wheelock94}. Beginning in 1989, DIRBE  mapped the 
+full sky at ten infrared wavelengths from 1.25$\mu$m to 240$\mu$m with a 
+reliable zero point, but inferior 0.7$^{\circ}$ angular resolution 
+\citep{boggess92}.mention FIRAS specifically, since it is important to FDS99.
 
@@
 
-\cite{planckdust} has recently conducted a study modeling
+With the advent of the Planck mission, we have an important opportunity to
+revisit foreground predictions in light of their superb data. Brief Planck
+background. \cite{planckdust} has recently conducted a study modeling
 \PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single

### 2013-12-15 ms.tex
IRIS reference, testing bare repository

@@
 which \cite{planckdust} admit their model does not adequately fit, and also
-data near the peak of the dust SED, for example Akari. We also anticipate 
+data near the peak of the dust SED, for example \AKARI. We also anticipate 
 the optical depth map we derive will be useful as a comparison for extinction
@@
 %striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping
+An important difference between our maps and those of \cite{planckdust} is our 
+use of SFD \verb|i100| instead of IRIS 100$\mu$m \citep{IRIS}.
 

### 2013-12-15 ms.tex
more

@@
 
+For each pixel, we initialize the Markov chain to have $T_2$ = $\bar{T}_2$ and
+. We run 500 steps of burn-in and then 2000 steps during which we keep track
+of the proposed $T_{2, j}$ and $I_{545, j}$ values. We use these 2000 values 
+for each parameter to compute estimates of each parameter,  $T_2$ = 
+$\langle T_{2, j} \rangle$, $I_{545}$ = $\langle I_{545, j} \rangle$, and of 
+each parameter's variance, $\sigma^2_{T_2}$ = $\langle T^2_{2, j} \rangle-\langle T_{2, j} \rangle ^2$ and $\sigma^2_{I_{545}}$=$\langle I^2_{545, j} 
+\rangle-\langle I_{545, j} \rangle ^2$
+
 \section{Results}
@@
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
-\epsfig{file=results.eps, width=7.0in}
-\caption{Our best-fit $T_2$, binned to 27.5$'$ resolution}
+\epsfig{file=tcomparison.eps, width=3.3in}
+\caption{Comparison of SFD temperature, two-component model $T_2$, and 
+\cite{planckdust} temperature. Note the differing colorscales. Both models 
+incorporating \PLANCK~data clearly show a major improvement in resolution 
+relative to SFD.}
 \end{center}
-\end{figure*}
+\end{figure}
 
@@
 
+\begin{figure*} [ht]
+\begin{center}
+\epsfig{file=results.eps, width=7.0in}
+\caption{Our best-fit $T_2$, binned to 27.5$'$ resolution}
+\end{center}
+\end{figure*}
+
 This material is based upon work supported by the National Science Foundation 

### 2013-12-15 ms.tex
more text, more references

@@
 %basic background about interstellar dust emission
-
-%maybe say instead ``over the past 30/40 years...''
-%Barnard first recognized evidence for dust in astronomical observations, and
-%ever since it has been mapped in increasing detail. 
 Over the past decades, satellite observations have dramatically enhanced our
@@
 
-FDS99 used FIRAS to make a globally best-fit model of dust emission 
-appropriate over a very broad range of frequencies. They showed that a 
-model consisting of a single MBB with power law index $\beta$ 
+FDS99 used FIRAS \citep{firas} to make a globally best-fit model of dust 
+emission appropriate over a very broad range of frequencies. They showed that 
+a model consisting of a single MBB with power law index $\beta$ 
 could not fit the IRAS/FIRAS/DIRBE spectrum at both the Wien and 
@@
 
-%For each pixel on the sky, Planck thus provides us with four data points of 
-%the dust emission SED. The angular resolution of these maps is $5.5$.
-
 %TODO: actually smooth all of the maps to a common PSF of 6.1 arcmin.
@@
 %and colour correction instructions v1.2''
-
-%\subsection{Zodiacal Light}
-%As mentioned above, we rely upon the \cite{planckzodi} zodiacal light 
-%correction.
 
@@
 
-% what about the instrumental noise n_{\nu_i} ---> can't find anything
-% in planck literature ... nevermind n^2 <-> ii_cov in binary tables
-
 This error budget is the same as that of \cite{planckdust} Equation 7. 
@@
 \epsfig{file=tcomparison.eps, width=3.3in}
-\caption{Comparison of SFD temperature, two-component model $T_2$, and 
-\cite{planckdust} temperature. Note the differing colorscales. Both models 
-incorporating \PLANCK~data clearly show a major improvement in resolution 
-relative to SFD.}
+\caption{\label{fig:comparison} Comparison of SFD temperature, two-component 
+model $T_2$, and \cite{planckdust} temperature. Note the differing colorscales.
+Both models incorporating \PLANCK~data clearly show a major improvement in 
+resolution relative to SFD.}
 \end{center}
@@
 \subsection{Limitations}
+Perhaps the dominant limitation of our fits is the presence of cosmic
+infrared background anisotropies (CIBA) bleeding through into our maps of 
+Galactic dust temperature and optical depth in high-latitude regions 
+\citep{ciba}.
 % CIBA !!!
@@
 An important difference between our maps and those of \cite{planckdust} is our 
-use of SFD \verb|i100| instead of IRIS 100$\mu$m \citep{IRIS}.
+use of SFD \verb|i100| instead of IRIS 100$\mu$m \citep{IRIS}. Residual 
+\IRAS~striping at levels higher than that remaining in SFD \verb|i100| is 
+clearly visible in the \cite{planckdust} maps.
+
+%we actually have 6.1' arcminute smoothing
+It is true that we have smoothed the input intensity maps for this study 
+to $6.1'$ FWHM, which is nominally lower resolution than the $5'$ 
+\cite{planckdust} maps. However, as is apparent from figure 
+\ref{fig:comparison}, the fact that \cite{planckdust} modeled $\beta$ at 
+$0.5^{\circ}$ resolution has effectively blurred their dust temperature map.
 

### 2013-12-16 ms.tex
fixing introduction, another figure

@@
 
-With the advent of the Planck mission, we have an important opportunity to
-revisit foreground predictions in light of their superb data. Brief Planck
-background. \cite{planckdust} has recently conducted a study modeling
+The \PLANCK~2013 data release \citep{planck2013} represents an important 
+opportunity to revisit foreground predictions in light of their superb, 
+relatively artifact-free broadband data covering the entire sky and a broad 
+range of frequencies. \cite{planckdust} has recently conducted a study modeling
 \PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
@@
 which \cite{planckdust} admit their model does not adequately fit, and also
-data near the peak of the dust SED, for example \AKARI. We also anticipate 
-the optical depth map we derive will be useful as a comparison for extinction
-estimates based directly upon optical/NIR observations of stars.
+data near the peak of the dust SED, for example \AKARI~140-160$\mu$m. We also 
+anticipate the optical depth map we derive will be useful as a comparison for 
+extinction estimates based directly upon optical/NIR observations of stars.
 
@@
 \label{sec:modeling}
+
+\begin{figure}
+\begin{center}
+\epsfig{file=sed.eps, width=3.3in}
+\caption{\label{fig:sed} Planck SED for a single nside=2048 pixel in the 
+Polaris region. Note that the two lowest-frequency data points (\PLANCK~100, 
+143 GHz) were not used in our fit, while the four lowest-frequency data
+points were not used in the \cite{planckdust} fit.}
+\end{center}
+\end{figure}
+
 Our model is that of FDS99, which consists of two populations of dust 
@@
 
+\begin{figure}
+\begin{center}
+\epsfig{file=tcomparison.eps, width=3.3in}
+\caption{\label{fig:comparison} Comparison of SFD temperature, two-component 
+model $T_2$, and \cite{planckdust} temperature. Note the differing colorscales.
+Both models incorporating \PLANCK~data clearly show a major improvement in 
+resolution relative to SFD.}
+\end{center}
+\end{figure}
+
 For each pixel, we initialize the Markov chain to have $T_2$ = $\bar{T}_2$ and
@@
 \label{sec:results}
-
-\begin{figure}
-\begin{center}
-\epsfig{file=tcomparison.eps, width=3.3in}
-\caption{\label{fig:comparison} Comparison of SFD temperature, two-component 
-model $T_2$, and \cite{planckdust} temperature. Note the differing colorscales.
-Both models incorporating \PLANCK~data clearly show a major improvement in 
-resolution relative to SFD.}
-\end{center}
-\end{figure}
 
@@
 
-%we actually have 6.1' arcminute smoothing
+%we actually have 6.1' arcminute resolution
 It is true that we have smoothed the input intensity maps for this study 

### 2013-12-16 ms.tex
clean-up

@@
 \newcommand{\AKARI}{{\it Akari}}
+\newcommand{\FIRAS}{{\it FIRAS}}
 
@@
 The presence of Galactic interstellar dust affects
-astronomical observations over a wide range of wavelengths. At mid-infrared
-and far-infrared wavelengths, Galactic dust emission is a major contributor
-to the observed sky intensity. In the optical and ultraviolet, extinction
-by foreground dust grains attenuates the signal from extragalactic sources
-over the entire sky. Understanding the properties of dust in the interstellar 
-medium (ISM) is valuable in its own right, as the ISM is the site of star 
-formation, thereby playing a crucial role in galaxy evolution. Equally, or 
-perhaps even more important to the practice of astronomy, however, is 
+astronomical observations over a wide range of wavelengths. In the mid-infrared
+and far-infrared, Galactic dust emission is a major contributor
+to the observed sky intensity. At optical and ultraviolet wavelengths, 
+extinction by foreground dust grains attenuates the signal from extragalactic 
+sources over the entire sky. Understanding the properties of dust in the 
+interstellar medium (ISM) is valuable in its own right, as the ISM is the site 
+of star formation, thereby playing a crucial role in galaxy evolution. Equally,
+ or perhaps even more important to the practice of astronomy, however, is 
 accurately accounting for dust as a foreground which reddens optical/UV o
@@
 Over the past decades, satellite observations have dramatically enhanced our
-knowledge about infrared emission from the ISM. IRAS, with its $\sim$6$'$ 
+knowledge about infrared emission from the ISM. \IRAS, with its $\sim$4$'$ 
 resolution, revolutionized the study of Galactic dust emission, first revealing
- the high-latitude ``infrared cirrus'' using \IRAS~60$\mu$m and 100$\mu$m 
-observations \citep{low84, wheelock94}. Beginning in 1989, DIRBE  mapped the 
-full sky at ten infrared wavelengths from 1.25$\mu$m to 240$\mu$m with a 
-reliable zero point, but inferior 0.7$^{\circ}$ angular resolution 
-\citep{boggess92}.mention FIRAS specifically, since it is important to FDS99.
+ the high-latitude ``infrared cirrus'' using 60$\mu$m and 100$\mu$m 
+observations \citep{low84, wheelock94}. Then, beginning in 1989, DIRBE provided
+complementary full-sky measurements at ten infrared wavelengths from 
+1.25$\mu$m to 240$\mu$m with inferior 0.7$^{\circ}$ angular resolution, but 
+with a reliable zero point \citep{boggess92}. COBE/\FIRAS~\citep{firas} also 
+provided full-sky infrared dust spectra at $7^{\circ}$ resolution in 213 
+narrow frequency bins between 200 GHz and 2100 GHz.
 
-FDS99 used FIRAS \citep{firas} to make a globally best-fit model of dust 
-emission appropriate over a very broad range of frequencies. They showed that 
-a model consisting of a single MBB with power law index $\beta$ 
-could not fit the IRAS/FIRAS/DIRBE spectrum at both the Wien and 
+\cite{FDS99} (hereafter FDS99) used \FIRAS~data to derive a globally best-fit 
+model of dust emission applicable over a very broad range of frequencies. 
+FDS99 showed that a model consisting of a single MBB with power law index 
+$\beta$ 
+could not accurately match the \IRAS/\FIRAS/DIRBE spectrum at both the Wien and 
 Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 proposed
-a spectrum consisting of two MBBs, each with a different
+a dust emission model consisting of two MBBs, each with a different
 temperature and power law index. Physically, these two components
 represent distinct dust grain species within the ISM, specifically 
-silicates and carbonaceous grains.
+amorphous silicates and carbonaceous grains.
 
 The \PLANCK~2013 data release \citep{planck2013} represents an important 
-opportunity to revisit foreground predictions in light of their superb, 
+opportunity to revisit foreground predictions in light of \PLANCK's superb, 
 relatively artifact-free broadband data covering the entire sky and a broad 
@@
 as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
-doing so, we obtain $6.1'$ maps of dust temperature and optical depth. Because
+doing so, we obtain $6.1'$ resolution maps of dust temperature and optical 
+depth. Because
 we are using a model that has been validated using FIRAS data down to sub-mm
-wavelengths, this model should be useful in constructing predictions of dust
-emission over a very broad range of wavelengths. This includes low frequencies,
-which \cite{planckdust} admit their model does not adequately fit, and also
-data near the peak of the dust SED, for example \AKARI~140-160$\mu$m. We also 
-anticipate the optical depth map we derive will be useful as a comparison for 
-extinction estimates based directly upon optical/NIR observations of stars.
+wavelengths, e expect our best-fit parameters to be useful in constructing high-resolution
+ predictions of dust emission over a very broad range of wavelengths. This 
+includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
+model may not adequately fit, and also data near the peak of the dust SED, for
+ example \AKARI~140-160$\mu$m. We also anticipate our derived optical depth map
+ will serve as a useful comparison for extinction estimates based 
+directly upon optical/NIR observations of stars.
 
@@
 
-In $\S$\ref{sec:data} we discuss the data used in throughout this study. In 
+In $\S$\ref{sec:data} we discuss the data used throughout this study. In 
 $\S$\ref{sec:prepro} we describe our preprocessing of the data to isolate 
@@
 $S$\ref{sec:fitting} we provide details of the Markov Chain Monte Carlo method 
-we use to estimate the parameters of our model. In $\S$\ref{sec:results} we 
-present the full-sky maps of dust temperature and optical depth we have 
-obtained, and conclude and $\S$\ref{sec:conclusion}
+with which we have estimated the parameters of our model. In 
+$\S$\ref{sec:results} we present the full-sky maps of dust temperature and 
+optical depth thus obtained, and conclude and $\S$\ref{sec:conclusion}
 
@@
 
-\section{Dust Emission Model}
-\label{sec:modeling}
-
 \begin{figure}
@@
 Polaris region. Note that the two lowest-frequency data points (\PLANCK~100, 
-143 GHz) were not used in our fit, while the four lowest-frequency data
+143 GHz) were not used in our fit, while the three lowest-frequency data
 points were not used in the \cite{planckdust} fit.}
@@
 \end{figure}
+
+\section{Dust Emission Model}
+\label{sec:modeling}
 
@@
 \caption{\label{fig:comparison} Comparison of SFD temperature, two-component 
-model $T_2$, and \cite{planckdust} temperature. Note the differing colorscales.
+model $T_2$, and \cite{planckdust} temperature (labeled $T_{R1.20}$). Note the differing colorscales.
 Both models incorporating \PLANCK~data clearly show a major improvement in 

### 2013-12-17 ms.tex
some clean-up, more needed

@@
 We present full-sky maps of dust optical depth and temperature derived by 
-applying the \cite{FDS99} two-component dust emission model fitted to 
+fitting the \cite{FDS99} two-component dust emission model to
 \PLANCK~217, 353, 545, 857 GHz and \cite{SFD} \IRAS~100$\mu$m data. Both the 
@@
 and far-infrared, Galactic dust emission is a major contributor
-to the observed sky intensity. At optical and ultraviolet wavelengths, 
+to the observed sky intensity. At optical and ultraviolet (UV) wavelengths, 
 extinction by foreground dust grains attenuates the signal from extragalactic 
@@
  or perhaps even more important to the practice of astronomy, however, is 
-accurately accounting for dust as a foreground which reddens optical/UV o
-bservations and superimposes Galactic emission on low-frequency observations 
+accurately accounting for dust as a foreground which reddens optical/UV 
+observations and superimposes Galactic emission on low-frequency observations 
 of the cosmic microwave background (CMB). 
@@
 opportunity to revisit foreground predictions in light of \PLANCK's superb, 
-relatively artifact-free broadband data covering the entire sky and a broad 
+relatively artifact-free broadband data covering the entire sky and a wide 
 range of frequencies. \cite{planckdust} has recently conducted a study modeling
@@
 we are using a model that has been validated using FIRAS data down to sub-mm
-wavelengths, e expect our best-fit parameters to be useful in constructing high-resolution
+wavelengths, we expect our best-fit parameters to be useful in constructing 
+high-resolution
  predictions of dust emission over a very broad range of wavelengths. This 
@@
 thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we describe the 
-dust emission model we fit to the \PLANCK and \IRAS~data. In 
-$S$\ref{sec:fitting} we provide details of the Markov Chain Monte Carlo method 
+dust emission model we fit to the \PLANCK~and \IRAS~data. In 
+$\S$\ref{sec:fitting} we provide details of the Markov Chain Monte Carlo method
 with which we have estimated the parameters of our model. In 

### 2013-12-17 ms.tex
clean up

@@
 \newcommand{\AKARI}{{\it Akari}}
-\newcommand{\FIRAS}{{\it FIRAS}}
+\newcommand{\COBE}{{\it COBE}}
 
@@
 Over the past decades, satellite observations have dramatically enhanced our
-knowledge about infrared emission from the ISM. \IRAS, with its $\sim$4$'$ 
-resolution, revolutionized the study of Galactic dust emission, first revealing
- the high-latitude ``infrared cirrus'' using 60$\mu$m and 100$\mu$m 
-observations \citep{low84, wheelock94}. Then, beginning in 1989, DIRBE provided
-complementary full-sky measurements at ten infrared wavelengths from 
+knowledge about infrared emission from the ISM. The \textit{Infrared Astronomy 
+Satellite} (\IRAS), with its $\sim$4$'$ resolution, revolutionized the study of
+ Galactic dust emission, first revealing the high-latitude ``infrared cirrus'' 
+using 60$\mu$m and 100$\mu$m observations \citep{low84, wheelock94}. Later, the
+Diffuse Infrared Background Experiment (DIRBE) aboard the \COBE~satellite 
+provided complementary full-sky measurements at ten infrared wavelengths from 
 1.25$\mu$m to 240$\mu$m with inferior 0.7$^{\circ}$ angular resolution, but 
-with a reliable zero point \citep{boggess92}. COBE/\FIRAS~\citep{firas} also 
-provided full-sky infrared dust spectra at $7^{\circ}$ resolution in 213 
-narrow frequency bins between 200 GHz and 2100 GHz.
+with a reliable zero point \citep{boggess92}. \COBE/FIRAS \citep{firas} also 
+provided full-sky infrared dust spectra at $7^{\circ}$ resolution in 213 narrow
+frequency bins between 200 GHz and 2100 GHz.
 
-\cite{FDS99} (hereafter FDS99) used \FIRAS~data to derive a globally best-fit 
+\cite{FDS99} (hereafter FDS99) used FIRAS data to derive a globally best-fit 
 model of dust emission applicable over a very broad range of frequencies. 
 FDS99 showed that a model consisting of a single MBB with power law index 
-$\beta$ 
-could not accurately match the \IRAS/\FIRAS/DIRBE spectrum at both the Wien and 
-Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 proposed
-a dust emission model consisting of two MBBs, each with a different
+$\beta$ could not accurately match the \IRAS/FIRAS/DIRBE spectrum at both the 
+Wien and Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 
+proposed a dust emission model consisting of two MBBs, each with a different
 temperature and power law index. Physically, these two components

### 2013-12-18 ms.tex
note to self
added figure showing posterior PDF examples

@@
 
+% for CO line list see ~/wise/pro/planck_co_lines.pro
+
 \subsection{Compact Sources}
@@
 \end{figure}
+
+\begin{figure*}
+\begin{center}
+\epsfig{file=posteriors.eps, width=7.0in}
+\caption{Gridded osterior PDFs for three nside=2048 pixels. Red crosses mark 
+the best-fit parameters based on our Markov Chain sampling of the posterior. 
+The posterior distributions are in general extremely well-behaved, showing
+no multimodality, and our MCMC parameter estimates coincide well with the
+peaks in the gridded posteriors. The colorscale is linear in log(P), with black representing the maximum of log(P) and white represent max(log(P))-5. Left: Low S/N pixel at high-latitude in 
+Galactic north. Center: High S/N pixel in the Polaris region. Right: Low S/N pixel at high-latitude in the Galactic 
+south. }
+\end{center}
+\end{figure*}
 

### 2013-12-18 ms.tex
introduction clean-up, added Akari reference

@@
 MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
-as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
-doing so, we obtain $6.1'$ resolution maps of dust temperature and optical 
-depth. Because
-we are using a model that has been validated using FIRAS data down to sub-mm
-wavelengths, we expect our best-fit parameters to be useful in constructing 
-high-resolution
- predictions of dust emission over a very broad range of wavelengths. This 
-includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
-model may not adequately fit, and also data near the peak of the dust SED, for
- example \AKARI~140-160$\mu$m. We also anticipate our derived optical depth map
- will serve as a useful comparison for extinction estimates based 
+as an alernative model for the dust spectral energy distribution (SED) composed
+ of \PLANCK~and \IRAS~data. In doing so, we obtain $6.1'$ resolution maps of 
+dust temperature and optical depth. Because we employ a model that has been 
+validated with FIRAS data down to sub-mm wavelengths, we expect our best-fit 
+parameters to be useful in constructing high-resolution predictions of dust 
+emission over a very broad range of wavelengths. This includes low frequencies 
+($<$350 GHz), which \cite{planckdust} caution their model may not adequately 
+fit, and also measurements near the peak of the dust SED, for example 
+\AKARI~140-160$\mu$m \citep{akari}. We also anticipate our derived optical 
+depth map will serve as a useful comparison for extinction estimates based 
 directly upon optical/NIR observations of stars.

### 2013-12-20 ms.tex
clean-up

@@
 \epsfig{file=posteriors.eps, width=7.0in}
-\caption{Gridded osterior PDFs for three nside=2048 pixels. Red crosses mark 
+\caption{Gridded posterior PDFs for three nside=2048 pixels. Red crosses mark 
 the best-fit parameters based on our Markov Chain sampling of the posterior. 
 The posterior distributions are in general extremely well-behaved, showing
-no multimodality, and our MCMC parameter estimates coincide well with the
-peaks in the gridded posteriors. The colorscale is linear in log(P), with black representing the maximum of log(P) and white represent max(log(P))-5. Left: Low S/N pixel at high-latitude in 
-Galactic north. Center: High S/N pixel in the Polaris region. Right: Low S/N pixel at high-latitude in the Galactic 
-south. }
+no multimodality or other pathological qualities. Our MCMC parameter 
+estimates coincide well with the peaks in the gridded posteriors. The 
+colorscale is linear in $log(P)$, with black representing the maximum of 
+$log(P)$ and white representing $max(log(P))-5$. Left: Low S/N pixel at 
+high-latitude in Galactic north. Center: High S/N pixel in the Polaris region. 
+Right: Low S/N pixel at high-latitude in the Galactic south.}
 \end{center}
@@
 Our model is that of FDS99, which consists of two populations of dust 
-grains emitting as MBBs, but with different temperatures
-and different emissivity power law indices $\beta$. The shape of this spectrum 
-is given by:
+grains emitting as MBBs, but with different temperatures and different 
+emissivity power law indices $\beta$. The shape of this spectrum is given by:
 

### 2014-01-16 ms.tex
caption

@@
 \caption{\label{fig:comparison} Comparison of SFD temperature, two-component 
-model $T_2$, and \cite{planckdust} temperature (labeled $T_{R1.20}$). Note the differing colorscales.
-Both models incorporating \PLANCK~data clearly show a major improvement in 
-resolution relative to SFD.}
+model $T_2$, and \cite{planckdust} temperature (labeled $T_{R1.20}$) for a
+ $10.5^{\circ}\times8.3^{\circ}$  region centered about 
+$(l,b) = (111.6^{\circ}, 20.3^{\circ})$. Note the 
+differing colorscales. Both models incorporating \PLANCK~data clearly show a 
+major improvement in angular resolution relative to SFD.}
 \end{center}

### 2014-01-16 ms.tex
more complete discussion of zero-point and residual Solar dipole removal

@@
 reprocessing of IRAS 100$\mu$m, which we will refer to as \verb|i100|, and at 
-times by frequency as 3000 GHz. \verb|i100| has angular resolution of $6.1'$. 
+times by frequency as 3000 GHz. The \verb|i100| map has angular resolution of 
+$6.1'$. 
 %list other %important characteristics of i100 e.g. that it has been 
@@
 latitudes. To remove the CMB anisotropies, we have subtracted the SMICA model
-from each of our Planck maps \citep{smica}, after appropriate unit conversions.
+from each of the relevant \PLANCK~maps \citep{smica}, after appropriate unit conversions.
 
@@
 
-\subsection{Correlation versus HI}
-The raw \PLANCK~maps we have downloaded show offsets relative to HI, in the
-sense that the FIR emission does not go to zero when HI emission goes to
-zero. Since HI correlates linearly with far-IR emission in the diffuse ISM, 
-when the optical depth is low and molecular effects are negligible, we modeled
-far IR emission as a constant times HI emission, plus some offset. We then
-subtracted the best-fit offset such that
+\subsection{Zero-Point}
+Although we wish to isolate and model thermal emission from Galactic dust, the
+\PLANCK~maps contain additional components. At each frequency, there can
+exist an overall, constant offset that must be subtracted to set the
+zero level of Galactic dust. Additionally, faint residuals 
+of the Solar dipole remain at low frequencies. At 353 GHz, 545 GHz, 857 GHz, 
+we have adopted the zero-point offsets of \cite{planckdust} Table 1, which 
+were derived by correlating \PLANCK~857 GHz versus HI at low column density, 
+and then by correlating the other Planck channels against the corrected 857 
+GHz map. We have not altered the \verb|i100| zero-point in any way. We have
+also removed the Solar dipole residual according to \cite{planckdust}, 
+by subtracting a dipole pattern oriented toward $(l, b) = ()$ and scaled
+according to their Table 1.
+
+The offset and residual dipole parameters for \PLANCK~217 GHz were not 
+available from \cite{planckdust} Table 1. In order to set the zero-point of 
+Galactic emission in the 217 GHz map, we simultaneously fit the constant 
+offset and residual dipole amplitude. Restricting to regions of low column 
+density (HI $<$ 200 K km/s), we modeled the 217 GHz map as:
+
+\begin{equation}
+\mathcal{I}_{217, i} = a\mathcal{I}_{857, i} + b\mathcal{D}_{i} + c
+\end{equation}
+
+With $i$ denoting a single nside=64 HEALPix pixel in the maps 
+$\mathcal{I}_{857}$, $\mathcal{I}_{217}$, and $\mathcal{D}$. Here 
+$\mathcal{I}_{857}$ is the Planck 857 GHz map with zodiacal emission, compact 
+sources, and constant offset removed, smoothed to $1^{\circ}$ resolution. 
+$\mathcal{I}_{217}$ is the corresponding $1^{\circ}$ resolution Planck 217 GHz 
+map with zodiacal emission and compact sources removed. $\mathcal{D}$ is a
+scaling of the Solar dipole with unit amplitude. Because $\sim$18,000 pixels
+satisfy the low HI cut, we have an overconstrained linear model with three
+parameters: a, b, and c. $a$ represents the slope of Planck 217 GHz 
+versus Planck 857 GHz assuming they are linearly correlated, and is not
+of any importance to our downstream analysis. $b$ represents the scaling of 
+the Solar dipole that makes the 857 GHz vs. 217 GHz correlation tightest, and 
+$c$ represents the constant offset necessary to make the zero level of the 217 
+GHz map consistent with that of the 857 GHz map. Performing a linear least
+squares fit with uniform weights and iterative outlier rejection, we find 
+$a=4.33\times10^{-5}\ K/(MJy/sr)$, $b=-1.40\times10^{-5}\ K$, and 
+$c=8.12\times10^{-5}\ K$. Note that $b$ represents 0.42\% of the Solar dipole 
+amplitude, which is within the calibration uncertainty of the 217 GHz band. 
+Figure 1 shows scatterplots of the 857 GHz versus 217 GHz correlation before 
+and after correcting for our best-fit offset and dipole residual. Not only is 
+the improvement striking in this scatterplot, but the residual dipole also 
+appears visually well-corrected in the 217 GHz map itself.
 

### 2014-01-16 ms.tex
clean-up

@@
 latitudes. To remove the CMB anisotropies, we have subtracted the SMICA model
-from each of the relevant \PLANCK~maps \citep{smica}, after appropriate unit conversions.
+from each of the relevant \PLANCK~maps \citep{smica}, after appropriate unit 
+conversions. Removal of the residual Solar dipole at low frequencies is 
+discussed in $\S$\ref{sec:zp}.
 
@@
 \subsection{Zero-Point}
+\label{sec:zp}
 Although we wish to isolate and model thermal emission from Galactic dust, the
-\PLANCK~maps contain additional components. At each frequency, there can
-exist an overall, constant offset that must be subtracted to set the
-zero level of Galactic dust. Additionally, faint residuals 
-of the Solar dipole remain at low frequencies. At 353 GHz, 545 GHz, 857 GHz, 
-we have adopted the zero-point offsets of \cite{planckdust} Table 1, which 
-were derived by correlating \PLANCK~857 GHz versus HI at low column density, 
-and then by correlating the other Planck channels against the corrected 857 
-GHz map. We have not altered the \verb|i100| zero-point in any way. We have
-also removed the Solar dipole residual according to \cite{planckdust}, 
-by subtracting a dipole pattern oriented toward $(l, b) = ()$ and scaled
-according to their Table 1.
+\PLANCK~maps contain additional components on large angular scales. At each 
+frequency, there can exist an overall, constant offset that must be subtracted 
+to set the zero level of Galactic dust. Additionally, faint residuals of the 
+Solar dipole remain at low frequencies. At 353 GHz, 545 GHz, 857 GHz, we have 
+adopted the zero-point offsets of \cite{planckdust} Table 1, which were derived
+ by correlating \PLANCK~857 GHz versus HI at low column density, and then by 
+correlating the other Planck channels against the corrected 857 GHz map. We 
+have not altered the \verb|i100| zero-point in any way. We have also removed 
+the Solar dipole residual according to \cite{planckdust}, by subtracting a 
+dipole pattern oriented toward $(l, b) = ()$ and scaled according to their 
+Table 1.
 

### 2014-01-16 ms.tex
more clean-up of zero-point section

@@
  by correlating \PLANCK~857 GHz versus HI at low column density, and then by 
-correlating the other Planck channels against the corrected 857 GHz map. We 
+correlating the other \PLANCK~channels against the corrected 857 GHz map. We 
 have not altered the \verb|i100| zero-point in any way. We have also removed 
 the Solar dipole residual according to \cite{planckdust}, by subtracting a 
-dipole pattern oriented toward $(l, b) = ()$ and scaled according to their 
-Table 1.
+dipole pattern oriented toward $(l, b) = (263.99^{\circ}, 48.26^{\circ})$ and 
+scaled according to their Table 1.
 
@@
 $\mathcal{I}_{857}$, $\mathcal{I}_{217}$, and $\mathcal{D}$. Here 
-$\mathcal{I}_{857}$ is the Planck 857 GHz map with zodiacal emission, compact 
+$\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
 sources, and constant offset removed, smoothed to $1^{\circ}$ resolution. 
-$\mathcal{I}_{217}$ is the corresponding $1^{\circ}$ resolution Planck 217 GHz 
-map with zodiacal emission and compact sources removed. $\mathcal{D}$ is a
+$\mathcal{I}_{217}$ is the corresponding $1^{\circ}$ resolution \PLANCK~217 
+GHz map with zodiacal emission and compact sources removed. $\mathcal{D}$ is a
 scaling of the Solar dipole with unit amplitude. Because $\sim$18,000 pixels
 satisfy the low HI cut, we have an overconstrained linear model with three
-parameters: a, b, and c. $a$ represents the slope of Planck 217 GHz 
-versus Planck 857 GHz assuming they are linearly correlated, and is not
+parameters: a, b, and c. $a$ represents the slope of \PLANCK~217 GHz 
+versus \PLANCK~857 GHz assuming they are linearly correlated, and is not
 of any importance to our downstream analysis. $b$ represents the scaling of 
@@
 $c=8.12\times10^{-5}\ K$. Note that $b$ represents 0.42\% of the Solar dipole 
-amplitude, which is within the calibration uncertainty of the 217 GHz band. 
-Figure 1 shows scatterplots of the 857 GHz versus 217 GHz correlation before 
-and after correcting for our best-fit offset and dipole residual. Not only is 
-the improvement striking in this scatterplot, but the residual dipole also 
-appears visually well-corrected in the 217 GHz map itself.
+amplitude, which is within the calibration uncertainty of the \PLANCK~217 GHz 
+band. Figure 1 shows scatterplots of the 857 GHz versus 217 GHz correlation 
+before and after correcting for our best-fit offset and dipole residual. Not 
+only is the improvement striking in this scatterplot, but the residual dipole 
+also appears visually well-corrected in the 217 GHz map itself. Before 
+performing thermal dust fits, we therefore subtract $c$ and $b\mathcal{D}$ from
+the 217 GHz map.
 

### 2014-01-16 ms.tex
added scatter plots showing 217 GHz vs 857 GHz correlation

@@
 scaled according to their Table 1.
+
+\begin{figure}
+\begin{center}
+\epsfig{file=scatter_857_217.eps, width=3.3in}
+\caption{\label{fig:scatter} Scatter plot of \PLANCK~217 GHz versus \PLANCK~857
+GHz. Left: before correcting for offset and residual Solar dipole. Right: after
+correcting or the best-fit offset and dipole amplitude, as described in 
+$\S$\ref{sec:zp}. The dashed red line shows the best-fit linear relationship
+between 857 GHz and 217 GHz.}
+\end{center}
+\end{figure}
 

### 2014-01-20 ms.tex
lots of clean up and some re-organization

@@
 
+re
 The \PLANCK~2013 data release \citep{planck2013} represents an important 
@@
 range of frequencies. \cite{planckdust} has recently conducted a study modeling
-\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
+\PLANCK~353 GHz, 545 GHz, 857 GHz and \IRAS~100$\mu$m emission with a single
 MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
@@
 dust emission model we fit to the \PLANCK~and \IRAS~data. In 
-$\S$\ref{sec:fitting} we provide details of the Markov Chain Monte Carlo method
+$\S$\ref{sec:fitting} we provide details of the Markov chain Monte Carlo method
 with which we have estimated the parameters of our model. In 
 $\S$\ref{sec:results} we present the full-sky maps of dust temperature and 
-optical depth thus obtained, and conclude and $\S$\ref{sec:conclusion}
-
-%how what we're doing fits in
-%     where FDS99 fit in
-%     Planck data qualities that improve on data used in FDS99
-%     benefits of using Planck + FDS99 model
-%utility/applications of what we're doing
-
-%list of figures : 
-% posterior surface for some pixel, with samples from markov chain overplotted
-%    --> also overplot output best-fit (T,I545) and unctertainty estimate
-% plot for some set of pixels of SED overlaid with best-fit two-component model
-%    --> done in Python instead of IDL
-%    --> overlay 
-% plot of resulting T2 and tau
-% plots of full-sky residuals relative to our model ?
-%  ---> and for lower-frequency bands to emphasize that FDS99 is better for
-%       extrapolating towards mm wavelengths
-% zoom-in of region with interesting dust showing :
-%  SFD T map, two-component T map, Planck team one-component T map
-%      good spot is in polaris, centered on (lgal,bgal) ~ (112, 20)
+optical depth thus obtained, and conclude in $\S$\ref{sec:conclusion}.
 
@@
 All \PLANCK~data products utilized throughout this work are drawn from the 
-\PLANCK~2013 data release \citep{planck2013}. Specifically, we have made use 
-of the the 217 GHz, 353 GHz, 545 GHz and 857 GHz intensity maps. We use the 
-versions of these maps which have been corrected for zodiacal light 
+\PLANCK~2013 release \citep{planck2013}. Specifically, we have made use 
+of the 217 GHz, 353 GHz, 545 GHz and 857 GHz intensity maps which have been 
+corrected for zodiacal light 
 \citep[\texttt{R1.10\_nominal\_ZodiCorrected},][]{planckzodi}.
 
-%TODO: actually smooth all of the maps to a common PSF of 6.1 arcmin.
+To incorporate measurements on the Wien side of the dust emission spectrum, 
+we include 100$\mu$m data in our SED fits. In particular, we use the SFD 
+reprocessing of \IRAS~100$\mu$m, which we will refer to as \verb|i100|, and at 
+times by frequency as 3000 GHz. The \verb|i100| map has angular resolution of 
+$6.1'$, and was constructed so as to contain only thermal 
+emission from Galactic dust, with compact sources and zodiacal light removed, 
+and its zero level tied to HI. We use the \verb|i100| map as-is, without any 
+custom modifications.
+%maybe clarify that throughout we use SFD i100 totally as-is, with no
+% customization
 
-To incorporate information about the dust emission on the Wien side of its 
-spectrum, we make use of 100$\mu$m data. In particular, we use the SFD 
-reprocessing of IRAS 100$\mu$m, which we will refer to as \verb|i100|, and at 
-times by frequency as 3000 GHz. The \verb|i100| map has angular resolution of 
-$6.1'$. 
 %list other %important characteristics of i100 e.g. that it has been 
@@
 
-\section{Pre-processing}
+\section{Preprocessing}
 \label{sec:prepro}
@@
 
-\subsection{Unit Conversions}
+\subsection{CMB Removal}
+The CMB is effectively imperceptible in \PLANCK~857 GHz, but can be noticed at 
+a low level in \PLANCK~545 GHz, and is prominent in \PLANCK~217 GHz and 353 
+GHz relative to the diffuse Galactic emission we wish to characterize, 
+especially at high latitudes. To remove the CMB anisotropies, we have 
+subtracted the SMICA model from each of the relevant \PLANCK~maps 
+\citep{smica}, after appropriate unit conversions. Removal of the residual 
+Solar dipole at low frequencies is discussed in $\S$\ref{sec:zp}.
 
-Some of the maps in native format are provided in thermodynamic $\delta T$, 
-while others are provided in units of MJy/sr. Before performing any fits, 
-we convert all measurements to MJy/sr following the guidelines of \cite{planckresponse}.
-
-%i think it's table 5 that I specifically want to cite within the ``spectral
-%response'' paper, but i need to check that those values are consistent
-% with the ones i actually used from the other document ``HFI-unit conversion 
-%and colour correction instructions v1.2''
-
-\subsection{CMB Removal}
-The CMB is effectively imperceptible at 857 GHz, but can be noticed at a 
-low level at 545 GHz, and is prominent at 217 GHz and 353 GHz relative 
-to the diffuse Galactic emission we wish to characterize, especially at high
-latitudes. To remove the CMB anisotropies, we have subtracted the SMICA model
-from each of the relevant \PLANCK~maps \citep{smica}, after appropriate unit 
-conversions. Removal of the residual Solar dipole at low frequencies is 
-discussed in $\S$\ref{sec:zp}.
-
-\subsection{Finite Bandpass Correction}
-The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
-intensity $M_{\nu}$ in MJy/sr for any single frequency $\nu$. But in reality
-we are comparing to broad bands typically hundreds of GHz wide. The shape of 
-model spectrum $M_{\nu}$ is only dependent upon one parameter: the hot
-dust temperature $T_2$. We have therefore computed bandpass correction factors
-$b_{\nu_i}$ such that $M_{\nu_i}b_{\nu_i}$ is the predicted observation for the
-\PLANCK~or \IRAS~band of interest. We have used the \PLANCK~transmission 
-curves provided in the file \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. 
-For 3000 GHz, we have used the \IRAS~bandpass, following the treatment of
-\cite{planckdust}. We note that it is not clear which bandpass should
-properly be considered for the IRAS/DIRBE composite 100$\mu$m maps used in 
-this analysis (here SFD \verb|i100|) and that of \cite{planckdust}.
-
-% check that RIMO file i've used is actually the most up-to-date version
+\subsection{Compact Sources}
+To mask compact sources, we use the SFD compact source mask, which was 
+originally constructed to mask point sources and resolved compact objects
+that are not part of the Galactic cirrus at 3000 GHz. Given our pixelization 
+(see $\S$\ref{sec:pix}), 1.56\% of pixels are masked. We have inspected all of 
+the maps used in this analysis and do not see any evidence that this compact 
+source mask fails to adequately mask compact sources in the \PLANCK~data. In 
+practice, we perform our dust SED fits in all pixels, even those flagged by 
+the point source mask. Compact source affected pixels can be ignored or 
+interpolated over downstream.
+%maybe say that we're releasing a version of the map with point sources
+%interpolated over by us as well
 
@@
 amplitude, which is within the calibration uncertainty of the \PLANCK~217 GHz 
-band. Figure 1 shows scatterplots of the 857 GHz versus 217 GHz correlation 
-before and after correcting for our best-fit offset and dipole residual. Not 
-only is the improvement striking in this scatterplot, but the residual dipole 
-also appears visually well-corrected in the 217 GHz map itself. Before 
-performing thermal dust fits, we therefore subtract $c$ and $b\mathcal{D}$ from
-the 217 GHz map.
+band. Figure \ref{fig:scatter} shows scatterplots of the 857 GHz versus 217 
+GHz correlation before and after correcting for our best-fit offset and dipole 
+residual. Not only is the improvement striking in this scatterplot, but the 
+residual dipole also appears visually well-corrected in the 217 GHz map 
+itself. Before performing thermal dust fits, we therefore subtract $c$ and 
+$b\mathcal{D}$ from the 217 GHz map.
+
+\subsection{Unit Conversions}
+
+Some of the maps in native format are provided in thermodynamic $\delta T$, 
+while others are provided in units of MJy/sr. Before performing any fits, 
+we convert all measurements to MJy/sr following the guidelines of \cite{planckresponse}.
+
+%i think it's table 5 that I specifically want to cite within the ``spectral
+%response'' paper, but i need to check that those values are consistent
+% with the ones i actually used from the other document ``HFI-unit conversion 
+%and colour correction instructions v1.2''
 
@@
 
-\subsection{Compact Sources}
-To mask compact sources, we use the SFD compact source mask, which was 
-originally constructed to mask point sources and resolved compact objects
-that are not part of the Galactic cirrus at 3000 GHz. Given our pixelization 
-(see $\S$\ref{sec:pix}), 1.56\% of pixels are masked. We have inspected all of 
-the maps used in this analysis and do not see any evidence that this compact 
-source mask fails to adequately mask compact sources in the \PLANCK~data. In 
-practice, we perform our dust SED fits in all pixels, even those flagged by 
-the point source mask. Compact source affected pixels can be ignored or 
-interpolated over downstream.
-%maybe say that we're releasing a version of the map with point sources
-%interpolated over by us as well
-
 \begin{figure}
@@
 \caption{Gridded posterior PDFs for three nside=2048 pixels. Red crosses mark 
-the best-fit parameters based on our Markov Chain sampling of the posterior. 
+the best-fit parameters based on our Markov chain sampling of the posterior. 
 The posterior distributions are in general extremely well-behaved, showing
@@
 FDS99 found typical values for $T_2$ and 
+%basically just finish clarifying here that we want to start simple by fitting
+%only two parameters for each pixel since we only have 5 intensity
+% measurements per pixel in our baseline fits at 6.1 arcmin resoluiton
 
@@
 neighboring pixels.
+
+\subsection{Finite Bandpass Correction}
+The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
+intensity $M_{\nu}$ in MJy/sr for any single frequency $\nu$. But in reality
+we are comparing to broad bands typically hundreds of GHz wide. The shape of 
+model spectrum $M_{\nu}$ is only dependent upon one parameter: the hot
+dust temperature $T_2$. We have therefore computed bandpass correction factors
+$b_{\nu_i}$ such that $M_{\nu_i}b_{\nu_i}$ is the predicted observation for the
+\PLANCK~or \IRAS~band of interest. We have used the \PLANCK~transmission 
+curves provided in the file \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. 
+For 3000 GHz, we have used the \IRAS~bandpass, following the treatment of
+\cite{planckdust}. We note that it is not clear which bandpass should
+properly be considered for the \IRAS/DIRBE composite 100$\mu$m maps used in 
+this analysis (here SFD \verb|i100|) and that of \cite{planckdust}.
+
+% check that RIMO file i've used is actually the most up-to-date version
 

### 2014-01-21 ms.tex
more clean up and reorganization

@@
 
-\subsection{Smoothing}
-We wish to simultaneously fit \verb|i100| along with four \PLANCK~bands. To 
-properly combine these maps, they must have the same point spread function 
-(PSF). \verb|i100|, with its $6.1'$ symmetric Gaussian PSF, is the 
-lowest-resolution map we have included. To match PSFs, we have therefore 
-smoothed each of the \PLANCK~maps under consideration to $6.1'$ resolution by 
-considering each native map to have a symmetric Gaussian beam and smoothing by 
-the appropriate symmetric Gaussian such that the resulting map has a FWHM of 
-$6.1'$. The FWHM we assign to the native \PLANCK~maps is taken from 
-\cite{planckbeam}, specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, 
-$4.84'$ for 545 GHz, and $4.63'$ for 857 GHz.
+%maybe one sentence here stating that the goal of next few subsections
+%is to isolate Galactic thermal dust emission
 
-\subsection{CMB Removal}
-The CMB is effectively imperceptible in \PLANCK~857 GHz, but can be noticed at 
-a low level in \PLANCK~545 GHz, and is prominent in \PLANCK~217 GHz and 353 
-GHz relative to the diffuse Galactic emission we wish to characterize, 
-especially at high latitudes. To remove the CMB anisotropies, we have 
-subtracted the SMICA model from each of the relevant \PLANCK~maps 
-\citep{smica}, after appropriate unit conversions. Removal of the residual 
-Solar dipole at low frequencies is discussed in $\S$\ref{sec:zp}.
+\subsection{CMB Anisotropy Removal}
+\label{sec:cmb}
+In preparing the \PLANCK~maps for thermal dust SED fitting, we first addressed
+the CMB anisotropies before performing any of the interpolation/smoothing 
+described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. The CMB anisotropies are 
+effectively imperceptible in \PLANCK~857 GHz, but can be perceived at a low 
+level in \PLANCK~545 GHz, and are prominent in \PLANCK~217 GHz and 353 GHz 
+relative to the Galactic emission we wish to characterize, especially at high 
+latitudes. To remove the CMB anisotropies, we have subtracted the Spectral 
+Matching Independent Component Analysis (\verb|SMICA|) model from each of the 
+\PLANCK~maps \citep{smica}, after applying appropriate unit conversions. 
+Removal of the residual Solar dipole at low frequencies is discussed in 
+$\S$\ref{sec:zp}.
+% SMICA is subtracted from ALL Planck maps being used, including 545, 857 GHz
 
 \subsection{Compact Sources}
+\label{sec:ptsrc}
 To mask compact sources, we use the SFD compact source mask, which was 
@@
 %interpolated over by us as well
+
+\subsection{Smoothing}
+\label{sec:smth}
+We wish to simultaneously fit \verb|i100| along with the four 
+highest-frequency \PLANCK~bands. To properly combine these maps, they must have
+ the same point spread function (PSF). \verb|i100|, with its $6.1'$ symmetric 
+Gaussian PSF, is the lowest-resolution map we have included. To match PSFs, we 
+have therefore smoothed each of the \PLANCK~maps under consideration to $6.1'$ 
+resolution by considering each native map to have a symmetric Gaussian beam and
+ smoothing by the appropriate symmetric Gaussian such that the resulting map 
+has a FWHM of $6.1'$. The FWHM we assign to the native \PLANCK~maps is taken 
+from \cite{planckbeam}, specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, 
+$4.84'$ for 545 GHz, and $4.63'$ for 857 GHz.
 

### 2014-01-21 ms.tex
more clean up

@@
 emission from Galactic dust, with compact sources and zodiacal light removed, 
-and its zero level tied to HI. We use the \verb|i100| map as-is, without any 
+and its zero level tied to H\,\textsc{i}. We use the \verb|i100| map as-is, without any 
 custom modifications.
@@
 
-%maybe one sentence here stating that the goal of next few subsections
-%is to isolate Galactic thermal dust emission
+The following subsections detail the processing steps we have applied to 
+isolate thermal emission from Galactic dust in the \PLANCK~maps and prepare
+these maps for our joint \IRAS/\PLANCK~SED fits.
 
@@
 \label{sec:cmb}
-In preparing the \PLANCK~maps for thermal dust SED fitting, we first addressed
-the CMB anisotropies before performing any of the interpolation/smoothing 
-described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. The CMB anisotropies are 
-effectively imperceptible in \PLANCK~857 GHz, but can be perceived at a low 
-level in \PLANCK~545 GHz, and are prominent in \PLANCK~217 GHz and 353 GHz 
-relative to the Galactic emission we wish to characterize, especially at high 
-latitudes. To remove the CMB anisotropies, we have subtracted the Spectral 
-Matching Independent Component Analysis (\verb|SMICA|) model from each of the 
-\PLANCK~maps \citep{smica}, after applying appropriate unit conversions. 
-Removal of the residual Solar dipole at low frequencies is discussed in 
-$\S$\ref{sec:zp}.
+We first addressed the CMB anisotropies before performing any of the 
+interpolation/smoothing described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. 
+The CMB anisotropies are effectively imperceptible in \PLANCK~857 GHz, but can 
+be perceived at a low level in \PLANCK~545 GHz, and are prominent in 
+\PLANCK~217 GHz and 353 GHz relative to the Galactic emission we wish to 
+characterize, especially at high latitudes. To remove the CMB anisotropies, we 
+have subtracted the Spectral Matching Independent Component Analysis 
+(\verb|SMICA|) model from each of the \PLANCK~maps \citep{smica}, after 
+applying appropriate unit conversions. Removal of the residual Solar dipole at 
+low frequencies is discussed in $\S$\ref{sec:zp}.
 % SMICA is subtracted from ALL Planck maps being used, including 545, 857 GHz
@@
 adopted the zero-point offsets of \cite{planckdust} Table 1, which were derived
- by correlating \PLANCK~857 GHz versus HI at low column density, and then by 
-correlating the other \PLANCK~channels against the corrected 857 GHz map. We 
-have not altered the \verb|i100| zero-point in any way. We have also removed 
-the Solar dipole residual according to \cite{planckdust}, by subtracting a 
-dipole pattern oriented toward $(l, b) = (263.99^{\circ}, 48.26^{\circ})$ and 
-scaled according to their Table 1.
+ by correlating \PLANCK~857 GHz versus H\,\textsc{i} at low column density, and
+then by correlating the other \PLANCK~channels against the corrected 857 GHz 
+map. We have not altered the \verb|i100| zero-point in any way. We have also 
+removed the Solar dipole residual according to \cite{planckdust}, by 
+subtracting a dipole pattern oriented toward 
+$(l, b) = (263.99^{\circ}, 48.26^{\circ})$ and scaled according to their 
+Table 1.
 
@@
 offset and residual dipole amplitude. Restricting to regions of low column 
-density (HI $<$ 200 K km/s), we modeled the 217 GHz map as:
+density (H\,\textsc{i} $<$ 200 K km/s), we modeled the 217 GHz map as:
+
+%in previous sentence, mention the specific cut on HI velocities considered
 
@@
 scaling of the Solar dipole with unit amplitude. Because $\sim$18,000 pixels
-satisfy the low HI cut, we have an overconstrained linear model with three
-parameters: a, b, and c. $a$ represents the slope of \PLANCK~217 GHz 
+satisfy the low H\,\textsc{i} cut, we have an overconstrained linear model with
+three parameters: a, b, and c. $a$ represents the slope of \PLANCK~217 GHz 
 versus \PLANCK~857 GHz assuming they are linearly correlated, and is not
@@
 GHz correlation before and after correcting for our best-fit offset and dipole 
-residual. Not only is the improvement striking in this scatterplot, but the 
-residual dipole also appears visually well-corrected in the 217 GHz map 
-itself. Before performing thermal dust fits, we therefore subtract $c$ and 
+residual. Not only is the improved correlation striking in this scatterplot, 
+but the residual dipole also appears visually well-corrected in the 217 GHz 
+map itself. Before performing thermal dust fits, we therefore subtract $c$ and 
 $b\mathcal{D}$ from the 217 GHz map.
@@
 while others are provided in units of MJy/sr. Before performing any fits, 
-we convert all measurements to MJy/sr following the guidelines of \cite{planckresponse}.
+we convert all measurements to MJy/sr following the guidelines of 
+\cite{planckresponse}.
 
@@
 \cite{planckdust}. We note that it is not clear which bandpass should
-properly be considered for the \IRAS/DIRBE composite 100$\mu$m maps used in 
-this analysis (here SFD \verb|i100|) and that of \cite{planckdust}.
+properly be ascribed to the \IRAS/DIRBE composite 100$\mu$m maps under
+consideration. % (here SFD \verb|i100|) and that of \cite{planckdust}).
 

### 2014-01-21 ms.tex
more clean up, especially in explanation of bandpass corrections

@@
 emission from Galactic dust, with compact sources and zodiacal light removed, 
-and its zero level tied to H\,\textsc{i}. We use the \verb|i100| map as-is, without any 
+and its zero level tied to H\,\textsc{i}. We use the \verb|i100| map as is, without any 
 custom modifications.
@@
 
-Our model is that of FDS99, which consists of two populations of dust 
-grains emitting as MBBs, but with different temperatures and different 
-emissivity power law indices $\beta$. The shape of this spectrum is given by:
+We adopt the thermal dust emission model of FDS99, which consists of two 
+populations of dust grains emitting as MBBs, but with different temperatures 
+and different emissivity power law indices $\beta$. The shape of this spectrum 
+is given by:
 
@@
 
-At each sky location, we have five independent intensity measurements (four ) 
-FDS99 found typical values for $T_2$ and 
+At each sky location, our baseline fit at the full $6.1'$ resolution 
+incorporates only five independent intensity measurements (\verb|i100| along 
+with the four highest-frequency \PLANCK~bands). FDS99 found typical values for 
+$T_2$ and
+
 %basically just finish clarifying here that we want to start simple by fitting
@@
 
+%mention that we're using healpix in Galactic coordinates !!!!!!
+
 \subsection{Finite Bandpass Correction}
 The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
-intensity $M_{\nu}$ in MJy/sr for any single frequency $\nu$. But in reality
-we are comparing to broad bands typically hundreds of GHz wide. The shape of 
-model spectrum $M_{\nu}$ is only dependent upon one parameter: the hot
-dust temperature $T_2$. We have therefore computed bandpass correction factors
-$b_{\nu_i}$ such that $M_{\nu_i}b_{\nu_i}$ is the predicted observation for the
-\PLANCK~or \IRAS~band of interest. We have used the \PLANCK~transmission 
-curves provided in the file \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. 
-For 3000 GHz, we have used the \IRAS~bandpass, following the treatment of
-\cite{planckdust}. We note that it is not clear which bandpass should
-properly be ascribed to the \IRAS/DIRBE composite 100$\mu$m maps under
-consideration. % (here SFD \verb|i100|) and that of \cite{planckdust}).
+intensity $M_{\nu}$ in MJy/sr for any single frequency $\nu$. In practice, 
+however, we wish to constrain our model using measurements in the broad 
+\IRAS/\PLANCK~bandpasses, typically hundreds of GHz wide. We have therefore 
+computed dimensionless bandpass correction factors $b_{\nu_i}$ such that 
+$M_{\nu_i}b_{\nu_i}$ is the predicted observation for the \PLANCK~or \IRAS~band
+ of interest, in MJy/sr. Here $\nu_i$ represents the $i^{th}$ of the five 
+nominal band center frequencies for which we have measurements, $\nu_i \in$
+\{217, 353, 545, 857, 3000\} GHz. The shape of model spectrum $M_{\nu}$ is only
+dependent upon one parameter: the hot dust temperature $T_2$. We have used the 
+\PLANCK~transmission curves provided in the file 
+\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have 
+used the \IRAS~bandpass, following the treatment of \cite{planckdust}. We note 
+that it is not clear which bandpass should properly be ascribed to the 
+\IRAS/DIRBE composite 100$\mu$m maps under consideration. 
+% (here SFD \verb|i100|) and that of \cite{planckdust}).
+
+% introduce nu_i notation in above paragraph with some mention of what it
+% means
 

### 2014-01-22 ms.tex
re-write of unit conversion subsection

@@
 \begin{center}
-\epsfig{file=scatter_857_217.eps, width=3.3in}
+\epsfig{file=scatter_857_217.eps, width=3.4in}
 \caption{\label{fig:scatter} Scatter plot of \PLANCK~217 GHz versus \PLANCK~857
@@
 offset and residual dipole amplitude. Restricting to regions of low column 
-density (H\,\textsc{i} $<$ 200 K km/s), we modeled the 217 GHz map as:
-
-%in previous sentence, mention the specific cut on HI velocities considered
+density (H\,\textsc{i} $<$ 200 K km/s for $-72$$<$$v_{LSR}$$<$$+25$ km/s), we 
+modeled the 217 GHz map as:
 
@@
 
-Some of the maps in native format are provided in thermodynamic $\delta T$, 
-while others are provided in units of MJy/sr. Before performing any fits, 
-we convert all measurements to MJy/sr following the guidelines of 
-\cite{planckresponse}.
+The \PLANCK~217 GHz and 353 GHz data are provided in thermodynamic $\delta T$, 
+while \verb|i100| and the higher frequency \PLANCK~maps are provided in units 
+of MJy/sr. Although the aforementioned preprocessing steps were conducted with 
+each map in its native units, we converted the 217 GHz and 353 GHz 
+measurements to MJy/sr according to \cite{planckresponse} prior to performing 
+SED fits.
 
-%i think it's table 5 that I specifically want to cite within the ``spectral
+%i think it's table 6 that I specifically want to cite within the ``spectral
 %response'' paper, but i need to check that those values are consistent

### 2014-01-22 ms.tex
clean up of pixelization subsection

@@
 
-The \PLANCK~217 GHz and 353 GHz data are provided in thermodynamic $\delta T$, 
-while \verb|i100| and the higher frequency \PLANCK~maps are provided in units 
-of MJy/sr. Although the aforementioned preprocessing steps were conducted with 
-each map in its native units, we converted the 217 GHz and 353 GHz 
-measurements to MJy/sr according to \cite{planckresponse} prior to performing 
-SED fits.
+The \PLANCK~217 GHz and 353 GHz data are provided in units of thermodynamic 
+$\delta T$, while \verb|i100| and the higher frequency \PLANCK~maps are 
+provided in units of MJy/sr. Although the aforementioned preprocessing steps 
+were conducted with each map in its native units, we converted the 217 GHz and 
+353 GHz measurements to MJy/sr according to \cite{planckresponse} prior to 
+performing SED fits.
 
@@
 
+% sentence here summarizing what the following subsections will describe ?
+
 \subsection{Pixelization}
 \label{sec:pix}
-For the purpose of fitting, we break the sky into independent pixels of 
-angular size $\sim$1.72$'$, defined by the HEALPix pixelization with nside=2048
-\citep{healpix}. This is convenient because the Planck maps are provided in 
-this format and this pixelization adequately samples the $6.1'$ resolution maps
-under consideration. We reiterate that each pixel is fit independently of 
-neighboring pixels.
-
-%mention that we're using healpix in Galactic coordinates !!!!!!
+For the purpose of fitting, we break the sky into $\sim$50 million 
+non-overlapping pixels of angular size $\sim$1.72$'$, defined by the HEALPix 
+pixelization in Galactic coordinates, with $N_{side}$=2048 \citep{healpix}. 
+This pixelization is convenient because it is the same format in which the 
+\PLANCK~HFI maps were released, and because it adequately samples the $6.1'$ 
+resolution maps under consideration. Our procedure will fit the intensity 
+measurements in each spatial pixel independently of those in neighboring 
+pixels.
 

### 2014-01-22 ms.tex
some progress on compact source subsection, still needs major work

@@
 \label{sec:ptsrc}
-To mask compact sources, we use the SFD compact source mask, which was 
-originally constructed to mask point sources and resolved compact objects
-that are not part of the Galactic cirrus at 3000 GHz. Given our pixelization 
-(see $\S$\ref{sec:pix}), 1.56\% of pixels are masked. We have inspected all of 
-the maps used in this analysis and do not see any evidence that this compact 
-source mask fails to adequately mask compact sources in the \PLANCK~data. In 
-practice, we perform our dust SED fits in all pixels, even those flagged by 
-the point source mask. Compact source affected pixels can be ignored or 
-interpolated over downstream.
-%maybe say that we're releasing a version of the map with point sources
-%interpolated over by us as well
+%start by mentioning that SFD removed compact sources (outside of b +/- 5)
+After subtracting the \verb|SMICA| CMB model, we next proceeded to interpolate 
+over compact sources, including both point sources and resolved galaxies. 
+Removing compact sources at this stage is important as it prevents 
+contamination of compact-source-free pixels in our downstream analyses which 
+require smoothing of the \PLANCK~maps. SFD carefully removed point sources and 
+galaxies from the \verb|i100| map everywhere outside of 
+$|b|$$<$$5^{\circ}$. We do not perform any further modifications of the 
+\verb|i100| map to account for compact sources. To mask compact sources in the 
+\PLANCK~maps, we use the SFD compact source mask, which was originally 
+constructed to mask point sources and resolved compact objects that are not 
+part of the Galactic cirrus at 3000 GHz. Given our pixelization (see 
+$\S$\ref{sec:pix}), 1.56\% of pixels are masked.
+
+%this compact source section still needs a lot of work
+
+% probably best to refer to an appendix for details of the point source
+% masking
 

### 2014-01-23 ms.tex
more notes to self, other minor tweaks

@@
 
-\title{Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps}
+\title{Two-component thermal dust emission model: application to the 
+{\it PLANCK} HFI maps}
 \author{Aaron M. Meisner\altaffilmark{1,2}}
@@
 % SMICA is subtracted from ALL Planck maps being used, including 545, 857 GHz
+% WHAT IS THE ANGULAR RESOLUTION OF THE SMICA MAP, AND IS IT EVEN
+% WELL-DEFINED??
 
@@
 offset and residual dipole amplitude. Restricting to regions of low column 
-density (H\,\textsc{i} $<$ 200 K km/s for $-72$$<$$v_{LSR}$$<$$+25$ km/s), we 
-modeled the 217 GHz map as:
+density (H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for $-72$$<$$v_{LSR}$$<$$+25$ 
+km\,s$^{-1}$), we modeled the 217 GHz map as:
 
@@
  of interest, in MJy/sr. Here $\nu_i$ represents the $i^{th}$ of the five 
-nominal band center frequencies for which we have measurements, $\nu_i \in$
-\{217, 353, 545, 857, 3000\} GHz. The shape of model spectrum $M_{\nu}$ is only
-dependent upon one parameter: the hot dust temperature $T_2$. We have used the 
-\PLANCK~transmission curves provided in the file 
-\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have 
-used the \IRAS~bandpass, following the treatment of \cite{planckdust}. We note 
-that it is not clear which bandpass should properly be ascribed to the 
-\IRAS/DIRBE composite 100$\mu$m maps under consideration. 
+nominal band center frequencies for which we have broadband measurements, 
+$\nu_i \in$ \{217, 353, 545, 857, 3000\} GHz. The shape of model spectrum 
+$M_{\nu}$ is only dependent upon one parameter: the hot dust temperature $T_2$.
+ We have used the \PLANCK~transmission curves provided in the file 
+\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have used 
+the \IRAS~bandpass, following the treatment of \cite{planckdust}. We note that 
+it is not clear which bandpass should properly be ascribed to the \IRAS/DIRBE 
+composite 100$\mu$m maps under consideration. 
 % (here SFD \verb|i100|) and that of \cite{planckdust}).
@@
 are sampling the posterior given by:
+
+% check whether I545 normalization parameter is the monochromatic
+% 545 GHz intensity, or if it is for the Planck bandpass
+% i think it should eventually be monochromatic, since that will be
+% more useful to people who want SED predictions
 
@@
 \end{equation}
+
+% is I_nu on RHS inclusive of offsets or is it the ``pure'' thermal dust
+% intensity
 
@@
 \subsection{Calculating $\tau$}
+
+%at some point in this should make statements re: the fact that in terms
+%of predicting *emission* the conversion to tau is unnecessary and
+%and actually the raw uncertainty on Ghz 545 amplitude is the relevant quantity
 

### 2014-01-24 ms.tex
more clean up, especially in introduction, and more notes to self

@@
 \begin{abstract}
-We present full-sky maps of dust optical depth and temperature derived by 
-fitting the \cite{FDS99} two-component dust emission model to
-\PLANCK~217, 353, 545, 857 GHz and \cite{SFD} \IRAS~100$\mu$m data. Both the 
-optical depth and temperature maps have angular resolution of $6.1'$. Such maps
- serve as an important alternative to and comparison for other dust 
-emission models, especially the single modified blackbody (MBB) model in which 
-$\beta$ and $T$ both vary spatially. We also expect the derived optical 
-depth to provide valuable cross-checks for other dust-column related data 
-products, specifically the \cite{SFD} map, which assumed 
-$\beta = 2$ single-component dust emission and included a temperature map of 
-inferior $\sim$$1.3^{\circ}$ resolution. We briefly compare our 
-best-fit two-component spectral energy distributions to those of the 
-\cite{planckdust} single-component parametrization.
-%mention the enhanced temperature resolution relative to SFD
+We present full-sky, $6.1'$ resolution maps of dust optical depth and 
+temperature derived by fitting the \cite{FDS99} two-component dust emission 
+model to \PLANCK~217, 353, 545, and 857 GHz, along with \cite{SFD} 
+\IRAS~100$\mu$m data. These maps serve as an important alternative to and 
+point of comparison for other dust emission models, especially the single 
+modified blackbody model in which both the emissivity power law index and dust 
+temperature vary continuously. We also expect the derived optical depth to 
+provide valuable cross-checks for other dust-column related data products, 
+specifically the \cite{SFD} map, which assumed a single modified blackbody 
+with $\nu^2$ emissivity and included a temperature map of inferior 
+$\sim$$1.3^{\circ}$ resolution. We compare our best-fit two-component spectral 
+energy distributions to those of the \cite{planckdust} single-component 
+parametrization.
+%MENTION USE IN MAKING IR FOREGROUND PREDICTIONS
+%mention more explicitly the enhanced temperature resolution relative to SFD??
 %Our optical depth map will also provide a useful reference for dust maps 
@@
 provided full-sky infrared dust spectra at $7^{\circ}$ resolution in 213 narrow
-frequency bins between 200 GHz and 2100 GHz.
+frequency bins between 30 GHz and 2850 GHz.
 
-\cite{FDS99} (hereafter FDS99) used FIRAS data to derive a globally best-fit 
+\citet[hereafter FDS99]{FDS99} used FIRAS data to derive a globally best-fit 
 model of dust emission applicable over a very broad range of frequencies. 
-FDS99 showed that a model consisting of a single MBB with power law index 
-$\beta$ could not accurately match the \IRAS/FIRAS/DIRBE spectrum at both the 
-Wien and Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 
+FDS99 showed that no model consisting of a single modified blackbody (MBB) 
+could accurately match the \IRAS/FIRAS/DIRBE spectrum at both the Wien and 
+Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 therefore 
 proposed a dust emission model consisting of two MBBs, each with a different 
-temperature and power law index. Physically, these two components
-represent distinct dust grain species within the ISM, specifically 
-amorphous silicates and carbonaceous grains.
+temperature and power law index. Physically, these two components might 
+represent distinct dust grain species within the ISM, namely amorphous 
+silicates and carbonaceous grains.
 
-re
+% FDS used 100 GHz to 3000 GHz in their two-component fits
+%mention which grain species is large vs. small
+
+% should mention somewhere (probably in above paragraph, the range of
+% frequencies over which FDS99 model was shown to be applicable
+
 The \PLANCK~2013 data release \citep{planck2013} represents an important 
@@
 MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
-as an alernative model for the dust spectral energy distribution (SED) composed
- of \PLANCK~and \IRAS~data. In doing so, we obtain $6.1'$ resolution maps of 
-dust temperature and optical depth. Because we employ a model that has been 
-validated with FIRAS data down to sub-mm wavelengths, we expect our best-fit 
-parameters to be useful in constructing high-resolution predictions of dust 
-emission over a very broad range of wavelengths. This includes low frequencies 
-($<$350 GHz), which \cite{planckdust} caution their model may not adequately 
-fit, and also measurements near the peak of the dust SED, for example 
-\AKARI~140-160$\mu$m \citep{akari}. We also anticipate our derived optical 
-depth map will serve as a useful comparison for extinction estimates based 
-directly upon optical/NIR observations of stars.
+as an alernative parametrization for the dust spectral energy distribution 
+(SED) composed  of \PLANCK~and \IRAS~data. In doing so, we obtain $6.1'$ 
+resolution maps of dust temperature and optical depth. Because we employ a 
+model that has been validated with FIRAS data down to sub-mm wavelengths, we 
+expect our best-fit parameters to be useful in constructing high-resolution 
+predictions of dust emission over a very broad range of wavelengths. This 
+includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
+model may not adequately fit, and also measurements near the peak of the dust 
+SED, for example \AKARI~140-160$\mu$m \citep{akari}. We also anticipate our 
+derived optical depth map will serve as a useful comparison for extinction 
+estimates based directly upon optical/NIR observations of stars. % and as
+% a baseline or a next generation dust extinction map incorporating
+% high resolution, fulls-sky infrared data sets such as WISE and Akari.
 
@@
 
-In $\S$\ref{sec:data} we discuss the data used throughout this study. In 
-$\S$\ref{sec:prepro} we describe our preprocessing of the data to isolate 
-thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we describe the 
-dust emission model we fit to the \PLANCK~and \IRAS~data. In 
-$\S$\ref{sec:fitting} we provide details of the Markov chain Monte Carlo method
-with which we have estimated the parameters of our model. In 
+In $\S$\ref{sec:data} we introduce the data used throughout this study. In 
+$\S$\ref{sec:prepro} we describe our preprocessing of the \PLANCK~maps to 
+isolate thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we 
+describe the dust emission model we fit to the \PLANCK~and \IRAS~data. In 
+$\S$\ref{sec:fitting} we provide details of the Markov chain Monte Carlo (MCMC)
+ method with which we have estimated the parameters of our model. In 
 $\S$\ref{sec:results} we present the full-sky maps of dust temperature and 
@@
 
+%the below statements seem like they might best be moved to a generic
+%opening of the next section, stating our philosophy of breaking sky
+%into pixels, each with 5 SED measurements, and that with this small
+%number of constraints per pixel, it makes sense to have a baseline
+% fit at full resolution that has only two free parameters
 At each sky location, our baseline fit at the full $6.1'$ resolution 
@@
 
+% maybe have a section justifying the T2 prior value of 16.2K, presumably using
+% FIRAS as a cross-check?
+
 With $\bar{T}_2$ = 16.2 K and $\sigma_{\bar{T}_2}$ = 1.4 K. In practice we 

### 2014-01-24 ms.tex
clean up

@@
 temperature derived by fitting the \cite{FDS99} two-component dust emission 
-model to \PLANCK~217, 353, 545, and 857 GHz, along with \cite{SFD} 
-\IRAS~100$\mu$m data. These maps serve as an important alternative to and 
-point of comparison for other dust emission models, especially the single 
-modified blackbody model in which both the emissivity power law index and dust 
-temperature vary continuously. We also expect the derived optical depth to 
-provide valuable cross-checks for other dust-column related data products, 
-specifically the \cite{SFD} map, which assumed a single modified blackbody 
-with $\nu^2$ emissivity and included a temperature map of inferior 
-$\sim$$1.3^{\circ}$ resolution. We compare our best-fit two-component spectral 
-energy distributions to those of the \cite{planckdust} single-component 
-parametrization.
+model to \PLANCK~217, 353, 545, and 857 GHz, along with  \IRAS~100$\mu$m data. 
+These maps serve as an important alternative to and point of comparison for 
+other dust emission models, especially the single modified blackbody model in 
+which both the emissivity power law index and dust temperature vary 
+continuously. We also expect the derived optical depth to provide valuable 
+cross-checks for other dust-column related data products, specifically the 
+\cite{SFD} map, which assumed a single modified blackbody with $\nu^2$ 
+emissivity and included a temperature map of inferior $\sim$$1.3^{\circ}$ 
+resolution. We compare our best-fit two-component spectral energy distributions
+to those of the \cite{planckdust} single-component parametrization.
 %MENTION USE IN MAKING IR FOREGROUND PREDICTIONS
@@
 To incorporate measurements on the Wien side of the dust emission spectrum, 
-we include 100$\mu$m data in our SED fits. In particular, we use the SFD 
-reprocessing of \IRAS~100$\mu$m, which we will refer to as \verb|i100|, and at 
-times by frequency as 3000 GHz. The \verb|i100| map has angular resolution of 
-$6.1'$, and was constructed so as to contain only thermal 
-emission from Galactic dust, with compact sources and zodiacal light removed, 
-and its zero level tied to H\,\textsc{i}. We use the \verb|i100| map as is, without any 
-custom modifications.
+we include 100$\mu$m data in our SED fits. In particular, we use the 
+\citet[henceforth SFD]{SFD} reprocessing of \IRAS~100$\mu$m, which we will 
+refer to as \verb|i100|, and at times by frequency as 3000 GHz. The \verb|i100|
+ map has angular resolution of $6.1'$, and was constructed so as to contain 
+only thermal emission from Galactic dust, with compact sources and zodiacal 
+light removed, and its zero level tied to H\,\textsc{i}. We use the \verb|i100|
+map as is, without any custom modifications.
 %maybe clarify that throughout we use SFD i100 totally as-is, with no
@@
 %list other %important characteristics of i100 e.g. that it has been 
-%zodi-corrected and relies on dirbe on scales larger than ???
+%zodi-corrected and relies on dirbe on s
 

### 2014-01-24 ms.tex
more work on intro

@@
 \newcommand{\COBE}{{\it COBE}}
+\newcommand{\WISE}{{\it WISE}}
 
@@
 
-%basic background about interstellar dust emission
 Over the past decades, satellite observations have dramatically enhanced our
@@
 provided complementary full-sky measurements at ten infrared wavelengths from 
-1.25$\mu$m to 240$\mu$m with inferior 0.7$^{\circ}$ angular resolution, but 
-with a reliable zero point \citep{boggess92}. \COBE/FIRAS \citep{firas} also 
-provided full-sky infrared dust spectra at $7^{\circ}$ resolution in 213 narrow
-frequency bins between 30 GHz and 2850 GHz.
+1.25$\mu$m to 240$\mu$m, boasting a reliable zero point despite inferior 
+$\sim$0.7$^{\circ}$ angular resolution \citep{boggess92}. \COBE/FIRAS 
+\citep{firas} also provided full-sky infrared dust spectra at $7^{\circ}$ 
+resolution in 213 narrow frequency bins between 30 GHz and 2850 GHz.
 
-\citet[hereafter FDS99]{FDS99} used FIRAS data to derive a globally best-fit 
-model of dust emission applicable over a very broad range of frequencies. 
-FDS99 showed that no model consisting of a single modified blackbody (MBB) 
-could accurately match the \IRAS/FIRAS/DIRBE spectrum at both the Wien and 
-Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 therefore 
-proposed a dust emission model consisting of two MBBs, each with a different 
-temperature and power law index. Physically, these two components might 
-represent distinct dust grain species within the ISM, namely amorphous 
-silicates and carbonaceous grains.
+% DIRBE beam solid angles:
+% http://lambda.gsfc.nasa.gov/product/cobe/dirbe_products.cfm
+
+\citet[hereafter FDS99]{FDS99} used these FIRAS data to derive a globally 
+best-fit model of dust emission applicable over a very broad range of 
+frequencies. FDS99 showed that no model consisting of a single modified 
+blackbody (MBB) could accurately match the FIRAS/DIRBE spectrum at both the 
+Wien and Rayleigh-Jeans extremes. To fit the thermal dust spectrum between 100 
+and 3000 GHz, FDS99 therefore proposed an emission model consisting of two 
+MBBs, each with a different temperature and emissivity power law index. 
+Physically, these two components might represent distinct dust grain species 
+within the ISM, namely amorphous silicates and carbonaceous grains.
+
+% ^^final sentence about what FDS99 meant for foreground predictions (and how
+% those predictions actually worked)
+
+%did FDS99 actually use DIRBE (pretty sure they did)
 
@@
 SED, for example \AKARI~140-160$\mu$m \citep{akari}. We also anticipate our 
-derived optical depth map will serve as a useful comparison for extinction 
-estimates based directly upon optical/NIR observations of stars. % and as
-% a baseline or a next generation dust extinction map incorporating
-% high resolution, fulls-sky infrared data sets such as WISE and Akari.
+derived optical depth map will serve as a useful cross-check for extinction 
+estimates based directly upon optical observations of stars
+\citep[e.g.][]{green14} and as a baseline for next-generation dust extinction 
+maps incorporating high-resolution, full-sky infrared data sets such as 
+\WISE~\citep{wright10, meisner14} and \AKARI.
 

### 2014-01-24 ms.tex
intro

@@
 Physically, these two components might represent distinct dust grain species 
-within the ISM, namely amorphous silicates and carbonaceous grains.
+within the ISM, namely amorphous silicates and carbonaceous grains. By 
+combining this best-fit two-component model with a custom reprocessing of 
+\IRAS~100$\mu$m, FDS99 provided widely used foreground predictions with 
+$6.1'$ FHWM, limited largely by their $1.3^{\circ}$ resolution DIRBE-based 
+temperature correction.
 
@@
 as an alernative parametrization for the dust spectral energy distribution 
-(SED) composed  of \PLANCK~and \IRAS~data. In doing so, we obtain $6.1'$ 
-resolution maps of dust temperature and optical depth. Because we employ a 
+(SED) composed  of \PLANCK~and \IRAS~data. In doing so, we obtain maps of dust 
+temperature and optical depth, both at $6.1'$ resolution. Because we employ a 
 model that has been validated with FIRAS data down to sub-mm wavelengths, we 

### 2014-01-24 ms.tex
more about dust emission model

@@
 % fit at full resolution that has only two free parameters
-At each sky location, our baseline fit at the full $6.1'$ resolution 
-incorporates only five independent intensity measurements (\verb|i100| along 
-with the four highest-frequency \PLANCK~bands). FDS99 found typical values for 
-$T_2$ and
+FDS99 found $T_2 \approx 16.2$K, $T_1 \approx 9.4$K to be typical at 
+high-latitude. In the present formulation, there are only two free parameters 
+to describe an observed SED: the hot dust temperature $T_2$ and the 
+normalization of $M_{\nu}$. In principle, we could allow additional parameters,
+ such as $f_1$ and the ratio $q_1/q_2$, to vary. However the number of free 
+parameters in our baseline fit at the full $6.1'$ resolution is limited by the 
+fact that, for each sky location, the observed SED contains only five 
+independent intensity measurements (\verb|i100| along with the four 
+highest-frequency \PLANCK~bands).
 

### 2014-01-25 ms.tex
outlining

@@
 \begin{equation}
-\sigma_{\nu_i} = \sqrt{c^2_{\nu_i}I^2_{\nu_i} + c^2_{\nu_i}CMB^2_{\nu_i} + (\delta O_{\nu_i})^2 + n^2_{\nu_i}}
+\sigma_{\nu_i}(p) = \sqrt{c^2_{\nu_i}I_{\nu_i}(p)^2 + c^2_{\nu_i}CMB(p)^2 + (\delta O_{\nu_i})^2 + n_{\nu_i}(p)^2}
 \end{equation}
@@
 
+\subsection{Low Resolution Fits}
+%mention that the pixelization changes ---> to lower HEALpix nside
+%mention that over some region of the sky with high signal and high
+%S/N we try fitting t2, normalization and one of q1/q2, f_1
+%using more bands (including 143, and maybe 100 GHz)
+
+\section{Systematics}
+
+\subsection{CIBA}
+Perhaps the dominant limitation of our fits is the presence of cosmic
+infrared background anisotropies (CIBA) bleeding through into our maps of 
+Galactic dust temperature and optical depth in high-latitude regions 
+\citep{ciba}.
+\subsubsection{Simulations}
+
+\subsubsection{Optimizing Relative Weights}
+
+%not sure if below subsection is necessary, idea of giving zero weight to 217 
+%GHz may belong in above subsection
+
+%\subsubsection{Omitting 217 GHz}
+%The \cite{planckdust} result used only 353, 545, 857, and 3000 GHz. When we 
+%repeat our analysis ignoring 217 GHz, so that we are using the same
+%set of frequencies, we find that no major changes arise. This actually
+%should be done/investigated though.
+
+\subsection{Zero Point}
+Simulate the effect of getting zero points wrong to quantiy this
+systematic a bit.
+
+\subsection{$T_{2}$ Prior}
+Use FIRAS data to justify $T_2$ prior.
+
+\subsection{Other Limitations}
+\IRAS~is missing in some parts of sky which will therefore not truly have 6.1' 
+resolution.
+%any other miscellaneous issues?
+
 \section{Results}
@@
 \subsection{Calculating $\tau$}
+
+% this subsection should probably be moved to the ``dust emission model'' 
+% section of the paper eventually
 
@@
 
+%software utilities
 %provide maps at multiple different nsides ?
@@
 % provide uncertainty maps for tau and T2 ??
-
-\subsection{Limitations}
-Perhaps the dominant limitation of our fits is the presence of cosmic
-infrared background anisotropies (CIBA) bleeding through into our maps of 
-Galactic dust temperature and optical depth in high-latitude regions 
-\citep{ciba}.
-% CIBA !!!
-% IRAS missing so that parts of sky not truly 6.1' resolution map
 
@@
 
-\subsubsection{Omitting 217 GHz}
-The \cite{planckdust} result used only 353, 545, 857, and 3000 GHz. When we 
-repeat our analysis ignoring 217 GHz, so that we are using the same
-set of frequencies, we find that no major changes arise. This actually
-should be done/investigated though.
+\subsection{Validation with FIRAS}
 

### 2014-02-03 ms.tex
added figure showing best-fit map of f_1 parameter

@@
 
-\subsection{Low Resolution Fits}
+\subsection{Low-resolution Fits}
 %mention that the pixelization changes ---> to lower HEALpix nside
@@
 %using more bands (including 143, and maybe 100 GHz)
+
+As mentioned previously, our baseline fits fix several parameters which
+in principle could vary spatially. If we are willing to sacrifice angular
+resolution in order to incorporate lower-frequency \PLANCK~bands and
+enhance signal to noise, we can introduce additional free parameters
+and run the Markov chains in higher dimensions.
+
+We ran the Markov chains in three dimensions by allowing 
+$f_1$ to be a third free parameter. We added to our standard posterior a 
+term involving.
 
@@
 \subsection{$T_{2}$ Prior}
-Use FIRAS data to justify $T_2$ prior.
+Use FIRAS data to justify $T_2$ prior. Could I use the DIRBE 100/240 micron
+ratio to get a $1.3^{\circ}$ resolution prior on $T_2$?
 
@@
 
+\begin{figure}
+\begin{center}
+\epsfig{file=f1_1deg.eps, width=3.3in}
+\caption{\label{fig:f1} The results of our low-resolution fit with $f_1$
+allowed to vary, but with a strong prior 
+$P(f_1)=\mathcal{N}(f_1|0.0363, 0.003)$.}
+\end{center}
+\end{figure}
+
 \subsection{Validation with FIRAS}

### 2014-02-04 ms.tex
clarified notation, added source function, other clean up

@@
 high-latitude. In the present formulation, there are only two free parameters 
-to describe an observed SED: the hot dust temperature $T_2$ and the 
-normalization of $M_{\nu}$. In principle, we could allow additional parameters,
- such as $f_1$ and the ratio $q_1/q_2$, to vary. However the number of free 
-parameters in our baseline fit at the full $6.1'$ resolution is limited by the 
-fact that, for each sky location, the observed SED contains only five 
-independent intensity measurements (\verb|i100| along with the four 
-highest-frequency \PLANCK~bands).
+to describe an observed SED: the hot dust temperature $T_2$ determines the SED 
+shape and the normalization of $M_{\nu}$ determines the SED amplitude. In 
+principle, we could allow additional parameters, such as $f_1$ and the ratio 
+$q_1/q_2$, to vary. However the number of free parameters in our baseline fit 
+at the full $6.1'$ resolution is limited by the fact that, for each sky 
+location, the observed SED contains only five independent intensity 
+measurements (\verb|i100| along with the four highest-frequency \PLANCK~bands).
 
+To calculate the optical depth in the context of this model, we assume
+optically thin conditions, meaning that $\tau_{\nu}$ = $M_{\nu}/S_{\nu}$, where
+$M_{\nu}$ is the appropriately scaled two-component intensity and the source
+function is given by:
+
+\begin{equation}
+\label{eqn:source}
+S_{\nu} = \frac{f_1q_1(\nu/\nu_0)^{\beta_1}B_{\nu}(T_1) + f_2q_2(\nu/\nu_0)^{\beta_2}B_{\nu}(T_2)}{f_1q_1(\nu/\nu_0)^{\beta_1}+f_2q_2(\nu/\nu_0)^{\beta_2}}
+\end{equation}
 %basically just finish clarifying here that we want to start simple by fitting
 %only two parameters for each pixel since we only have 5 intensity
-% measurements per pixel in our baseline fits at 6.1 arcmin resoluiton
+% measurements per pixel in our baseline fits at 6.1 arcmin resolution
 
@@
 composite 100$\mu$m maps under consideration.
+
+\subsection{Fitting Parameters}
+In order to fit the \PLANCK/\IRAS~dust SED, we must combine the underlying 
+two-component spectrum $M_{\nu}$ with the bandpass corrections $b_{\nu_i}$ to 
+yield predictions which can be compared against the observed broadband 
+intensities. The model-predicted broadband intensities $\tilde{I}_{\nu_i}$ are 
+given by:
+
+\begin{equation}
+\label{eqn:inten}
+\tilde{I}_{\nu_i} = \frac{b_{\nu_i}(T_2)M_{\nu_i}}{b_{545}(T_2)M_{545}}\tilde{I}_{545}
+\end{equation}
+
+We will treat the SED normalization $\tilde{I}_{545}$ as a free parameter in
+our fitting procedure. In our baseline fits, second free parameter is $T_2$, 
+which determines the shape of the SED through $M_{\nu}$ as well as 
+$b_{\nu_i}(T_2)$.
+
 % (here SFD \verb|i100|) and that of \cite{planckdust}).
@@
 per-pixel dust emission SED are the hot dust temperature $T_2$, which 
-determinesthe shape of the SED, and the spectrum normalization. In practice,
+determines the shape of the SED, and the spectrum normalization. In practice,
 the normalization is controlled via $\tilde{I}_{545}$, the amplitude of the 
@@
 \begin{equation}
+\label{eqn:post}
 P(\tilde{I}_{545}, T_2|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2)P(T_2)
@@
 
-The likelihood function is given by:
+Here \{$I$\} denotes the set of observed broadband intensities, $I_{217}$, 
+$I_{353}$, etc. The likelihood function is given by:
+
 \begin{equation}
-\mathcal{L}(\{I\}|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(M_{\nu_{i}}(\tilde{I}_{545}, T_2)|I_{\nu_{i}}, \sigma_{\nu_i})
+\mathcal{L}(\{I\}|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(\tilde{I}_{\nu_{i}}|I_{\nu_{i}}, \sigma_{\nu_i})
 \end{equation}
@@
 
-Where the product runs over $\nu_i$ in $\{217,\ 353,\ 545,\ 857,\ 3000\}$ GHz. 
-For each pixel, the errors on each intensity measurement $\sigma_{\nu_i}$ are 
-given by:
+Where the product runs over $\nu_i$ in $\{217,\ 353,\ 545,\ 857,\ 3000\}$ GHz
+and $\tilde{I}_{\nu_i}$ is a function of $\tilde{I}_{545}$ and $T_2$ as 
+specified by Equation \ref{eqn:inten}. For each pixel, the errors on each 
+intensity measurement $\sigma_{\nu_i}$ are given by:
 
@@
 subtracted at the relevant pixel. $\delta0_{\nu_i}$ represents the uncertainty
-in the offset used to tie \PLANCK~intensity to HI. We have adopted the 
- $\delta0_{\nu_i}$ values of \cite{planckdust} Table 1. $n_{\nu_i}$ represents 
-the instrumental noise in the pixel of interest, and is taken to be the square 
-root of the \verb|ii_cov| parameter that accompanies each \PLANCK~intensity 
-map. In order to obtain reasonable fitting results at high latitude where the 
-data is noisy, we include a prior on $T_2$:
+in the offset used to tie \PLANCK~intensity to H\,\textsc{i}. We have adopted 
+the  $\delta0_{\nu_i}$ values of \cite{planckdust} Table 1. $n_{\nu_i}$ 
+represents the instrumental noise in the pixel of interest, and is taken to be 
+the square root of the \verb|ii_cov| parameter that accompanies each 
+\PLANCK~intensity map. In order to obtain reasonable fitting results at high 
+latitude where the data is noisy, we include a prior on $T_2$:
 
@@
 With $\bar{T}_2$ = 16.2 K and $\sigma_{\bar{T}_2}$ = 1.4 K. In practice we 
-always perform computations using the logarithm of relevant probabilities.
+always perform computations using logarithms of the relevant probabilities.
 %mention something about the proposal distribution at some point?
@@
  $10.5^{\circ}\times8.3^{\circ}$  region centered about 
-$(l,b) = (111.6^{\circ}, 20.3^{\circ})$. Note the 
-differing colorscales. Both models incorporating \PLANCK~data clearly show a 
-major improvement in angular resolution relative to SFD.}
+$(l,b) = (111.6^{\circ}, 20.3^{\circ})$. Note the differing colorscales. Both 
+models incorporating \PLANCK~data clearly show a major improvement in angular 
+resolution relative to SFD.}
 \end{center}
@@
 
-For each pixel, we initialize the Markov chain to have $T_2$ = $\bar{T}_2$ and
-. We run 500 steps of burn-in and then 2000 steps during which we keep track
-of the proposed $T_{2, j}$ and $I_{545, j}$ values. We use these 2000 values 
-for each parameter to compute estimates of each parameter,  $T_2$ = 
-$\langle T_{2, j} \rangle$, $I_{545}$ = $\langle I_{545, j} \rangle$, and of 
-each parameter's variance, $\sigma^2_{T_2}$ = $\langle T^2_{2, j} \rangle-\langle T_{2, j} \rangle ^2$ and $\sigma^2_{I_{545}}$=$\langle I^2_{545, j} 
-\rangle-\langle I_{545, j} \rangle ^2$
+For each pixel, we initialize the Markov chain with parameters $T_2$ = 
+$\bar{T}_2$ and $\tilde{I}_{545}$ = $I_{545}$. We run 500 steps of burn-in and 
+then 2000 steps during which we keep track of the proposed $T_{2, j}$ and 
+$\tilde{I}_{545, j}$ values at the $j^{th}$ step since the end of burn-in. From
+these 2000 samples, we compute estimates of each parameter, 
+$T_2$ = $\langle T_{2, j} \rangle$, $\tilde{I}_{545}$ = 
+$\langle \tilde{I}_{545, j} \rangle$, and of each parameter's variance, 
+$\sigma^2_{T_2}$ = $\langle T^2_{2, j} \rangle-\langle T_{2, j} \rangle ^2$ and
+ $\sigma^2_{\tilde{I}_{545}}$=$\langle \tilde{I}^2_{545, j} 
+\rangle-\langle \tilde{I}_{545, j} \rangle ^2$. We also compute the
+ corresponding estimate of the monochromatic two-component intensity at 545 
+GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
+$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$  and its variance. 
+$M_{545}$ is of more general utility in making foreground predictions because 
+it provides the normalization for the two-component spectrum $M_{\nu}$, 
+independent of the \PLANCK~545 GHz bandpass. Lastly, we compute the 545 GHz
+optical depth as $\tau_{545}$ = $\langle \tau_{545, j} \rangle$ = 
+$\langle M_{545, j}/S_{545, j} \rangle$ and its variance, with the source 
+function $S_{545}$ calculated according to Equation \ref{eqn:source}.
+
+%in the above need to mention/introduce the use of ``j'' to denothe the j'th
+%step of the MH sampling **after** burn-in has finished
+
+% actually we I think we want to keep track of $\tilde{I}_{545}$/b_{545}
+% which is the monochromatic value, since that is most useful downstream
+% when making foreground predictions that typically won't have anything
+% to do with Planck bandpasses
 
@@
 
-\subsection{Calculating $\tau$}
+%\subsection{Calculating $\tau$}
 

### 2014-03-16 ms.tex
better-justified starting point for Markov chains
more work on abstract and intro

@@
 \usepackage{subfigure}
+\usepackage{mathrsfs}
 
@@
 temperature derived by fitting the \cite{FDS99} two-component dust emission 
-model to \PLANCK~217, 353, 545, and 857 GHz, along with  \IRAS~100$\mu$m data. 
-These maps serve as an important alternative to and point of comparison for 
-other dust emission models, especially the single modified blackbody model in 
-which both the emissivity power law index and dust temperature vary 
-continuously. We also expect the derived optical depth to provide valuable 
-cross-checks for other dust-column related data products, specifically the 
-\cite{SFD} map, which assumed a single modified blackbody with $\nu^2$ 
-emissivity and included a temperature map of inferior $\sim$$1.3^{\circ}$ 
-resolution. We compare our best-fit two-component spectral energy distributions
-to those of the \cite{planckdust} single-component parametrization.
+model to the \PLANCK~217, 353, 545, and 857 GHz maps along with  
+\IRAS~100$\mu$m data. This parametrization of the far infrared thermal dust 
+spectrum as the sum of two modified blackbodies serves as an important 
+alternative to the commonly adopted single modified blackbody dust emission 
+model. Because our two-component model matches the dust spectrum near its 
+peak, accounts for the flattening of the dust spectrum at millimeter 
+wavelengths, and specifies dust temperature at 6.1$'$ FWHM, our model 
+provides accurate, high-resolution thermal dust emission foreground predictions
+ from 100 GHz to 3000 GHz. We also calibrate the derived optical depth to 
+reddening at visible wavelengths, and compare the resulting reddening estimates
+with those based on stellar spectra, as well as those of \cite{SFD} and 
+\cite{planckdust} based on infrared emission.
+
+%We also expect the derived optical depth to provide 
+%valuable cross-checks for other dust-column related 
+%data products, specifically the \cite{SFD} map, which assumed a single 
+%modified blackbody with $\nu^2$ emissivity and included a temperature map of 
+%inferior $\sim$$1.3^{\circ}$ resolution. We compare our best-fit two-component
+% spectral energy distributions to those of the \cite{planckdust} 
+% single-component parametrization.
+
+%specify early on that this is 'Galactic dust', 'dust' is kind of a vague
+% term ... on the other hand the Planck dust paper is pretty lax about this
 %MENTION USE IN MAKING IR FOREGROUND PREDICTIONS
@@
 astronomical observations over a wide range of wavelengths. In the mid-infrared
-and far-infrared, Galactic dust emission is a major contributor
-to the observed sky intensity. At optical and ultraviolet (UV) wavelengths, 
-extinction by foreground dust grains attenuates the signal from extragalactic 
-sources over the entire sky. Understanding the properties of dust in the 
-interstellar medium (ISM) is valuable in its own right, as the ISM is the site 
-of star formation, thereby playing a crucial role in galaxy evolution. Equally,
- or perhaps even more important to the practice of astronomy, however, is 
-accurately accounting for dust as a foreground which reddens optical/UV 
-observations and superimposes Galactic emission on low-frequency observations 
-of the cosmic microwave background (CMB). 
+and far-infrared, Galactic dust emission contributes significantly
+to the total observed sky intensity. At optical and ultraviolet (UV) 
+wavelengths, extinction by foreground dust grains attenuates the signal from 
+extragalactic sources over the entire sky. Observations of interstellar dust 
+emission/absorption can improve our understanding of the composition and 
+physical conditions that prevail in the interstellar medium (ISM), an 
+environment which plays a crucial role in Galactic evolution and star 
+formation. Equally, or perhaps even more important to the practice of 
+astronomy, however, is accurately accounting for dust as a foreground which 
+reddens optical/UV observations of stars/galaxies and superimposes Galactic 
+emission on low-frequency observations of the cosmic microwave background 
+(CMB). 
 %specify ``low frequency more precisely eventually
@@
 
-For each pixel, we initialize the Markov chain with parameters $T_2$ = 
-$\bar{T}_2$ and $\tilde{I}_{545}$ = $I_{545}$. We run 500 steps of burn-in and 
-then 2000 steps during which we keep track of the proposed $T_{2, j}$ and 
+For each pixel, we initialize the Markov chain with parameters 
+$\tilde{I}_{545}$ = $I_{545}$ and $T_2$ consistent with the FDS99 
+DIRBE 100$\mu$m/240$\mu$m ratio map $\mathscr{R}$. We run 500 steps of burn-in 
+and then 2000 steps during which we keep track of the proposed $T_{2, j}$ and 
 $\tilde{I}_{545, j}$ values at the $j^{th}$ step since the end of burn-in. From

### 2014-03-17 ms.tex
more work on sections 2 and 3

@@
 \PLANCK~2013 release \citep{planck2013}. Specifically, we have made use 
-of the 217 GHz, 353 GHz, 545 GHz and 857 GHz intensity maps which have been 
-corrected for zodiacal light 
-\citep[\texttt{R1.10\_nominal\_ZodiCorrected},][]{planckzodi}.
+of all six of the zodiacal light corrected HFI intensity maps
+\citep[\texttt{R1.10\_nominal\_ZodiCorrected},][]{planckzodi}. Our 
+full-resolution (6.1$'$ FWHM) SED fits neglect the two lowest HFI frequencies, 
+100 and 143 GHz, as these have FWHM of 9.66$'$ and 7.27$'$ respectively.
 
@@
 interpolation/smoothing described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. 
-The CMB anisotropies are effectively imperceptible in \PLANCK~857 GHz, but can 
-be perceived at a low level in \PLANCK~545 GHz, and are prominent in 
-\PLANCK~217 GHz and 353 GHz relative to the Galactic emission we wish to 
-characterize, especially at high latitudes. To remove the CMB anisotropies, we 
-have subtracted the Spectral Matching Independent Component Analysis 
-(\verb|SMICA|) model from each of the \PLANCK~maps \citep{smica}, after 
-applying appropriate unit conversions. Removal of the residual Solar dipole at 
-low frequencies is discussed in $\S$\ref{sec:zp}.
+The CMB anisotropies are effectively imperceptible upon visual inspection 
+in \PLANCK~857 GHz, but can be perceived at a low level in \PLANCK~545 GHz, and
+are prominent from 100 to 353 GHz relative to the Galactic emission
+we wish to characterize, especially at high latitudes. To remove the CMB 
+anisotropies, we have subtracted the Spectral Matching Independent Component 
+Analysis \citep[SMICA,][]{smica} model from each of the \PLANCK~maps, 
+after applying appropriate unit conversions for the 545 and 857 GHz maps 
+with native units of MJy/sr. Low-order corrections, particularly removal of the
+residual Solar dipole, are discussed in $\S$\ref{sec:zp}.
 % SMICA is subtracted from ALL Planck maps being used, including 545, 857 GHz
@@
 %start by mentioning that SFD removed compact sources (outside of b +/- 5)
-After subtracting the \verb|SMICA| CMB model, we next proceeded to interpolate 
+After subtracting the SMICA CMB model, we next proceeded to interpolate 
 over compact sources, including both point sources and resolved galaxies. 
@@
 \label{sec:smth}
-We wish to simultaneously fit \verb|i100| along with the four 
-highest-frequency \PLANCK~bands. To properly combine these maps, they must have
- the same point spread function (PSF). \verb|i100|, with its $6.1'$ symmetric 
-Gaussian PSF, is the lowest-resolution map we have included. To match PSFs, we 
-have therefore smoothed each of the \PLANCK~maps under consideration to $6.1'$ 
-resolution by considering each native map to have a symmetric Gaussian beam and
- smoothing by the appropriate symmetric Gaussian such that the resulting map 
-has a FWHM of $6.1'$. The FWHM we assign to the native \PLANCK~maps is taken 
-from \cite{planckbeam}, specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, 
-$4.84'$ for 545 GHz, and $4.63'$ for 857 GHz.
+For our full-resolution model,  wish to simultaneously fit \verb|i100| along 
+with the four highest-frequency \PLANCK~bands. To properly combine these maps, 
+they must have the same point spread function (PSF). \verb|i100|, with its 
+$6.1'$ symmetric Gaussian beam, has the lowest angular resolution of the 
+relevant maps. To match PSFs, we have therefore smoothed each of the 
+\PLANCK~maps under consideration to $6.1'$ resolution by considering each 
+native map to have a symmetric Gaussian beam and smoothing by the appropriate 
+symmetric Gaussian such that the resulting map has a FWHM of $6.1'$. The FWHM 
+we assign to the native \PLANCK~maps is taken from \cite{planckbeam}, 
+specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, $4.84'$ for 545 GHz, and
+$4.63'$ for 857 GHz.
 

### 2014-03-18 ms.tex
rearranging

@@
 \label{sec:smth}
-For our full-resolution model,  wish to simultaneously fit \verb|i100| along 
+For our full-resolution model, we wish to simultaneously fit \verb|i100| along 
 with the four highest-frequency \PLANCK~bands. To properly combine these maps, 
@@
 relevant maps. To match PSFs, we have therefore smoothed each of the 
-\PLANCK~maps under consideration to $6.1'$ resolution by considering each 
-native map to have a symmetric Gaussian beam and smoothing by the appropriate 
-symmetric Gaussian such that the resulting map has a FWHM of $6.1'$. The FWHM 
-we assign to the native \PLANCK~maps is taken from \cite{planckbeam}, 
+\PLANCK~maps under consideration to \verb|i100| resolution by considering each 
+native \PLANCK~map to have a symmetric Gaussian beam and smoothing by the 
+appropriate symmetric Gaussian such that the resulting map has a  $6.1'$ FWHM. 
+The FWHM we assign to the native \PLANCK~maps is taken from \cite{planckbeam}, 
 specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, $4.84'$ for 545 GHz, and
  $4.63'$ for 857 GHz.
+
+\subsection{Molecular Emission}
+Because the FIRAS spectra consist of many narrow frequency bins, FDS99 were
+able to discard the relatively small number of frequency intervals contaminated
+by strong molecular line emission. Unfortunately, while the \PLANCK~data 
+considered in this study are of high angular resolution, their broad bandpasses
+do not offer the same luxury of spectral resolution in dealing with line 
+emission. Thereore, we must subtract estimates of the molecular line 
+contamination from each band in order to best isolate the thermal continuum we 
+wish to characterize. The most prominent molecular line emission in the
+\PLANCK~bands of interest arises from the three lowest CO rotational
+transitions: J=1$\rightarrow$0 at 115 GHz, J=2$\rightarrow$1 at 230 GHz and 
+J=3$\rightarrow$2 at 345 GHz, respectively affecting the \PLANCK~100, 217 and 
+353 GHz bands.
+
+%We investigated the possibility of subtracting out CO emission 
+%based on the template of \cite{planckco}. However, we found that the CO 
+%emission rarely amounted to more than XX\% of the total intensity, and 
+%following the treatment of \cite{planckdust}, $\S$2.1, we do not attempt to 
+%remove CO emission.
+
+%We did not attempt to correct for higher J CO transitions beyond J=3->2
+
+% for CO line list see ~/wise/pro/planck_co_lines.pro
 
@@
 
-\subsection{Unit Conversions}
-
-The \PLANCK~217 GHz and 353 GHz data are provided in units of thermodynamic 
-$\delta T$, while \verb|i100| and the higher frequency \PLANCK~maps are 
-provided in units of MJy/sr. Although the aforementioned preprocessing steps 
-were conducted with each map in its native units, we converted the 217 GHz and 
-353 GHz measurements to MJy/sr according to \cite{planckresponse} prior to 
-performing SED fits.
-
-%i think it's table 6 that I specifically want to cite within the ``spectral
-%response'' paper, but i need to check that those values are consistent
-% with the ones i actually used from the other document ``HFI-unit conversion 
-%and colour correction instructions v1.2''
-
-\subsection{Molecular Emission}
-One advantage of the FIRAS data used by FDS99 was its many narrow bins in 
-frequency, which allowed those frequency ranges contaminated by strong 
-molecular line emission to be discarded from the analysis. Unfortunately, with 
-the broad \PLANCK~and \IRAS~bandpasses we do not have such a luxury. This means
- that we cannot truly separate out the thermal continuum of dust emission we 
-wish to study from the molecular line emission. The most prominent molecular 
-line emission in the Planck bands of interest arises from CO lines in the XX, 
-YY bands. We investigated the possibility of subtracting out CO emission based 
-on the template of \cite{planckco}. However, we found that the CO emission
-rarely amounted to more than XX\% of the total intensity, and following
-the treatment of \cite{planckdust}, $\S$2.1, we do not attempt to remove CO
-emission.
-
-% for CO line list see ~/wise/pro/planck_co_lines.pro
-
 \begin{figure}
@@
 \end{figure}
+
+% add error bars to this example SED plot
 
@@
 \end{figure*}
+
+% overplot ellipses showing 1 sigma errors in posterior grayscales
 
@@
 composite 100$\mu$m maps under consideration.
+
+\subsection{Unit Conversions}
+
+The \PLANCK~217 GHz and 353 GHz data are provided in units of thermodynamic 
+$\delta T$, while \verb|i100| and the higher frequency \PLANCK~maps are 
+provided in units of MJy/sr. Although the aforementioned preprocessing steps 
+were conducted with each map in its native units, we converted the 217 GHz and 
+353 GHz measurements to MJy/sr according to \cite{planckresponse} prior to 
+performing SED fits.
+
+%i think it's table 6 that I specifically want to cite within the ``spectral
+%response'' paper, but i need to check that those values are consistent
+% with the ones i actually used from the other document ``HFI-unit conversion 
+%and colour correction instructions v1.2''
 

### 2014-03-19 ms.tex
more detail on CO treatment, needs lots of clean up

@@
 do not offer the same luxury of spectral resolution in dealing with line 
-emission. Thereore, we must subtract estimates of the molecular line 
+emission. Therefore, we must subtract estimates of the molecular line 
 contamination from each band in order to best isolate the thermal continuum we 
@@
 J=3$\rightarrow$2 at 345 GHz, respectively affecting the \PLANCK~100, 217 and 
-353 GHz bands.
+353 GHz bands. J=1$\rightarrow$0 does also impart some signal upon \PLANCK~143 
+GHz, but at a negligible level, $\sim$1000$\times$ fainter relative to the
+dust continuum signal than at 100 GHz
+
+%TODO : actually smooth the CO map to 6.1 arcmin
+To correct for molecular emission, we employed the \PLANCK~Type 3 CO 
+data product, which boasts the highest S/N 
+among the available full-sky CO maps based on \PLANCK~HFI/LFI 
+data \citep{planckco}. The native angular resolution of the Type 3 CO map is 
+5.5$'$. We therefore began by smoothing the raw Type 3 CO map to $6.1'$, to 
+match the PSF of the smoothed \PLANCK~intensity maps we wish to correct 
+for molecular emission (for our full-resolution two-parameter fits, these are 
+217 GHz and 353 GHz).
+
+%take a few sentences to mention how exactly the CO was scaled, i.e. conversion
+% factors from K km/s and line ratio assumptions
+
+We must apply the appropriate unit conversions to the PSF-matched Type 3 CO
+map before we can subtract it from the \PLANCK~intensity maps, which at the
+frequencies of interest have native units of $K_{CMB}$. The Type 3 CO map
+is natively provided in units of K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. 
+To convert this quantity to $K_{CMB}$, we assume that all of the CO emission 
+arises from the $^{12}$CO isotope, and use the $^{12}$CO conversion factors 
+from \cite{planckco} as follows:
+
+\begin{equation}
+I_{CO, \nu_i, N, N-1} = I_{3}F_{12CO, \nu_i, N, N-1} R_{N, N-1}
+\end{equation}
+
+% state what I_3 is 
+Where $I_{CO, \nu_i, N, N-1}$ is the intensity in $K_{CMB}$ due to 
+CO emission in \PLANCK~band $\nu_i$ due to the CO transition from J=$N$ to
+J=$(N$$-$1). The $F_{12CO, \nu_i, N, N-1}$ are taken to be PP, QQ, RR. 
+$R_{N, N-1}$ represents the line ratio of the transition from J=$N$ to 
+J=$(N$$-$1) relative to the J=1$\rightarrow$0. Thus, $R_{1,0}$=1, and we
+further adopt $R_{2,1}$=0.595 and $R_{3,2}$=0.297 based on \cite{planckco}.
+Formally, then, the CO contamination in band $\nu_i$ is given
+by:
+
+\begin{equation}
+I_{CO, \nu_i} = \sum\limits_{N} I_{CO, \nu_i, N, N-1}
+\end{equation}
+
+In fact, for each of the \PLANCK~bands in which molecular emission is 
+non-negligible (100, 217 and 353 GHz), only a single $N$ contributes ($N$=1, 
+$N$=2 and $N$=3, respectively).
+
+Unfortunately, the CO maps at $6.1'$ are rather noisy,
+and the vast majority of the sky has completely neglibible CO emission. Thus,
+in order to avoid adding unnecessary noise outside of molecular cloud complexes
+and at high latitudes, we have zeroed out low-signal regions of the CO Type 3
+map. We identify  low-signal regions as those with $\mathcal{I}_3$$<$1 K km/s, 
+where $\mathcal{I}_3$ is the Type 3 CO map smoothed to 0.25$^{\circ}$ 
+resolution. This cut results in 90\% of the sky being unaffected by the CO 
+correction, particularly the vast majority of high Galactic latitude regions.
+
+%did i ever spell out the acronyms HFI, LFI ????
 

### 2014-03-20 ms.tex
some clean up of new CO subtraction paragraphs/equations

--- 2014-03-18 ms.tex
@@
 do not offer the same luxury of spectral resolution in dealing with line 
-emission. Thereore, we must subtract estimates of the molecular line 
-contamination from each band in order to best isolate the thermal continuum we 
-wish to characterize. The most prominent molecular line emission in the
-\PLANCK~bands of interest arises from the three lowest CO rotational
+emission. Therefore, we must subtract estimates of the molecular line 
+contamination from each \PLANCK~band in order to best isolate the thermal 
+continuum we wish to characterize. The most prominent molecular line emission 
+in the \PLANCK~bands of interest arises from the three lowest CO rotational
 transitions: J=1$\rightarrow$0 at 115 GHz, J=2$\rightarrow$1 at 230 GHz and 
 J=3$\rightarrow$2 at 345 GHz, respectively affecting the \PLANCK~100, 217 and 
-353 GHz bands.
+353 GHz bands. The J=1$\rightarrow$0 line also imparts a signal upon 
+\PLANCK~143 GHz, but at a negligible level, $\sim$1000$\times$ fainter relative
+to the dust continuum than J=1$\rightarrow$0 at 100 GHz.
+
+%TODO : actually smooth the CO map to 6.1 arcmin
+To correct for molecular emission, we employed the \PLANCK~Type 3 CO 
+data product, which boasts the highest S/N 
+among the available full-sky CO maps based on \PLANCK~HFI/LFI 
+data \citep{planckco}. The native angular resolution of the Type 3 CO map is 
+5.5$'$. We therefore began by smoothing the raw Type 3 CO map to $6.1'$, to 
+match the PSF of the smoothed \PLANCK~intensity maps we wish to correct 
+for molecular emission (for our full-resolution two-parameter fits, these are 
+217 GHz and 353 GHz).
+
+%take a few sentences to mention how exactly the CO was scaled, i.e. conversion
+% factors from K km/s and line ratio assumptions
+
+We must apply the appropriate unit conversions to the $6.1'$ Type 3 CO
+map before we can subtract it from the \PLANCK~intensity maps, which at the
+frequencies of interest have native units of $K_{CMB}$. The Type 3 CO map
+is provided in units of K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. 
+To convert this quantity to $K_{CMB}$, we assume that all of the CO emission 
+arises from the $^{12}$CO isotope, and derived the \PLANCK-observed CO 
+intensity in units of $K_{CMB}$ as follows:
+
+\begin{equation}
+I_{CO, \nu_i, N, N-1} = I_{3}F_{12CO, \nu_i, N, N-1} R_{N, N-1}
+\end{equation}
+
+% state what I_3 is 
+Where $I_{CO, \nu_i, N, N-1}$ is the intensity in $K_{CMB}$ in \PLANCK~band 
+$\nu_i$ due to the CO transition from J=$N$ to J=$(N$$-$1). $I_3$ represents 
+the Type 3 CO amplitude in  K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. The 
+$F_{12CO, \nu_i, N, N-1}$ are conversion factors between K$_{RJ}$ km/s and 
+$K_{CMB}$ for particular band/transition pairs. The relevant values adopted are
+$F_{12CO, 100, 1, 0}$=1.478$\times$10$^{-5}$, 
+$F_{12CO, 217, 2, 1}$=4.585$\times$$10^{-5}$, and 
+$F_{12CO, 353, 3, 2}$=1.751$\times$$10^{-4}$.
+$R_{N, N-1}$ represents the line ratio of the transition from J=$N$ to 
+J=$(N$$-$1) relative to the J=1$\rightarrow$0. Thus, $R_{1,0}$=1, and we 
+further adopt $R_{2,1}$=0.595 and $R_{3,2}$=0.297 based on \cite{planckco}. 
+These line ratios are assumed to be constant over the entire sky. Formally, 
+then, the CO contamination in band $\nu_i$ is given by:
+
+\begin{equation}
+I_{CO, \nu_i} = \sum\limits_{N} I_{CO, \nu_i, N, N-1}
+\end{equation}
+
+It turns out that, for each of the \PLANCK~bands in which CO emission is
+non-negligible (100, 217 and 353 GHz), only a single $N$ contributes ($N$=1, 
+$N$=2 and $N$=3, respectively).
+
+Unfortunately, the CO maps at $6.1'$ are rather noisy,
+and the vast majority of the sky has completely negligible CO emission. Thus,
+in order to avoid adding unnecessary noise outside of molecular cloud complexes
+and at high latitudes, we have zeroed out low-signal regions of the CO Type 3
+map. We identify  low-signal regions as those with $\mathcal{I}_3$$<$1 K$_{RJ}$
+ km/s, where $\mathcal{I}_3$ is the Type 3 CO map smoothed to 0.25$^{\circ}$ 
+resolution. This cut results in 90\% of the sky being unaffected by the CO 
+correction, particularly the vast majority of the high Galactic latitude sky.
+
+%did i ever spell out the acronyms HFI, LFI ????
 

### 2014-03-20 ms.tex
started describing absolute zero point procedure

@@
 \label{sec:zp}
+
+% for quantitative assessment of the zero-point difference due to
+% flattening of 857 GHz vs. HI, see 
+% ~/Desktop/dust/planck_hi/piecewise.pdf (on my Mac)
+
+% -> at low HI, slope decreases by a factor of 1.88
+%    the resulting difference in 857 GHz zero points is 0.373 MJy/sr
+
 Although we wish to isolate and model thermal emission from Galactic dust, the
@@
 to set the zero level of Galactic dust. Additionally, faint residuals of the 
-Solar dipole remain at low frequencies. At 353 GHz, 545 GHz, 857 GHz, we have 
+Solar dipole remain at low frequencies. We will address these issues by
+separately solving two sub-problems: the relative offsets and low order
+corrections derived by correlating the \PLANCK~bands against one another,
+and second the absolute zero-level offset.
+%this last sentence needs lots of work
+
+\subsubsection{Absolute Zero Level}
+In \cite{planckdust}, the absolute zero level of infrared thermal dust emission
+is set by requiring that \PLANCK~infrared emission tends to zero when 
+H\,\textsc{i} is zero, assuming a linear correlation between these two 
+measurements at low column density. However, this approach is somewhat
+unsatisfying in that there appear to be different slopes of 857 GHz versus
+H\,\textsc{i} for different ranges of H\,\textsc{i}. In particular, 
+\PLANCK~857 GHz appears to ``flatten out'' at very low H\,\textsc{i}. More 
+quantitavely, we have found using the LAB H\,\textsc{i} data \citep{lab} for
+$-72$$<$$v_{LSR}$$<$$+25$ that the best-fit slope for H\,\textsc{i}$<$70 K km/s
+is a factor of $\sim$1.9 lower than the best fit slope for 
+110 K km/s $<$H\,\textsc{i}$<$70 K km/s, and as a result the implied 
+zero-point offsets for \PLANCK~857 GHz differ by $\sim$0.37 MJy/sr.
+
+% CITE KALBERLA LAB PAPER !!!!!
+
+Because of these ambiguities in the relationship between 857 GHz emission
+and H\,\textsc{i}, we decided to instead constrain the 857 GHz zero level
+by comparison to the FDS99 857 GHz prediction. This renders the 857 GHz 
+absolute zero level tied largely to the reliable FIRAS zero point, and to some 
+lesser extent to H\,\textsc{i} through the \verb|i100| zero point. 
+Specifically, we fit a linear model to the \PLANCK~857 GHz values as a function
+of FDS99 predicted 857 GHz. We used a version of the \PLANCK~857 GHz map with 
+zodiacal light and point sources removed and smoothed to 1 degree resolution, 
+which we will refer to as $\mathcal{I}_{857}$. For this analysis, we considered
+$\mathcal{I}_{857}$ to be the independent variable, as it has much higher S/N 
+than the FDS99 prediction, henceforward referred to as $\mathcal{F}_{857}$.
+We then rebin to $N_{side}$=64 and restrict to pixels with 
+$\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to degree 
+resolution has such high S/N, we can safely perform such a cut on 
+$\mathcal{I}_{857}$. Figure XX shows the a scatterplot of $\mathcal{I}_{857}$
+versus $\mathcal{F}_{857}$, with a moving median and linear fit overplotted.
+
+% mention uniform weights in linear fit, but don't think i want an equation
+% for linear fit since it's so simple to begin with
+
+% sentence saying slope is close to unity, and relationship indeed looks linear
+
+% sentence or two explaining split into quadrants, differences in slope
+% and offset probably due to zodiacal light and/or issues with FDS T2 map
+% say how this quadrants exercise (via rms) allows us to define 857 GHz
+% uncertainty
+
+% what HI intensity does the 2.15 MJy/sr 857 GHz correspond to ?
+%  ---> pretty high actually
+
+% mention use of bandpass correction factors when doing Planck vs. prediction
+% regressions
+
+\subsubsection{Relative Zero Level}
+
+At 353 GHz, 545 GHz, 857 GHz, we have 
 adopted the zero-point offsets of \cite{planckdust} Table 1, which were derived

### 2014-03-20 ms.tex
more on absolute zero point

--- 2014-03-20 ms.tex
@@
 to set the zero level of Galactic dust. Additionally, faint residuals of the 
-Solar dipole remain at low frequencies. At 353 GHz, 545 GHz, 857 GHz, we have 
+Solar dipole remain at low frequencies. We will address these issues by
+separately solving two sub-problems: first, fixing the absolute zero level 
+relative to external data, and second fitting per-band relative offsets 
+and low order corrections by correlating the \PLANCK~bands against one another.
+%this last sentence needs lots of work
+
+\subsubsection{Absolute Zero Level}
+In \cite{planckdust}, the absolute zero level of infrared thermal dust emission
+was set by requiring that \PLANCK~infrared emission tends to zero when 
+H\,\textsc{i} is zero, assuming a linear correlation between these two 
+measurements at low column density. However, this approach is somewhat
+unsatisfying in that there appear to be different slopes of \PLANCK~857 GHz 
+versus H\,\textsc{i} for different ranges of H\,\textsc{i} intensity. In 
+particular, \PLANCK~857 GHz appears to ``flatten out'' at very low 
+H\,\textsc{i}. More quantitavely, we have found using the LAB H\,\textsc{i} 
+data \citep{lab} for $-72$$<$$v_{LSR}$$<$$+25$ that the best-fit slope for 
+H\,\textsc{i}$<$70 K km/s is a factor of $\sim$1.9 lower than the best fit 
+slope for 110 K km/s $<$H\,\textsc{i}$<$200 K km/s, and as a result the implied
+zero-point offsets for \PLANCK~857 GHz differ by $\sim$0.37 MJy/sr.
+
+% CITE KALBERLA LAB PAPER !!!!!
+
+Because of these ambiguities in the relationship between 857 GHz and 
+H\,\textsc{i} emission, we decided to instead constrain the 857 GHz zero level
+by comparison to the FDS99 857 GHz prediction. This renders the \PLANCK~857 GHz
+absolute zero level tied largely to the reliable FIRAS zero point, and to some 
+lesser extent to H\,\textsc{i} through the \verb|i100| zero point. 
+Specifically, we fit a linear model to the FDS99 predicted 857 GHz values as a 
+function of \PLANCK~857 GHz. We used a version of the \PLANCK~857 GHz map with 
+zodiacal light and point sources removed and smoothed to 1$^{\circ}$ 
+resolution, which we will refer to as $\mathcal{I}_{857}$. For this analysis, 
+we considered $\mathcal{I}_{857}$ to be the independent variable, as it has 
+much higher S/N than the FDS99 prediction, henceforward referred to as 
+$\mathcal{F}_{857}$. Note that $\mathcal{F}_{857}$ is not a monochromatic 
+prediction, as we have incorporated the finite bandpass correction factors 
+described in $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine
+the dust spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels 
+with $\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to 
+degree resolution has very high S/N, we can safely perform such a cut on 
+$\mathcal{I}_{857}$. Figure XX shows a scatterplot of $\mathcal{I}_{857}$ 
+versus $\mathcal{F}_{857}$, with a moving median and linear fit overplotted.
+The linear fit was performed with uniform weights and iterative outlier
+rejection. It is encouraging that the slope is quite close to unity, and 
+the offset near zero.
+
+The formal statistical errors on these parameters are small. Undoubtedly,
+just as in the case of performing the regression versus  H\,\textsc{i}, 
+systematic issues will dominate the uncertainty in the derived zero point
+offset. Specifically, the likely culprits are imperfect zodiacal light 
+corrections and the FDS99 temperature map. To quantify the level of systematic
+error
+
+% actually evaluate the statistical errors !!!!
+
+% in previous sentence fill in specifics of slope and offset
+
+% sentence saying slope is close to unity, and relationship indeed looks linear
+
+% sentence or two explaining split into quadrants, differences in slope
+% and offset probably due to zodiacal light and/or issues with FDS T2 map
+% say how this quadrants exercise (via rms) allows us to define 857 GHz
+% uncertainty
+
+% what HI intensity does the 2.15 MJy/sr 857 GHz correspond to ?
+%  ---> pretty high actually
+
+% mention use of bandpass correction factors when doing Planck vs. prediction
+% regressions
+
+\subsubsection{Relative Zero Level}
+
+At 353 GHz, 545 GHz, 857 GHz, we have 
 adopted the zero-point offsets of \cite{planckdust} Table 1, which were derived
@@
 \subsection{Finite Bandpass Correction}
+\label{sec:bpcorr}
 The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 

### 2014-03-21 ms.tex
more on absolute zero level

@@
 degree resolution has very high S/N, we can safely perform such a cut on 
-$\mathcal{I}_{857}$. Figure XX shows a scatterplot of $\mathcal{I}_{857}$ 
-versus $\mathcal{F}_{857}$, with a moving median and linear fit overplotted.
-The linear fit was performed with uniform weights and iterative outlier
-rejection. It is encouraging that the slope is quite close to unity, and 
-the offset near zero.
+$\mathcal{I}_{857}$. Figure XX shows a scatterplot of 
+$\mathcal{I}_{857}$ versus $\mathcal{F}_{857}$, with a moving median and linear
+fit overplotted. The linear fit was performed with uniform weights and 
+iterative outlier rejection. The best-fit linear model is given by 
+$\mathcal{F}_{857}$=0.994$\mathcal{I}_{857}$$-$0.018. It is encouraging that 
+the slope is quite close to unity, and the offset near zero.
 
-The formal statistical errors on these parameters are small. Undoubtedly,
-just as in the case of performing the regression versus  H\,\textsc{i}, 
+The formal statistical errors on these parameters are small. Just as in the 
+case of performing the regression versus  H\,\textsc{i}, 
 systematic issues will dominate the uncertainty in the derived zero point
-offset. Specifically, the likely culprits are imperfect zodiacal light 
+offset. The likely culprits in this case are imperfect zodiacal light 
 corrections and the FDS99 temperature map. To quantify the level of systematic
-error
+error, we split the sky into four quadrants, with the dividing boundaries
+being $b$=0$^{\circ}$ and $l$=0$^{\circ}$, $l$=180$^{\circ}$. We again
+restricted to $\mathcal{I}_{857}$$<$2.15 MJy/sr, and repeated the 
+regression in each quadrant. The slopes varied from 0.948 to 0.993, with an
+rms of 0.0188, while the offsets varied from $-$0.056 MJy/sr to $+$0.089 
+MJy/sr, with an rms of 0.0586 MJy/sr.
+
+% Maybe it's not necessary to mention the 545 GHz check ... although
+% i should do the check eventually as to whether choosing 545 GHz
+% for the absolute zero point is consistent with choosing 857 GHz
+% to within the errors that i'm quoting
+
+%We also repeated the full-sky FDS99 prediction versus \PLANCK~regression at 
+%545 GHz. After
+
+%We also repeated the full-sky and quadrant regressions with the FDS99 
+%predictions at 545 GHz (see bottom panel of Figure XX). We find the 
+%slopes vary from XX to YY with an rms scatter of ZZ. The 545 GHz zero points
+%have an rms scatter of SS, which is consistent with the 545 GHz zero 
+%point rms implied by the scatter in 857 GHz zero point.
 
@@
 %  ---> pretty high actually
-
-% mention use of bandpass correction factors when doing Planck vs. prediction
-% regressions
 
@@
 \section{Conclusion}
+
+% should mention that one definitive improvement of this work relative
+% to FDS99 is that there are uncertainty/covariances provided for
+% the derived parameters !!!!
+
 \label{sec:conclusion}

### 2014-03-22 ms.tex
adding figure illustrating FDS-based zero point
starting table with basic map properties, and derived offsets and low-order corrections
more table entries
fix units in column headers

@@
 
+\begin{figure}
+\begin{center}
+\epsfig{file=zp_857.eps, width=3.4in}
+\caption{\label{fig:fdsref} Scatterplot of $\mathcal{F}_{857}$ versus 
+$\mathcal{I}_{857}$, illustrating our absolute zero point determination by
+comparison to the FDS99 prediction for \PLANCK~857 GHz.}
+\end{center}
+\end{figure}
+
 Because of these ambiguities in the relationship between 857 GHz and 
@@
 
+%mention that all of this assumes that residual CMB dipole
+% and other low order-corrections are negligible at 857 GHz
+
 % Maybe it's not necessary to mention the 545 GHz check ... although
@@
 %  ---> pretty high actually
+
+\begin{deluxetable*}{rrrrrr} 
+\tabletypesize{\scriptsize}
+\tablecolumns{6} 
+\tablewidth{0pc} 
+\tablecaption{\label{obs} Planck/IRAS Map Properties \& Pre-processing} 
+\tablehead{
+\colhead{$\nu$ (GHz)} &
+\colhead{Offset ($K_{CMB}$)} & 
+\colhead{Dipole ($K_{CMB}$)} & 
+\colhead{Quadrupole ($K_{CMB}$)} & 
+\colhead{$c_{\nu}$} &
+\colhead{FWHM ($'$)}
+}
+\startdata
+100 & 1.69$\times$10$^{-5}$$\pm$3.61$\times$10$^{-7}$ &  & $-$7.17$\times$10$^{-6}$ &  0.0054 & 9.66 \\
+143 & 3.58$\times$10$^{-5}$$\pm$7.58$\times$10$^{-7}$ &  & - & 0.0054 &  7.27 \\
+217 & 7.79$\times$10$^{-5}$$\pm$2.60$\times$10$^{-6}$ &  & - & 0.0054 &  5.01 \\
+353 & 2.76$\times$10$^{-4}$$\pm$1.95$\times$10$^{-5}$ &  & - & 0.012 & 4.86 \\
+    & Offset (MJy/sr) & Dipole (MJy/sr) & Quadrupole (MJy/sr) & & \\ \cline{2-4} \\ [-2ex]
+545 & 7.28$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ &  - & - & 0.10 & 4.84 \\
+857 & 1.82$\times$10$^{-2}$$\pm$6.02$\times$10$^{-2}$ &  - & - & 0.10 & 4.63 \\
+3000 & 0.0$\pm$4.3$\times$10$^{-2}$ & - & - & 0.10 & 6.1
+\enddata
+\end{deluxetable*}
 

### 2014-03-22 ms.tex
finished table

@@
 \startdata
-100 & 1.69$\times$10$^{-5}$$\pm$3.61$\times$10$^{-7}$ &  & $-$7.17$\times$10$^{-6}$ &  0.0054 & 9.66 \\
-143 & 3.58$\times$10$^{-5}$$\pm$7.58$\times$10$^{-7}$ &  & - & 0.0054 &  7.27 \\
-217 & 7.79$\times$10$^{-5}$$\pm$2.60$\times$10$^{-6}$ &  & - & 0.0054 &  5.01 \\
-353 & 2.76$\times$10$^{-4}$$\pm$1.95$\times$10$^{-5}$ &  & - & 0.012 & 4.86 \\
+100 & 1.69$\times$10$^{-5}$$\pm$3.61$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & $-$7.17$\times$10$^{-6}$ &  0.0054 & 9.66 \\
+143 & 3.58$\times$10$^{-5}$$\pm$7.58$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & - & 0.0054 &  7.27 \\
+217 & 7.79$\times$10$^{-5}$$\pm$2.60$\times$10$^{-6}$ & $-$1.40$\times$10$^{-5}$ & - & 0.0054 &  5.01 \\
+353 & 2.76$\times$10$^{-4}$$\pm$1.95$\times$10$^{-5}$ & $-$3.08$\times$10$^{-5}$ & - & 0.012 & 4.86 \\
     & Offset (MJy/sr) & Dipole (MJy/sr) & Quadrupole (MJy/sr) & & \\ \cline{2-4} \\ [-2ex]
-545 & 7.28$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ &  - & - & 0.10 & 4.84 \\
+545 & 7.28$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ & 1.63$\times$10$^{-2}$  & - & 0.10 & 4.84 \\
 857 & 1.82$\times$10$^{-2}$$\pm$6.02$\times$10$^{-2}$ &  - & - & 0.10 & 4.63 \\

### 2014-03-23 ms.tex
replace 217 GHz vs 857 GHz scatterplot with figure including additional Planck bands

@@
 
+\begin{figure}
+\begin{center}
+\epsfig{file=dipole_all.eps, width=3.4in}
+\caption{\label{fig:dip}  Scatter plots of \PLANCK~143, 217, 353, and 545 GHz 
+versus \PLANCK~857 GHz. Left: before correcting for offset and residual Solar 
+dipole. Right: after correcting or the best-fit offset and dipole amplitude, as
+described in $\S$\ref{sec:zp}. The dashed red line shows the best-fit linear 
+relationship in each case.}
+\end{center}
+\end{figure}
+
 Because of these ambiguities in the relationship between 857 GHz and 
@@
 
-\begin{figure}
-\begin{center}
-\epsfig{file=scatter_857_217.eps, width=3.4in}
-\caption{\label{fig:scatter} Scatter plot of \PLANCK~217 GHz versus \PLANCK~857
-GHz. Left: before correcting for offset and residual Solar dipole. Right: after
-correcting or the best-fit offset and dipole amplitude, as described in 
-$\S$\ref{sec:zp}. The dashed red line shows the best-fit linear relationship
-between 857 GHz and 217 GHz.}
-\end{center}
-\end{figure}
+%\begin{figure}
+%\begin{center}
+%\epsfig{file=scatter_857_217.eps, width=3.4in}
+%\caption{\label{fig:scatter} Scatter plot of \PLANCK~217 GHz versus \PLANCK~857
+%GHz. Left: before correcting for offset and residual Solar dipole. Right: after
+%correcting or the best-fit offset and dipole amplitude, as described in 
+%$\S$\ref{sec:zp}. The dashed red line shows the best-fit linear relationship
+%between 857 GHz and 217 GHz.}
+%\end{center}
+%\end{figure}
 

### 2014-03-27 ms.tex
added three-panel 100 GHz low-order correction summary figure
outline
added 2nd table
clean-up
started re-write of relative zero level subsection

--- 2014-03-22 ms.tex
@@
 \subsubsection{Absolute Zero Level}
+\label{sec:zp_abs}
 In \cite{planckdust}, the absolute zero level of infrared thermal dust emission
@@
 
-% CITE KALBERLA LAB PAPER !!!!!
-
 \begin{figure}
@@
 \end{figure}
+
+\begin{figure}
+\begin{center}
+\epsfig{file=dipole_all.eps, width=3.4in}
+\caption{\label{fig:dip}  Scatter plots of \PLANCK~143, 217, 353, and 545 GHz 
+versus \PLANCK~857 GHz. Left: before correcting for offset and residual Solar 
+dipole. Right: after correcting or the best-fit offset and dipole amplitude, as
+described in $\S$\ref{sec:zp}. The dashed red line shows the best-fit linear 
+relationship in each case.}
+\end{center}
+\end{figure}
+
+\begin{figure*}
+\begin{center}
+\epsfig{file=quad_100.eps, width=6.5in}
+\caption{\label{fig:quad} Summary of low-order corrections at 100 GHz.}
+\end{center}
+\end{figure*}
 
@@
 degree resolution has very high S/N, we can safely perform such a cut on 
-$\mathcal{I}_{857}$. Figure XX shows a scatterplot of 
+$\mathcal{I}_{857}$. Figure \ref{fig:fdsref} shows a scatterplot of 
 $\mathcal{I}_{857}$ versus $\mathcal{F}_{857}$, with a moving median and linear
@@
 The formal statistical errors on these parameters are small. Just as in the 
-case of performing the regression versus  H\,\textsc{i}, 
-systematic issues will dominate the uncertainty in the derived zero point
-offset. The likely culprits in this case are imperfect zodiacal light 
+case of performing the regression versus  H\,\textsc{i}, systematic problems 
+will dominate the uncertainty in the derived zero point offset. The systematics
+likely to dominate our FDS-based zero level are imperfect zodiacal light 
 corrections and the FDS99 temperature map. To quantify the level of systematic 
-error, we split the sky into four quadrants, with the dividing boundaries
-being $b$=0$^{\circ}$ and $l$=0$^{\circ}$, $l$=180$^{\circ}$. We again
-restricted to $\mathcal{I}_{857}$$<$2.15 MJy/sr, and repeated the 
-regression in each quadrant. The slopes varied from 0.948 to 0.993, with an
-rms of 0.0188, while the offsets varied from $-$0.056 MJy/sr to $+$0.089 
-MJy/sr, with an rms of 0.0586 MJy/sr.
+error, we split the sky into four quadrants, with the dividing boundaries being
+ $b$=0$^{\circ}$ and $l$=0$^{\circ}$, $l$=180$^{\circ}$. We again restricted to
+ $\mathcal{I}_{857}$$<$2.15 MJy/sr, and repeated the regression in each 
+quadrant. The slopes varied from 0.948 to 0.993, with an rms of 0.0188, while 
+the offsets varied from $-$0.056 MJy/sr to $+$0.089 MJy/sr, with an rms of 
+0.0586 MJy/sr.
 
@@
 
-% in previous sentence fill in specifics of slope and offset
-
-% sentence saying slope is close to unity, and relationship indeed looks linear
-
-% sentence or two explaining split into quadrants, differences in slope
-% and offset probably due to zodiacal light and/or issues with FDS T2 map
-% say how this quadrants exercise (via rms) allows us to define 857 GHz
-% uncertainty
-
 % what HI intensity does the 2.15 MJy/sr 857 GHz correspond to ?
@@
 \tablewidth{0pc} 
-\tablecaption{\label{obs} Planck/IRAS Map Properties \& Pre-processing} 
+\tablecaption{\label{table:offs} Planck/IRAS Map Properties \& Pre-processing} 
 \tablehead{
@@
 
-At 353 GHz, 545 GHz, 857 GHz, we have 
-adopted the zero-point offsets of \cite{planckdust} Table 1, which were derived
- by correlating \PLANCK~857 GHz versus H\,\textsc{i} at low column density, and
-then by correlating the other \PLANCK~channels against the corrected 857 GHz 
-map. We have not altered the \verb|i100| zero-point in any way. We have also 
-removed the Solar dipole residual according to \cite{planckdust}, by 
-subtracting a dipole pattern oriented toward 
-$(l, b) = (263.99^{\circ}, 48.26^{\circ})$ and scaled according to their 
-Table 1.
+In the course of this study we use not only \PLANCK~857 GHz, but also all of
+the remaining \PLANCK~HFI bands as well as \verb|i100|. To derive the 
+absolute zero level offsets that must be applied to each of the five
+lowest-frequency \PLANCK~bands, we perform a regression versus the 
+\PLANCK~857 GHz map corrected for the absolute zero level offset derived in
+ $\S$\ref{sec:zp_abs}. We assume no offset need be applied
+to \verb|i100|, which has a zero level tied to H\,\textsc{i} by SFD.
+% maybe need to restate the idea that we're deriving zero points by assuming
+% that the band of interest must approach zero linearly as the reference
+% (in this case 857 ghz) approaches zero.
 
-\begin{figure}
-\begin{center}
-\epsfig{file=scatter_857_217.eps, width=3.4in}
-\caption{\label{fig:scatter} Scatter plot of \PLANCK~217 GHz versus \PLANCK~857
-GHz. Left: before correcting for offset and residual Solar dipole. Right: after
-correcting or the best-fit offset and dipole amplitude, as described in 
-$\S$\ref{sec:zp}. The dashed red line shows the best-fit linear relationship
-between 857 GHz and 217 GHz.}
-\end{center}
-\end{figure}
+Inspecting the HFI maps at 100-545 GHz, the need for low-order corrections beyond
+a scalar offset were evident. In particular, we noticed the presence of a residual 
+Solar dipole. To best recover the amplitudes of the low-order corrections, it is
+necessary to have the highest-possible signal in the independent variable of our
+regression. For this reason we have used 857 GHz as a reference for the other HFI 
+bands, as opposed to the FDS99 predictions or H\,\textsc{i}.
 
-The offset and residual dipole parameters for \PLANCK~217 GHz were not 
-available from \cite{planckdust} Table 1. In order to set the zero-point of 
-Galactic emission in the 217 GHz map, we simultaneously fit the constant 
-offset and residual dipole amplitude. Restricting to regions of low column 
-density (H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for $-72$$<$$v_{LSR}$$<$$+25$ 
-km\,s$^{-1}$), we modeled the 217 GHz map as:
+Importantly, we have performed one regression per HFI band to simultaneously fit for the 
+zero level offset, the slope relative to 857 GHz, and the residual dipole amplitude.
+For each 100-545 GHz HFI band, we restrict tor regions of low column density
+(H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for $-72$$<$$v_{LSR}$$<$$+25$ km\,s$^{-1}$)
+and fit the following model:
+
+%At 353 GHz, 545 GHz, 857 GHz, we have 
+%adopted the zero-point offsets of \cite{planckdust} Table 1, which were derived
+% by correlating \PLANCK~857 GHz versus H\,\textsc{i} at low column density, and
+%then by correlating the other \PLANCK~channels against the corrected 857 GHz 
+%map. We have not altered the \verb|i100| zero-point in any way. We have also 
+%removed the Solar dipole residual according to \cite{planckdust}, by 
+%subtracting a dipole pattern oriented toward 
+%$(l, b) = (263.99^{\circ}, 48.26^{\circ})$ and scaled according to their 
+%Table \ref{table:offs}.
+
+%The offset and residual dipole parameters for \PLANCK~217 GHz were not 
+%available from \cite{planckdust} Table 1. In order to set the zero-point of 
+%Galactic emission in the 217 GHz map, we simultaneously fit the constant 
+%offset and residual dipole amplitude. Restricting to regions of low column 
+%density (H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for $-72$$<$$v_{LSR}$$<$$+25$ 
+%km\,s$^{-1}$), we modeled the 217 GHz map as:
 
 \begin{equation}
-\mathcal{I}_{217, i} = a\mathcal{I}_{857, i} + b\mathcal{D}_{i} + c
+\mathcal{I}_{\nu_i, p} = a\mathcal{I}_{857, p} + b\mathcal{D}_{p} + c
 \end{equation}
 
-With $i$ denoting a single nside=64 HEALPix pixel in the maps 
+With $p$ denoting a single nside=64 HEALPix pixel in the maps 
 $\mathcal{I}_{857}$, $\mathcal{I}_{217}$, and $\mathcal{D}$. Here 
@@
 $b\mathcal{D}$ from the 217 GHz map.
+
+%in above paragraph, clarify what dipole means i.e. in what direction
+% on sky it's oriented
+
+%mention the special case of 100 GHz w/ quadrupole term ... do i need
+% another equation ?
+
+% mention how offset/dipole values compare to those derived in the Planck
+% team paper ?
 
@@
 % measurements per pixel in our baseline fits at 6.1 arcmin resolution
+
+\section{Global Model Parameters}
+
+%%%%
+
+\begin{deluxetable}{rrrrr} 
+\tabletypesize{\scriptsize}
+\tablecolumns{5} 
+\tablewidth{0pc} 
+\tablecaption{\label{obs} Global Model Parameters} 
+\tablehead{
+\colhead{Data} &
+\colhead{$f_1$} &
+\colhead{$q_1/q_2$} & 
+\colhead{$\beta_1$} & 
+\colhead{$\beta_2$}
+}
+\startdata
+FIRAS+\IRAS & 0.0363 & 13.0 & 1.67 & 2.70 \\
+\PLANCK+\IRAS & 0.0267 & 3.68 & 1.19 & 2.61
+\enddata
+\end{deluxetable}
+
+%%%%
+
+\subsection{Correlation Slopes}
+
+% multi-panel figure showing more scatterplots of Planck vs. FDS predictions
+
+\subsection{Hierarchical Approach?}
 
@@
 
-\subsection{Validation with FIRAS}
+%\subsection{Validation with FIRAS}
 

### 2014-03-29 ms.tex
more work on low-order corrections section

@@
 In the course of this study we use not only \PLANCK~857 GHz, but also all of
-the remaining \PLANCK~HFI bands as well as \verb|i100|. To derive the 
+the remaining \PLANCK~HFI bands, as well as \verb|i100|. To derive the 
 absolute zero level offsets that must be applied to each of the five
@@
 
-Inspecting the HFI maps at 100-545 GHz, the need for low-order corrections beyond
-a scalar offset were evident. In particular, we noticed the presence of a residual 
-Solar dipole. To best recover the amplitudes of the low-order corrections, it is
-necessary to have the highest-possible signal in the independent variable of our
-regression. For this reason we have used 857 GHz as a reference for the other HFI 
-bands, as opposed to the FDS99 predictions or H\,\textsc{i}.
+The need for additional low-order corrections beyond a simple scalar offset 
+became evident upon inspecting the HFI maps at 100-545 GHz. In particular, we 
+noticed the presence of a residual dipole pattern, with an orientation 
+consistent with that of the Solar dipole. To most precisely recover the 
+amplitude of the residual dipole, it is necessary to have the 
+highest-possible S/N in the independent variable of our regression. For 
+this reason we have used 857 GHz as a reference for the 100-545 GHz bands, as 
+opposed to the FDS99 predictions or H\,\textsc{i}.
 
-Importantly, we have performed one regression per HFI band to simultaneously fit for the 
-zero level offset, the slope relative to 857 GHz, and the residual dipole amplitude.
-For each 100-545 GHz HFI band, we restrict tor regions of low column density
-(H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for $-72$$<$$v_{LSR}$$<$$+25$ km\,s$^{-1}$)
-and fit the following model:
+We have performed one regression per HFI band to simultaneously 
+fit for the zero level offset, the slope relative to 857 GHz, and the residual 
+dipole amplitude. For each 100-545 GHz HFI band, we restrict tor regions of low
+column density (H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for 
+$-72$$<$$v_{LSR}$$<$$+25$ km\,s$^{-1}$) and fit the following model:
 
-%At 353 GHz, 545 GHz, 857 GHz, we have 
-%adopted the zero-point offsets of \cite{planckdust} Table 1, which were derived
-% by correlating \PLANCK~857 GHz versus H\,\textsc{i} at low column density, and
+% At 353 GHz, 545 GHz, 857 GHz, we have 
+% adopted the zero-point offsets of \cite{planckdust} Table 1, which were 
+% derived by correlating \PLANCK~857 GHz versus H\,\textsc{i} at low column 
+% density, and
 %then by correlating the other \PLANCK~channels against the corrected 857 GHz 
@@
 
-\begin{equation}
+\begin{equation} \label{equ:dip}
 \mathcal{I}_{\nu_i, p} = a\mathcal{I}_{857, p} + b\mathcal{D}_{p} + c
@@
 With $p$ denoting a single nside=64 HEALPix pixel in the maps 
-$\mathcal{I}_{857}$, $\mathcal{I}_{217}$, and $\mathcal{D}$. Here 
+$\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
 $\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
-sources, and constant offset removed, smoothed to $1^{\circ}$ resolution. 
-$\mathcal{I}_{217}$ is the corresponding $1^{\circ}$ resolution \PLANCK~217 
-GHz map with zodiacal emission and compact sources removed. $\mathcal{D}$ is a
-scaling of the Solar dipole with unit amplitude. Because $\sim$18,000 pixels
-satisfy the low H\,\textsc{i} cut, we have an overconstrained linear model with
-three parameters: a, b, and c. $a$ represents the slope of \PLANCK~217 GHz 
-versus \PLANCK~857 GHz assuming they are linearly correlated, and is not
-of any importance to our downstream analysis. $b$ represents the scaling of 
-the Solar dipole that makes the 857 GHz vs. 217 GHz correlation tightest, and 
-$c$ represents the constant offset necessary to make the zero level of the 217 
-GHz map consistent with that of the 857 GHz map. Performing a linear least
-squares fit with uniform weights and iterative outlier rejection, we find 
-$a=4.33\times10^{-5}\ K/(MJy/sr)$, $b=-1.40\times10^{-5}\ K$, and 
+sources, and the constant offset of $\S$\ref{sec:zp_abs} removed, smoothed to 
+$1^{\circ}$ resolution. $\mathcal{I}_{\nu_i}$ is the corresponding $1^{\circ}$ 
+resolution \PLANCK~HFI map with zodiacal emission and compact sources removed. 
+In the context of Equation \ref{equ:dip}, $\nu_i \in$  
+\{100, 143, 217, 353, 545\} GHz. $\mathcal{D}$ is a scaling of the Solar dipole
+pattern oriented toward $(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit 
+amplitude. Because $\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we 
+have an overconstrained linear model with three parameters: a, b, and c. $a$ 
+represents the slope of \PLANCK~band $\nu_i$ GHz versus \PLANCK~857 GHz 
+assuming they are linearly correlated. $b$ represents the scaling of the Solar 
+dipole that makes the 857 GHz vs. \PLANCK~band $\nu_i$ correlation most tightly
+linear, and $c$ represents the constant offset necessary to make the zero level
+ of the band $\nu_i$ map consistent with that of the 857 GHz map. Performing a 
+linear least squares fit with uniform weights and iterative outlier rejection, 
+we find $a=4.33\times10^{-5}\ K/(MJy/sr)$, $b=-1.40\times10^{-5}\ K$, and 
 $c=8.12\times10^{-5}\ K$. Note that $b$ represents 0.42\% of the Solar dipole 

### 2014-03-29 ms.tex
more on dipole fits

@@
 
+% should really change labels to have **script** I to be consistent with the
+% notation used in the text
+
 \begin{figure*}
@@
 In the context of Equation \ref{equ:dip}, $\nu_i \in$  
-\{100, 143, 217, 353, 545\} GHz. $\mathcal{D}$ is a scaling of the Solar dipole
-pattern oriented toward $(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit 
-amplitude. Because $\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we 
-have an overconstrained linear model with three parameters: a, b, and c. $a$ 
-represents the slope of \PLANCK~band $\nu_i$ GHz versus \PLANCK~857 GHz 
-assuming they are linearly correlated. $b$ represents the scaling of the Solar 
-dipole that makes the 857 GHz vs. \PLANCK~band $\nu_i$ correlation most tightly
-linear, and $c$ represents the constant offset necessary to make the zero level
- of the band $\nu_i$ map consistent with that of the 857 GHz map. Performing a 
-linear least squares fit with uniform weights and iterative outlier rejection, 
-we find $a=4.33\times10^{-5}\ K/(MJy/sr)$, $b=-1.40\times10^{-5}\ K$, and 
-$c=8.12\times10^{-5}\ K$. Note that $b$ represents 0.42\% of the Solar dipole 
-amplitude, which is within the calibration uncertainty of the \PLANCK~217 GHz 
-band. Figure \ref{fig:scatter} shows scatterplots of the 857 GHz versus 217 
-GHz correlation before and after correcting for our best-fit offset and dipole 
-residual. Not only is the improved correlation striking in this scatterplot, 
-but the residual dipole also appears visually well-corrected in the 217 GHz 
-map itself. Before performing thermal dust fits, we therefore subtract $c$ and 
-$b\mathcal{D}$ from the 217 GHz map.
+\{100, 143, 217, 353, 545\} GHz. Note that $\mathcal{I}_{\nu_i}$ is always in
+the native units of the relevant \PLANCK~band. $\mathcal{D}$ is a scaling of 
+the Solar dipole pattern oriented toward 
+$(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit amplitude. Because 
+$\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we have an 
+overconstrained linear model with three parameters: a, b, and c. $a$ represents
+the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz assuming 
+they are linearly related. $b$ represents the scaling of the Solar dipole that 
+makes the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly linear. 
+$c$ represents the constant offset necessary to make the zero level of the 
+band $\nu_i$ map consistent with that of the 857 GHz map. For each band
+$\nu_i$, we obtain estimates of $a$, $b$, and $c$ by performing a linear least 
+squares fit with uniform weights and iterative outlier rejection. Figure 
+\ref{fig:dip} shows scatterplots of the band $\nu_i$ versus 857 GHz correlation
+before and after correcting for the best-fit offset and residual dipole, for
+each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only are the tightened 
+correlations striking in these scatterplots, but the residual dipole 
+subtractions appear very successful in the two-dimensional band $\nu_i$ maps 
+themselves. Before performing thermal dust fits, we therefore subtract the 
+best-fit $c$ and $b\mathcal{D}$ from each band $\nu_i$ map. The best-fit
+offsets and residual dipole amplitudes are listed in Table \ref{table:offs}.
 
-%in above paragraph, clarify what dipole means i.e. in what direction
-% on sky it's oriented
-
-%mention the special case of 100 GHz w/ quadrupole term ... do i need
-% another equation ?
+% mention the special case of 100 GHz w/ quadrupole term !!!!!!
+% do i need another equation ?
 

### 2014-03-31 ms.tex
more on dipole fits

@@
 fit for the zero level offset, the slope relative to 857 GHz, and the residual 
-dipole amplitude. For each 100-545 GHz HFI band, we restrict tor regions of low
+dipole amplitude. For each 100-545 GHz HFI band, we restrict to regions of low
 column density (H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for 
@@
 
-% At 353 GHz, 545 GHz, 857 GHz, we have 
-% adopted the zero-point offsets of \cite{planckdust} Table 1, which were 
-% derived by correlating \PLANCK~857 GHz versus H\,\textsc{i} at low column 
-% density, and
-%then by correlating the other \PLANCK~channels against the corrected 857 GHz 
-%map. We have not altered the \verb|i100| zero-point in any way. We have also 
-%removed the Solar dipole residual according to \cite{planckdust}, by 
-%subtracting a dipole pattern oriented toward 
-%$(l, b) = (263.99^{\circ}, 48.26^{\circ})$ and scaled according to their 
-%Table \ref{table:offs}.
-
-%The offset and residual dipole parameters for \PLANCK~217 GHz were not 
-%available from \cite{planckdust} Table 1. In order to set the zero-point of 
-%Galactic emission in the 217 GHz map, we simultaneously fit the constant 
-%offset and residual dipole amplitude. Restricting to regions of low column 
-%density (H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for $-72$$<$$v_{LSR}$$<$$+25$ 
-%km\,s$^{-1}$), we modeled the 217 GHz map as:
-
 \begin{equation} \label{equ:dip}
-\mathcal{I}_{\nu_i, p} = a\mathcal{I}_{857, p} + b\mathcal{D}_{p} + c
+\mathcal{I}_{\nu_i, p} = m\mathcal{I}_{857, p} + d\mathcal{D}_{p} + b
 \end{equation}
@@
 $\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we have an 
-overconstrained linear model with three parameters: a, b, and c. $a$ represents
-the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz assuming 
-they are linearly related. $b$ represents the scaling of the Solar dipole that 
-makes the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly linear. 
-$c$ represents the constant offset necessary to make the zero level of the 
-band $\nu_i$ map consistent with that of the 857 GHz map. For each band
-$\nu_i$, we obtain estimates of $a$, $b$, and $c$ by performing a linear least 
-squares fit with uniform weights and iterative outlier rejection. Figure 
-\ref{fig:dip} shows scatterplots of the band $\nu_i$ versus 857 GHz correlation
-before and after correcting for the best-fit offset and residual dipole, for
-each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only are the tightened 
-correlations striking in these scatterplots, but the residual dipole 
-subtractions appear very successful in the two-dimensional band $\nu_i$ maps 
-themselves. Before performing thermal dust fits, we therefore subtract the 
-best-fit $c$ and $b\mathcal{D}$ from each band $\nu_i$ map. The best-fit
+overconstrained linear model with three parameters: $m$, $d$, and $b$. $m$ 
+represents the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz 
+assuming they are linearly related. $d$ gives the residual Solar dipole
+amplitude, and its best-fit value represents the scaling of the Solar dipole 
+that makes the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly 
+linear. $b$ represents the constant offset that must be subtracted from the 
+band $\nu_i$ map to make its zero level consistent with that of the 857 GHz 
+map. For each band $\nu_i$, we obtain estimates of $m$, $d$, and $b$ by 
+performing a linear least squares fit with uniform weights and iterative 
+outlier rejection. Figure \ref{fig:dip} shows scatterplots of the band $\nu_i$ 
+versus 857 GHz correlation before and after correcting for the best-fit offset 
+and residual dipole, for each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only 
+are the tightened correlations striking in these scatterplots, but the residual
+dipole subtractions appear very successful in the two-dimensional band $\nu_i$ 
+maps themselves. Before performing thermal dust fits, we therefore subtract the
+best-fit $b$ and $d\mathcal{D}$ from each band $\nu_i$ map. The best-fit
 offsets and residual dipole amplitudes are listed in Table \ref{table:offs}.
+
+For \PLANCK~100 GHz, we found an additional low-order correction to be
+necessary. Therefore, for 100 GHz, we performed a modified version of the 
+Eqation \ref{equ:dip} fit, using the following model:
+
+\begin{equation} \label{equ:quad}
+\mathcal{I}_{100, p} = a\mathcal{I}_{857, p} + b\mathcal{D}_p + c + qQ_p
+\end{equation}
 

### 2014-03-31 ms.tex
100 GHz quadrupole description

@@
 For \PLANCK~100 GHz, we found an additional low-order correction to be
-necessary. Therefore, for 100 GHz, we performed a modified version of the 
-Eqation \ref{equ:dip} fit, using the following model:
+necessary (see Figure \ref{fig:quad}). Therefore, for 100 GHz, we performed a 
+modified version of the Equation \ref{equ:dip} fit, using the following model:
 
 \begin{equation} \label{equ:quad}
-\mathcal{I}_{100, p} = a\mathcal{I}_{857, p} + b\mathcal{D}_p + c + qQ_p
+\mathcal{I}_{100, p} = m\mathcal{I}_{857, p} + d\mathcal{D}_p + b + qQ_p
 \end{equation}
 
-% mention the special case of 100 GHz w/ quadrupole term !!!!!!
-% do i need another equation ?
+We will refer to the additional term $qQ_p$ as the ``quadrupole correction''. 
+The shape of the quadrupole template is given by:
+
+\begin{equation}
+Q_p = cos^2(\theta_p)
+\end{equation}
+
+Where $\theta_p$ is the angle of pixel $p$ relative to the Solar velocity 
+vector. It is not clear physically why such a term should improve the 
+correlation between $\mathcal{I}_{100}$ and $\mathcal{I}_{857}$. However, the 
+scatter plots shown in Figure \ref{fig:quad} make it clear that such a term, 
+with best-fit amplitude $q$=$-7.17$$\times$10$^{-6}$, dramatically improves the
+quality of the linear correlation between the 100 GHz and 857 GHz channels. We 
+tried re-running the fits at 143-545 GHz including the $Q_p$ quadrupole term, 
+but in all cases found the best-fit quadrupole to be negligible, and yield no 
+substantial tightening of the correlation versus 857 GHz.
+
+% worth clarifying that, for quadrupole fit at 100 GHz, we still do the
+% fit with uniform weights and iterative outlier rejection ?
 

### 2014-04-02 ms.tex
added figure showing best-fit f1 in Lambert projection, to highlight north Galactic pole

@@
 
-% should really change labels to have **script** I to be consistent with the
-% notation used in the text
-
 \begin{figure*}
@@
 We adopt the thermal dust emission model of FDS99, which consists of two 
-populations of dust grains emitting as MBBs, but with different temperatures 
-and different emissivity power law indices $\beta$. The shape of this spectrum 
-is given by:
+populations of dust grains emitting as MBBs, each with distinct 
+emission/absorption characteristics. Importantly, the emissivity power 
+law indices $\beta$ of the two species differ. The shape of this spectrum is 
+given by:
 
@@
 
-With $\nu_0$ = 3000 GHz, $f_{1}$ = 0.0363, $\beta_1$ = 1.67, $\beta_2$ = 2.70, 
-and $q_1/q_2$ = 13.0. For the parameters thus far specified, the two dust 
-temperatures are further related by:
+With $f_{1}$ = 0.0363, $\beta_1$ = 1.67, $\beta_2$ = 2.70, and $q_1/q_2$ = 
+13.0. $\nu_0$ is chosen to be 3000 GHz. For the parameters thus far specified, 
+the two dust temperatures are further related by:
 
@@
 \end{equation}
+
+% more important than the details of the above equation is the notion
+% that, for any set of f1, q1/q2, beta1, beta2, the relationship between
+% T1 and T2 is a simple power law
 
@@
 
+\begin{figure}
+\begin{center}
+\epsfig{file=f1_lambert.eps, width=3.3in}
+\caption{\label{fig:f1lambert} The results of our low-resolution fit with $f_1$
+allowed to vary, shown in Lambert projection to highlight the salient features 
+near the north Galactic pole.}
+\end{center}
+\end{figure}
+
 %\subsection{Validation with FIRAS}

### 2014-04-05 ms.tex
added scatter plot of EBV vs. tau
hugely improved presentation of two-component emission model

@@
 
+% maybe a sentence to transition from preprocessing -> modeling
+% e.g. With pre-processing completed, we turned to modeling the 
+% thermal dust emission.
+
+% mention that the two different emissivity power laws allow 
+% the model to simultaneously explain narrow SED peak, and flattening
+% of SED toward the millimeter
 We adopt the thermal dust emission model of FDS99, which consists of two 
 populations of dust grains emitting as MBBs, each with distinct 
-emission/absorption characteristics. Importantly, the emissivity power 
-law indices $\beta$ of the two species differ. The shape of this spectrum is 
-given by:
+emission/absorption characteristics. Importantly, the emissivity power law 
+indices $\beta$ of the two species differ. The shape of this spectrum is given 
+by:
 
@@
 
-With $f_{1}$ = 0.0363, $\beta_1$ = 1.67, $\beta_2$ = 2.70, and $q_1/q_2$ = 
-13.0. $\nu_0$ is chosen to be 3000 GHz. For the parameters thus far specified, 
-the two dust temperatures are further related by:
-
-\begin{equation}
-T_1 = 0.352T_2^{1.18}
-\end{equation}
+% With $f_{1}$ = 0.0363, $\beta_1$ = 1.67, $\beta_2$ = 2.70, and $q_1/q_2$ = 
+% 13.0.
+
+In accordance with the conventions of FDS99, $\nu_0$ is chosen to be 3000 GHz.
+In principle, one could imagine this two MBB model to be specified by seven 
+free parameters for every line of sight: $T_1$, $T_2$, $\beta_1$, $\beta_2$, 
+$f_1$, and $q_1$/$q_2$ and the normalization of $M_{\nu}$. However, as 
+discussed in FDS99, $T_1$=$T_1$($T_2$, $\beta_1$, $\beta_2$, $q_1/q_2$) is 
+fully specified by these other parameters under the assumption that the 
+temperature of each species is determined by maintaining thermal equilibrium 
+with the same interstellar radiation field (ISRF). $T_1$ is always related to 
+$T_2$ via a simple power law, although the prefactor and exponent depend on the
+ parameters $q_1/q_2$, $\beta_1$ and $\beta_2$. $q_1/q_2$ encodes the
+relative emission/absorption cross-sections of the two dust species, while
+$f_1$ dictates the relative amounts of each species present.
+
+These considerations still leave us with six potentially free parameters per 
+line of sight. Unfortunately, fitting this many parameters per spatial pixel is
+not feasible for our full-resolution $6.1$$'$ fits, as these are constrained by
+only five broadband intensity measurements. Hence, as in FDS99, we 
+deem certain parameters to be ``global'', i.e. spatially constant over the 
+entire sky. In our full-resolution five-band fits, we designate $\beta_1$, 
+$\beta_2$, $f_1$ and $q_1/q_2$ to be spatially constant. This same approach 
+was employed by FDS99, and the globally best-fit values obtained by FDS99 for 
+these parameters are listed in the first row of Table \ref{tab:global}. With 
+these global parameters, FDS99 found $T_2$$\approx$$16.2$K, 
+$T_1$$\approx$$9.4$K to be typical at high-latitude. In $\S$\ref{sec:global}, 
+we discuss the best-fit global parameters favored by the \PLANCK~HFI data; 
+these are listed in the second row of Table \ref{tab:global}.
+
+Fixing the four parameters of Table \ref{tab:global}, our full-resolution, 
+five-band fits have two remaining free parameters per line of sight: the hot 
+dust temperature $T_2$ determines the SED shape and the normalization of 
+$M_{\nu}$ determines the SED amplitude. In the lower-resolution fits of 
+$\S$\ref{sec:lores} which include all HFI bands, we will allow $f_1$ to be a 
+third free parameter, still holding $\beta_1$, $\beta_2$, and $q_1/q_2$ fixed.
+
+%explain that we take the ``hot'' dust temperature to be T2 rather than T1
+
+% maybe point to the SED fit summary figure as an example of what
+%
+
+% For the parameters thus far specified, the two dust temperatures are further 
+% related by:
+
+%\begin{equation}
+%T_1 = 0.352T_2^{1.18}
+%\end{equation}
 
@@
 % fit at full resolution that has only two free parameters
-FDS99 found $T_2 \approx 16.2$K, $T_1 \approx 9.4$K to be typical at 
-high-latitude. In the present formulation, there are only two free parameters 
-to describe an observed SED: the hot dust temperature $T_2$ determines the SED 
-shape and the normalization of $M_{\nu}$ determines the SED amplitude. In 
-principle, we could allow additional parameters, such as $f_1$ and the ratio 
-$q_1/q_2$, to vary. However the number of free parameters in our baseline fit 
-at the full $6.1'$ resolution is limited by the fact that, for each sky 
-location, the observed SED contains only five independent intensity 
-measurements (\verb|i100| along with the four highest-frequency \PLANCK~bands).
+
+%FDS99 found $T_2 \approx 16.2$K, $T_1 \approx 9.4$K to be typical at 
+%high-latitude. In the present formulation, there are only two free parameters 
+%to describe an observed SED: the hot dust temperature $T_2$ determines the SED
+%shape and the normalization of $M_{\nu}$ determines the SED amplitude. In 
+%principle, we could allow additional parameters, such as $f_1$ and the ratio 
+%$q_1/q_2$, to vary. However the number of free parameters in our baseline fit 
+%at the full $6.1'$ resolution is limited by the fact that, for each sky 
+%location, the observed SED contains only five independent intensity 
+%measurements (\verb|i100| along with the four highest-frequency 
+%\PLANCK~bands).
 
@@
 \section{Global Model Parameters}
-
+\label{sec:global}
 %%%%
@@
 \tablewidth{0pc} 
-\tablecaption{\label{obs} Global Model Parameters} 
+\tablecaption{\label{tab:global} Global Model Parameters} 
 \tablehead{
@@
 \subsection{Low-resolution Fits}
+\label{sec:lores}
 %mention that the pixelization changes ---> to lower HEALpix nside
@@
 term involving.
+
+\section{Calibrating to Optical Reddening}
+\label{sec:ebv}
+
+%FILL THIS SECTION IN !!!!!
+
+% scatterplot figure showing linear regression of EBV vs. tau
+\begin{figure}
+\begin{center}
+\epsfig{file=calib_ebv.eps, width=3.3in}
+\caption{\label{fig:calib} Linear fit of $E(B-V)_{SSPP}$ as function of
+$\tau_{545}$.}
+\end{center}
+\end{figure}
+
+% need 2d histogram figure that is as closely analogous as possible to
+% Figure 2 of Eddie's draft at : 
+% http://faun.rc.fas.harvard.edu/eschlafly/2dmap/2dmap.pdf
 

### 2014-04-05 ms.tex
starting discussion about revised global parameters

@@
 
-\subsection{Correlation Slopes}
+In light of the \PLANCK~HFI data, it is possible to revisit the best-fit global
+parameters of the two-component emission model. To derive the 
+\{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} that best represent the \PLANCK~HFI
+maps, we employed a correlation slope analysis (see Figure XX). Specifically,
+we correlated the observed \PLANCK~data against the appropriate FDS99 
+prediction for each HFI band from 143-857 GHz. We omitted 100 GHz from 
+consideration due to the sensitivity of the 100 GHz trend to our ad hoc
+low order corrections (see Figure \ref{fig:quad}). All comparisons between
+\PLANCK~and the FDS99 predictions were made after smoothing both to 
+$1^{\circ}$, subtracting the SMICA CMB model, and ignoring SMICA inpainted 
+pixels. For 100-857 GHz, the linearity between the FDS and \PLANCK~is
+excellent.
+
+%also emphasize that FDS99 predictions are broadband, not monochromatic
+% (i think i can borrow a sentence about this from the absolute zero point 
+% section above)
+
+However, the slopes at low frequencies are not precisely unity, as would
+be expected if the global two-component parameters derived from FIRAS by
+FDS99 were also the best-fitting global parameters with respect to the 
+\PLANCK~data set.
+
+% maybe a table listing the correlation slopes and their uncertainties
+% would be useful here
+
+We then derive \{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} as constrained by 
+the correlation slopes and their uncertainties given in Table QQ by 
+taking $T_2$=$16.2$K and running Markov chains to sample the posterior:
+
+Figure ZZ shows a corner plot of the 150,000 samples. Clearly, there are
+strong covariances, but even so several conclusions are clear: (1) a lower 
+value of $q_1/q_2$ is favored by the \PLANCK~data than by the FIRAS data (2) 
+(3). Because
 
@@
 
-\subsection{Hierarchical Approach?}
+% at the end of this section state that we do all of our fits etc. with
+% both models (call one of them model 1, and the other model 2, similar
+% to what FDS99 did
+
+%\subsection{Hierarchical Approach?}
 

### 2014-04-05 ms.tex
give models numerical names in global parameter table
starting update of fitting procedure section

@@
 
-\begin{deluxetable}{rrrrr} 
+\begin{deluxetable}{rrrrrr} 
 \tabletypesize{\scriptsize}
-\tablecolumns{5} 
+\tablecolumns{6} 
 \tablewidth{0pc} 
@@
 \tablehead{
+\colhead{Model} &
 \colhead{Data} &
@@
 \startdata
-FIRAS+\IRAS & 0.0363 & 13.0 & 1.67 & 2.70 \\
-\PLANCK+\IRAS & 0.0267 & 3.68 & 1.19 & 2.61
+ 1 & FIRAS+\IRAS & 0.0363 & 13.0 & 1.67 & 2.70 \\
+ 2 & PLANCK+\IRAS & 0.0267 & 3.68 & 1.19 & 2.61
 \enddata
@@
 
+The following subsections detail our procedure for constraining the 
+two-component dust emission model parameters which are permitted to vary
+spatially. In the case of our full-resolution $6.1'$fits, these parameters
+are the SED normalization and the hot dust temperature $T_2$. The same 
+formalism will apply to our lower-resolution fits in which $f_1$ is also 
+allowed to vary from one line of sight to another.
+
 % sentence here summarizing what the following subsections will describe ?
@@
 \PLANCK~HFI maps were released, and because it adequately samples the $6.1'$ 
-resolution maps under consideration. Our procedure will fit the intensity 
-measurements in each spatial pixel independently of those in neighboring 
-pixels.
+FWHM maps under consideration in our full-resolution fits. Our procedure will 
+fit the intensity measurements in each spatial pixel independently of those in 
+neighboring pixels.
 

### 2014-04-05 ms.tex
rewriting bandpass correction section to reflect switch to per-MBB approach

@@
 \IRAS/\PLANCK~bandpasses, typically hundreds of GHz wide. We have therefore 
-computed dimensionless bandpass correction factors $b_{\nu_i}$ such that 
-$M_{\nu_i}b_{\nu_i}$ is the predicted observation for the \PLANCK~or \IRAS~band
- of interest, in MJy/sr. Here $\nu_i$ represents the $i^{th}$ of the five 
-nominal band center frequencies for which we have broadband measurements, 
-$\nu_i \in$ \{217, 353, 545, 857, 3000\} GHz. The shape of model spectrum 
-$M_{\nu}$ is only dependent upon one parameter: the hot dust temperature $T_2$.
- We have used the \PLANCK~transmission curves provided in the file 
-\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have used 
-the \IRAS~bandpass, following the treatment of \cite{planckdust}. We note that 
-it is not clear which bandpass should properly be ascribed to the \IRAS/DIRBE 
-composite 100$\mu$m maps under consideration.
+computed dimensionless bandpass correction factors:$b_{\nu_i}(T, \alpha)$
+
+\begin{equation}
+b_{\nu_i}(T, \alpha) = 
+\end{equation}
+
+The two-component model prediction in band $\nu_i$ is then constructed
+as a linear combination of color-corrected MBB terms as:
+
+\begin{equation}
+M_{\nu_i}b_{\nu_i}
+\end{equation}
+
+%pre-computing lookup tables of b_{\nu_i} allows us to evaluate the 
+% relevant modified blackbodies at the nominal  band center frequency 
+% and then obtain the broadband measurement by virtue of multiplying by
+% by the relevant b_{\nu_i}
+
+Is the predicted observation for the \PLANCK~or \IRAS~band of interest, in 
+MJy/sr. Here $\nu_i$ represents the $i^{th}$ of the 
+five nominal band center frequencies for which we have broadband measurements, 
+$\nu_i \in$ \{217, 353, 545, 857, 3000\} GHz. We have used the 
+\PLANCK~transmission curves provided in the file \verb|HFI_RIMO_R1.10.fits| 
+\citep{planckresponse}. For 3000 GHz, we have used the DIRBE bandpass.
+
+% We note that it is not clear which bandpass should properly be ascribed to 
+% the \IRAS/DIRBE composite 100$\mu$m maps under consideration.
 

### 2014-04-05 ms.tex
clarify definitions of model 1 and model 2 in the text
fixed weird table issue, more on Planck vs. FIRAS global parameters

@@
  1 & FIRAS+\IRAS & 0.0363 & 13.0 & 1.67 & 2.70 \\
- 2 & PLANCK+\IRAS & 0.0267 & 3.68 & 1.19 & 2.61
+ 2 & \PLANCK+\IRAS & 0.0267 & 3.68 & 1.19 & 2.61 \\ [-2ex]
 \enddata
 \end{deluxetable}
+
+% would be great to have uncertainties on each parameter as well (in the
+% Planck case at least...) !!!!!!!!!!!!!!!
 
@@
 value of $q_1/q_2$ is favored by the \PLANCK~data than by the FIRAS data (2) 
-(3). Because
+the best-fit emissivity power law index of the hot dust component ($\beta_2$) 
+is effectively identical to that found by FDS99 to within uncertainties and (3)
+a somewhat lower $\beta_1$ is favored by \PLANCK~than by FIRAS, meaning the
+\PLANCK-based SED is shallower toward the millimeter. Because $f_1$ is so 
+strongly covariant with $\beta_1$, the difference of $f_1$ between the 
+\PLANCK~and FIRAS best fits is not particularly significant.
+
+% actually quantitatively assess, for a typical temperature (and frequency?)
+% how the new f_1 value basically balances out the change in beta_1 ???
+
+The MCMC fitting procedure described in $\S$\ref{sec:fitting} is performed
+separately for both model 1 (FIRAS+\IRAS) and model 2 (\PLANCK+\IRAS), each
+defined by their respective global parameters listed in Table \ref{tab:global}.
 

### 2014-04-05 ms.tex
still reworking bandpass correction discussion

@@
 
+% does this statement accidentally give the impression that I do separate 
+% MCMC fits, one in which i fit Planck/IRAS **data** and one in which
+% i fit FIRAS/IRAS data ????
+
 % multi-panel figure showing more scatterplots of Planck vs. FDS predictions
-
-% at the end of this section state that we do all of our fits etc. with
-% both models (call one of them model 1, and the other model 2, similar
-% to what FDS99 did
 
@@
 The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
-intensity $M_{\nu}$ in MJy/sr for any single frequency $\nu$. In practice, 
-however, we wish to constrain our model using measurements in the broad 
-\IRAS/\PLANCK~bandpasses, typically hundreds of GHz wide. We have therefore 
-computed dimensionless bandpass correction factors:$b_{\nu_i}(T, \alpha)$
+flux density $M_{\nu}$ in e.g. MJy/sr for any single frequency $\nu$. In 
+practice, however, we wish to constrain our model using measurements in the 
+broad \IRAS/\PLANCK~bandpasses, typically hundreds of GHz wide. We have 
+therefore computed dimensionless bandpass correction factors:
 
 \begin{equation}
-b_{\nu_i}(T, \alpha) = 
-\end{equation}
+b_{\nu_i}(T, \beta) = \frac{\int \mathcal{T}(\nu)\nu^{\beta}B_{\nu}(T) d\nu \bigg[\int \mathcal{T}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
+\end{equation}
+
+% now i need to define what \nu_{i,c} is (it's the nominal central 
+% frequency of band \nu_i) e.g. 857 GHz for Planck 857, etc..
+
+% also need to define what \mathcal{T} is (planck transmission, 
+% dimensionless)
 
 The two-component model prediction in band $\nu_i$ is then constructed
-as a linear combination of color-corrected MBB terms as:
+as a linear combination of color-corrected MBB terms:
 
 \begin{equation}
-M_{\nu_i}b_{\nu_i}
-\end{equation}
+\tilde{I}_{\nu_i} \propto \sum_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k)
+\end{equation}
+
+Note that by convention $f_2$=(1$-$$f_1$)
 
@@
 
-Is the predicted observation for the \PLANCK~or \IRAS~band of interest, in 
-MJy/sr. Here $\nu_i$ represents the $i^{th}$ of the 
-five nominal band center frequencies for which we have broadband measurements, 
-$\nu_i \in$ \{217, 353, 545, 857, 3000\} GHz. We have used the 
-\PLANCK~transmission curves provided in the file \verb|HFI_RIMO_R1.10.fits| 
-\citep{planckresponse}. For 3000 GHz, we have used the DIRBE bandpass.
+Is the predicted observation for the \PLANCK~or \IRAS~band of interest. Here 
+$\nu_i$ represents the $i^{th}$ of the five nominal band center frequencies for
+which we have broadband measurements, $\nu_i \in$ \{217, 353, 545, 857, 3000\} 
+GHz. We have used the \PLANCK~transmission curves provided in the file 
+\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have used 
+the DIRBE bandpass.
 
@@
 
-The \PLANCK~217 GHz and 353 GHz data are provided in units of thermodynamic 
-$\delta T$, while \verb|i100| and the higher frequency \PLANCK~maps are 
-provided in units of MJy/sr. Although the aforementioned preprocessing steps 
-were conducted with each map in its native units, we converted the 217 GHz and 
-353 GHz measurements to MJy/sr according to \cite{planckresponse} prior to 
-performing SED fits.
+The \PLANCK~100-353 GHz data are provided in units of thermodynamic 
+$\delta T$, while \verb|i100| and the higher frequency HFI maps are provided in
+units of MJy/sr. Although the aforementioned preprocessing steps were conducted
+with each map in its native units, we converted the 217 GHz and 353 GHz 
+measurements to MJy/sr according to \cite{planckresponse} prior to performing 
+SED fits.
 

### 2014-04-06 ms.tex
still revising bandpass correction discussion

@@
 practice, however, we wish to constrain our model using measurements in the 
-broad \IRAS/\PLANCK~bandpasses, typically hundreds of GHz wide. We have 
-therefore computed dimensionless bandpass correction factors:
+broad \verb|i100|/\PLANCK~bandpasses, typically hundreds of GHz wide. We have 
+therefore computed dimensionless finite bandpass correction factors to 
+account for the MBB($\beta$, $T$) spectral shape and the transmission as a 
+function of frequency:
 
 \begin{equation}
-b_{\nu_i}(T, \beta) = \frac{\int \mathcal{T}(\nu)\nu^{\beta}B_{\nu}(T) d\nu \bigg[\int \mathcal{T}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
-\end{equation}
+b_{\nu_i}(T, \beta) = \frac{\int \mathcal{T}_{\nu_i}(\nu)\nu^{\beta}B_{\nu}(T) d\nu \bigg[\int \mathcal{T}_{\nu_i}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
+\end{equation}
+
+% integral limits ??? check planck paper to see what they did
 
@@
 
-% also need to define what \mathcal{T} is (planck transmission, 
+% also need to define what \mathcal{T} is (relative transmission, 
 % dimensionless)
 
-The two-component model prediction in band $\nu_i$ is then constructed
-as a linear combination of color-corrected MBB terms:
+Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
+$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 3000\} GHz. 
+$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
+of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
+given by the \PLANCK~transmission curves provided in the file 
+\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have 
+adopted the DIRBE bandpass.
+
+The broadband, two-component model prediction in band $\nu_i$, termed 
+$\tilde{I}_{\nu_i}$,is then constructed as a linear combination of 
+color-corrected MBB terms:
 
@@
 
-Note that by convention $f_2$=(1$-$$f_1$)
-
-%pre-computing lookup tables of b_{\nu_i} allows us to evaluate the 
-% relevant modified blackbodies at the nominal  band center frequency 
-% and then obtain the broadband measurement by virtue of multiplying by
-% by the relevant b_{\nu_i}
-
-Is the predicted observation for the \PLANCK~or \IRAS~band of interest. Here 
-$\nu_i$ represents the $i^{th}$ of the five nominal band center frequencies for
-which we have broadband measurements, $\nu_i \in$ \{217, 353, 545, 857, 3000\} 
-GHz. We have used the \PLANCK~transmission curves provided in the file 
-\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have used 
-the DIRBE bandpass.
+Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. This finite bandpass 
+correction approach allows us to predict the \textit{broadband} measurement 
+$\tilde{I}_{\nu_i}$ by computing monochromatic flux densities at the central 
+frequency $\nu_{i,c}$ and then multiplying by factors $b_{\nu_i}(T, \beta)$ 
+which are interpolated off of a set of precomputed, one-dimensional lookup 
+tables. Here the single dimension is $T_k$, as we avoid the necessity of a 
+two-dimensional interpolation in both $\beta$ and $T$ by computing a small set 
+of one dimensional correction factors for the particular set of $\beta$ values
+of interest ($\beta$$\in$\{1.67, 2.7, 1.19, 2.61\}, see Table \ref{tab:global}.
+
+% maybe a final sentence to emphasize explicitly that this approach
+% is much more computationally feasible than computing integrals
+% on-the-fly every time a putative model is proposed (during sampling)
+
+% maybe mention the motivation for computing b_{\nu_i} on a **per MBB**
+% basis, the fact that this is more versatile, especially when 
+% the ``global parameters'' like f_1 or others are being changed
 

### 2014-04-06 ms.tex
made it all the way through the bandpass correction discussion

@@
 therefore computed dimensionless finite bandpass correction factors to 
-account for the MBB($\beta$, $T$) spectral shape and the transmission as a 
+account for the MBB($T$, $\beta$) spectral shape and the transmission as a 
 function of frequency:
 
-\begin{equation}
+\begin{equation} \label{equ:bpcorr}
 b_{\nu_i}(T, \beta) = \frac{\int \mathcal{T}_{\nu_i}(\nu)\nu^{\beta}B_{\nu}(T) d\nu \bigg[\int \mathcal{T}_{\nu_i}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
@@
 \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have 
-adopted the DIRBE bandpass.
+adopted the DIRBE transmission curve.
 
 The broadband, two-component model prediction in band $\nu_i$, termed 
-$\tilde{I}_{\nu_i}$,is then constructed as a linear combination of 
+$\tilde{I}_{\nu_i}$, is then constructed as a linear combination of 
 color-corrected MBB terms:
@@
 which are interpolated off of a set of precomputed, one-dimensional lookup 
-tables. Here the single dimension is $T_k$, as we avoid the necessity of a 
-two-dimensional interpolation in both $\beta$ and $T$ by computing a small set 
-of one dimensional correction factors for the particular set of $\beta$ values
-of interest ($\beta$$\in$\{1.67, 2.7, 1.19, 2.61\}, see Table \ref{tab:global}.
-
-% maybe a final sentence to emphasize explicitly that this approach
-% is much more computationally feasible than computing integrals
-% on-the-fly every time a putative model is proposed (during sampling)
-
-% maybe mention the motivation for computing b_{\nu_i} on a **per MBB**
-% basis, the fact that this is more versatile, especially when 
-% the ``global parameters'' like f_1 or others are being changed
+tables each listing $b_{\nu_i}(T, \beta)$ as a function of $T$. We avoided the 
+need to interpolate in both $\beta$ and $T$ by computing only a small set of 
+one dimensional correction factors for the particular set of $\beta$ values of 
+interest ($\beta \in$ \{1.67, 2.7, 1.19, 2.61\}, see Table \ref{tab:global}).
+
+This finite bandpass correction approach makes the MCMC sampling described in 
+$\S$\ref{sec:mcmc} much more computationally efficient by circumventing the 
+need to perform the integral in the numerator of Equation \ref{equ:bpcorr} 
+on-the-fly for each proposed dust temperature. We have chosen to compute the 
+bandpass corrections on a per-MBB basis because this approach is very 
+versatile; all possible two-component models are linear combinations of MBBs, 
+so we can apply all of our finite bandpass machinery even when we allow 
+parameters other than temperature (e.g. $f_1$) to vary and thereby change the 
+dust spectrum shape.
 
@@
 \subsection{Markov Chains}
+\label{sec:mcmc}
 As explained in $\S$\ref{sec:modeling}, the two free parameters in our 

### 2014-04-06 ms.tex
typose

@@
 Table 11 of \cite{planckcalib}. $CMB$ represents the CMB intensity 
-subtracted at the relevant pixel. $\delta0_{\nu_i}$ represents the uncertainty
+subtracted at the relevant pixel. $\delta O_{\nu_i}$ represents the uncertainty
 in the offset used to tie \PLANCK~intensity to H\,\textsc{i}. We have adopted 
-the  $\delta0_{\nu_i}$ values of \cite{planckdust} Table 1. $n_{\nu_i}$ 
+the  $\delta O_{\nu_i}$ values of \cite{planckdust} Table 1. $n_{\nu_i}$ 
 represents the instrumental noise in the pixel of interest, and is taken to be 

### 2014-04-06 ms.tex
avoid referring to SFD i100 as IRAS whenever possible

@@
 \startdata
- 1 & FIRAS+\IRAS & 0.0363 & 13.0 & 1.67 & 2.70 \\
- 2 & \PLANCK+\IRAS & 0.0267 & 3.68 & 1.19 & 2.61 \\ [-2ex]
+ 1 & FIRAS+\verb|i100| & 0.0363 & 13.0 & 1.67 & 2.70 \\
+ 2 & \PLANCK+\verb|i100| & 0.0267 & 3.68 & 1.19 & 2.61 \\ [-2ex]
 \enddata
@@
 The MCMC fitting procedure described in $\S$\ref{sec:fitting} is performed
-separately for both model 1 (FIRAS+\IRAS) and model 2 (\PLANCK+\IRAS), each
-defined by their respective global parameters listed in Table \ref{tab:global}.
+separately for both model 1 (FIRAS+\verb|i100|) and model 2 
+(\PLANCK+\verb|i100|), each defined by their respective global parameters 
+listed in Table \ref{tab:global}.
 
@@
 
-The \PLANCK~100-353 GHz data are provided in units of thermodynamic 
-$\delta T$, while \verb|i100| and the higher frequency HFI maps are provided in
-units of MJy/sr. Although the aforementioned preprocessing steps were conducted
-with each map in its native units, we converted the 217 GHz and 353 GHz 
-measurements to MJy/sr according to \cite{planckresponse} prior to performing 
-SED fits.
-
-%i think it's table 6 that I specifically want to cite within the ``spectral
-%response'' paper, but i need to check that those values are consistent
-% with the ones i actually used from the other document ``HFI-unit conversion 
-%and colour correction instructions v1.2''
+The \PLANCK~100-353 GHz data are provided in units of $K_{CMB}$, while 
+\verb|i100| and the higher frequency HFI maps are provided in units of 
+MJy/sr.
 
 \subsection{Fitting Parameters}
-In order to fit the \PLANCK/\IRAS~dust SED, we must combine the underlying 
-two-component spectrum $M_{\nu}$ with the bandpass corrections $b_{\nu_i}$ to 
-yield predictions which can be compared against the observed broadband 
-intensities. The model-predicted broadband intensities $\tilde{I}_{\nu_i}$ are 
-given by:
+In order to fit the \PLANCK/\verb|i100| dust SED, we must combine the 
+underlying two-component spectrum $M_{\nu}$ with the bandpass corrections 
+$b_{\nu_i}$ to yield predictions which can be compared against the observed 
+broadband intensities. The model-predicted broadband intensities 
+$\tilde{I}_{\nu_i}$ are given by:
 

### 2014-04-06 ms.tex
start explaining broadband model predictions

@@
 
-\begin{equation}
+\begin{equation} \label{equ:broadband}
 \tilde{I}_{\nu_i} \propto \sum_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k)
@@
 
-\subsection{Unit Conversions}
+\subsection{Predicting the Observed SED}
+With the formalism established in $\S$\ref{sec:modeling} and 
+$\S$\ref{sec:bpcorr}, we can mathematically state the model we will use during 
+MCMC sampling to predict the observed SED, which we will denote by 
+\{$\tilde{I}_{\nu_i}$\}. The predicted broadband intensities are given by:
+
+\begin{equation}
+\label{eqn:inten}
+\tilde{I}_{\nu_i} = \frac{\sum\limits_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k) u_{\nu_i}^{-1}(T_k, \beta_k)}{\sum\limits_{k=1}^{2} b_{545}(T_k, \beta_k) f_k q_k (545 \textrm{GHz}/\nu_0)^{\beta_k} B_{545}(T_k)}\tilde{I}_{545}
+\end{equation}
+
+This equation is quite similar to Equation \ref{equ:broadband}, but with two 
+important differences. The first is that the normalization of 
+$\tilde{I}_{\nu_i}$ is now specified by $\tilde{I}_{545}$, which represents the
+ broadband intensity measured in \PLANCK~545 GHz. Also, each term in the 
+numerator is multiplied by a conversion factor $u_{\nu_i}^{-1}(T_k, \beta_k)$. 
+This factor is necessary because some of the \PLANCK~maps of interest have 
+units of $K_{CMB}$ (100-353 GHz), while others (545-3000 GHz) have units of 
+MJy/sr. Therefore, we wish to predict the low frequency bands in $K_{CMB}$, and
+the high frequency bands in MJy/sr. For this reason, we evaluate $B_{\nu_i}$ in
+Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 for all 
+$\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
+represents the conversion factor from $K_{CMB}$ to MJy/sr
+
+% equation for u goes here
+
+To reiterate, $u_{\nu_i}(T_k, \beta_k)$ has units of (MJy/sr)/$K_{CMB}$, and
+therefore $I_{\nu_{i}}$ will have different units depending on the band 
+$\nu_i$, though $I_{\nu_{i}}$ always has the same units as the native 
+\PLANCK~HFI band $\nu_i$ map.
+
+The denominator serves to ensure that,
+for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent.
+
+% add a sentence in the middle of the previous paragraph explaining why
+% it doesn't make sense to just multiply the Kcmb maps by some factor
+% and pretend they're in MJy/sr for the sake of making predictions
 
@@
 \verb|i100| and the higher frequency HFI maps are provided in units of 
-MJy/sr.
-
-\subsection{Fitting Parameters}
-In order to fit the \PLANCK/\verb|i100| dust SED, we must combine the 
-underlying two-component spectrum $M_{\nu}$ with the bandpass corrections 
-$b_{\nu_i}$ to yield predictions which can be compared against the observed 
-broadband intensities. The model-predicted broadband intensities 
-$\tilde{I}_{\nu_i}$ are given by:
-
-\begin{equation}
-\label{eqn:inten}
-\tilde{I}_{\nu_i} = \frac{b_{\nu_i}(T_2)M_{\nu_i}}{b_{545}(T_2)M_{545}}\tilde{I}_{545}
-\end{equation}
-
-We will treat the SED normalization $\tilde{I}_{545}$ as a free parameter in
-our fitting procedure. In our baseline fits, second free parameter is $T_2$, 
-which determines the shape of the SED through $M_{\nu}$ as well as 
+MJy/sr. We will treat the SED normalization $\tilde{I}_{545}$ as a free 
+parameter in our fitting procedure. In our baseline fits, second free parameter
+ is $T_2$, which determines the shape of the SED through $M_{\nu}$ as well as 
 $b_{\nu_i}(T_2)$.

### 2014-04-06 ms.tex
fixing up explanation of units

@@
 This equation is quite similar to Equation \ref{equ:broadband}, but with two 
-important differences. The first is that the normalization of 
-$\tilde{I}_{\nu_i}$ is now specified by $\tilde{I}_{545}$, which represents the
- broadband intensity measured in \PLANCK~545 GHz. Also, each term in the 
-numerator is multiplied by a conversion factor $u_{\nu_i}^{-1}(T_k, \beta_k)$. 
-This factor is necessary because some of the \PLANCK~maps of interest have 
-units of $K_{CMB}$ (100-353 GHz), while others (545-3000 GHz) have units of 
-MJy/sr. Therefore, we wish to predict the low frequency bands in $K_{CMB}$, and
-the high frequency bands in MJy/sr. For this reason, we evaluate $B_{\nu_i}$ in
-Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 for all 
-$\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
-represents the conversion factor from $K_{CMB}$ to MJy/sr
+important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
+specified by $\tilde{I}_{545}$, which represents the broadband intensity 
+measured in the \PLANCK~545 GHz band. The denominator serves to ensure that,
+for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. Second, 
+each term in the numerator is multiplied by a conversion factor 
+$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
+\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
+remaining maps (545-3000 GHz) have units of MJy/sr. Complicating matters, the 
+conversion from $K_{CMB}$ to MJy/sr depends on the spectrum under 
+consideration; attempting to apply conversion factors to put all of the 
+observed maps themselves into common units is not a particularly attractive 
+option. Therefore, we adopt the strategy of predicting each band in its native 
+units, whether MJy/sr or $K_{CMB}$. For this reason, we always evaluate 
+$B_{\nu_{i,c}}$ in Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 for
+all $\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
+represents the appropriate conversion factor from $K_{CMB}$ to MJy/sr.
 
@@
 
-The denominator serves to ensure that,
-for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent.
-
 % add a sentence in the middle of the previous paragraph explaining why
@@
 
-The \PLANCK~100-353 GHz data are provided in units of $K_{CMB}$, while 
-\verb|i100| and the higher frequency HFI maps are provided in units of 
-MJy/sr. We will treat the SED normalization $\tilde{I}_{545}$ as a free 
+%The \PLANCK~100-353 GHz data are provided in units of $K_{CMB}$, while 
+%\verb|i100| and the higher frequency HFI maps are provided in units of 
+%MJy/sr.
+
+We will treat the SED normalization $\tilde{I}_{545}$ as a free 
 parameter in our fitting procedure. In our baseline fits, second free parameter

### 2014-04-06 ms.tex
Kcmb to MJy/sr conversion equation

@@
 units, whether MJy/sr or $K_{CMB}$. For this reason, we always evaluate 
-$B_{\nu_{i,c}}$ in Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 for
+$B_{\nu_{i,c}}$ in Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for
 all $\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
-represents the appropriate conversion factor from $K_{CMB}$ to MJy/sr.
+represents the appropriate conversion factor from $K_{CMB}$ to MJy/sr:
 
@@
 
-To reiterate, $u_{\nu_i}(T_k, \beta_k)$ has units of (MJy/sr)/$K_{CMB}$, and
-therefore $I_{\nu_{i}}$ will have different units depending on the band 
-$\nu_i$, though $I_{\nu_{i}}$ always has the same units as the native 
-\PLANCK~HFI band $\nu_i$ map.
+\begin{equation}
+u_{\nu_i}(T, \beta) = u_{\nu_i, IRAS} \times u_{\nu_i, IRAS \ to \ (T, \beta)}
+\end{equation}
+
+Here $u_{\nu_i, IRAS}$ gives the conversion factor from $K_{CMB}$ to MJy/sr
+for band $\nu_i$ under the `\IRAS~convention', which corresponds to
+a spectral index $\alpha$=$-1$ spectrum. The values of $u_{\nu_i, IRAS}$
+are listed in the second column of \cite{planckresponse} Table 6. 
+$u_{\nu_i, IRAS \ to \ (T, \beta)}$ is a color correction factor relative to
+the \IRAS~convention for band $\nu_i$ and a MBB($T$, $\beta$) spectrum.
+To reiterate, for $\nu_i$$\le$353 GHz $u_{\nu_i}(T_k, \beta_k)$ has units 
+of (MJy/sr)/$K_{CMB}$, and therefore $I_{\nu_{i}}$ will have different 
+units depending on the band $\nu_i$, though $I_{\nu_{i}}$ always has 
+the same units as the native band $\nu_i$ map.
 

### 2014-04-07 ms.tex
explain Kcmb to MJy/sr conversion factor

@@
 units, whether MJy/sr or $K_{CMB}$. For this reason, we always evaluate 
-$B_{\nu_{i,c}}$ in Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for
-all $\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
-represents the appropriate conversion factor from $K_{CMB}$ to MJy/sr:
+$B_{\nu_{i,c}}$ in Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 
+(dimensionless) for all $\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, 
+$u_{\nu_i}(T_k, \beta_k)$ represents the appropriate conversion factor from 
+$K_{CMB}$ to MJy/sr:
 
@@
 for band $\nu_i$ under the `\IRAS~convention', which corresponds to
-a spectral index $\alpha$=$-1$ spectrum. The values of $u_{\nu_i, IRAS}$
-are listed in the second column of \cite{planckresponse} Table 6. 
-$u_{\nu_i, IRAS \ to \ (T, \beta)}$ is a color correction factor relative to
-the \IRAS~convention for band $\nu_i$ and a MBB($T$, $\beta$) spectrum.
-To reiterate, for $\nu_i$$\le$353 GHz $u_{\nu_i}(T_k, \beta_k)$ has units 
-of (MJy/sr)/$K_{CMB}$, and therefore $I_{\nu_{i}}$ will have different 
-units depending on the band $\nu_i$, though $I_{\nu_{i}}$ always has 
-the same units as the native band $\nu_i$ map.
+a power law specrum with spectral index $\alpha$=$-1$. The values of 
+$u_{\nu_i, IRAS}$ are listed in the second column of \cite{planckresponse} 
+Table 6. $u_{\nu_i, IRAS \ to \ (T, \beta)}$ is a color correction factor 
+relative to the \IRAS~convention for band $\nu_i$, assuming a MBB($T$, $\beta$)
+spectrum. In practice, we retrieve $u_{\nu_i}(T, \beta)$ in a fashion similar 
+to that used for the $b_{\nu_i}(T, \beta)$ color corrections, using a set of 
+precomputed one-dimensional look-up tables. To reiterate, for $\nu_i$$\le$353 
+GHz $u_{\nu_i}(T_k, \beta_k)$ has units of (MJy/sr)/$K_{CMB}$, and therefore 
+$\tilde{I}_{\nu_{i}}$ will have different units depending on the band $\nu_i$, 
+though $\tilde{I}_{\nu_{i}}$ always has the same units as the native band 
+$\nu_i$ map.
 

### 2014-04-07 ms.tex
section clarifying parameters sampled during MCMC

@@
 relative to the \IRAS~convention for band $\nu_i$, assuming a MBB($T$, $\beta$)
-spectrum. In practice, we retrieve $u_{\nu_i}(T, \beta)$ in a fashion similar 
-to that used for the $b_{\nu_i}(T, \beta)$ color corrections, using a set of 
-precomputed one-dimensional look-up tables. To reiterate, for $\nu_i$$\le$353 
-GHz $u_{\nu_i}(T_k, \beta_k)$ has units of (MJy/sr)/$K_{CMB}$, and therefore 
-$\tilde{I}_{\nu_{i}}$ will have different units depending on the band $\nu_i$, 
-though $\tilde{I}_{\nu_{i}}$ always has the same units as the native band 
-$\nu_i$ map.
-
-% add a sentence in the middle of the previous paragraph explaining why
-% it doesn't make sense to just multiply the Kcmb maps by some factor
-% and pretend they're in MJy/sr for the sake of making predictions
-
-%The \PLANCK~100-353 GHz data are provided in units of $K_{CMB}$, while 
-%\verb|i100| and the higher frequency HFI maps are provided in units of 
-%MJy/sr.
-
-We will treat the SED normalization $\tilde{I}_{545}$ as a free 
-parameter in our fitting procedure. In our baseline fits, second free parameter
- is $T_2$, which determines the shape of the SED through $M_{\nu}$ as well as 
-$b_{\nu_i}(T_2)$.
-
-% (here SFD \verb|i100|) and that of \cite{planckdust}).
+spectrum. In practice, we retrieve $u_{\nu_i}(T, \beta)$ values in a fashion 
+similar to that used for the $b_{\nu_i}(T, \beta)$ color corrections, using a 
+set of precomputed one-dimensional look-up tables. To reiterate, for 
+$\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ has units of (MJy/sr)/$K_{CMB}$,
+and therefore $\tilde{I}_{\nu_{i}}$ will have different units depending on the 
+band $\nu_i$, though $\tilde{I}_{\nu_{i}}$ always has the same units as the 
+native band $\nu_i$ map.
+
+%We will treat the SED normalization $\tilde{I}_{545}$ as a free 
+%parameter in our fitting procedure. In our baseline fits, second free 
+%parameter is $T_2$, which determines the shape of the SED through $M_{\nu}$ as
+% well as $b_{\nu_i}(T_2)$.
 
@@
 
+\subsection{Sampling Parameters}
+As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
+consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
+ fixed, while the dust spectrum normalization and dust temperature vary for
+each line-of-sight. In order to predict the dust SED for a given pixel, we are 
+therefore left with two remaining degrees of freedom, and must choose an 
+appropriate set of two parameters to sample and thereby constrain via MCMC. To 
+determine the SED normalization in each pixel, we draw samples in 
+$\tilde{I}_{545}$, the broadband intensity in the 545 GHz bandpass, as defined 
+in Equation \ref{eqn:inten}. With the four aforementioned global parameters 
+fixed, the dust spectrum shape is determined entirely by the two dust 
+temperatures, which are coupled. To constrain the dust temperatures,
+ we sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we 
+compute the corresponding value of $T_1$, thereby specifying ($\beta$, $T$) for
+both MBB components and thus fully specifying the SED shape.
+
+For the lower resolution fits described in $\S$\ref{sec:lores}, we sample
+in three parameters: $\tilde{I}_{545}$, $T_2$, and $f_1$.
+
+% sentence or two mentioning reduced resolution fits where we sample in
+% three dimensions (f_1, T_2, tilde{I}_{545})
+
 \subsection{Markov Chains}
 \label{sec:mcmc}
+
 As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
@@
 Metropolis-Hastings Markov chain sampling the posterior probability as a 
-function of the two parameters $T_2$ and $\tilde{I}_{545}$. For each pixel, we 
+function of the two parameters $\tilde{I}_{545}$ and $T_2$. For each pixel, we 
 are sampling the posterior given by:

### 2014-04-07 ms.tex
beginning of Markov chain section became redundant following recent changes

@@
 
-As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
-per-pixel dust emission SED are the hot dust temperature $T_2$, which 
-determines the shape of the SED, and the spectrum normalization. In practice,
-the normalization is controlled via $\tilde{I}_{545}$, the amplitude of the 
-model SED in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a 
+In our full-resolution fits, we use a MCMC approach to constrain the 
+parameters $\tilde{I}_{545}$ and $T_2$. For each pixel, we run a 
 Metropolis-Hastings Markov chain sampling the posterior probability as a 
-function of the two parameters $\tilde{I}_{545}$ and $T_2$. For each pixel, we 
-are sampling the posterior given by:
+function of the two parameters $\tilde{I}_{545}$ and $T_2$. More specifically, 
+we are sampling the posterior given by:
 
@@
 \end{equation}
+
+% be careful about notational consistency with e.g. tildes, etc.. in this sect
 

### 2014-04-07 ms.tex
starting optical extinction/reddening discussion

@@
 
-%FILL THIS SECTION IN !!!!!
+While the dust temperature and optical depth maps thus far derived are
+useful for making predictions of thermal dust foreground emission, 
+estimating optical reddening/extinction is another important application of the
+optical depth map. We choose to calibrate to empirically to reddening,
+rather than make additional assumptions about the dust grain size distribution
+and physics that would be necessary to perform an analytic calculation.
+
+To achieve this empirical calibration, we must adopt a set of ``calibrators''
+for which true reddening is known. There are various possibilities
+at our disposal. SFD used XX. \cite{planckdust} used quasars. Here we use
+the SSPP stars with SDSS spectra and photometry studied by \cite{schlafly10}.
+
+Information from the spectral lines of these SSPP stars can be used, along with
+ a library of synthetic stellar spectra, to predict the true optical broadband 
+colors. The `true' reddening then is simply the difference in the observed
+$g-r$ color and the $g-r$ color predicted from the spectral lines. This
+gives us $E(B-V)$ estimates for $\sim$250,000 lines of sight, mostly at
+high Galactic latitude. The calibration of two-component optical depth
+to $E(B-V)$ is then performed as a linear regression of $E(B-V)_{SSPP}$ versus
+$\tau_{545}$. The results of this regression are shown in Figure 
+\ref{fig:calib}. Indeed there appears to be a strong linear relation
+between $E(B-V)_{SSPP}$ and $\tau_{545}$ The conversion factor from 
+$\tau_{545}$ to $E(B-V)$ is $\sim$2400.
 

### 2014-04-08 ms.tex
added figure showing two-dimensional histogram of reddening residuals
starting to fix up reddening discussion

@@
 
-While the dust temperature and optical depth maps thus far derived are
-useful for making predictions of thermal dust foreground emission, 
-estimating optical reddening/extinction is another important application of the
-optical depth map. We choose to calibrate to empirically to reddening,
-rather than make additional assumptions about the dust grain size distribution
-and physics that would be necessary to perform an analytic calculation.
+While the temperature and optical depth maps thus far derived are
+useful for making thermal dust emission foreground predictions, estimating 
+optical reddening/extinction is another important application of the 
+$\tau_{545}$ map. We calibrate to reddening empirically rather than derive
+a relationshp between $\tau_{545}$ and reddening by introducing additional 
+assumptions about the dust grain physics and size distribution.
+
+% scatterplot figure showing linear regression of EBV vs. tau
+\begin{figure}
+\begin{center}
+\epsfig{file=calib_ebv.eps, width=3.3in}
+\caption{\label{fig:calib} Linear fit of $E(B-V)_{SSPP}$ as function of
+$\tau_{545}$.}
+\end{center}
+\end{figure}
 
@@
 
-% scatterplot figure showing linear regression of EBV vs. tau
 \begin{figure}
 \begin{center}
-\epsfig{file=calib_ebv.eps, width=3.3in}
-\caption{\label{fig:calib} Linear fit of $E(B-V)_{SSPP}$ as function of
-$\tau_{545}$.}
+\epsfig{file=ebv_2comp.eps, width=2.5in, angle=90}
+\caption{\label{fig:resid} Residuals for best-fit $E(B-V)_{2comp}$ as a 
+function of SFD $E(B-V)$.}
 \end{center}
@@
 
-% need 2d histogram figure that is as closely analogous as possible to
-% Figure 2 of Eddie's draft at : 
-% http://faun.rc.fas.harvard.edu/eschlafly/2dmap/2dmap.pdf
+% should eventually try re-making 2d scatterplot figure in python..
 

### 2014-04-08 ms.tex
revised more of reddening discussion

@@
 
-To achieve this empirical calibration, we must adopt a set of ``calibrators''
-for which true reddening is known. There are various possibilities
-at our disposal. SFD used XX. \cite{planckdust} used quasars. Here we use
-the SSPP stars with SDSS spectra and photometry studied by \cite{schlafly10}.
+To achieve this empirical calibration, we must adopt a set of calibrator
+objects for which true optical reddening is known. There are various 
+possibilities at our disposal. \cite{planckdust} calibrated their single MBB
+$\tau_{353}$ to $E(B-V)$ using broadband SDSS photometry for a set of 
+$\sim$10$^5$ quasars. The SFD calibration was originally tied to a few
+hundred elliptical galaxies, but was later revised by \cite{schlafly10} using 
+several hundred thousand stars with both spectroscopy and broadband photometry 
+available from SDSS. To calibrate our $\tau_{545}$ to reddening, we make use of
+the same set of stars studied by \cite{schlafly10}.
+
+% do I need to cite a reference the first time that i mention SDSS ?
+
+% maybe note the possibility in the future of calibrating to a 3D dust
+% map type data product rather than directly to a set of individual 
+% stars/galaxies
 

### 2014-04-08 ms.tex
SDSS acronym, reference

@@
 objects for which true optical reddening is known. There are various 
-possibilities at our disposal. \cite{planckdust} calibrated their single MBB
-$\tau_{353}$ to $E(B-V)$ using broadband SDSS photometry for a set of 
-$\sim$10$^5$ quasars. The SFD calibration was originally tied to a few
-hundred elliptical galaxies, but was later revised by \cite{schlafly10} using 
-several hundred thousand stars with both spectroscopy and broadband photometry 
-available from SDSS. To calibrate our $\tau_{545}$ to reddening, we make use of
-the same set of stars studied by \cite{schlafly10}.
+possibilities at our disposal. \cite{planckdust} calibrated their $\tau_{353}$ 
+to $E(B-V)$ using broadband Sloan Digital Sky Survey \citep[SDSS;][]{sdss} 
+photometry for a set of $\sim$10$^5$ quasars. The SFD calibration was 
+originally tied to a few hundred elliptical galaxies, but was later revised by 
+\cite{schlafly10} using several hundred thousand stars with both spectroscopy 
+and broadband photometry available from SDSS. To calibrate our $\tau_{545}$ to 
+reddening, we make use of the same set of stars studied by \cite{schlafly10}.
 

### 2014-04-08 ms.tex
finished first pass at reddening discussion

@@
 
-Information from the spectral lines of these SSPP stars can be used, along with
- a library of synthetic stellar spectra, to predict the true optical broadband 
-colors. The `true' reddening then is simply the difference in the observed
-$g-r$ color and the $g-r$ color predicted from the spectral lines. This
-gives us $E(B-V)$ estimates for $\sim$250,000 lines of sight, mostly at
-high Galactic latitude. The calibration of two-component optical depth
-to $E(B-V)$ is then performed as a linear regression of $E(B-V)_{SSPP}$ versus
-$\tau_{545}$. The results of this regression are shown in Figure 
-\ref{fig:calib}. Indeed there appears to be a strong linear relation
-between $E(B-V)_{SSPP}$ and $\tau_{545}$ The conversion factor from 
-$\tau_{545}$ to $E(B-V)$ is $\sim$2400.
+Along with a library of stellar atmosphere models, the spectral lines of these
+stars can be used to predict their intrinsic optical broadband colors. The 
+`true' reddening is then simply the difference in the observed $g-r$ color and
+the $g-r$ color predicted from the spectral lines. Applying a 
+color transformation then yields `true' $E(B-V)$ values for $\sim$250,000 lines
+of sight, mostly at high Galactic latitude. The calibration of two-component 
+optical depth to $E(B-V)$ is then performed as a linear regression of 
+$E(B-V)_{SSPP}$ versus $\tau_{545}$. $\tau_{545}$ is considered to the 
+independent variable in this regression, as we ultimately wish to predict 
+$E(B-V)$ as a function of optical depth, and $\tau_{545}$ has much higher S/N 
+than the SSPP $E(B-V)$ estimates.
+
+The result of this regression is shown in Figure \ref{fig:calib}. Indeed there 
+appears to be a strong linear correlation between $E(B-V)_{SSPP}$ 
+and $\tau_{545}$. The conversion factor from $\tau_{545}$ to $E(B-V)$ is 
+2.41$\times$10$^{3}$. Reassuringly, the best-fit offset is quite close to 
+zero, $\sim$3 mmag.
+
+Figure \ref{fig:resid} shows a two-dimensional histogram of the residuals of
+the $\tau_{545}$-based $E(B-V)$ predictions relative to the corresponding
+spectrum-based $E(B-V)$ predictions, as a function of SFD $E(B-V)$. Clearly 
+there are some systematic trends in the residuals. Still, for 
+$E(B-V)_{SFD}$$<$0.28 ($\sim$80\% of the sky), the residual median is always 
+within 10 mmag of zero. Over the entire range $E(B-V)_{SFD}$$<$0.7, the 
+residual median is always within 30 mmag of zero.
 

### 2014-04-08 ms.tex
caption for EBV residuals figure

@@
 \epsfig{file=ebv_2comp.eps, width=2.5in, angle=90}
-\caption{\label{fig:resid} Residuals for best-fit $E(B-V)_{2comp}$ as a 
-function of SFD $E(B-V)$.}
+\caption{\label{fig:resid} $E(B-V)_{2comp}$ residuals as a function of
+SFD $E(B-V)$. The grayscale represents the conditional probability within each
+bin in SFD $E(B-V)$. The central black line shows the moving median. The upper
+and lower black lines represent the moving 75th and 25th percentiles 
+respectively.}
 \end{center}

### 2014-04-08 ms.tex
removed some outdated outline items

@@
 
-\section{Systematics}
-
-\subsection{CIBA}
-Perhaps the dominant limitation of our fits is the presence of cosmic
-infrared background anisotropies (CIBA) bleeding through into our maps of 
-Galactic dust temperature and optical depth in high-latitude regions 
-\citep{ciba}.
-\subsubsection{Simulations}
-
-\subsubsection{Optimizing Relative Weights}
-
-%not sure if below subsection is necessary, idea of giving zero weight to 217 
-%GHz may belong in above subsection
-
-%\subsubsection{Omitting 217 GHz}
-%The \cite{planckdust} result used only 353, 545, 857, and 3000 GHz. When we 
-%repeat our analysis ignoring 217 GHz, so that we are using the same
-%set of frequencies, we find that no major changes arise. This actually
-%should be done/investigated though.
-
-\subsection{Zero Point}
-Simulate the effect of getting zero points wrong to quantiy this
-systematic a bit.
-
-\subsection{$T_{2}$ Prior}
-Use FIRAS data to justify $T_2$ prior. Could I use the DIRBE 100/240 micron
-ratio to get a $1.3^{\circ}$ resolution prior on $T_2$?
-
-\subsection{Other Limitations}
-\IRAS~is missing in some parts of sky which will therefore not truly have 6.1' 
-resolution.
-%any other miscellaneous issues?
+%%\section{Systematics}
+%%
+%%\subsection{CIBA}
+%%Perhaps the dominant limitation of our fits is the presence of cosmic
+%%infrared background anisotropies (CIBA) bleeding through into our maps of 
+%%Galactic dust temperature and optical depth in high-latitude regions 
+%%\citep{ciba}.
+%%\subsubsection{Simulations}
+
+%%\subsubsection{Optimizing Relative Weights}
+
+%%\subsection{Zero Point}
+%%Simulate the effect of getting zero points wrong to quantiy this
+%%systematic a bit.
+
+%%\subsection{$T_{2}$ Prior}
+%%Use FIRAS data to justify $T_2$ prior. Could I use the DIRBE 100/240 micron
+%%ratio to get a $1.3^{\circ}$ resolution prior on $T_2$?
+
+%%\subsection{Other Limitations}
+%%\IRAS~is missing in some parts of sky which will therefore not truly have 
+%%6.1' resolution.
+%%any other miscellaneous issues?
 
@@
 
-%\subsection{Calculating $\tau$}
-
-% this subsection should probably be moved to the ``dust emission model'' 
-% section of the paper eventually
+\subsection{Data Release}
+We are releasing $N_{side}$=2048 HEALPix maps in Galactic coordinates 
+summarizing the results of of our two-component dust fits.
 
@@
 %and actually the raw uncertainty on Ghz 545 amplitude is the relevant quantity
-
-\subsection{Data Release}
-We are releasing nside=2048 HEALPix maps in Galactic coordinates summarizing 
-the results of of our two-component dust fits.
 

### 2014-04-08 ms.tex
starting reworking section on three parameter fits

@@
 
-It turns out that, for each of the \PLANCK~bands in which CO emission is
+It happens that, for each of the \PLANCK~bands in which CO emission is
 non-negligible (100, 217 and 353 GHz), only a single $N$ contributes ($N$=1, 
@@
 \subsection{Sampling Parameters}
+\label{sec:samp}
 As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
@@
 
-As mentioned previously, our baseline fits fix several parameters which
-in principle could vary spatially. If we are willing to sacrifice angular
-resolution in order to incorporate lower-frequency \PLANCK~bands and
-enhance signal to noise, we can introduce additional free parameters
-and run the Markov chains in higher dimensions.
+As explained in $\S$\ref{sec:modeling} and $\S$\ref{sec:samp}, our 
+full-resolution fits fix the parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ 
+globally so that only the dust temperatures and SED normalization vary on a 
+per-pixel basis. The reason for fixing so many parameters is that, at $6.1'$
+FWHM, only five SED measurements are available per pixel.
+
+% need some sort of add on to last sentence or another sentence entirely
+% to the effect of ``staying in overconstrained regime''
+
+However, sacrificing angular resolution in order to incorporate 
+the \PLANCK~100, 143 GHz bands can allow us to introduce an additional free 
+parameter and run our Markov chains in three-dimensional parameter space.
 
 We ran the Markov chains in three dimensions by allowing 
-$f_1$ to be a third free parameter. We added to our standard posterior a 
-term involving.
+$f_1$ to be a third free parameter. In these chains, we sampled the posterior
+given by:
+
+\begin{equation}
+\label{eqn:post}
+P(\tilde{I}_{545}, T_2, f_1|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2, f_1)P(T_2)P(f_1)
+\end{equation}
 

### 2014-04-08 ms.tex
more on three parameter fits
more on f_1 prior

@@
 
-\begin{equation}
+\begin{equation} \label{equ:like}
 \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(\tilde{I}_{\nu_{i}}|I_{\nu_{i}}, \sigma_{\nu_i})
@@
 
-\begin{equation}
+\begin{equation} \label{equ:t2prior}
 P(T_2) = \mathcal{N}(T_2|\bar{T}_2, \sigma_{\bar{T}_2})
@@
 
+We still employ the likelihood function of Equation \ref{equ:like}, the only
+difference being that $f_1$ can vary from proposal to proposal within each 
+individual pixel when predicting \{$\tilde{I}_{\nu_i}$\} with Equation 
+\ref{eqn:inten}. The prior $P(T_2)$ from Equation \ref{equ:t2prior} remains 
+unchanged. The prior on $f_1$ is:
+
+\begin{equation} \label{equ:f1prior}
+P(f_1) = \mathcal{N}(f_1|\bar{f}_1, \sigma_{\bar{f}_1})
+\end{equation}
+
+With $\bar{f}_1$=0.0363 and $\sigma_{\bar{f}_1}$=0.003. This is a fairly
+stringent prior, but we must restrict the fit from wandering with too much
+freedom, as we are attempting to constrain three parameters using an SED
+with only seven intensity measurements.
+
+% add comment about high f_1 regions near NGP
+
 \section{Calibrating to Optical Reddening}

### 2014-04-08 ms.tex
move f_1 map figures to more appropriate location

@@
 freedom, as we are attempting to constrain three parameters using an SED
-with only seven intensity measurements.
+with only seven intensity measurements. To boost S/N, we have performed
+the fits using maps smoothed to $1^{\circ}$ resolution.
+
+\begin{figure}
+\begin{center}
+\epsfig{file=f1_1deg.eps, width=3.3in}
+\caption{\label{fig:f1} The results of our low-resolution fit with $f_1$
+allowed to vary.}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\epsfig{file=f1_lambert.eps, width=3.3in}
+\caption{\label{fig:f1lambert} The results of our low-resolution fit with $f_1$
+allowed to vary, shown in Lambert projection to highlight the salient features 
+near the north Galactic pole.}
+\end{center}
+\end{figure}
+
+The resulting full-sky map of $f_1$ is shown in Figure \ref{}. Some of the most
 
 % add comment about high f_1 regions near NGP
+% also add sentences referring reader to the two f_1 figures
 
@@
 
-\begin{figure}
-\begin{center}
-\epsfig{file=f1_1deg.eps, width=3.3in}
-\caption{\label{fig:f1} The results of our low-resolution fit with $f_1$
-allowed to vary, but with a strong prior 
-$P(f_1)=\mathcal{N}(f_1|0.0363, 0.003)$.}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\epsfig{file=f1_lambert.eps, width=3.3in}
-\caption{\label{fig:f1lambert} The results of our low-resolution fit with $f_1$
-allowed to vary, shown in Lambert projection to highlight the salient features 
-near the north Galactic pole.}
-\end{center}
-\end{figure}
-
 %\subsection{Validation with FIRAS}

### 2014-04-08 ms.tex
mention north Galactic pole f_1 features, reference f_1 maps from text

@@
 
-The resulting full-sky map of $f_1$ is shown in Figure \ref{}. Some of the most
+The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. Some of 
+the most striking features occurr near the north Galactic pole, and to 
+highlight these regions of unusually high $f_1$, we display the northern
+Galactic hemisphere in Lambert projection in Figure \ref{fig:f1lambert}.
 

### 2014-04-08 ms.tex
wrong year

@@
 originally tied to a few hundred elliptical galaxies, but was later revised by 
-\cite{schlafly10} using several hundred thousand stars with both spectroscopy 
+\cite{schlafly11} using several hundred thousand stars with both spectroscopy 
 and broadband photometry available from SDSS. To calibrate our $\tau_{545}$ to 
-reddening, we make use of the same set of stars studied by \cite{schlafly10}.
+reddening, we make use of the same set of stars studied by \cite{schlafly11}.
 

### 2014-04-11 ms.tex
no more multiply-defined labels
different figure name for 2d histogram of reddening residuals
clean-up, addressing comments on intro

@@
 model to the \PLANCK~217, 353, 545, and 857 GHz maps along with  
-\IRAS~100$\mu$m data. This parametrization of the far infrared thermal dust 
+\IRAS~100$\mu$m data. This parametrization of the far-infrared thermal dust 
 spectrum as the sum of two modified blackbodies serves as an important 
@@
 \cite{planckdust} based on infrared emission.
+
+% might consider changing the word `specifies' in penultimate sentence
 
@@
 Physically, these two components might represent distinct dust grain species 
-within the ISM, namely amorphous silicates and carbonaceous grains. By 
+within the ISM, or they might simply provide a convenient fitting function. By 
 combining this best-fit two-component model with a custom reprocessing of 
-\IRAS~100$\mu$m, FDS99 provided widely used foreground predictions with 
-$6.1'$ FHWM, limited largely by their $1.3^{\circ}$ resolution DIRBE-based 
-temperature correction.
-
-% ^^final sentence about what FDS99 meant for foreground predictions (and how
-% those predictions actually worked)
-
-%did FDS99 actually use DIRBE (pretty sure they did)
-
-% FDS used 100 GHz to 3000 GHz in their two-component fits
+\IRAS~100$\mu$m, FDS99 provided widely used foreground predictions with $6.1'$ 
+FHWM, limited largely by their $1.3^{\circ}$ resolution DIRBE-based temperature
+correction.
+
+% additional sentence suggested by doug : 
+% The fact that the range of optical
+% properties of small silicate particles measured in the lab (Agladze et
+% al. 1996) spans the range needed by the FDS99 model makes plausible
+% that the distinct species are real.
+
 %mention which grain species is large vs. small
-
-% should mention somewhere (probably in above paragraph, the range of
-% frequencies over which FDS99 model was shown to be applicable
 
@@
 \begin{equation}
-\label{eqn:post}
+\label{eqn:f1post}
 P(\tilde{I}_{545}, T_2, f_1|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2, f_1)P(T_2)P(f_1)
@@
 \begin{center}
-\epsfig{file=ebv_2comp.eps, width=2.5in, angle=90}
+\epsfig{file=ebv_resid.eps, width=2.5in, angle=90}
 \caption{\label{fig:resid} $E(B-V)_{2comp}$ residuals as a function of

### 2014-04-11 ms.tex
cleaning up some wording in molecular emission discussion

@@
 We must apply the appropriate unit conversions to the $6.1'$ Type 3 CO
-map before we can subtract it from the \PLANCK~intensity maps, which at the
-frequencies of interest have native units of $K_{CMB}$. The Type 3 CO map
-is provided in units of K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. 
-To convert this quantity to $K_{CMB}$, we assume that all of the CO emission 
-arises from the $^{12}$CO isotope, and derived the \PLANCK-observed CO 
-intensity in units of $K_{CMB}$ as follows:
+map before subtracting it from the \PLANCK~intensity maps, which have native 
+units of $K_{CMB}$ at the frequencies of interest. The Type 3 CO map is 
+provided in units of K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. To convert 
+this quantity to $K_{CMB}$, we assume that all of the CO emission arises from 
+the $^{12}$CO isotope, and derived the \PLANCK-observed CO intensity in units 
+of $K_{CMB}$ as follows:
 

### 2014-04-11 ms.tex
addressing more comments

@@
 %start by mentioning that SFD removed compact sources (outside of b +/- 5)
-After subtracting the SMICA CMB model, we next proceeded to interpolate 
-over compact sources, including both point sources and resolved galaxies. 
-Removing compact sources at this stage is important as it prevents 
-contamination of compact-source-free pixels in our downstream analyses which 
-require smoothing of the \PLANCK~maps. SFD carefully removed point sources and 
-galaxies from the \verb|i100| map everywhere outside of 
-$|b|$$<$$5^{\circ}$. We do not perform any further modifications of the 
-\verb|i100| map to account for compact sources. To mask compact sources in the 
-\PLANCK~maps, we use the SFD compact source mask, which was originally 
-constructed to mask point sources and resolved compact objects that are not 
-part of the Galactic cirrus at 3000 GHz. Given our pixelization (see 
-$\S$\ref{sec:pix}), 1.56\% of pixels are masked.
+After subtracting the SMICA CMB model, we interpolate over compact sources, 
+including both point sources and resolved galaxies. Removing compact sources at
+this stage is important as it prevents contamination of compact-source-free 
+pixels in our downstream analyses which require smoothing of the \PLANCK~maps. 
+SFD carefully removed point sources and galaxies from the \verb|i100| map 
+everywhere outside of $|b|$$<$$5^{\circ}$. We do not perform any further 
+modifications of the \verb|i100| map to account for compact sources. To mask 
+compact sources in the \PLANCK~maps, we use the SFD compact source mask, which 
+was originally constructed to mask point sources and resolved compact objects 
+that are not part of the Galactic cirrus at 3000 GHz. Given our pixelization 
+(see $\S$\ref{sec:pix}), 1.56\% of pixels are masked.
 
@@
 frequency, there can exist an overall, constant offset that must be subtracted 
-to set the zero level of Galactic dust. Additionally, faint residuals of the 
-Solar dipole remain at low frequencies. We will address these issues by
+to set the zero level of Galactic dust by removing the mean cosmic IR 
+background, as well as any instrumental offset. Additionally, faint residuals 
+of the Solar dipole remain at low frequencies. We will address these issues by 
 separately solving two sub-problems: first, fixing the absolute zero level 
-relative to external data, and second fitting per-band relative offsets 
-and low order corrections by correlating the \PLANCK~bands against one another.
+relative to external data, and second fitting per-band relative offsets and low
+order corrections by correlating the \PLANCK~bands against one another.
 %this last sentence needs lots of work
@@
 zero-point offsets for \PLANCK~857 GHz differ by $\sim$0.37 MJy/sr.
+
+% maybe state approximately what 0.37 MJy/sr at 857 GHz equates to in EBV
+% --> did a quick calculation and it's only ~0.0118 mags ... thought it
+%     would be more ??
 

### 2014-04-11 ms.tex
reference all sections in concluding paragraph of introduction

@@
 isolate thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we 
-describe the dust emission model we fit to the \PLANCK~and \IRAS~data. In 
-$\S$\ref{sec:fitting} we provide details of the Markov chain Monte Carlo (MCMC)
- method with which we have estimated the parameters of our model. In 
+explain the dust emission model we fit to the \PLANCK~and \IRAS~data. In 
+$\S$\ref{sec:global} we describe our constraints on this model's global 
+parameters derived from the \PLANCK~HFI maps. In $\S$\ref{sec:fitting} we 
+detail the Markov chain Monte Carlo (MCMC) method with which we have estimated 
+the spatially varying parameters of our model. In $\S$\ref{sec:ebv} we 
+calibrate our derived optical depth to optical reddening. In 
 $\S$\ref{sec:results} we present the full-sky maps of dust temperature and 
-optical depth thus obtained, and conclude in $\S$\ref{sec:conclusion}.
+optical depth we have obtained, and conclude in $\S$\ref{sec:conclusion}.
 

### 2014-04-24 ms.tex
starting to address comments

@@
 case of performing the regression versus  H\,\textsc{i}, systematic problems 
-will dominate the uncertainty in the derived zero point offset. The systematics
+dominate the uncertainty in the derived zero point offset. The systematics
 likely to dominate our FDS-based zero level are imperfect zodiacal light 

### 2014-04-24 ms.tex
addressed another comment

@@
  km/s, where $\mathcal{I}_3$ is the Type 3 CO map smoothed to 0.25$^{\circ}$ 
-resolution. This cut results in 90\% of the sky being unaffected by the CO 
+FWHM. This cut results in 90\% of the sky being unaffected by the CO 
 correction, particularly the vast majority of the high Galactic latitude sky.
@@
 function of \PLANCK~857 GHz. We used a version of the \PLANCK~857 GHz map with 
-zodiacal light and point sources removed and smoothed to 1$^{\circ}$ 
-resolution, which we will refer to as $\mathcal{I}_{857}$. For this analysis, 
-we considered $\mathcal{I}_{857}$ to be the independent variable, as it has 
-much higher S/N than the FDS99 prediction, henceforward referred to as 
-$\mathcal{F}_{857}$. Note that $\mathcal{F}_{857}$ is not a monochromatic 
-prediction, as we have incorporated the finite bandpass correction factors 
-described in $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine
-the dust spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels 
-with $\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to 
-degree resolution has very high S/N, we can safely perform such a cut on 
+zodiacal light and point sources removed and smoothed to 1$^{\circ}$ FWHM, 
+which we will refer to as $\mathcal{I}_{857}$. For this analysis, we considered
+$\mathcal{I}_{857}$ to be the independent variable, as it has much higher S/N 
+than the FDS99 prediction, henceforward referred to as $\mathcal{F}_{857}$. 
+Note that $\mathcal{F}_{857}$ is not a monochromatic prediction, as we have 
+incorporated the finite bandpass correction factors described in 
+$\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine the dust 
+spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels with 
+$\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to degree 
+resolution has very high S/N, we can safely perform such a cut on 
 $\mathcal{I}_{857}$. Figure \ref{fig:fdsref} shows a scatterplot of 

### 2014-04-24 ms.tex
rephrasing to address comment, notes to self

@@
 by strong molecular line emission. Unfortunately, while the \PLANCK~data 
-considered in this study are of high angular resolution, their broad bandpasses
-do not offer the same luxury of spectral resolution in dealing with line 
-emission. Therefore, we must subtract estimates of the molecular line 
-contamination from each \PLANCK~band in order to best isolate the thermal 
-continuum we wish to characterize. The most prominent molecular line emission 
-in the \PLANCK~bands of interest arises from the three lowest CO rotational
-transitions: J=1$\rightarrow$0 at 115 GHz, J=2$\rightarrow$1 at 230 GHz and 
-J=3$\rightarrow$2 at 345 GHz, respectively affecting the \PLANCK~100, 217 and 
-353 GHz bands. The J=1$\rightarrow$0 line also imparts a signal upon 
+considered in this study are of high angular resolution, the broad 
+\PLANCK~bandpasses do not allow us to adopt the same appraoch as FDS99 in 
+dealing with line emission. Instead, we must subtract estimates of the 
+molecular line contamination from each \PLANCK~band in order to best isolate 
+the thermal continuum we wish to characterize. The most prominent molecular 
+line emission in the \PLANCK~bands of interest arises from the three lowest CO 
+rotational transitions: J=1$\rightarrow$0 at 115 GHz, J=2$\rightarrow$1 at 230 
+GHz and J=3$\rightarrow$2 at 345 GHz, respectively affecting the \PLANCK~100, 
+217 and 353 GHz bands. The J=1$\rightarrow$0 line also imparts a signal upon 
 \PLANCK~143 GHz, but at a negligible level, $\sim$1000$\times$ fainter relative
@@
 
-%We investigated the possibility of subtracting out CO emission 
-%based on the template of \cite{planckco}. However, we found that the CO 
-%emission rarely amounted to more than XX\% of the total intensity, and 
-%following the treatment of \cite{planckdust}, $\S$2.1, we do not attempt to 
-%remove CO emission.
+% maybe a final sentence or two explaining that, to whatever extent
+% CO line ratios vary over the sky and/or other molecules make a substantial
+% contribution to the observed Planck intensities, our molecular emission
+% correction will be insufficient
 

### 2014-04-24 ms.tex
cleaned up last paragraph of CO correction discussion

@@
 
-Unfortunately, the CO maps at $6.1'$ are rather noisy,
-and the vast majority of the sky has completely negligible CO emission. Thus,
-in order to avoid adding unnecessary noise outside of molecular cloud complexes
-and at high latitudes, we have zeroed out low-signal regions of the CO Type 3
-map. We identify  low-signal regions as those with $\mathcal{I}_3$$<$1 K$_{RJ}$
- km/s, where $\mathcal{I}_3$ is the Type 3 CO map smoothed to 0.25$^{\circ}$ 
-FWHM. This cut results in 90\% of the sky being unaffected by the CO 
-correction, particularly the vast majority of the high Galactic latitude sky.
+Unfortunately, the Type 3 CO map at $6.1'$ FWHM is rather noisy, and the vast
+ majority of the sky has completely negligible CO emission. Thus, in order to 
+avoid adding unnecessary noise outside of molecular cloud complexes and at high
+ latitudes, we have zeroed out low-signal regions of the Type 3 CO map. We 
+identify  low-signal regions as those with $\mathcal{I}_3$$<$1 K$_{RJ}$ km/s, 
+where $\mathcal{I}_3$ is the Type 3 CO map smoothed to 0.25$^{\circ}$ FWHM. As 
+a result of this cut, 90\% of the sky remains unaffected by our CO correction, 
+particularly the vast majority of the high Galactic latitude sky.
 

### 2014-04-24 ms.tex
addressing comments about first couple of paragraphs in zero level discussion

@@
 
-\subsection{Zero-Point}
+\subsection{Zero Level}
 \label{sec:zp}
@@
 to set the zero level of Galactic dust by removing the mean cosmic IR 
-background, as well as any instrumental offset. Additionally, faint residuals 
-of the Solar dipole remain at low frequencies. We will address these issues by 
-separately solving two sub-problems: first, fixing the absolute zero level 
-relative to external data, and second fitting per-band relative offsets and low
-order corrections by correlating the \PLANCK~bands against one another.
-%this last sentence needs lots of work
+background (CIB), as well as any instrumental offset. Additionally, faint 
+residuals of the Solar dipole remain at low frequencies. We will address these 
+issues by separately solving two sub-problems: first, fixing the absolute zero 
+level of \PLANCK~857 GHz relative to external data, and second fitting 
+100-545 GHz offsets and low order corrections by correlating these 
+\PLANCK~bands against \PLANCK~857 GHz.
 
@@
 \label{sec:zp_abs}
-In \cite{planckdust}, the absolute zero level of infrared thermal dust emission
-was set by requiring that \PLANCK~infrared emission tends to zero when 
-H\,\textsc{i} is zero, assuming a linear correlation between these two 
-measurements at low column density. However, this approach is somewhat
-unsatisfying in that there appear to be different slopes of \PLANCK~857 GHz 
-versus H\,\textsc{i} for different ranges of H\,\textsc{i} intensity. In 
-particular, \PLANCK~857 GHz appears to ``flatten out'' at very low 
-H\,\textsc{i}. More quantitavely, we have found using the LAB H\,\textsc{i} 
-data \citep{lab} for $-72$$<$$v_{LSR}$$<$$+25$ that the best-fit slope for 
-H\,\textsc{i}$<$70 K km/s is a factor of $\sim$1.9 lower than the best fit 
-slope for 110 K km/s $<$H\,\textsc{i}$<$200 K km/s, and as a result the implied
-zero-point offsets for \PLANCK~857 GHz differ by $\sim$0.37 MJy/sr.
+In \cite{planckdust}, the absolute zero level of thermal dust emission was set 
+by requiring that \PLANCK~infrared emission tends to zero when H\,\textsc{i} is
+zero, assuming a linear correlation between these two measurements at low 
+column density. However, this approach is somewhat unsatisfying in that there 
+appear to be different slopes of \PLANCK~857 GHz versus H\,\textsc{i} for 
+different ranges of H\,\textsc{i} intensity. In particular, \PLANCK~857 GHz 
+appears to ``flatten out'' at very low H\,\textsc{i}. More quantitavely, we 
+have found using the LAB H\,\textsc{i} data \citep{lab} for 
+$-72$$<$$v_{LSR}$$<$$+25$ that the best-fit slope for H\,\textsc{i}$<$70 K km/s
+is a factor of $\sim$1.9 lower than the best fit slope for 110 K km/s 
+$<$H\,\textsc{i}$<$200 K km/s, and as a result the implied zero-point offsets 
+for \PLANCK~857 GHz differ by $\sim$0.37 MJy/sr.
 

### 2014-04-24 ms.tex
switch order of terms in dipole/quadrupole regression equations
address more comments in zero level discussion, define c_nu earlier

@@
 consistent with that of the Solar dipole. To most precisely recover the 
-amplitude of the residual dipole, it is necessary to have the 
-highest-possible S/N in the independent variable of our regression. For 
-this reason we have used 857 GHz as a reference for the 100-545 GHz bands, as 
-opposed to the FDS99 predictions or H\,\textsc{i}.
-
-We have performed one regression per HFI band to simultaneously 
-fit for the zero level offset, the slope relative to 857 GHz, and the residual 
-dipole amplitude. For each 100-545 GHz HFI band, we restrict to regions of low
-column density (H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for 
-$-72$$<$$v_{LSR}$$<$$+25$ km\,s$^{-1}$) and fit the following model:
+amplitude of the residual dipole, it is necessary to have the highest available
+S/N in the independent variable of our regression. For this reason we have used
+857 GHz as a reference for the 100-545 GHz bands, as opposed to the FDS99 
+predictions or H\,\textsc{i}.
+
+We have performed one regression per HFI band to simultaneously fit for the 
+zero level offset, the slope relative to 857 GHz, and the residual dipole 
+amplitude. For each 100-545 GHz HFI band, we restrict to regions of low column 
+density (H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for $-72$$<$$v_{LSR}$$<$$+25$ 
+km\,s$^{-1}$) and fit the following model:
 
 \begin{equation} \label{equ:dip}
-\mathcal{I}_{\nu_i, p} = m\mathcal{I}_{857, p} + d\mathcal{D}_{p} + b
+\mathcal{I}_{\nu_i, p} = m\mathcal{I}_{857, p} + b + d\mathcal{D}_{p}
 \end{equation}
@@
 best-fit $b$ and $d\mathcal{D}$ from each band $\nu_i$ map. The best-fit
-offsets and residual dipole amplitudes are listed in Table \ref{table:offs}.
+offsets and residual dipole amplitudes are listed in Table \ref{table:offs},
+along with other important per-band parameters, such as the fractional 
+multiplicative calibration uncertainty $c_{\nu}$.
 
@@
 \begin{equation} \label{equ:quad}
-\mathcal{I}_{100, p} = m\mathcal{I}_{857, p} + d\mathcal{D}_p + b + qQ_p
+\mathcal{I}_{100, p} = m\mathcal{I}_{857, p} + b + d\mathcal{D}_p + qQ_p
 \end{equation}

### 2014-04-24 ms.tex
addressing more comments, cite HEALPix at first mention

@@
 
-With $p$ denoting a single nside=64 HEALPix pixel in the maps 
+With $p$ denoting a single nside=64 HEALPix pixel \citep{healpix} in the maps 
 $\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
@@
 two-component dust emission model parameters which are permitted to vary
-spatially. In the case of our full-resolution $6.1'$fits, these parameters
+spatially. In the case of our full-resolution $6.1'$ fits, these parameters
 are the SED normalization and the hot dust temperature $T_2$. The same 
@@
 
-% sentence here summarizing what the following subsections will describe ?
-
 \subsection{Pixelization}
 \label{sec:pix}
-For the purpose of fitting, we break the sky into $\sim$50 million 
-non-overlapping pixels of angular size $\sim$1.72$'$, defined by the HEALPix 
-pixelization in Galactic coordinates, with $N_{side}$=2048 \citep{healpix}. 
-This pixelization is convenient because it is the same format in which the 
-\PLANCK~HFI maps were released, and because it adequately samples the $6.1'$ 
-FWHM maps under consideration in our full-resolution fits. Our procedure will 
-fit the intensity measurements in each spatial pixel independently of those in 
-neighboring pixels.
+For the purpose of fitting, we break the sky into $\sim$50 million pixels of 
+angular size $\sim$1.72$'$, defined by the HEALPix pixelization in Galactic 
+coordinates, with $N_{side}$=2048. This pixelization is convenient because it 
+is the same format in which the \PLANCK~HFI maps were released, and because it 
+adequately samples the $6.1'$ FWHM maps under consideration in our 
+full-resolution fits. Our procedure will fit the intensity measurements in each
+spatial pixel independently of those in neighboring pixels.
 

### 2014-04-24 ms.tex
quote typical delta(nu)/nu for Planck bandpasses
addressing various minor comments

@@
 full-resolution fits. Our procedure will fit the intensity measurements in each
-spatial pixel independently of those in neighboring pixels.
+spatial pixel independently.
 
@@
 practice, however, we wish to constrain our model using measurements in the 
-broad \verb|i100|/\PLANCK~bandpasses, typically hundreds of GHz wide. We have 
-therefore computed dimensionless finite bandpass correction factors to 
+broad \verb|i100|/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. We 
+have therefore computed dimensionless finite bandpass correction factors to 
 account for the MBB($T$, $\beta$) spectral shape and the transmission as a 
 function of frequency:
+
+% is delta(nu)/nu conventionally (nu_off-nu_on)/nu_c or 1/2 of that ?
 
@@
 The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. Some of 
-the most striking features occurr near the north Galactic pole, and to 
+the most striking features occur near the north Galactic pole, and to 
 highlight these regions of unusually high $f_1$, we display the northern
@@
 $\tau_{545}$ map. We calibrate to reddening empirically rather than derive
-a relationshp between $\tau_{545}$ and reddening by introducing additional 
+a relationship between $\tau_{545}$ and reddening by introducing additional 
 assumptions about the dust grain physics and size distribution.
@@
 
-Along with a library of stellar atmosphere models, the spectral lines of these
-stars can be used to predict their intrinsic optical broadband colors. The 
-`true' reddening is then simply the difference in the observed $g-r$ color and
-the $g-r$ color predicted from the spectral lines. Applying a 
-color transformation then yields `true' $E(B-V)$ values for $\sim$250,000 lines
-of sight, mostly at high Galactic latitude. The calibration of two-component 
-optical depth to $E(B-V)$ is then performed as a linear regression of 
-$E(B-V)_{SSPP}$ versus $\tau_{545}$. $\tau_{545}$ is considered to the 
-independent variable in this regression, as we ultimately wish to predict 
-$E(B-V)$ as a function of optical depth, and $\tau_{545}$ has much higher S/N 
-than the SSPP $E(B-V)$ estimates.
+Given a library of stellar atmosphere models, the spectral lines of these stars
+can be used to predict their intrinsic optical broadband colors. The `true' 
+reddening is then simply the difference in the observed $g-r$ color and the 
+$g-r$ color predicted from the spectral lines. Applying a color transformation 
+then yields `true' $E(B-V)$ values for $\sim$250,000 lines of sight, mostly at 
+high Galactic latitude. The calibration of two-component optical depth to 
+$E(B-V)$ is then performed as a linear regression of $E(B-V)_{SSPP}$ versus 
+$\tau_{545}$. $\tau_{545}$ is considered to be the independent variable in this
+regression, as we ultimately wish to predict $E(B-V)$ as a function of optical 
+depth, and $\tau_{545}$ has much higher S/N than the SSPP $E(B-V)$ estimates.
 

### 2014-04-24 ms.tex
acknowledge NASA grant

@@
 This material is based upon work supported by the National Science Foundation 
-Graduate Research Fellowship under Grant No.Based on observations obtained with
- Planck (http://www.esa.int/Planck), an ESA science mission with instruments 
-and contributions directly funded by ESA Member States, NASA, and Canada. This 
+Graduate Research Fellowship under Grant No. We acknowledge support of NASA 
+grant NNX12AE08G for this research. Based on observations obtained with Planck 
+(http://www.esa.int/Planck), an ESA science mission with instruments and 
+contributions directly funded by ESA Member States, NASA, and Canada. This 
 research made use of the NASA Astrophysics Data System (ADS) and the IDL 

### 2014-04-25 ms.tex
improve absolute zero level discussion, remove mention of FIRAS zero point

@@
 by comparison to the FDS99 857 GHz prediction. This renders the \PLANCK~857 GHz
-absolute zero level tied largely to the reliable FIRAS zero point, and to some 
-lesser extent to H\,\textsc{i} through the \verb|i100| zero point. 
-Specifically, we fit a linear model to the FDS99 predicted 857 GHz values as a 
-function of \PLANCK~857 GHz. We used a version of the \PLANCK~857 GHz map with 
-zodiacal light and point sources removed and smoothed to 1$^{\circ}$ FWHM, 
-which we will refer to as $\mathcal{I}_{857}$. For this analysis, we considered
-$\mathcal{I}_{857}$ to be the independent variable, as it has much higher S/N 
-than the FDS99 prediction, henceforward referred to as $\mathcal{F}_{857}$. 
-Note that $\mathcal{F}_{857}$ is not a monochromatic prediction, as we have 
-incorporated the finite bandpass correction factors described in 
-$\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine the dust 
-spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels with 
-$\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to degree 
-resolution has very high S/N, we can safely perform such a cut on 
+absolute zero level tied indirectly to H\,\textsc{i} through the FDS99 
+100$\mu$m and 240$\mu$m zero points.
+
+Specifically, we perform a linear fit to the FDS99-predicted 857 GHz values as 
+a function of \PLANCK~857 GHz. For this purpose, we employ a version of the 
+\PLANCK~857 GHz map with zodiacal light and point sources removed and smoothed 
+to 1$^{\circ}$ FWHM, which we will refer to as $\mathcal{I}_{857}$. We 
+consider $\mathcal{I}_{857}$ to be the independent variable, as it has much 
+higher S/N than the FDS99 prediction, henceforward referred to as 
+$\mathcal{F}_{857}$. Note that $\mathcal{F}_{857}$ is not a monochromatic 
+prediction, as we have incorporated the finite bandpass correction factors 
+described in $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine
+the dust spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels 
+with $\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to 
+degree resolution has very high S/N, we can safely perform such a cut on 
 $\mathcal{I}_{857}$. Figure \ref{fig:fdsref} shows a scatterplot of 

### 2014-04-25 ms.tex
explain why we sample in T_2 rather than T_1
address possibility of SED normalization prior

@@
 compute the corresponding value of $T_1$, thereby specifying ($\beta$, $T$) for
-both MBB components and thus fully specifying the SED shape.
+both MBB components and thus fully specifying the SED shape. In principle,
+we could sample in either $T_1$ or $T_2$, but have chosen to sample in $T_2$ 
+because emission from this component dominates in the relatively high frequency
+bands which most strongly constrain the dust temperatures.
 
@@
 \label{eqn:post}
-P(\tilde{I}_{545}, T_2|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2)P(T_2)
+P(\tilde{I}_{545}, T_2|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2)P(T_2)P(\tilde{I}_{545})
 \end{equation}
@@
 the square root of the \verb|ii_cov| parameter that accompanies each 
-\PLANCK~intensity map. In order to obtain reasonable fitting results at high 
-latitude where the data is noisy, we include a prior on $T_2$:
+\PLANCK~intensity map.
+
+In order to obtain reasonable fitting results at high latitude where the data 
+is noisy, we include the prior on $T_2$:
 
@@
 
-With $\bar{T}_2$ = 16.2 K and $\sigma_{\bar{T}_2}$ = 1.4 K. In practice we 
-always perform computations using logarithms of the relevant probabilities.
+With $\bar{T}_2$ = 16.2 K and $\sigma_{\bar{T}_2}$ = 1.4 K. In principle, there
+can also be an informative prior on $\tilde{I}_{545}$. However, we have chosen 
+to assume a uniform prior on the SED normalization and, as a matter of 
+notation, will omit $P(\tilde{I}_{545})$ henceforward. In practice we always 
+perform computations using logarithms of the relevant probabilities.
 %mention something about the proposal distribution at some point?

### 2014-04-28 ms.tex
quote more exact numbers for EBV calibration sample sizes

@@
 photometry for a set of $\sim$10$^5$ quasars. The SFD calibration was 
-originally tied to a few hundred elliptical galaxies, but was later revised by 
-\cite{schlafly11} using several hundred thousand stars with both spectroscopy 
-and broadband photometry available from SDSS. To calibrate our $\tau_{545}$ to 
+originally tied to a sample of 384 elliptical galaxies, but was later revised 
+by \cite{schlafly11} using $\sim$250,000 stars with both spectroscopy and 
+broadband photometry available from SDSS. To calibrate our $\tau_{545}$ to 
 reddening, we make use of the same set of stars studied by \cite{schlafly11}.

### 2014-04-28 ms.tex
address comment about first paragraph of fitting procedure section

@@
 two-component dust emission model parameters which are permitted to vary
-spatially. In the case of our full-resolution $6.1'$ fits, these parameters
-are the SED normalization and the hot dust temperature $T_2$. The same 
-formalism will apply to our lower-resolution fits in which $f_1$ is also 
-allowed to vary from one line of sight to another.
+spatially. We perform two types of fits: (1) full-resolution 
+$6.1'$ fits, in which just two parameters, the SED normalization and the hot 
+dust temperature $T_2$, vary spatially and (2) lower-resolution fits in which 
+$f_1$ is also allowed to vary from one line of sight to another.
 

### 2014-04-28 ms.tex
fixed bandpass correction equation
starting re-write of bandpass correction discussion

@@
 
-\subsection{Finite Bandpass Correction}
+\subsection{Color Correction}
 \label{sec:bpcorr}
 The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
-flux density $M_{\nu}$ in e.g. MJy/sr for any single frequency $\nu$. In 
-practice, however, we wish to constrain our model using measurements in the 
-broad \verb|i100|/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. We 
-have therefore computed dimensionless finite bandpass correction factors to 
-account for the MBB($T$, $\beta$) spectral shape and the transmission as a 
-function of frequency:
+flux density per solid angle $M_{\nu}$ in e.g. MJy/sr for any single frequency 
+$\nu$. In practice, however, we wish to constrain our model using measurements 
+in the broad \verb|i100|/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. 
+The \PLANCK~data products quote flux density per solid angle in MJy/sr under 
+the `IRAS convention'. More precisely, each value reported in the \PLANCK~maps 
+gives the amplitude of a power-law spectrum with $\alpha$=$-1$, evaluated at 
+the nominal band center frequency, such that this spectrum integrated against 
+the transmission reproduces the bolometer-measured power. Because our model 
+spectra do not conform to the $\alpha$=$-1$ convention, we have computed color 
+correction factors to account for the MBB($T$, $\beta$) spectral shape and the 
+transmission as a function of frequency:
 
@@
 \begin{equation} \label{equ:bpcorr}
-b_{\nu_i}(T, \beta) = \frac{\int \mathcal{T}_{\nu_i}(\nu)\nu^{\beta}B_{\nu}(T) d\nu \bigg[\int \mathcal{T}_{\nu_i}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
+b_{\nu_i}(T, \beta) = \frac{\int \nu^{\beta}B_{\nu}(T)\mathcal{T}_{\nu_i}(\nu) d\nu \bigg[\int (\nu_{i,c}/\nu)\mathcal{T}_{\nu_i}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
 \end{equation}
@@
 \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have 
-adopted the DIRBE transmission curve.
+adopted the DIRBE transmission curve. These bandpass correction factors 
+are applied in the sense that $b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ 
+is a prediction suitable for comparison to the \PLANCK~data products.
 

### 2014-04-29 ms.tex
separate out sentences explaining 3000 GHz color correction
more clean-up of color correction discussion

@@
 given by the \PLANCK~transmission curves provided in the file 
-\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have 
-adopted the DIRBE transmission curve. These bandpass correction factors 
-are applied in the sense that $b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ 
+\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. These bandpass correction 
+factors are applied in the sense that $b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$
 is a prediction suitable for comparison to the \PLANCK~data products.
 
-The broadband, two-component model prediction in band $\nu_i$, termed 
-$\tilde{I}_{\nu_i}$, is then constructed as a linear combination of 
+For 3000 GHz, we have adopted the DIRBE transmission curve. Since DIRBE-quoted
+fluxes also follow the $\alpha$=$-1$ convention, Equation \ref{equ:bpcorr}
+remains applicable.
+
+The two-component model prediction in band $\nu_i$ under the IRAS convention, 
+termed $\tilde{I}_{\nu_i}$, is then constructed as a linear combination of 
 color-corrected MBB terms:
 
-\begin{equation} \label{equ:broadband}
+\begin{equation} \label{equ:iras}
 \tilde{I}_{\nu_i} \propto \sum_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k)
@@
 
-Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. This finite bandpass 
-correction approach allows us to predict the \textit{broadband} measurement 
-$\tilde{I}_{\nu_i}$ by computing monochromatic flux densities at the central 
-frequency $\nu_{i,c}$ and then multiplying by factors $b_{\nu_i}(T, \beta)$ 
-which are interpolated off of a set of precomputed, one-dimensional lookup 
-tables each listing $b_{\nu_i}(T, \beta)$ as a function of $T$. We avoided the 
-need to interpolate in both $\beta$ and $T$ by computing only a small set of 
-one dimensional correction factors for the particular set of $\beta$ values of 
-interest ($\beta \in$ \{1.67, 2.7, 1.19, 2.61\}, see Table \ref{tab:global}).
-
-This finite bandpass correction approach makes the MCMC sampling described in 
+Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. Our color correction 
+approach allows us to predict $\tilde{I}_{\nu_i}$ by computing monochromatic 
+flux densities at the central frequency $\nu_{i,c}$ and then multiplying by 
+factors $b_{\nu_i}(T, \beta)$ which are interpolated off of a set of 
+precomputed, one-dimensional lookup tables each listing $b_{\nu_i}(T, \beta)$ 
+as a function of $T$. We avoided the need to interpolate in both $\beta$ and 
+$T$ by computing only a small set of one dimensional correction factors for the
+particular set of $\beta$ values of interest 
+($\beta \in$ \{1.67, 2.7, 1.19, 2.61\}, see Table \ref{tab:global}).
+
+% need some sort of clarification about the fact that, in the parts of the 
+% analysis where beta floats, this precomputation/interpolation is NOT 
+% what we do
+
+This color correction approach makes the MCMC sampling described in 
 $\S$\ref{sec:mcmc} much more computationally efficient by circumventing the 
@@
 on-the-fly for each proposed dust temperature. We have chosen to compute the 
-bandpass corrections on a per-MBB basis because this approach is very 
+color corrections on a per-MBB basis because this approach is very 
 versatile; all possible two-component models are linear combinations of MBBs, 
-so we can apply all of our finite bandpass machinery even when we allow 
+so we can apply all of our color correction machinery even when we allow 
 parameters other than temperature (e.g. $f_1$) to vary and thereby change the 
@@
 
-This equation is quite similar to Equation \ref{equ:broadband}, but with two 
+This equation is quite similar to Equation \ref{equ:iras}, but with two 
 important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 

### 2014-04-29 ms.tex
cleaning up color correction discussion

@@
 % integral limits ??? check planck paper to see what they did
-
-% now i need to define what \nu_{i,c} is (it's the nominal central 
-% frequency of band \nu_i) e.g. 857 GHz for Planck 857, etc..
-
-% also need to define what \mathcal{T} is (relative transmission, 
-% dimensionless)
+% -> planck spectral response paper just leaves the integrals indefinite
 
 Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
-$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 3000\} GHz. 
+$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 2997.92\} GHz. 
 $\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
@@
 given by the \PLANCK~transmission curves provided in the file 
-\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. These bandpass correction 
-factors are applied in the sense that $b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$
-is a prediction suitable for comparison to the \PLANCK~data products.
+\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. The color correction factors
+of Equation \ref{equ:bpcorr} are applied in the sense that 
+$b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ is a prediction suitable for 
+direct comparison to the \PLANCK~data products.
 

### 2014-04-29 ms.tex
more minor clean-up in discussion of predicting Planck observations

@@
 MCMC sampling to predict the observed SED, which we will denote by 
-\{$\tilde{I}_{\nu_i}$\}. The predicted broadband intensities are given by:
+\{$\tilde{I}_{\nu_i}$\}. The predicted observations are given by:
 
@@
 important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
-specified by $\tilde{I}_{545}$, which represents the broadband intensity 
-measured in the \PLANCK~545 GHz band. The denominator serves to ensure that,
-for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. Second, 
-each term in the numerator is multiplied by a conversion factor 
+specified by $\tilde{I}_{545}$, which represents the flux density per solid
+angle measured in the \PLANCK~545 GHz band. The denominator serves to ensure 
+that, for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. 
+Second, each term in the numerator is multiplied by a conversion factor 
 $u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 

### 2014-04-29 ms.tex
getting rid of incorrect statements in model prediction discussion

@@
 \PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
-remaining maps (545-3000 GHz) have units of MJy/sr. Complicating matters, the 
-conversion from $K_{CMB}$ to MJy/sr depends on the spectrum under 
-consideration; attempting to apply conversion factors to put all of the 
-observed maps themselves into common units is not a particularly attractive 
-option. Therefore, we adopt the strategy of predicting each band in its native 
-units, whether MJy/sr or $K_{CMB}$. For this reason, we always evaluate 
-$B_{\nu_{i,c}}$ in Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 
-(dimensionless) for all $\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, 
-$u_{\nu_i}(T_k, \beta_k)$ represents the appropriate conversion factor from 
-$K_{CMB}$ to MJy/sr:
-
-% equation for u goes here
-
-\begin{equation}
-u_{\nu_i}(T, \beta) = u_{\nu_i, IRAS} \times u_{\nu_i, IRAS \ to \ (T, \beta)}
-\end{equation}
-
-Here $u_{\nu_i, IRAS}$ gives the conversion factor from $K_{CMB}$ to MJy/sr
-for band $\nu_i$ under the `\IRAS~convention', which corresponds to
-a power law specrum with spectral index $\alpha$=$-1$. The values of 
-$u_{\nu_i, IRAS}$ are listed in the second column of \cite{planckresponse} 
-Table 6. $u_{\nu_i, IRAS \ to \ (T, \beta)}$ is a color correction factor 
-relative to the \IRAS~convention for band $\nu_i$, assuming a MBB($T$, $\beta$)
-spectrum. In practice, we retrieve $u_{\nu_i}(T, \beta)$ values in a fashion 
-similar to that used for the $b_{\nu_i}(T, \beta)$ color corrections, using a 
-set of precomputed one-dimensional look-up tables. To reiterate, for 
-$\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ has units of (MJy/sr)/$K_{CMB}$,
-and therefore $\tilde{I}_{\nu_{i}}$ will have different units depending on the 
-band $\nu_i$, though $\tilde{I}_{\nu_{i}}$ always has the same units as the 
-native band $\nu_i$ map.
-
-%We will treat the SED normalization $\tilde{I}_{545}$ as a free 
-%parameter in our fitting procedure. In our baseline fits, second free 
-%parameter is $T_2$, which determines the shape of the SED through $M_{\nu}$ as
-% well as $b_{\nu_i}(T_2)$.
-
-% introduce nu_i notation in above paragraph with some mention of what it
-% means
+remaining maps (545-3000 GHz) have units of MJy/sr. We have adopted the 
+strategy of predicting each band in its native units, whether MJy/sr or 
+$K_{CMB}$. For this reason, we always evaluate $B_{\nu_{i,c}}$ in Equation 
+\ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for all 
+$\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
+represents the conversion factor from $K_{CMB}$ to MJy/sr, given by 
+\cite{planckresponse} Equation 32.
+
+%is the old sentence below worth reinstating ?
+
+%To reiterate, for 
+%$\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ has units of 
+%(MJy/sr)/$K_{CMB}$,and therefore $\tilde{I}_{\nu_{i}}$ will have different 
+%units depending on the band $\nu_i$, though $\tilde{I}_{\nu_{i}}$ always has 
+%the same units as the native band $\nu_i$ map.
 

### 2014-05-07 ms.tex
more precise value for speed of light
starting more thorough motivation/background for FDS99 emission model

@@
 % of SED toward the millimeter
+At sufficiently high frequencies, Galactic thermal dust emission can be 
+adequately modeled as a single MBB with power-law emissivity 
+\citep[e.g. SFD;][]{planckdust}. However, it has long been recognized, 
+particularly in view of the FIRAS spectra, that the dust SED flattens toward 
+the millimeter in a manner which is not consistent with a simple extrapolation 
+of the single-MBB model to low frequencies. In the diffuse ISM, \cite{reach95} 
+found an improved fit to the FIRAS data using a superposition of two $\beta$=2 
+MBBs, one representing a `hot' grain population ($T$$\approx$), the other a 
+`cold' grain population ($T$$\approx$).
+
 We adopt the thermal dust emission model of FDS99, which consists of two 
@@
 Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
-$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 2997.92\} GHz. 
+$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 2997.92458\} GHz. 
 $\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
@@
 $K_{CMB}$. For this reason, we always evaluate $B_{\nu_{i,c}}$ in Equation 
-\ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for all 
+\ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for 
 $\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
@@
 
+% make argument that, in models with f1 and the beta's constant, the choice
+% of frequency at which tau is evaluated does not matter
+
 Given a library of stellar atmosphere models, the spectral lines of these stars
@@
 
+% cite Green appendix for details of deriving EBV_SSPP from Schlafly 11 data ?
+
 The result of this regression is shown in Figure \ref{fig:calib}. Indeed there 

### 2014-05-07 ms.tex
Reach dust temperature ranges

@@
 found an improved fit to the FIRAS data using a superposition of two $\beta$=2 
-MBBs, one representing a `hot' grain population ($T$$\approx$), the other a 
-`cold' grain population ($T$$\approx$).
+MBBs, one representing a `hot' grain population ($T$$\approx$16$-$21K), the 
+other a `cold' grain population ($T$$\approx$4$-$7K).
 

### 2014-05-07 ms.tex
close to a complete introduction of the two-component emission model

--- 2014-05-07 ms.tex
@@
 of the single-MBB model to low frequencies. In the diffuse ISM, \cite{reach95} 
-found an improved fit to the FIRAS data using a superposition of two $\beta$=2 
-MBBs, one representing a `hot' grain population ($T$$\approx$), the other a 
-`cold' grain population ($T$$\approx$).
-
-We adopt the thermal dust emission model of FDS99, which consists of two 
-populations of dust grains emitting as MBBs, each with distinct 
-emission/absorption characteristics. Importantly, the emissivity power law 
-indices $\beta$ of the two species differ. The shape of this spectrum is given 
-by:
+found an improved fit to the FIRAS data using an empirically motivated 
+superposition of two $\beta$=2 MBBs, one representing a `hot' grain population 
+($T$$\approx$16$-$21 K), the other a `cold' grain population 
+($T$$\approx$4$-$7 K). FDS99 built a more physically motivated two-MBB model, 
+in which different grain emission/absorption properties account for the 
+differing temperatures of each population, and these temperatures are coupled 
+by assuming thermal equilibrium with the same interstellar radiation field 
+(ISRF).
+
+The primary FDS99 analysis considered the grain properties, for example the
+emissivity power law indices $\beta$, to be constant over the sky, and 
+performed a correlation slope analysis to constrain these parameters with
+FIRAS and DIRBE observations. A DIRBE 240$\mu$m/100$\mu$m ratio was used
+to account for temperature variation at $\sim$1.3$^{\circ}$ resolution. In this
+work we seek to apply FDS99-like emission models to the \PLANCK~data set, which
+offers a dramatic enhancement in angular resolution relative to the FIRAS 
+spectra. The \PLANCK~data allow us to derive a temperature correction at 
+near-\IRAS~resolution, re-evaluate the best-fit global dust properties, and
+fit addition parameters of the two-component model as a function of position
+on the sky.
+
+% could add a last sentence 'ultimately this allows us to make high-resolution
+% foreground and extinction predictions' and/or even find a way to mention
+% other predictions, such as polarization/R_v
+
+% in the above paragraph, should I mention the Planck collaboration result
+% of beta_mm vs. beta_fir being different, with (beta_fir-beta_mm) > 0
+
+% should i also try to justify why it's worth doing this fit even
+% if it's possible to just claim different beta's at different frequencies?
+
+The shape of the two-component spectrum we will consider is given by:
 
@@
 
-In accordance with the conventions of FDS99, $\nu_0$ is chosen to be 3000 GHz.
-In principle, one could imagine this two MBB model to be specified by seven 
-free parameters for every line of sight: $T_1$, $T_2$, $\beta_1$, $\beta_2$, 
-$f_1$, and $q_1$/$q_2$ and the normalization of $M_{\nu}$. However, as 
-discussed in FDS99, $T_1$=$T_1$($T_2$, $\beta_1$, $\beta_2$, $q_1/q_2$) is 
+Importantly, the emissivity power law indices $\beta$ of the two species 
+differ.In accordance with the conventions of FDS99, $\nu_0$ is chosen to be 
+3000 GHz. In principle, one could imagine this two MBB model to be specified by
+seven free parameters for every line of sight: $T_1$, $T_2$, $\beta_1$, 
+$\beta_2$, $f_1$, and $q_1$/$q_2$ and the normalization of $M_{\nu}$. However, 
+as discussed in FDS99, $T_1$=$T_1$($T_2$, $\beta_1$, $\beta_2$, $q_1/q_2$) is 
 fully specified by these other parameters under the assumption that the 
 temperature of each species is determined by maintaining thermal equilibrium 
-with the same interstellar radiation field (ISRF). $T_1$ is always related to 
-$T_2$ via a simple power law, although the prefactor and exponent depend on the
- parameters $q_1/q_2$, $\beta_1$ and $\beta_2$. $q_1/q_2$ encodes the
-relative emission/absorption cross-sections of the two dust species, while
-$f_1$ dictates the relative amounts of each species present.
+with the same ISRF. $T_1$ is always related to $T_2$ via a simple power law, 
+although the prefactor and exponent depend on the parameters $q_1/q_2$, 
+$\beta_1$ and $\beta_2$. $q_1/q_2$ encodes the relative emission/absorption 
+cross-sections of the two dust species, while $f_1$ dictates the relative 
+amounts of each species present.
 

### 2014-05-07 ms.tex
minor clean-up of section introducing two-component model

@@
 performed a correlation slope analysis to constrain these parameters with
-FIRAS and DIRBE observations. A DIRBE 240$\mu$m/100$\mu$m ratio was used
+FIRAS and DIRBE observations. A DIRBE 240$\mu$m/100$\mu$m ratio was constructed
 to account for temperature variation at $\sim$1.3$^{\circ}$ resolution. In this
@@
 near-\IRAS~resolution, re-evaluate the best-fit global dust properties, and
-fit addition parameters of the two-component model as a function of position
+fit additional parameters of the two-component model as a function of position
 on the sky.
@@
 
-The shape of the two-component spectrum we will consider is given by:
+The shape of the two-component model spectrum we will consider is given by:
 
 \begin{equation}
-M_{\nu} \propto f_{1}q_{1}(\frac{\nu}{\nu_{0}})^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}(\frac{\nu}{\nu_0})^{\beta_2}B_{\nu}(T_2)
+M_{\nu} \propto f_{1}q_{1}\Big(\frac{\nu}{\nu_{0}}\Big)^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}\Big(\frac{\nu}{\nu_0}\Big)^{\beta_2}B_{\nu}(T_2)
 \end{equation}

### 2014-05-07 ms.tex
more fix up of model description

@@
 
-The primary FDS99 analysis considered the grain properties, for example the
-emissivity power law indices $\beta$, to be constant over the sky, and 
-performed a correlation slope analysis to constrain these parameters with
-FIRAS and DIRBE observations. A DIRBE 240$\mu$m/100$\mu$m ratio was constructed
-to account for temperature variation at $\sim$1.3$^{\circ}$ resolution. In this
-work we seek to apply FDS99-like emission models to the \PLANCK~data set, which
-offers a dramatic enhancement in angular resolution relative to the FIRAS 
-spectra. The \PLANCK~data allow us to derive a temperature correction at 
-near-\IRAS~resolution, re-evaluate the best-fit global dust properties, and
-fit additional parameters of the two-component model as a function of position
-on the sky.
+The primary FDS99 analysis considered the intrinsic grain properties, for 
+example the emissivity power law indices, to be constant over the sky, and 
+performed a correlation slope analysis to constrain these parameters with FIRAS
+and DIRBE observations. FDS99 also constructed a DIRBE 240$\mu$m/100$\mu$m 
+ratio to account for temperature variation at $\sim$1.3$^{\circ}$ resolution. 
+In this work we seek to apply FDS99-like emission models to the \PLANCK~data 
+set, which offers a dramatic enhancement in angular resolution relative to the 
+FIRAS spectra. The \PLANCK~data thereby allow us to derive an improved 
+temperature correction at near-\IRAS~resolution, re-evaluate the best-fit 
+global dust properties, and fit additional parameters of the two-component 
+model as a function of position on the sky.
+
+% kind of feel like i'm re-writing the introduction here ??
 
@@
 
-Importantly, the emissivity power law indices $\beta$ of the two species 
-differ.In accordance with the conventions of FDS99, $\nu_0$ is chosen to be 
-3000 GHz. In principle, one could imagine this two MBB model to be specified by
-seven free parameters for every line of sight: $T_1$, $T_2$, $\beta_1$, 
-$\beta_2$, $f_1$, and $q_1$/$q_2$ and the normalization of $M_{\nu}$. However, 
-as discussed in FDS99, $T_1$=$T_1$($T_2$, $\beta_1$, $\beta_2$, $q_1/q_2$) is 
-fully specified by these other parameters under the assumption that the 
-temperature of each species is determined by maintaining thermal equilibrium 
-with the same ISRF. $T_1$ is always related to $T_2$ via a simple power law, 
-although the prefactor and exponent depend on the parameters $q_1/q_2$, 
-$\beta_1$ and $\beta_2$. $q_1/q_2$ encodes the relative emission/absorption 
-cross-sections of the two dust species, while $f_1$ dictates the relative 
-amounts of each species present.
+% re: following sentence --- in the code nu_0 is actually 2997.92458
+% because this is the frequency with respect to which DIRBE color correction
+% K_100 (and my color correction as well) is referenced
+
+Following the convention of FDS99, $\nu_0$ is chosen to be 3000 GHz. In 
+principle, one could imagine this two MBB model to be specified by seven free 
+parameters for every line of sight: $T_1$, $T_2$, $\beta_1$, $\beta_2$, $f_1$, 
+and $q_1$/$q_2$ and the normalization of $M_{\nu}$. However, as discussed in 
+FDS99, $T_1$=$T_1$($T_2$, $\beta_1$, $\beta_2$, $q_1/q_2$) is fully specified 
+by these other parameters under the assumption that the temperature of each 
+species is determined by maintaining thermal equilibrium with the same ISRF. 
+$T_1$ is always related to $T_2$ via a simple power law, although the prefactor
+and exponent depend on the parameters $q_1/q_2$, $\beta_1$ and $\beta_2$. 
+$q_1/q_2$ encodes the relative emission/absorption cross-sections of the two 
+dust species, while $f_1$ dictates the relative amounts of each species 
+present.
+
+% Importantly, the emissivity power law indices $\beta$ of the two species 
+% differ.
 

### 2014-05-08 ms.tex
rearranging explanation of two-component SED shape equation
still working on description of two-component model...

@@
 
-% re: following sentence --- in the code nu_0 is actually 2997.92458
+% re: following paragraph --- in the code nu_0 is actually 2997.92458
 % because this is the frequency with respect to which DIRBE color correction
@@
 
-Following the convention of FDS99, $\nu_0$ is chosen to be 3000 GHz. In 
-principle, one could imagine this two MBB model to be specified by seven free 
-parameters for every line of sight: $T_1$, $T_2$, $\beta_1$, $\beta_2$, $f_1$, 
-and $q_1$/$q_2$ and the normalization of $M_{\nu}$. However, as discussed in 
-FDS99, $T_1$=$T_1$($T_2$, $\beta_1$, $\beta_2$, $q_1/q_2$) is fully specified 
-by these other parameters under the assumption that the temperature of each 
-species is determined by maintaining thermal equilibrium with the same ISRF. 
-$T_1$ is always related to $T_2$ via a simple power law, although the prefactor
-and exponent depend on the parameters $q_1/q_2$, $\beta_1$ and $\beta_2$. 
+% not sure if `Planck function' is the correct jargon
+
+Where $B_{\nu}$ is the Planck function, $T_1$ is the `cold' dust temperature, 
+$T_2$ is the `hot' dust temperature, and $\beta_1$ and $\beta_2$ are the
+emissivity power-law indices of the cold and hot components respectively. 
 $q_1/q_2$ encodes the relative emission/absorption cross-sections of the two 
 dust species, while $f_1$ dictates the relative amounts of each species 
-present.
+present. Following the convention of FDS99, $\nu_0$ is chosen to be 3000 GHz.
+
+Mathematically, this two-MBB model requires specification of seven 
+parameters for every line of sight: $T_1$, $T_2$, $\beta_1$, $\beta_2$, $f_1$, 
+$q_1$/$q_2$ and the normalization of $M_{\nu}$. However, under the 
+assumption that the temperature of each species is determined by maintaining 
+thermal equilibrium with the same ISRF, $T_1$=$T_1$($T_2$, $\beta_1$, 
+$\beta_2$, $q_1/q_2$) is fully determined by these other parameters. $T_1$ is 
+always related to $T_2$ via a simple power law, although the prefactor and 
+exponent depend on the parameters $q_1/q_2$, $\beta_1$ and $\beta_2$ (see FDS99
+Equation 14).
 
@@
 not feasible for our full-resolution $6.1$$'$ fits, as these are constrained by
-only five broadband intensity measurements. Hence, as in FDS99, we 
-deem certain parameters to be ``global'', i.e. spatially constant over the 
-entire sky. In our full-resolution five-band fits, we designate $\beta_1$, 
-$\beta_2$, $f_1$ and $q_1/q_2$ to be spatially constant. This same approach 
-was employed by FDS99, and the globally best-fit values obtained by FDS99 for 
-these parameters are listed in the first row of Table \ref{tab:global}. With 
-these global parameters, FDS99 found $T_2$$\approx$$16.2$K, 
-$T_1$$\approx$$9.4$K to be typical at high-latitude. In $\S$\ref{sec:global}, 
-we discuss the best-fit global parameters favored by the \PLANCK~HFI data; 
-these are listed in the second row of Table \ref{tab:global}.
+only five broadband intensity measurements. Hence, as in FDS99, we deem certain
+ parameters to be ``global'', i.e. spatially constant over the entire sky. In 
+our full-resolution five-band fits, we designate $\beta_1$, $\beta_2$, $f_1$ 
+and $q_1/q_2$ to be spatially constant. This same approach was employed by 
+FDS99, and the globally best-fit values obtained by FDS99 for these parameters 
+are listed in the first row of Table \ref{tab:global}. With these global 
+parameters, FDS99 found $T_2$$\approx$$16.2$K, $T_1$$\approx$$9.4$K to be 
+typical at high-latitude. In $\S$\ref{sec:global}, we discuss the best-fit 
+global parameters favored by the \PLANCK~HFI data; these are listed in the 
+second row of Table \ref{tab:global}.
 

### 2014-05-11 ms.tex
cleaning up comments
more clean up, defining HFI/LFI acronyms

@@
 
-%We also expect the derived optical depth to provide 
-%valuable cross-checks for other dust-column related 
-%data products, specifically the \cite{SFD} map, which assumed a single 
-%modified blackbody with $\nu^2$ emissivity and included a temperature map of 
-%inferior $\sim$$1.3^{\circ}$ resolution. We compare our best-fit two-component
-% spectral energy distributions to those of the \cite{planckdust} 
-% single-component parametrization.
-
-%specify early on that this is 'Galactic dust', 'dust' is kind of a vague
+% specify early on that this is 'Galactic dust', 'dust' is kind of a vague
 % term ... on the other hand the Planck dust paper is pretty lax about this
-%MENTION USE IN MAKING IR FOREGROUND PREDICTIONS
-%mention more explicitly the enhanced temperature resolution relative to SFD??
-%Our optical depth map will also provide a useful reference for dust maps 
-%based on stellar colors rather than infrared emission.
+
+% mention more explicitly the enhanced temperature resolution relative to SFD??
+
 \end{abstract}
@@
 \section{Introduction}
-%why dust important in astronomy/astrophysics
 The presence of Galactic interstellar dust affects
@@
 (CMB).
-%specify ``low frequency more precisely eventually
-% somewhere mention re-radiation
+
+% mention re-radiation somewhere ?
 
@@
 % that the distinct species are real.
-
-%mention which grain species is large vs. small
 
@@
 
-%would be nice if i had a citation here for Eddie/Greg pan-starrs dust stuff
+% might be more appropriate to cite the 2D dust map Eddie is making rather
+% than the `methods' paper
 
@@
 $\S$\ref{sec:global} we describe our constraints on this model's global 
-parameters derived from the \PLANCK~HFI maps. In $\S$\ref{sec:fitting} we 
-detail the Markov chain Monte Carlo (MCMC) method with which we have estimated 
-the spatially varying parameters of our model. In $\S$\ref{sec:ebv} we 
-calibrate our derived optical depth to optical reddening. In 
-$\S$\ref{sec:results} we present the full-sky maps of dust temperature and 
+parameters derived from the \PLANCK~High Frequency Instrument (HFI) maps. In 
+$\S$\ref{sec:fitting} we detail the Markov chain Monte Carlo (MCMC) method with
+which we have estimated the spatially varying parameters of our model. In 
+$\S$\ref{sec:ebv} we calibrate our derived optical depth to optical reddening. 
+In $\S$\ref{sec:results} we present the full-sky maps of dust temperature and 
 optical depth we have obtained, and conclude in $\S$\ref{sec:conclusion}.
@@
 map as is, without any custom modifications.
-%maybe clarify that throughout we use SFD i100 totally as-is, with no
-% customization
-
-%list other %important characteristics of i100 e.g. that it has been 
-%zodi-corrected and relies on dirbe on s
 
@@
 residual Solar dipole, are discussed in $\S$\ref{sec:zp}.
-% SMICA is subtracted from ALL Planck maps being used, including 545, 857 GHz
-% WHAT IS THE ANGULAR RESOLUTION OF THE SMICA MAP, AND IS IT EVEN
-% WELL-DEFINED??
+
+% NEED TO MENTION SMOOTHING OF THE SMICA MAP TO 6.1 ARMCIN !!!!!!
 
@@
 \label{sec:ptsrc}
-%start by mentioning that SFD removed compact sources (outside of b +/- 5)
+% this compact source section still needs a lot of work
 After subtracting the SMICA CMB model, we interpolate over compact sources, 
@@
 modifications of the \verb|i100| map to account for compact sources. To mask 
-compact sources in the \PLANCK~maps, we use the SFD compact source mask, which 
-was originally constructed to mask point sources and resolved compact objects 
-that are not part of the Galactic cirrus at 3000 GHz. Given our pixelization 
-(see $\S$\ref{sec:pix}), 1.56\% of pixels are masked.
-
-%this compact source section still needs a lot of work
-
-% probably best to refer to an appendix for details of the point source
-% masking
+compact sources in the \PLANCK~217-857 GHz maps, we use the SFD compact source 
+mask. At 100, 143 GHz we use the compact source masks provided by the 
+\PLANCK~collaboration in the file \verb|HFI_Mask_PointSrc_2048_R1.10.fits|. 
+Given our pixelization (see $\S$\ref{sec:pix}), 1.56\% of pixels are masked 
+at 217-857 GHz (1.05\%, 1.02\% at 100, 143 GHz)
+
+% best to refer to an appendix for details of the point source masking ?
 
@@
 
-%TODO : actually smooth the CO map to 6.1 arcmin
-To correct for molecular emission, we employed the \PLANCK~Type 3 CO 
-data product, which boasts the highest S/N 
-among the available full-sky CO maps based on \PLANCK~HFI/LFI 
-data \citep{planckco}. The native angular resolution of the Type 3 CO map is 
-5.5$'$. We therefore began by smoothing the raw Type 3 CO map to $6.1'$, to 
-match the PSF of the smoothed \PLANCK~intensity maps we wish to correct 
-for molecular emission (for our full-resolution two-parameter fits, these are 
-217 GHz and 353 GHz).
-
-%take a few sentences to mention how exactly the CO was scaled, i.e. conversion
-% factors from K km/s and line ratio assumptions
-
-We must apply the appropriate unit conversions to the $6.1'$ Type 3 CO
-map before subtracting it from the \PLANCK~intensity maps, which have native 
-units of $K_{CMB}$ at the frequencies of interest. The Type 3 CO map is 
-provided in units of K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. To convert 
-this quantity to $K_{CMB}$, we assume that all of the CO emission arises from 
-the $^{12}$CO isotope, and derived the \PLANCK-observed CO intensity in units 
-of $K_{CMB}$ as follows:
+To correct for molecular emission, we employed the \PLANCK~Type 3 CO data 
+product, which boasts the highest S/N among the available full-sky CO 
+maps based on the \PLANCK~HFI and Low Frequency Instrument (LFI) data 
+\citep{planckco}. The native angular resolution of the Type 3 CO map is 5.5$'$.
+We therefore began by smoothing the raw Type 3 CO map to $6.1'$, to match the 
+PSF of the smoothed \PLANCK~intensity maps we wish to correct for molecular 
+emission (for our full-resolution two-parameter fits, these are 217 GHz and 353
+GHz).
+
+We must apply the appropriate unit conversions to the $6.1'$ Type 3 CO map 
+before subtracting it from the \PLANCK~intensity maps, which have native units 
+of $K_{CMB}$ at the frequencies of interest. The Type 3 CO map is provided in 
+units of K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. To convert this quantity 
+to $K_{CMB}$, we assume that all of the CO emission arises from the $^{12}$CO 
+isotope, and derived the \PLANCK-observed CO intensity in units of $K_{CMB}$ as
+follows:
 
@@
 
-% state what I_3 is 
 Where $I_{CO, \nu_i, N, N-1}$ is the intensity in $K_{CMB}$ in \PLANCK~band 
@@
 
-%did i ever spell out the acronyms HFI, LFI ????
-
-% maybe a final sentence or two explaining that, to whatever extent
+% maybe a final sentence or two warning that, to whatever extent
 % CO line ratios vary over the sky and/or other molecules make a substantial
@@
 
-%We did not attempt to correct for higher J CO transitions beyond J=3->2
+% We did not attempt to correct for higher J CO transitions beyond J=3->2
 

### 2014-05-11 ms.tex
more clean-up of CO subtraction discussion

@@
 
-To correct for molecular emission, we employed the \PLANCK~Type 3 CO data 
-product, which boasts the highest S/N among the available full-sky CO 
-maps based on the \PLANCK~HFI and Low Frequency Instrument (LFI) data 
+To correct for molecular emission, we employ the \PLANCK~Type 3 CO data 
+product, which boasts the highest S/N among the available full-sky CO maps 
+based on the \PLANCK~HFI and Low Frequency Instrument (LFI) data 
 \citep{planckco}. The native angular resolution of the Type 3 CO map is 5.5$'$.
-We therefore began by smoothing the raw Type 3 CO map to $6.1'$, to match the 
-PSF of the smoothed \PLANCK~intensity maps we wish to correct for molecular 
-emission (for our full-resolution two-parameter fits, these are 217 GHz and 353
-GHz).
-
-We must apply the appropriate unit conversions to the $6.1'$ Type 3 CO map 
-before subtracting it from the \PLANCK~intensity maps, which have native units 
-of $K_{CMB}$ at the frequencies of interest. The Type 3 CO map is provided in 
+We therefore begin by smoothing the raw Type 3 CO map to match the PSF of the 
+smoothed \PLANCK~intensity maps we wish to correct for molecular emission.
+
+We must apply the appropriate unit conversions to the Type 3 CO map before 
+subtracting it from the \PLANCK~intensity maps, which have native units of 
+$K_{CMB}$ at the frequencies of interest. The Type 3 CO map is provided in 
 units of K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. To convert this quantity 
 to $K_{CMB}$, we assume that all of the CO emission arises from the $^{12}$CO 
-isotope, and derived the \PLANCK-observed CO intensity in units of $K_{CMB}$ as
+isotope, and derive the \PLANCK-observed CO intensity in units of $K_{CMB}$ as
 follows:
@@
 % correction will be insufficient
-
-% We did not attempt to correct for higher J CO transitions beyond J=3->2
 

### 2014-05-11 ms.tex
more work on CO discussion

@@
 $F_{12CO, \nu_i, N, N-1}$ are conversion factors between K$_{RJ}$ km/s and 
-$K_{CMB}$ for particular band/transition pairs. The relevant values adopted are
-$F_{12CO, 100, 1, 0}$=1.478$\times$10$^{-5}$, 
-$F_{12CO, 217, 2, 1}$=4.585$\times$$10^{-5}$, and 
-$F_{12CO, 353, 3, 2}$=1.751$\times$$10^{-4}$.
+$K_{CMB}$ for particular band/transition pairs. The relevant values adopted 
+are:
+
+\noindent
+$F_{12CO, 100, 1, 0}$=1.478$\times$10$^{-5}$$K_{CMB}/K_{RJ}$,
+
+\noindent
+$F_{12CO, 217, 2, 1}$=4.585$\times$$10^{-5}$$K_{CMB}/K_{RJ}$, and
+
+\noindent
+$F_{12CO, 353, 3, 2}$=1.751$\times$$10^{-4}$$K_{CMB}/K_{RJ}$.
+
+\noindent
 $R_{N, N-1}$ represents the line ratio of the transition from J=$N$ to 
@@
 further adopt $R_{2,1}$=0.595 and $R_{3,2}$=0.297 based on \cite{planckco}. 
-These line ratios are assumed to be constant over the entire sky. Formally, 
-then, the CO contamination in band $\nu_i$ is given by:
+These line ratios are assumed to be constant over the entire sky.
+
+Formally, then, the CO contamination in band $\nu_i$ is given by:
+
+% need to cite reference for K_rj -> K_cmb conversion factors
 

### 2014-05-12 ms.tex
explain origin of CO Krj km/s to Kcmb conversion factors
get rid of outdated comments/notes to self
reference FWHM values listed in table rather than redundantly listing them in the text itself

@@
 appropriate symmetric Gaussian such that the resulting map has a  $6.1'$ FWHM. 
-The FWHM we assign to the native \PLANCK~maps is taken from \cite{planckbeam}, 
-specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, $4.84'$ for 545 GHz, and
- $4.63'$ for 857 GHz.
+The FWHM values we assign to the native \PLANCK~maps are taken from 
+\cite{planckbeam}, and are listed in Table \ref{table:offs}.
 
@@
 $F_{12CO, \nu_i, N, N-1}$ are conversion factors between K$_{RJ}$ km/s and 
-$K_{CMB}$ for particular band/transition pairs. The relevant values adopted 
-are:
+$K_{CMB}$ for particular band/transition pairs. The relevant values, 
+calculated with the \textit{Unit Conversion and Colour Correction} software 
+utilities (\verb|v1.2|), are:
 
 \noindent
-$F_{12CO, 100, 1, 0}$=1.478$\times$10$^{-5}$$K_{CMB}/K_{RJ}$,
+$F_{12CO, 100, 1, 0}$=1.478$\times$10$^{-5}$$K_{CMB}/(K_{RJ} \ km/s)$,
 
 \noindent
-$F_{12CO, 217, 2, 1}$=4.585$\times$$10^{-5}$$K_{CMB}/K_{RJ}$, and
+$F_{12CO, 217, 2, 1}$=4.585$\times$$10^{-5}$$K_{CMB}/(K_{RJ} \ km/s)$, and
 
 \noindent
-$F_{12CO, 353, 3, 2}$=1.751$\times$$10^{-4}$$K_{CMB}/K_{RJ}$.
+$F_{12CO, 353, 3, 2}$=1.751$\times$$10^{-4}$$K_{CMB}/(K_{RJ} \ km/s)$.
 
@@
 
-% need to cite reference for K_rj -> K_cmb conversion factors
+% might consider quoting rounder values in text, most precise values are:
+% 100 GHz, J=1->0 : 1.478e-5, 217 GHz, J=2->1 : 4.585e-5, 
+% 353 GHz, J=3->2 : 1.751e-4
 
@@
 
-%mention that all of this assumes that residual CMB dipole
+% mention that all of this assumes that residual CMB dipole
 % and other low order-corrections are negligible at 857 GHz
-
-% Maybe it's not necessary to mention the 545 GHz check ... although
-% i should do the check eventually as to whether choosing 545 GHz
-% for the absolute zero point is consistent with choosing 857 GHz
-% to within the errors that i'm quoting
-
-%We also repeated the full-sky FDS99 prediction versus \PLANCK~regression at 
-%545 GHz. After
-
-%We also repeated the full-sky and quadrant regressions with the FDS99 
-%predictions at 545 GHz (see bottom panel of Figure XX). We find the 
-%slopes vary from XX to YY with an rms scatter of ZZ. The 545 GHz zero points
-%have an rms scatter of SS, which is consistent with the 545 GHz zero 
-%point rms implied by the scatter in 857 GHz zero point.
 
@@
 to \verb|i100|, which has a zero level tied to H\,\textsc{i} by SFD.
-% maybe need to restate the idea that we're deriving zero points by assuming
-% that the band of interest must approach zero linearly as the reference
-% (in this case 857 ghz) approaches zero.
 
@@
 \end{equation}
-%basically just finish clarifying here that we want to start simple by fitting
-%only two parameters for each pixel since we only have 5 intensity
-% measurements per pixel in our baseline fits at 6.1 arcmin resolution
 

### 2014-05-13 ms.tex
minor clean up, specify statistical error on 857 GHz offset

@@
 100 and 143 GHz, as these have FWHM of 9.66$'$ and 7.27$'$ respectively.
+% in last sentence, reference Table 1 ?
 
@@
 The following subsections detail the processing steps we have applied to 
-isolate thermal emission from Galactic dust in the \PLANCK~maps and prepare
-these maps for our joint \IRAS/\PLANCK~SED fits.
+isolate Galactic dust emission in the \PLANCK~maps in preparation for our joint
+\PLANCK/\IRAS~SED fits. % reference fitting section at end of this sentence ?
 
@@
 in \PLANCK~857 GHz, but can be perceived at a low level in \PLANCK~545 GHz, and
-are prominent from 100 to 353 GHz relative to the Galactic emission
+are prominent at 100-353 GHz relative to the Galactic emission
 we wish to characterize, especially at high latitudes. To remove the CMB 
@@
 $\nu_i$ due to the CO transition from J=$N$ to J=$(N$$-$1). $I_3$ represents 
-the Type 3 CO amplitude in  K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. The 
-$F_{12CO, \nu_i, N, N-1}$ are conversion factors between K$_{RJ}$ km/s and 
-$K_{CMB}$ for particular band/transition pairs. The relevant values, 
-calculated with the \textit{Unit Conversion and Colour Correction} software 
-utilities (\verb|v1.2|), are:
+the appropriately smoothed Type 3 CO amplitude in  K$_{RJ}$ km/s of 
+J=1$\rightarrow$0 emission. The $F_{12CO, \nu_i, N, N-1}$ are conversion 
+factors between K$_{RJ}$ km/s and $K_{CMB}$ for particular band/transition 
+pairs. The relevant values, calculated with the \textit{Unit Conversion and 
+Colour Correction} software utilities (\verb|v1.2|), are:
 
@@
 higher S/N than the FDS99 prediction, henceforward referred to as 
-$\mathcal{F}_{857}$. Note that $\mathcal{F}_{857}$ is not a monochromatic 
-prediction, as we have incorporated the finite bandpass correction factors 
-described in $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine
-the dust spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels 
-with $\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to 
-degree resolution has very high S/N, we can safely perform such a cut on 
+$\mathcal{F}_{857}$. Note that $\mathcal{F}_{857}$ is not simply the FDS99
+model evaluated at 857 GHz, but also incorporates the color correction factor 
+of $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine the dust 
+spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels with 
+$\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to degree 
+resolution has very high S/N, we can safely perform such a cut on 
 $\mathcal{I}_{857}$. Figure \ref{fig:fdsref} shows a scatterplot of 
@@
 
-The formal statistical errors on these parameters are small. Just as in the 
-case of performing the regression versus  H\,\textsc{i}, systematic problems 
-dominate the uncertainty in the derived zero point offset. The systematics
-likely to dominate our FDS-based zero level are imperfect zodiacal light 
-corrections and the FDS99 temperature map. To quantify the level of systematic 
-error, we split the sky into four quadrants, with the dividing boundaries being
-$b$=0$^{\circ}$ and $l$=0$^{\circ}$, $l$=180$^{\circ}$. We again restricted to
-$\mathcal{I}_{857}$$<$2.15 MJy/sr, and repeated the regression in each 
-quadrant. The slopes varied from 0.948 to 0.993, with an rms of 0.0188, while 
-the offsets varied from $-$0.056 MJy/sr to $+$0.089 MJy/sr, with an rms of 
-0.0586 MJy/sr.
+% i evaluated the `formal statistical error' using the covar keyword in
+% hogg_iter_linfit
+
+The formal statistical error on the best-fit 857 GHz offset is quite small, 
+$\sim$0.002 MJy/sr. The systematics likely to dominate the actual uncertainty 
+on our FDS-based zero level are imperfections in the \PLANCK/\verb|i100| 
+zodiacal light models and the FDS99 temperature map. To quantify these 
+systematic uncertainties, we split the sky into four quadrants, with the 
+dividing boundaries being $b$=0$^{\circ}$ and $l$=0$^{\circ}$, 
+$l$=180$^{\circ}$. We again restricted to $\mathcal{I}_{857}$$<$2.15 MJy/sr, 
+and repeated the regression in each quadrant. The slopes varied from 0.948 to 
+0.993, with an rms of 0.0188, while the offsets varied from $-$0.056 MJy/sr to
+$+$0.089 MJy/sr, with an rms of 0.0586 MJy/sr.
+
+% in previous sentence, think it might be better to only quote rms, and
+% omit the ranges of values for each parameter ?
 
@@
 % and other low order-corrections are negligible at 857 GHz
-
-% actually evaluate the statistical errors !!!!
 

### 2014-05-14 ms.tex
revisions to relative zero level discussion

@@
 the remaining \PLANCK~HFI bands, as well as \verb|i100|. To derive the 
-absolute zero level offsets that must be applied to each of the five
-lowest-frequency \PLANCK~bands, we perform a regression versus the 
-\PLANCK~857 GHz map corrected for the absolute zero level offset derived in
- $\S$\ref{sec:zp_abs}. We assume no offset need be applied
-to \verb|i100|, which has a zero level tied to H\,\textsc{i} by SFD.
-
-The need for additional low-order corrections beyond a simple scalar offset 
+zero level offsets that must be applied to each of the five lowest-frequency 
+\PLANCK~bands, we perform a regression versus the \PLANCK~857 GHz map corrected
+for the absolute zero level offset derived in $\S$\ref{sec:zp_abs}. We assume 
+no offset need be applied to \verb|i100|, which already has its zero level 
+tied to H\,\textsc{i}.
+
+The need for additional low-order corrections beyond simple scalar offsets 
 became evident upon inspecting the HFI maps at 100-545 GHz. In particular, we 
-noticed the presence of a residual dipole pattern, with an orientation 
-consistent with that of the Solar dipole. To most precisely recover the 
-amplitude of the residual dipole, it is necessary to have the highest available
-S/N in the independent variable of our regression. For this reason we have used
-857 GHz as a reference for the 100-545 GHz bands, as opposed to the FDS99 
-predictions or H\,\textsc{i}.
+noticed the presence of a low-level dipole pattern, with an orientation 
+consistent with that of the Solar dipole. Our strategy will be to 
+simultaneously fit the residual dipole and zero-level offset amplitudes. To 
+most precisely recover these amplitudes, it is necessary to have the highest 
+available S/N in the independent variable of our regression. For this reason we
+have used 857 GHz as a reference for the 100-545 GHz bands, as opposed to the 
+FDS99 predictions or H\,\textsc{i} data.
 

### 2014-05-14 ms.tex
more clean-up of low-order correction discussion

@@
 consistent with that of the Solar dipole. Our strategy will be to 
-simultaneously fit the residual dipole and zero-level offset amplitudes. To 
-most precisely recover these amplitudes, it is necessary to have the highest 
+simultaneously fit both the residual dipole and zero-level offset amplitudes. 
+To most precisely recover these amplitudes, it is necessary to have the highest
 available S/N in the independent variable of our regression. For this reason we
@@
 
-We have performed one regression per HFI band to simultaneously fit for the 
+Thus, we perform one regression per HFI band to simultaneously fit for the 
 zero level offset, the slope relative to 857 GHz, and the residual dipole 
@@
 represents the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz 
-assuming they are linearly related. $d$ gives the residual Solar dipole
-amplitude, and its best-fit value represents the scaling of the Solar dipole 
-that makes the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly 
-linear. $b$ represents the constant offset that must be subtracted from the 
-band $\nu_i$ map to make its zero level consistent with that of the 857 GHz 
-map. For each band $\nu_i$, we obtain estimates of $m$, $d$, and $b$ by 
-performing a linear least squares fit with uniform weights and iterative 
-outlier rejection. Figure \ref{fig:dip} shows scatterplots of the band $\nu_i$ 
-versus 857 GHz correlation before and after correcting for the best-fit offset 
-and residual dipole, for each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only 
-are the tightened correlations striking in these scatterplots, but the residual
-dipole subtractions appear very successful in the two-dimensional band $\nu_i$ 
-maps themselves. Before performing thermal dust fits, we therefore subtract the
+assuming they are linearly related. $d$ is the residual Solar dipole amplitude,
+and its best-fit value represents the scaling of the Solar dipole that makes 
+the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly linear. $b$ 
+represents the constant offset that must be subtracted from the band $\nu_i$ 
+map to make its zero level consistent with that of the 857 GHz map. For each 
+band $\nu_i$, we obtain estimates of $m$, $d$, and $b$ by performing a linear 
+least squares fit with uniform weights and iterative outlier rejection. Figure 
+\ref{fig:dip} shows scatterplots of the band $\nu_i$ versus 857 GHz correlation
+ before and after correcting for the best-fit offset and residual dipole, for 
+each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only are the tightened 
+correlations striking in these scatterplots, but the residual dipole 
+subtractions appear very successful in the two-dimensional band $\nu_i$ maps 
+themselves. Before performing thermal dust fits, we therefore subtract the 
 best-fit $b$ and $d\mathcal{D}$ from each band $\nu_i$ map. The best-fit 
@@
 correlation between $\mathcal{I}_{100}$ and $\mathcal{I}_{857}$. However, the 
-scatter plots shown in Figure \ref{fig:quad} make it clear that such a term, 
-with best-fit amplitude $q$=$-7.17$$\times$10$^{-6}$, dramatically improves the
-quality of the linear correlation between the 100 GHz and 857 GHz channels. We 
-tried re-running the fits at 143-545 GHz including the $Q_p$ quadrupole term, 
-but in all cases found the best-fit quadrupole to be negligible, and yield no 
-substantial tightening of the correlation versus 857 GHz.
+scatter plots shown in Figure \ref{fig:quad} make it clear that such a term 
+dramatically improves the quality of the linear correlation between the 100 GHz
+and 857 GHz channels. We tried re-running the fits at 143-545 GHz including the
+$Q_p$ quadrupole term, but in all cases found the best-fit quadrupole to be 
+negligible, and yield no substantial tightening of the correlation versus 857 
+GHz.
 

### 2014-05-15 ms.tex
report only rms values from per-quadrant absolute zero level offset experiment
cite Schlafly+ 2014 PS1 4.5 kpc dust map instead of Green+ methods paper

@@
 estimates based directly upon optical observations of stars
-\citep[e.g.][]{green14} and as a baseline for next-generation dust extinction 
-maps incorporating high-resolution, full-sky infrared data sets such as 
-\WISE~\citep{wright10, meisner14} and \AKARI.
+\citep[e.g.][]{schlafly14} and as a baseline for next-generation dust 
+extinction maps incorporating high-resolution, full-sky infrared data sets such
+as \WISE~\citep{wright10, meisner14} and \AKARI.
 
@@
 $l$=180$^{\circ}$. We again restricted to $\mathcal{I}_{857}$$<$2.15 MJy/sr, 
-and repeated the regression in each quadrant. The slopes varied from 0.948 to 
-0.993, with an rms of 0.0188, while the offsets varied from $-$0.056 MJy/sr to
-$+$0.089 MJy/sr, with an rms of 0.0586 MJy/sr.
+and repeated the regression in each quadrant. The rms of the per-quadrant 
+slopes was found to be 0.0188, while the rms of the per-quadrant offsets was 
+0.0586 MJy/sr.
 

### 2014-05-30 ms.tex
correct best-fit absolute zero level regression result to account for 0.3% bandpass correction fix
propagate change in bandpass corrections to best-fit preprocessing parameters in Table 1

@@
 iterative outlier rejection. The best-fit linear model is given by 
-$\mathcal{F}_{857}$=0.994$\mathcal{I}_{857}$$-$0.018. It is encouraging that 
+$\mathcal{F}_{857}$=0.991$\mathcal{I}_{857}$$-$0.018. It is encouraging that 
 the slope is quite close to unity, and the offset near zero.
@@
     & Offset (MJy/sr) & Dipole (MJy/sr) & Quadrupole (MJy/sr) & & \\ \cline{2-4} \\ [-2ex]
-545 & 7.28$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ & 1.63$\times$10$^{-2}$  & - & 0.10 & 4.84 \\
+545 & 7.27$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ & 1.63$\times$10$^{-2}$  & - & 0.10 & 4.84 \\
 857 & 1.82$\times$10$^{-2}$$\pm$6.02$\times$10$^{-2}$ &  - & - & 0.10 & 4.63 \\

### 2014-05-31 ms.tex
some fix-up of reddening discussion

@@
 objects for which true optical reddening is known. There are various 
-possibilities at our disposal. \cite{planckdust} calibrated their $\tau_{353}$ 
-to $E(B-V)$ using broadband Sloan Digital Sky Survey \citep[SDSS;][]{sdss} 
-photometry for a set of $\sim$10$^5$ quasars. The SFD calibration was 
-originally tied to a sample of 384 elliptical galaxies, but was later revised 
-by \cite{schlafly11} using $\sim$250,000 stars with both spectroscopy and 
-broadband photometry available from SDSS. To calibrate our $\tau_{545}$ to 
-reddening, we make use of the same set of stars studied by \cite{schlafly11}.
+possibilities at our disposal. \cite{planckdust} calibrated their radiance 
+and $\tau_{353}$ maps to $E(B-V)$ using broadband Sloan Digital Sky Survey 
+\citep[SDSS;][]{sdss} photometry for a set of $\sim$10$^5$ quasars. The SFD 
+calibration was originally tied to a sample of 384 elliptical galaxies, but was
+later revised by \cite{schlafly11} using $\sim$250,000 stars with both 
+spectroscopy and broadband photometry available from SDSS. To calibrate our 
+$\tau_{545}$ to reddening, we make use of the same set of stars studied by 
+\cite{schlafly11}.
 
@@
 $g-r$ color predicted from the spectral lines. Applying a color transformation 
-then yields `true' $E(B-V)$ values for $\sim$250,000 lines of sight, mostly at 
-high Galactic latitude. The calibration of two-component optical depth to 
-$E(B-V)$ is then performed as a linear regression of $E(B-V)_{SSPP}$ versus 
-$\tau_{545}$. $\tau_{545}$ is considered to be the independent variable in this
-regression, as we ultimately wish to predict $E(B-V)$ as a function of optical 
-depth, and $\tau_{545}$ has much higher S/N than the SSPP $E(B-V)$ estimates.
+then yields `true' $E(B-V)$ values for $\sim$260,000 lines of sight. Throughout
+our SSPP calibration analysis, we restrict to the $\sim$230,000 lines of sight 
+with $|b|$$>$20$^{\circ}$ in order to avoid stars which may not lie behind the 
+full dust column. The calibration of two-component optical depth to $E(B-V)$ is
+performed as a linear regression of $E(B-V)_{SSPP}$ versus $\tau_{545}$. 
+$\tau_{545}$ is considered to be the independent variable in this regression, 
+as we ultimately wish to predict $E(B-V)$ as a function of optical depth, and 
+$\tau_{545}$ has much higher S/N than the SSPP $E(B-V)$ estimates.
 
@@
 and $\tau_{545}$. The conversion factor from $\tau_{545}$ to $E(B-V)$ is 
-2.41$\times$10$^{3}$. Reassuringly, the best-fit offset is quite close to 
-zero, $\sim$3 mmag.
+2.46$\times$10$^{3}$. Reassuringly, the best-fit offset is quite close to 
+zero, $\sim$0.6 mmag.
 
@@
 \begin{center}
-\epsfig{file=ebv_resid.eps, width=2.5in, angle=90}
+\epsfig{file=ebv_resid.eps, width=3.3in}
 \caption{\label{fig:resid} $E(B-V)_{2comp}$ residuals as a function of

### 2014-06-15 ms.tex
various relatively minor edits

@@
 which we have estimated the spatially varying parameters of our model. In 
-$\S$\ref{sec:ebv} we calibrate our derived optical depth to optical reddening. 
-In $\S$\ref{sec:results} we present the full-sky maps of dust temperature and 
-optical depth we have obtained, and conclude in $\S$\ref{sec:conclusion}.
+$\S$\ref{sec:ebv} we calibrate our derived optical depth to reddening at 
+optical wavelengths. In $\S$\ref{sec:results} we present the full-sky maps of 
+dust temperature and optical depth we have obtained, and conclude in 
+$\S$\ref{sec:conclusion}.
 
@@
 The CMB anisotropies are effectively imperceptible upon visual inspection 
-in \PLANCK~857 GHz, but can be perceived at a low level in \PLANCK~545 GHz, and
+of \PLANCK~857 GHz, but can be perceived at a low level in \PLANCK~545 GHz, and
 are prominent at 100-353 GHz relative to the Galactic emission
@@
 Analysis \citep[SMICA,][]{smica} model from each of the \PLANCK~maps, 
-after applying appropriate unit conversions for the 545 and 857 GHz maps 
-with native units of MJy/sr. Low-order corrections, particularly removal of the
-residual Solar dipole, are discussed in $\S$\ref{sec:zp}.
+applying appropriate unit conversions for the 545 and 857 GHz maps with native 
+units of MJy/sr. Low-order corrections, particularly removal of the residual 
+Solar dipole, are discussed in $\S$\ref{sec:zp}.
 
@@
 
-Specifically, we perform a linear fit to the FDS99-predicted 857 GHz values as 
+We perform a linear fit to the FDS99-predicted 857 GHz values as 
 a function of \PLANCK~857 GHz. For this purpose, we employ a version of the 
@@
 zodiacal light models and the FDS99 temperature map. To quantify these 
-systematic uncertainties, we split the sky into four quadrants, with the 
-dividing boundaries being $b$=0$^{\circ}$ and $l$=0$^{\circ}$, 
-$l$=180$^{\circ}$. We again restricted to $\mathcal{I}_{857}$$<$2.15 MJy/sr, 
-and repeated the regression in each quadrant. The rms of the per-quadrant 
-slopes was found to be 0.0188, while the rms of the per-quadrant offsets was 
-0.0586 MJy/sr.
+systematic uncertainties, we split the sky into four quadrants, with boundaries
+at $b$=0$^{\circ}$ and $l$=0$^{\circ}$, $l$=180$^{\circ}$. We again restricted 
+to $\mathcal{I}_{857}$$<$2.15 MJy/sr, and repeated the regression in each 
+quadrant. The rms of the per-quadrant slopes was found to be 0.0188, while the 
+rms of the per-quadrant offsets was 0.0586 MJy/sr.
 
@@
 \PLANCK~bands, we perform a regression versus the \PLANCK~857 GHz map corrected
-for the absolute zero level offset derived in $\S$\ref{sec:zp_abs}. We assume 
-no offset need be applied to \verb|i100|, which already has its zero level 
-tied to H\,\textsc{i}.
+for the best-fit absolute zero level offset from $\S$\ref{sec:zp_abs}. We 
+assume no offset need be applied to \verb|i100|, which already has its zero 
+level tied to H\,\textsc{i}.
 
@@
 available S/N in the independent variable of our regression. For this reason we
-have used 857 GHz as a reference for the 100-545 GHz bands, as opposed to the 
-FDS99 predictions or H\,\textsc{i} data.
-
-Thus, we perform one regression per HFI band to simultaneously fit for the 
-zero level offset, the slope relative to 857 GHz, and the residual dipole 
-amplitude. For each 100-545 GHz HFI band, we restrict to regions of low column 
-density (H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for $-72$$<$$v_{LSR}$$<$$+25$ 
-km\,s$^{-1}$) and fit the following model:
+have used \PLANCK~857 GHz as a reference for the 100-545 GHz bands, as opposed 
+to the FDS99 predictions or H\,\textsc{i} data. In doing so, we assume
+\PLANCK~857 GHz contains no appreciable Solar dipole residual or other 
+low-order problems. % grammar?
+
+We perform one regression per HFI band (other than 857 GHz) to simultaneously 
+fit for the zero level offset, the slope relative to 857 GHz, and the residual 
+dipole amplitude. For each 100-545 GHz HFI band, we restrict to regions of low 
+column density (H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for 
+$-72$$<$$v_{LSR}$$<$$+25$ km\,s$^{-1}$) and fit the following model:
 
@@
 $1^{\circ}$ resolution. $\mathcal{I}_{\nu_i}$ is the corresponding $1^{\circ}$ 
-resolution \PLANCK~HFI map with zodiacal emission and compact sources removed. 
-In the context of Equation \ref{equ:dip}, $\nu_i \in$  
+resolution \PLANCK~HFI map with zodiacal emission, CMB anisotropies, and
+compact sources removed. In the context of Equation \ref{equ:dip}, $\nu_i \in$ 
 \{100, 143, 217, 353, 545\} GHz. Note that $\mathcal{I}_{\nu_i}$ is always in

### 2014-06-21 ms.tex
new figures illustrating 100 GHz spherical harmonic template correction
swapped out quadrupole equation/discussion with spherical harmonic decompositon equation/discussion

@@
 \begin{center}
-\epsfig{file=dipole_all.eps, width=3.4in}
+\epsfig{file=dipole_all_100.eps, width=3.4in}
 \caption{\label{fig:dip}  Scatter plots of \PLANCK~143, 217, 353, and 545 GHz 
@@
 \begin{center}
-\epsfig{file=quad_100.eps, width=6.5in}
+\epsfig{file=harm_100.eps, width=6.5in}
 \caption{\label{fig:quad} Summary of low-order corrections at 100 GHz.}
@@
 consistent with that of the Solar dipole. Our strategy will be to 
-simultaneously fit both the residual dipole and zero-level offset amplitudes. 
-To most precisely recover these amplitudes, it is necessary to have the highest
-available S/N in the independent variable of our regression. For this reason we
-have used \PLANCK~857 GHz as a reference for the 100-545 GHz bands, as opposed 
-to the FDS99 predictions or H\,\textsc{i} data. In doing so, we assume
-\PLANCK~857 GHz contains no appreciable Solar dipole residual or other 
-low-order problems. % grammar?
+simultaneously fit both this residual dipole and the zero-level offset 
+amplitude for each band. To most precisely recover these amplitudes, it is 
+necessary to have the highest available S/N in the independent variable of our 
+regression. For this reason we have used \PLANCK~857 GHz as a reference for the
+100-545 GHz bands, as opposed to the FDS99 predictions or H\,\textsc{i} data. 
+In doing so, we assume \PLANCK~857 GHz contains no appreciable Solar dipole 
+residual or other low-order problems. % grammar?
 
@@
 
-For \PLANCK~100 GHz, we found an additional low-order correction to be
-necessary (see Figure \ref{fig:quad}). Therefore, for 100 GHz, we performed a 
-modified version of the Equation \ref{equ:dip} fit, using the following model:
-
-\begin{equation} \label{equ:quad}
-\mathcal{I}_{100, p} = m\mathcal{I}_{857, p} + b + d\mathcal{D}_p + qQ_p
-\end{equation}
-
-We will refer to the additional term $qQ_p$ as the ``quadrupole correction''. 
-The shape of the quadrupole template is given by:
-
-\begin{equation}
-Q_p = cos^2(\theta_p)
-\end{equation}
-
-Where $\theta_p$ is the angle of pixel $p$ relative to the Solar velocity 
-vector. It is not clear physically why such a term should improve the 
-correlation between $\mathcal{I}_{100}$ and $\mathcal{I}_{857}$. However, the 
-scatter plots shown in Figure \ref{fig:quad} make it clear that such a term 
-dramatically improves the quality of the linear correlation between the 100 GHz
-and 857 GHz channels. We tried re-running the fits at 143-545 GHz including the
-$Q_p$ quadrupole term, but in all cases found the best-fit quadrupole to be 
-negligible, and yield no substantial tightening of the correlation versus 857 
-GHz.
-
-% worth clarifying that, for quadrupole fit at 100 GHz, we still do the
-% fit with uniform weights and iterative outlier rejection ?
+We found that a dipole correction alone could not sufficiently rectify the 
+\PLANCK~100 GHz map (see Figure \ref{fig:quad}). Therefore, for 100 GHz, we 
+performed a modified version of the Equation \ref{equ:dip} fit, using the 
+following model:
+
+\begin{equation} \label{equ:harm}
+\mathcal{I}_{100, p} = m\mathcal{I}_{857, p} + b + \sum_{l=1}^{4} \sum_{m=-l}^{l} a_{lm}Y_{l}^{m}(\theta_p, \phi_p)
+\end{equation}
+
+Where $Y_{l}^{m}$ are the real spherical harmonics, and the $a_{lm}$ are their 
+corresponding real coefficients. The angle $\phi_p$ is taken simply to be 
+$l_{gal, p}$ and $\theta_p$=$(90^{\circ}-b_{gal, p})$. Thus, we have replaced 
+the Solar dipole term with a sum of 24 spherical harmonic templates, which, 
+when multiplied by the best-fit $a_{lm}$ coefficients and subtracted from 
+\PLANCK~100 GHz make the relation between 100 GHz and 857 GHz most tightly 
+linear. Figure \ref{fig:quad} illustrates the improved correlation of 100 GHz 
+vs. 857 GHz when including the spherical harmonic corrections relative to the 
+dipole-only correction. The spherical harmonic decomposition of Equation 
+\ref{equ:harm} did not improve the correlations at higher frequencies 
+sufficiently to warrant replacing the dipole-only correction in those cases.
 

### 2014-06-21 ms.tex
change name of dipole vs. spherical harmonic correction figure

@@
 \epsfig{file=harm_100.eps, width=6.5in}
-\caption{\label{fig:quad} Summary of low-order corrections at 100 GHz.}
+\caption{\label{fig:harm} Summary of low-order corrections at 100 GHz.}
 \end{center}
@@
 We found that a dipole correction alone could not sufficiently rectify the 
-\PLANCK~100 GHz map (see Figure \ref{fig:quad}). Therefore, for 100 GHz, we 
+\PLANCK~100 GHz map (see Figure \ref{fig:harm}). Therefore, for 100 GHz, we 
 performed a modified version of the Equation \ref{equ:dip} fit, using the 
@@
 \PLANCK~100 GHz make the relation between 100 GHz and 857 GHz most tightly 
-linear. Figure \ref{fig:quad} illustrates the improved correlation of 100 GHz 
+linear. Figure \ref{fig:harm} illustrates the improved correlation of 100 GHz 
 vs. 857 GHz when including the spherical harmonic corrections relative to the 
@@
 consideration due to the sensitivity of the 100 GHz trend to our ad hoc
-low order corrections (see Figure \ref{fig:quad}). All comparisons between
+low order corrections (see Figure \ref{fig:harm}). All comparisons between
 \PLANCK~and the FDS99 predictions were made after smoothing both to 

### 2014-06-22 ms.tex
removed quadrupole column from Table 1

@@
 \tabletypesize{\scriptsize}
-\tablecolumns{6} 
+\tablecolumns{5} 
 \tablewidth{0pc} 
@@
 \colhead{Dipole ($K_{CMB}$)} & 
-\colhead{Quadrupole ($K_{CMB}$)} & 
 \colhead{$c_{\nu}$} &
@@
 \startdata
-100 & 1.69$\times$10$^{-5}$$\pm$3.61$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & $-$7.17$\times$10$^{-6}$ &  0.0054 & 9.66 \\
-143 & 3.58$\times$10$^{-5}$$\pm$7.58$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & - & 0.0054 &  7.27 \\
-217 & 7.79$\times$10$^{-5}$$\pm$2.60$\times$10$^{-6}$ & $-$1.40$\times$10$^{-5}$ & - & 0.0054 &  5.01 \\
-353 & 2.76$\times$10$^{-4}$$\pm$1.95$\times$10$^{-5}$ & $-$3.08$\times$10$^{-5}$ & - & 0.012 & 4.86 \\
-    & Offset (MJy/sr) & Dipole (MJy/sr) & Quadrupole (MJy/sr) & & \\ \cline{2-4} \\ [-2ex]
-545 & 7.27$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ & 1.63$\times$10$^{-2}$  & - & 0.10 & 4.84 \\
-857 & 1.82$\times$10$^{-2}$$\pm$6.02$\times$10$^{-2}$ &  - & - & 0.10 & 4.63 \\
-3000 & 0.0$\pm$4.3$\times$10$^{-2}$ & - & - & 0.10 & 6.1
+100 & 1.69$\times$10$^{-5}$$\pm$3.61$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ &  0.0054 & 9.66 \\
+143 & 3.58$\times$10$^{-5}$$\pm$7.58$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & 0.0054 &  7.27 \\
+217 & 7.79$\times$10$^{-5}$$\pm$2.60$\times$10$^{-6}$ & $-$1.40$\times$10$^{-5}$ & 0.0054 &  5.01 \\
+353 & 2.76$\times$10$^{-4}$$\pm$1.95$\times$10$^{-5}$ & $-$3.08$\times$10$^{-5}$ & 0.012 & 4.86 \\
+    & Offset (MJy/sr) & Dipole (MJy/sr) & & \\ \cline{2-3} \\ [-2ex]
+545 & 7.27$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ & 1.63$\times$10$^{-2}$ & 0.10 & 4.84 \\
+857 & 1.82$\times$10$^{-2}$$\pm$6.02$\times$10$^{-2}$ &  - & 0.10 & 4.63 \\
+3000 & 0.0$\pm$4.3$\times$10$^{-2}$ & - & 0.10 & 6.1
 \enddata

### 2014-06-25 ms.tex
captions for scatter plots illustrating low-order corrections

@@
 \epsfig{file=dipole_all_100.eps, width=3.4in}
-\caption{\label{fig:dip}  Scatter plots of \PLANCK~143, 217, 353, and 545 GHz 
-versus \PLANCK~857 GHz. Left: before correcting for offset and residual Solar 
-dipole. Right: after correcting or the best-fit offset and dipole amplitude, as
-described in $\S$\ref{sec:zp}. The dashed red line shows the best-fit linear 
-relationship in each case.}
+\caption{\label{fig:dip}  Scatter plots of \PLANCK~100, 143, 217, 353, and 545 
+GHz versus \PLANCK~857 GHz. Left: before applying zero-level offsets and 
+additional low-order corrections. Right: after correcting for the best-fit 
+offset and residual Solar dipole (143-545 GHz). 100 GHz is shown after applying
+the spherical harmonic correction of Equation \ref{equ:harm}. The dashed red 
+line shows the best-fit linear relationship in all cases.}
 \end{center}
@@
 \epsfig{file=harm_100.eps, width=6.5in}
-\caption{\label{fig:harm} Summary of low-order corrections at 100 GHz.}
+\caption{\label{fig:harm} Summary of low-order corrections at 100 GHz. Left: 
+prior to our low-order corrections, a $\sim$17$\mu$K zero-level offset is 
+present and strong low-order problems reduce the linearity of the 100 GHz 
+scatter versus 857 GHz. Center: scatter plot versus 857 GHz after applying the 
+best-fit offset and residual Solar dipole corrections derived with Equation 
+\ref{equ:dip} to \PLANCK~100 GHz. The correlation is strengthened, but remains
+far less tight than for 143-545 GHz (see Figure \ref{fig:dip}, top four rows, 
+right column). Right: after applying the spherical harmonic correction of
+Equation \ref{equ:harm} to \PLANCK~100 GHz, the correlation versus 857 GHz is 
+far more tightly linear than following the dipole correction.}
 \end{center}

### 2014-07-04 ms.tex
updated global parameter table values
outlining
more outlining and a bit of reorganizing

@@
 $\S$\ref{sec:ebv} we calibrate our derived optical depth to reddening at 
-optical wavelengths. In $\S$\ref{sec:results} we present the full-sky maps of 
+optical wavelengths. In $\S$\ref{sec:release} we present the full-sky maps of 
 dust temperature and optical depth we have obtained, and conclude in 
@@
  1 & FIRAS+\verb|i100| & 0.0363 & 13.0 & 1.67 & 2.70 \\
- 2 & \PLANCK+\verb|i100| & 0.0267 & 3.68 & 1.19 & 2.61 \\ [-2ex]
+ 2 & \PLANCK+\verb|i100| & 0.0485 & 8.22 & 1.63 & 2.82 \\ [-2ex]
 \enddata
@@
 
-\section{Calibrating to Optical Reddening}
+\subsection{Global Parameters Revisited}
+% discuss goodness of fit tests based on running Markov chains with different
+% sets of global parameters
+
+\section{Optical Reddening}
 \label{sec:ebv}
@@
 optical reddening/extinction is another important application of the 
-$\tau_{545}$ map. We calibrate to reddening empirically rather than derive
-a relationship between $\tau_{545}$ and reddening by introducing additional 
-assumptions about the dust grain physics and size distribution.
+$\tau_{545}$ map.
+
+\subsection{Reddening Calibration Procedure}
 
@@
 
-To achieve this empirical calibration, we must adopt a set of calibrator
-objects for which true optical reddening is known. There are various 
-possibilities at our disposal. \cite{planckdust} calibrated their radiance 
-and $\tau_{353}$ maps to $E(B-V)$ using broadband Sloan Digital Sky Survey 
-\citep[SDSS;][]{sdss} photometry for a set of $\sim$10$^5$ quasars. The SFD 
-calibration was originally tied to a sample of 384 elliptical galaxies, but was
-later revised by \cite{schlafly11} using $\sim$250,000 stars with both 
-spectroscopy and broadband photometry available from SDSS. To calibrate our 
-$\tau_{545}$ to reddening, we make use of the same set of stars studied by 
-\cite{schlafly11}.
+We calibrate to reddening empirically rather than derive
+a relationship between $\tau_{545}$ and reddening by introducing additional 
+assumptions about the dust grain physics and size distribution. To achieve this
+empirical calibration, we must adopt a set of calibrator objects for which true
+optical reddening is known. There are various possibilities at our disposal. 
+\cite{planckdust} calibrated their radiance and $\tau_{353}$ maps to $E(B-V)$ 
+using broadband Sloan Digital Sky Survey \citep[SDSS;][]{sdss} photometry for a
+set of $\sim$10$^5$ quasars. The SFD calibration was originally tied to a 
+sample of 384 elliptical galaxies, but was later revised by \cite{schlafly11} 
+using $\sim$250,000 stars with both spectroscopy and broadband photometry 
+available from SDSS. To calibrate our $\tau_{545}$ to reddening, we make use of
+the same set of stars studied by \cite{schlafly11}.
 
@@
 
+\subsection{Rectifying Reddening Residuals}
+% discuss changing global params and offsets, and ecl plane cut
+
 % should eventually try re-making 2d scatterplot figure in python..
@@
 
-\section{Results}
-\label{sec:results}
-
-\subsection{Data Release}
-We are releasing $N_{side}$=2048 HEALPix maps in Galactic coordinates 
-summarizing the results of of our two-component dust fits.
-
-%at some point in this should make statements re: the fact that in terms
-%of predicting *emission* the conversion to tau is unnecessary and
-%and actually the raw uncertainty on Ghz 545 amplitude is the relevant quantity
-
-%software utilities
-%provide maps at multiple different nsides ?
-%   -> if so, actually smooth the maps before rebinning, or leave 
-%      undersampled?
-% provide uncertainty maps for tau and T2 ??
-
-\subsection{Comparison to Planck Collaboration Dust Map}
+\section{Low-frequency Emission Predictions}
+% compare 100-217 GHz predictions using my model versus Planck Collaboration
+% single-MBB model
+
+% is this the section where, potentially, plots of the residuals might go?
+
 %striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping
@@
 
-\section{Conclusion}
-
-% should mention that one definitive improvement of this work relative
-% to FDS99 is that there are uncertainty/covariances provided for
-% the derived parameters !!!!
-
-\label{sec:conclusion}
+\section{Data Release}
+\label{sec:release}
+We are releasing $N_{side}$=2048 HEALPix maps in Galactic coordinates 
+summarizing the results of of our two-component dust fits.
+
+%at some point in this should make statements re: the fact that in terms
+%of predicting *emission* the conversion to tau is unnecessary and
+%and actually the raw uncertainty on Ghz 545 amplitude is the relevant quantity
+
+%software utilities
+%provide maps at multiple different nsides ?
+%   -> if so, actually smooth the maps before rebinning, or leave 
+%      undersampled?
+% provide uncertainty maps for tau and T2 ??
 
@@
 \end{figure*}
+
+\section{Conclusions}
+\label{sec:conclusion}
+% should mention that one definitive improvement of this work relative
+% to FDS99 is that there are uncertainty/covariances provided for
+% the derived parameters !!!!
 

### 2014-07-04 ms.tex
small changes to global parameters table
complete overhaul of correlation slope global parameters section, overhaul of corresponding table as well

@@
 \subsubsection{Relative Zero Level}
+\label{sec:relzero}
 
@@
 
-\begin{deluxetable}{rrrrrr} 
+\begin{deluxetable*}{llrrrrrrrrrr} 
 \tabletypesize{\scriptsize}
-\tablecolumns{6} 
+\tablecolumns{11} 
 \tablewidth{0pc} 
@@
 \tablehead{
+\colhead{Number} &
 \colhead{Model} &
-\colhead{Data} &
 \colhead{$f_1$} &
@@
 \colhead{$\beta_1$} & 
-\colhead{$\beta_2$}
+\colhead{$\beta_2$} &
+\colhead{$T_2$} &
+\colhead{$T_1$} &
+\colhead{$n$} &
+\colhead{D.O.F.} &
+\colhead{$\chi^2$} &
+\colhead{$\chi^2_{\nu}$}
 }
 \startdata
- 1 & FIRAS+\verb|i100| & 0.0363 & 13.0 & 1.67 & 2.70 \\
- 2 & \PLANCK+\verb|i100| & 0.0485 & 8.22 & 1.63 & 2.82 \\ [-2ex]
+ 1 & FDS99 best-fit  & 0.0363 & 13.0  & 1.67 & 2.70 & 15.72 &  9.15 & 1.018 & 7 & 23.9 & 3.41 \\
+ 2 & FDS99 general   & 0.0485 & 8.22  & 1.63 & 2.82 & 15.70 &  9.75 & 0.980 & 3 & 3.99 & 1.33 \\
+ 3 & single MBB      &  1.0   &  ...  & 1.59 &  ... &  ...  & 19.63 & 0.999 & 6 & 33.9 & 5.65 \\ [-2ex]
 \enddata
-\end{deluxetable}
+\end{deluxetable*}
 
@@
 
-In light of the \PLANCK~HFI data, it is possible to revisit the best-fit global
-parameters of the two-component emission model. To derive the 
-\{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} that best represent the \PLANCK~HFI
-maps, we employed a correlation slope analysis (see Figure XX). Specifically,
-we correlated the observed \PLANCK~data against the appropriate FDS99 
-prediction for each HFI band from 143-857 GHz. We omitted 100 GHz from 
-consideration due to the sensitivity of the 100 GHz trend to our ad hoc
-low order corrections (see Figure \ref{fig:harm}). All comparisons between
-\PLANCK~and the FDS99 predictions were made after smoothing both to 
-$1^{\circ}$, subtracting the SMICA CMB model, and ignoring SMICA inpainted 
-pixels. For 100-857 GHz, the linearity between the FDS and \PLANCK~is
-excellent.
+FDS99 determined the best-fit values of the two-component model global 
+parameters $\beta_1$, $\beta_2$, $q_1/q_2$ and $f_1$ via a correlation slope
+analysis incorporating DIRBE and FIRAS data. In this section, we seek to 
+perform a correlation slope determination of these same global parameters, but
+swapping the \PLANCK~HFI maps for FIRAS at low frequencies, while still 
+relying on DIRBE at higher frequencies. We also seek to determine via this
+correlation slope analysis whether or not the combination of \PLANCK+DIRBE data
+favors two-component models over single-MBB models in the same way that the
+FIRAS+DIRBE data did in the FDS99 analysis.
+
+In the two-component model case, we wish to obtain estimates for six 
+free parameters: $\beta_1$, $\beta_2$, $q_1/q_2$, $f_1$, $T_2$ and the overall 
+spectrum normalization $n$. The constraints employ are the correlation
+slopes of each of the \PLANCK~HFI bands, as well as DIRBE 100$\mu$m (3000 GHz),
+140$\mu$m (2141 GHz) and 240$\mu$m (1250 GHz) against \PLANCK~857 GHz. We will 
+refer to the slope for band $\nu_i$ as $s_{i,857}$. All of the correlations are
+performed using $1^{\circ}$ smoothed maps. The slopes for \PLANCK~100-545 GHz 
+are taken to be those from the relative zero level fits of 
+\ref{sec:relzero}, and are illustrated by the dashed red lines in plots of 
+Figure \ref{fig:dip}, right column. The 857 GHz slope is taken to be unity by 
+definition. We use the SFD98 reprocessings of the DIRBE bands. Including 857 
+GHz, we thus have 9 correlation slope constraints for six free parameters. 
+Including DIRBE 140$\mu$m and 240$\mu$m is critical in making this problem 
+sufficiently constrained, and also in providing information near the peak of 
+the dust SED at $\sim$140$\mu$m, which is particularly sensitive to the 
+presence of a single versus multiple MBB components. % last sentence mentioning
+% that the large number of frequency channels and good coverage of the 
+% dust SED peak were what made FIRAS so appropriate for FDS99 analysis ??
+
+We assume an uncertainty of 2\% on each of the 9 correlation slopes and
+minimize the $\chi^2$ given by:
+
+% hmm it's really seeming like I need to move the color correction section
+% to be before this, because I need the \tilde{I} things in this equation
+
+\begin{equation}
+\chi^2 = \sum_{i=0}^{8}\frac{(s_{i, 857}-n\tilde{I}_{\nu_i}/\tilde{I}_{857})^2}{\sigma_{s}^2}
+\end{equation}
+
+%In light of the \PLANCK~HFI data, it is possible to revisit the best-fit 
+%global parameters of the two-component emission model. To derive the 
+%\{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} that best represent the \PLANCK~HFI
+%maps, we employed a correlation slope analysis (see Figure XX). Specifically,
+%we correlated the observed \PLANCK~data against the appropriate FDS99 
+%prediction for each HFI band from 143-857 GHz. We omitted 100 GHz from 
+%consideration due to the sensitivity of the 100 GHz trend to our ad hoc
+%low order corrections (see Figure \ref{fig:harm}). All comparisons between
+%\PLANCK~and the FDS99 predictions were made after smoothing both to 
+%$1^{\circ}$, subtracting the SMICA CMB model, and ignoring SMICA inpainted 
+%pixels. For 100-857 GHz, the linearity between the FDS and \PLANCK~is
+%excellent.
 
@@
 
-However, the slopes at low frequencies are not precisely unity, as would
-be expected if the global two-component parameters derived from FIRAS by
-FDS99 were also the best-fitting global parameters with respect to the 
-\PLANCK~data set.
+%However, the slopes at low frequencies are not precisely unity, as would
+%be expected if the global two-component parameters derived from FIRAS by
+%FDS99 were also the best-fitting global parameters with respect to the 
+%\PLANCK~data set.
 
@@
 
-We then derive \{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} as constrained by 
-the correlation slopes and their uncertainties given in Table QQ by 
-taking $T_2$=$16.2$K and running Markov chains to sample the posterior:
-
-Figure ZZ shows a corner plot of the 150,000 samples. Clearly, there are
-strong covariances, but even so several conclusions are clear: (1) a lower 
-value of $q_1/q_2$ is favored by the \PLANCK~data than by the FIRAS data (2) 
-the best-fit emissivity power law index of the hot dust component ($\beta_2$) 
-is effectively identical to that found by FDS99 to within uncertainties and (3)
-a somewhat lower $\beta_1$ is favored by \PLANCK~than by FIRAS, meaning the
-\PLANCK-based SED is shallower toward the millimeter. Because $f_1$ is so 
-strongly covariant with $\beta_1$, the difference of $f_1$ between the 
-\PLANCK~and FIRAS best fits is not particularly significant.
+%We then derive \{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} as constrained by 
+%the correlation slopes and their uncertainties given in Table QQ by 
+%taking $T_2$=$16.2$K and running Markov chains to sample the posterior:
+
+%Figure ZZ shows a corner plot of the 150,000 samples. Clearly, there are
+%strong covariances, but even so several conclusions are clear: (1) a lower 
+%value of $q_1/q_2$ is favored by the \PLANCK~data than by the FIRAS data (2) 
+%the best-fit emissivity power law index of the hot dust component ($\beta_2$) 
+%is effectively identical to that found by FDS99 to within uncertainties and 
+%(3)
+%a somewhat lower $\beta_1$ is favored by \PLANCK~than by FIRAS, meaning the
+%\PLANCK-based SED is shallower toward the millimeter. Because $f_1$ is so 
+%strongly covariant with $\beta_1$, the difference of $f_1$ between the 
+%\PLANCK~and FIRAS best fits is not particularly significant.
 
@@
 
-The MCMC fitting procedure described in $\S$\ref{sec:fitting} is performed
-separately for both model 1 (FIRAS+\verb|i100|) and model 2 
-(\PLANCK+\verb|i100|), each defined by their respective global parameters 
-listed in Table \ref{tab:global}.
+%The MCMC fitting procedure described in $\S$\ref{sec:fitting} is performed
+%separately for both model 1 (FIRAS+\verb|i100|) and model 2 
+%(\PLANCK+\verb|i100|), each defined by their respective global parameters 
+%listed in Table \ref{tab:global}.
 

### 2014-07-04 ms.tex
major fix-up of correlation slope discussion

@@
 global dust properties, and fit additional parameters of the two-component 
-model as a function of position on the sky.
+model as a function of position on the sky. % in this last sentence
+% reference the relevant sections for each sub-goal mentioned
 
@@
 parameters $\beta_1$, $\beta_2$, $q_1/q_2$ and $f_1$ via a correlation slope
-analysis incorporating DIRBE and FIRAS data. In this section, we seek to 
-perform a correlation slope determination of these same global parameters, but
-swapping the \PLANCK~HFI maps for FIRAS at low frequencies, while still 
-relying on DIRBE at higher frequencies. We also seek to determine via this
-correlation slope analysis whether or not the combination of \PLANCK+DIRBE data
-favors two-component models over single-MBB models in the same way that the
+analysis incorporating DIRBE and FIRAS data. Here we seek to estimate these 
+same global parameters via an analogous correlation slope analysis in which we 
+swap the \PLANCK~HFI maps for FIRAS at low frequencies, while still relying on 
+DIRBE at higher frequencies. We also seek to determine via this correlation 
+slope analysis whether or not the combination of \PLANCK+DIRBE data favors 
+two-component models over single-MBB models in the same way that the 
 FIRAS+DIRBE data did in the FDS99 analysis.
 
-In the two-component model case, we wish to obtain estimates for six 
-free parameters: $\beta_1$, $\beta_2$, $q_1/q_2$, $f_1$, $T_2$ and the overall 
-spectrum normalization $n$. The constraints employ are the correlation
-slopes of each of the \PLANCK~HFI bands, as well as DIRBE 100$\mu$m (3000 GHz),
-140$\mu$m (2141 GHz) and 240$\mu$m (1250 GHz) against \PLANCK~857 GHz. We will 
-refer to the slope for band $\nu_i$ as $s_{i,857}$. All of the correlations are
-performed using $1^{\circ}$ smoothed maps. The slopes for \PLANCK~100-545 GHz 
-are taken to be those from the relative zero level fits of 
-\ref{sec:relzero}, and are illustrated by the dashed red lines in plots of 
-Figure \ref{fig:dip}, right column. The 857 GHz slope is taken to be unity by 
-definition. We use the SFD98 reprocessings of the DIRBE bands. Including 857 
-GHz, we thus have 9 correlation slope constraints for six free parameters. 
-Including DIRBE 140$\mu$m and 240$\mu$m is critical in making this problem 
-sufficiently constrained, and also in providing information near the peak of 
-the dust SED at $\sim$140$\mu$m, which is particularly sensitive to the 
-presence of a single versus multiple MBB components. % last sentence mentioning
+In the case of the two-component model, based on a spectrum of \PLANCK~and 
+DIRBE correlations slopes, we wish to obtain estimates for six free parameters:
+$\beta_1$, $\beta_2$, $q_1/q_2$, $f_1$, $T_2$ and the overall spectrum 
+normalization $n$. The constraints we employ are the correlation slopes of each
+of the \PLANCK~HFI bands, as well as DIRBE 100$\mu$m (3000 GHz), 140$\mu$m 
+(2141 GHz) and 240$\mu$m (1250 GHz) relative \PLANCK~857 GHz, with 
+\PLANCK~857 GHz considered the independent variable. We will refer to the slope
+for band $\nu_i$ as $s_{i,857}$. All of the correlations are performed using 
+$1^{\circ}$ smoothed maps. The slopes for \PLANCK~100-545 GHz are taken to be 
+those from the relative zero level fits of \ref{sec:relzero}, and are 
+illustrated by the dashed red lines in plots of Figure \ref{fig:dip}, right 
+column. The 857 GHz slope is taken to be unity by definition. We use the SFD98 
+reprocessings of the DIRBE bands. Including 857 GHz, we thus have nine 
+correlation slope constraints for six free parameters. Including DIRBE 
+140$\mu$m and 240$\mu$m is critical in making this problem sufficiently 
+constrained, and also in providing information near the peak of the dust SED at
+$\sim$140$\mu$m, which is particularly sensitive to the presence of a single 
+versus multiple MBB components. % last sentence mentioning
 % that the large number of frequency channels and good coverage of the 

### 2014-07-04 ms.tex
trying to fix up presentation of chi-squared equation
clarifying notation for single-MBB case

@@
  2 & FDS99 general   & 0.0485 & 8.22  & 1.63 & 2.82 & 15.70 &  9.75 & 0.980 & 3 & 3.99 & 1.33 \\
- 3 & single MBB      &  1.0   &  ...  & 1.59 &  ... &  ...  & 19.63 & 0.999 & 6 & 33.9 & 5.65 \\ [-2ex]
+ 3 & single MBB      &  0.0   &  ...  &  ... & 1.59 & 19.63 &   ... & 0.999 & 6 & 33.9 & 5.65 \\ [-2ex]
 \enddata
@@
 
-We assume an uncertainty of 2\% on each of the 9 correlation slopes and
-minimize the $\chi^2$ given by:
+We assume an uncertainty of 2\% on each of the $s_{i, 857}$ and minimize the 
+chi-squared given by:
 
@@
 
-\begin{equation}
-\chi^2 = \sum_{i=0}^{8}\frac{(s_{i, 857}-n\tilde{I}_{\nu_i}/\tilde{I}_{857})^2}{\sigma_{s}^2}
-\end{equation}
+\begin{equation} \label{equ:chi2corr}
+\chi^2 = \sum_{i=0}^{8}\frac{\big[s_{i, 857}-n\frac{\tilde{I}_{\nu_i}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}{\tilde{I}_{857}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}\big]^2}{\sigma_{s}^2}
+\end{equation}
+
+Where $\nu_i$$\in$\{100, 143, 217, 353, 545, 857, 1250, 2141, 3000\} GHz. Note 
+that this formula encompasses the general two-component case. In the single-MBB
+case, we take $f_1$=0 and hence $q_1/q_2$, $\beta_1$ and $T_1$ are immaterial, 
+but Equation \ref{equ:chi2corr} still applies.
 

### 2014-07-05 ms.tex
removed a bunch of outdated/unnecessary stuff
re-organized with respect to the placement of color correction discussion

@@
 
+\section{Predicting the Observed SED}
+\label{sec:bpcorr}
+
+The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
+flux density per solid angle $M_{\nu}$ in e.g. MJy/sr for any single frequency 
+$\nu$. In practice, however, we wish to constrain our model using measurements 
+in the broad \verb|i100|/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. 
+Both the \PLANCK~data and DIRBE data products quote flux density per solid 
+angle in MJy/sr under the `IRAS convention'. More precisely, each value 
+reported in the \PLANCK~maps gives the amplitude of a power-law spectrum 
+with $\alpha$=$-1$, evaluated at the nominal band center frequency, such that 
+this spectrum integrated against the transmission reproduces the 
+bolometer-measured power. Because our model spectra do not conform to the 
+$\alpha$=$-1$ convention, we have computed color correction factors to account 
+for the MBB($T$, $\beta$) spectral shape and the transmission as a function of 
+frequency:
+
+% is delta(nu)/nu conventionally (nu_off-nu_on)/nu_c or 1/2 of that ?
+
+\begin{equation} \label{equ:bpcorr}
+b_{\nu_i}(T, \beta) = \frac{\int \nu^{\beta}B_{\nu}(T)\mathcal{T}_{\nu_i}(\nu) d\nu \bigg[\int (\nu_{i,c}/\nu)\mathcal{T}_{\nu_i}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
+\end{equation}
+
+% integral limits ??? check planck paper to see what they did
+% -> planck spectral response paper just leaves the integrals indefinite
+
+Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
+$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 2997.92458\} GHz. 
+$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
+of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
+given by the \PLANCK~transmission curves provided in the file 
+\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. The color correction factors
+of Equation \ref{equ:bpcorr} are applied in the sense that 
+$b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ is a prediction suitable for 
+direct comparison to the \PLANCK~data products.
+
+For 3000 GHz, we have adopted the DIRBE transmission curve. Since DIRBE-quoted
+fluxes also follow the $\alpha$=$-1$ convention, Equation \ref{equ:bpcorr}
+remains applicable.
+
+The two-component model prediction in band $\nu_i$ under the IRAS convention, 
+termed $\tilde{I}_{\nu_i}$, is then constructed as a linear combination of 
+color-corrected MBB terms:
+
+\begin{equation} \label{equ:iras}
+\tilde{I}_{\nu_i} \propto \sum_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k)
+\end{equation}
+
+Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. Our color correction 
+approach allows us to predict $\tilde{I}_{\nu_i}$ by computing monochromatic 
+flux densities at the central frequency $\nu_{i,c}$ and then multiplying by 
+factors $b_{\nu_i}(T, \beta)$ which are interpolated off of a set of 
+precomputed, one-dimensional lookup tables each listing $b_{\nu_i}(T, \beta)$ 
+as a function of $T$. We avoided the need to interpolate in both $\beta$ and 
+$T$ by computing only a small set of one dimensional correction factors for the
+particular set of $\beta$ values of interest 
+($\beta \in$ \{1.67, 2.7, 1.19, 2.61\}, see Table \ref{tab:global}).
+
+% need some sort of clarification about the fact that, in the parts of the 
+% analysis where beta floats, this precomputation/interpolation is NOT 
+% what we do
+
+This color correction approach makes the MCMC sampling described in 
+$\S$\ref{sec:mcmc} much more computationally efficient by circumventing the 
+need to perform the integral in the numerator of Equation \ref{equ:bpcorr} 
+on-the-fly for each proposed dust temperature. We have chosen to compute the 
+color corrections on a per-MBB basis because this approach is very 
+versatile; all possible two-component models are linear combinations of MBBs, 
+so we can apply all of our color correction machinery even when we allow 
+parameters other than temperature (e.g. $f_1$) to vary and thereby change the 
+dust spectrum shape.
+
+% We note that it is not clear which bandpass should properly be ascribed to 
+% the \IRAS/DIRBE composite 100$\mu$m maps under consideration.
+
+With these color corrections and the  formalism established in 
+$\S$\ref{sec:modeling} in hand, we can mathematically state the model we will 
+use e.g. during MCMC sampling to predict the observed SED, which we will 
+denote by \{$\tilde{I}_{\nu_i}$\}. The predicted observations are given by:
+
+\begin{equation}
+\label{eqn:inten}
+\tilde{I}_{\nu_i} = \frac{\sum\limits_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k) u_{\nu_i}^{-1}(T_k, \beta_k)}{\sum\limits_{k=1}^{2} b_{545}(T_k, \beta_k) f_k q_k (545 \textrm{GHz}/\nu_0)^{\beta_k} B_{545}(T_k)}\tilde{I}_{545}
+\end{equation}
+
+This equation is quite similar to Equation \ref{equ:iras}, but with two 
+important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
+specified by $\tilde{I}_{545}$, which represents the flux density per solid
+angle measured in the \PLANCK~545 GHz band. The denominator serves to ensure 
+that, for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. 
+Second, each term in the numerator is multiplied by a conversion factor 
+$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
+\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
+remaining maps (545-3000 GHz) have units of MJy/sr. We have adopted the 
+strategy of predicting each band in its native units, whether MJy/sr or 
+$K_{CMB}$. For this reason, we always evaluate $B_{\nu_{i,c}}$ in Equation 
+\ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for 
+$\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
+represents the conversion factor from $K_{CMB}$ to MJy/sr, given by 
+\cite{planckresponse} Equation 32.
+
+%is the old sentence below worth reinstating ?
+
+%To reiterate, for 
+%$\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ has units of 
+%(MJy/sr)/$K_{CMB}$,and therefore $\tilde{I}_{\nu_{i}}$ will have different 
+%units depending on the band $\nu_i$, though $\tilde{I}_{\nu_{i}}$ always has 
+%the same units as the native band $\nu_i$ map.
+
+% check that RIMO file i've used is actually the most up-to-date version
+
 \section{Global Model Parameters}
@@
 
-%In light of the \PLANCK~HFI data, it is possible to revisit the best-fit 
-%global parameters of the two-component emission model. To derive the 
-%\{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} that best represent the \PLANCK~HFI
-%maps, we employed a correlation slope analysis (see Figure XX). Specifically,
-%we correlated the observed \PLANCK~data against the appropriate FDS99 
-%prediction for each HFI band from 143-857 GHz. We omitted 100 GHz from 
-%consideration due to the sensitivity of the 100 GHz trend to our ad hoc
-%low order corrections (see Figure \ref{fig:harm}). All comparisons between
-%\PLANCK~and the FDS99 predictions were made after smoothing both to 
-%$1^{\circ}$, subtracting the SMICA CMB model, and ignoring SMICA inpainted 
-%pixels. For 100-857 GHz, the linearity between the FDS and \PLANCK~is
-%excellent.
-
-%also emphasize that FDS99 predictions are broadband, not monochromatic
-% (i think i can borrow a sentence about this from the absolute zero point 
-% section above)
-
-%However, the slopes at low frequencies are not precisely unity, as would
-%be expected if the global two-component parameters derived from FIRAS by
-%FDS99 were also the best-fitting global parameters with respect to the 
-%\PLANCK~data set.
+%All comparisons between %\PLANCK~and the FDS99 predictions were made after 
+%smoothing both to $1^{\circ}$, subtracting the SMICA CMB model, and ignoring 
+%SMICA inpainted pixels. For 100-857 GHz, the linearity between the FDS and 
+%\PLANCK~is excellent.
 
@@
 % would be useful here
-
-%We then derive \{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} as constrained by 
-%the correlation slopes and their uncertainties given in Table QQ by 
-%taking $T_2$=$16.2$K and running Markov chains to sample the posterior:
-
-%Figure ZZ shows a corner plot of the 150,000 samples. Clearly, there are
-%strong covariances, but even so several conclusions are clear: (1) a lower 
-%value of $q_1/q_2$ is favored by the \PLANCK~data than by the FIRAS data (2) 
-%the best-fit emissivity power law index of the hot dust component ($\beta_2$) 
-%is effectively identical to that found by FDS99 to within uncertainties and 
-%(3)
-%a somewhat lower $\beta_1$ is favored by \PLANCK~than by FIRAS, meaning the
-%\PLANCK-based SED is shallower toward the millimeter. Because $f_1$ is so 
-%strongly covariant with $\beta_1$, the difference of $f_1$ between the 
-%\PLANCK~and FIRAS best fits is not particularly significant.
-
-% actually quantitatively assess, for a typical temperature (and frequency?)
-% how the new f_1 value basically balances out the change in beta_1 ???
-
-%The MCMC fitting procedure described in $\S$\ref{sec:fitting} is performed
-%separately for both model 1 (FIRAS+\verb|i100|) and model 2 
-%(\PLANCK+\verb|i100|), each defined by their respective global parameters 
-%listed in Table \ref{tab:global}.
-
-% does this statement accidentally give the impression that I do separate 
-% MCMC fits, one in which i fit Planck/IRAS **data** and one in which
-% i fit FIRAS/IRAS data ????
-
-% multi-panel figure showing more scatterplots of Planck vs. FDS predictions
-
-%\subsection{Hierarchical Approach?}
 
@@
 spatial pixel independently.
-
-\subsection{Color Correction}
-\label{sec:bpcorr}
-The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
-flux density per solid angle $M_{\nu}$ in e.g. MJy/sr for any single frequency 
-$\nu$. In practice, however, we wish to constrain our model using measurements 
-in the broad \verb|i100|/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. 
-The \PLANCK~data products quote flux density per solid angle in MJy/sr under 
-the `IRAS convention'. More precisely, each value reported in the \PLANCK~maps 
-gives the amplitude of a power-law spectrum with $\alpha$=$-1$, evaluated at 
-the nominal band center frequency, such that this spectrum integrated against 
-the transmission reproduces the bolometer-measured power. Because our model 
-spectra do not conform to the $\alpha$=$-1$ convention, we have computed color 
-correction factors to account for the MBB($T$, $\beta$) spectral shape and the 
-transmission as a function of frequency:
-
-% is delta(nu)/nu conventionally (nu_off-nu_on)/nu_c or 1/2 of that ?
-
-\begin{equation} \label{equ:bpcorr}
-b_{\nu_i}(T, \beta) = \frac{\int \nu^{\beta}B_{\nu}(T)\mathcal{T}_{\nu_i}(\nu) d\nu \bigg[\int (\nu_{i,c}/\nu)\mathcal{T}_{\nu_i}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
-\end{equation}
-
-% integral limits ??? check planck paper to see what they did
-% -> planck spectral response paper just leaves the integrals indefinite
-
-Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
-$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 2997.92458\} GHz. 
-$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
-of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
-given by the \PLANCK~transmission curves provided in the file 
-\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. The color correction factors
-of Equation \ref{equ:bpcorr} are applied in the sense that 
-$b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ is a prediction suitable for 
-direct comparison to the \PLANCK~data products.
-
-For 3000 GHz, we have adopted the DIRBE transmission curve. Since DIRBE-quoted
-fluxes also follow the $\alpha$=$-1$ convention, Equation \ref{equ:bpcorr}
-remains applicable.
-
-The two-component model prediction in band $\nu_i$ under the IRAS convention, 
-termed $\tilde{I}_{\nu_i}$, is then constructed as a linear combination of 
-color-corrected MBB terms:
-
-\begin{equation} \label{equ:iras}
-\tilde{I}_{\nu_i} \propto \sum_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k)
-\end{equation}
-
-Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. Our color correction 
-approach allows us to predict $\tilde{I}_{\nu_i}$ by computing monochromatic 
-flux densities at the central frequency $\nu_{i,c}$ and then multiplying by 
-factors $b_{\nu_i}(T, \beta)$ which are interpolated off of a set of 
-precomputed, one-dimensional lookup tables each listing $b_{\nu_i}(T, \beta)$ 
-as a function of $T$. We avoided the need to interpolate in both $\beta$ and 
-$T$ by computing only a small set of one dimensional correction factors for the
-particular set of $\beta$ values of interest 
-($\beta \in$ \{1.67, 2.7, 1.19, 2.61\}, see Table \ref{tab:global}).
-
-% need some sort of clarification about the fact that, in the parts of the 
-% analysis where beta floats, this precomputation/interpolation is NOT 
-% what we do
-
-This color correction approach makes the MCMC sampling described in 
-$\S$\ref{sec:mcmc} much more computationally efficient by circumventing the 
-need to perform the integral in the numerator of Equation \ref{equ:bpcorr} 
-on-the-fly for each proposed dust temperature. We have chosen to compute the 
-color corrections on a per-MBB basis because this approach is very 
-versatile; all possible two-component models are linear combinations of MBBs, 
-so we can apply all of our color correction machinery even when we allow 
-parameters other than temperature (e.g. $f_1$) to vary and thereby change the 
-dust spectrum shape.
-
-% We note that it is not clear which bandpass should properly be ascribed to 
-% the \IRAS/DIRBE composite 100$\mu$m maps under consideration.
-
-\subsection{Predicting the Observed SED}
-With the formalism established in $\S$\ref{sec:modeling} and 
-$\S$\ref{sec:bpcorr}, we can mathematically state the model we will use during 
-MCMC sampling to predict the observed SED, which we will denote by 
-\{$\tilde{I}_{\nu_i}$\}. The predicted observations are given by:
-
-\begin{equation}
-\label{eqn:inten}
-\tilde{I}_{\nu_i} = \frac{\sum\limits_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k) u_{\nu_i}^{-1}(T_k, \beta_k)}{\sum\limits_{k=1}^{2} b_{545}(T_k, \beta_k) f_k q_k (545 \textrm{GHz}/\nu_0)^{\beta_k} B_{545}(T_k)}\tilde{I}_{545}
-\end{equation}
-
-This equation is quite similar to Equation \ref{equ:iras}, but with two 
-important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
-specified by $\tilde{I}_{545}$, which represents the flux density per solid
-angle measured in the \PLANCK~545 GHz band. The denominator serves to ensure 
-that, for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. 
-Second, each term in the numerator is multiplied by a conversion factor 
-$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
-\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
-remaining maps (545-3000 GHz) have units of MJy/sr. We have adopted the 
-strategy of predicting each band in its native units, whether MJy/sr or 
-$K_{CMB}$. For this reason, we always evaluate $B_{\nu_{i,c}}$ in Equation 
-\ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for 
-$\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
-represents the conversion factor from $K_{CMB}$ to MJy/sr, given by 
-\cite{planckresponse} Equation 32.
-
-%is the old sentence below worth reinstating ?
-
-%To reiterate, for 
-%$\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ has units of 
-%(MJy/sr)/$K_{CMB}$,and therefore $\tilde{I}_{\nu_{i}}$ will have different 
-%units depending on the band $\nu_i$, though $\tilde{I}_{\nu_{i}}$ always has 
-%the same units as the native band $\nu_i$ map.
-
-% check that RIMO file i've used is actually the most up-to-date version
 

### 2014-07-05 ms.tex
trying to clean up color correction section to reflect the introduction of additional DIRBE bands and single-MBB fits into the analysis

@@
 $\nu$. In practice, however, we wish to constrain our model using measurements 
-in the broad \verb|i100|/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. 
-Both the \PLANCK~data and DIRBE data products quote flux density per solid 
+in the broad DIRBE/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. 
+Both the \PLANCK~and DIRBE data products quote flux density per solid 
 angle in MJy/sr under the `IRAS convention'. More precisely, each value 
@@
 Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
-$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 2997.92458\} GHz. 
-$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
-of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
-given by the \PLANCK~transmission curves provided in the file 
-\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. The color correction factors
-of Equation \ref{equ:bpcorr} are applied in the sense that 
-$b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ is a prediction suitable for 
-direct comparison to the \PLANCK~data products.
-
-For 3000 GHz, we have adopted the DIRBE transmission curve. Since DIRBE-quoted
-fluxes also follow the $\alpha$=$-1$ convention, Equation \ref{equ:bpcorr}
-remains applicable.
+$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 1249.1352, 2141.3747, 
+2997.92458\} GHz. $\mathcal{T}_{\nu_i}(\nu)$ represents the relative 
+transmission as a function of frequency for band $\nu_i$. For the HFI maps, 
+$\mathcal{T}_{\nu_i}(\nu)$ is given by the \PLANCK~transmission curves provided
+in the file \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz and
+DIRBE 140$\mu$m, 240$\mu$m, we have adopted the corresponding DIRBE 
+transmission curves. Again, since DIRBE-quoted fluxes also follow the 
+$\alpha$=$-1$ convention, Equation \ref{equ:bpcorr} remains applicable.
+
+% what is the reference for the dirbe
+
+%The color correction factors
+%of Equation \ref{equ:bpcorr} are applied in the sense that 
+%$b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ is a prediction suitable for 
+%direct comparison to the \PLANCK~data products.
 
@@
 $T$ by computing only a small set of one dimensional correction factors for the
-particular set of $\beta$ values of interest 
-($\beta \in$ \{1.67, 2.7, 1.19, 2.61\}, see Table \ref{tab:global}).
+particular set of $\beta$ values of interest (e.g. $\beta$=1.67, 2.7, 
+1.63, 2.82 ..., see Table \ref{tab:global}).
 
 % need some sort of clarification about the fact that, in the parts of the 
-% analysis where beta floats, this precomputation/interpolation is NOT 
-% what we do
+% analysis where beta floats, i actually do interpolate color corrections 
+% off of a 2d grid in (T, beta)
 
@@
 color corrections on a per-MBB basis because this approach is very 
-versatile; all possible two-component models are linear combinations of MBBs, 
-so we can apply all of our color correction machinery even when we allow 
-parameters other than temperature (e.g. $f_1$) to vary and thereby change the 
-dust spectrum shape.
+versatile; all possible two-component (and single-MBB) models are linear 
+combinations of MBBs, so we can apply all of our color correction machinery 
+even when we allow parameters other than temperature (e.g. $f_1$) to vary and 
+thereby modify the dust spectrum shape.
 
@@
 
+% extremely abrupt transition here...
 \section{Global Model Parameters}

### 2014-07-05 ms.tex
transition sentence/paragraph between color correction section and global parameter discussion
still working on DIRBE discussion in correlation slope section

@@
 
+While we ultimately aim to obtain \PLANCK-resolution maps of the spatially 
+varying dust temperature and optical depth, we start by applying the 
+machinery/formalism thus far developed to reassess the best-fit global 
+two-component model parameters in light of the \PLANCK~HFI data.
+
 FDS99 determined the best-fit values of the two-component model global 
@@
 of the \PLANCK~HFI bands, as well as DIRBE 100$\mu$m (3000 GHz), 140$\mu$m 
-(2141 GHz) and 240$\mu$m (1250 GHz) relative \PLANCK~857 GHz, with 
-\PLANCK~857 GHz considered the independent variable. We will refer to the slope
-for band $\nu_i$ as $s_{i,857}$. All of the correlations are performed using 
-$1^{\circ}$ smoothed maps. The slopes for \PLANCK~100-545 GHz are taken to be 
-those from the relative zero level fits of \ref{sec:relzero}, and are 
-illustrated by the dashed red lines in plots of Figure \ref{fig:dip}, right 
-column. The 857 GHz slope is taken to be unity by definition. We use the SFD98 
-reprocessings of the DIRBE bands. Including 857 GHz, we thus have nine 
-correlation slope constraints for six free parameters. Including DIRBE 
-140$\mu$m and 240$\mu$m is critical in making this problem sufficiently 
-constrained, and also in providing information near the peak of the dust SED at
-$\sim$140$\mu$m, which is particularly sensitive to the presence of a single 
-versus multiple MBB components. % last sentence mentioning
+(2141 GHz) and 240$\mu$m (1250 GHz) relative to \PLANCK~857 GHz, i.e. 
+$dI_{\nu_i}/dI_{857}$. We will refer to the slope for band $\nu_i$ relative to 
+\PLANCK~857 GHz as $s_{i,857}$. The slopes for \PLANCK~100-545 GHz are taken 
+to be those derived from the relative zero level fits of $\S$\ref{sec:relzero},
+and are illustrated by the dashed red lines in plots of Figure \ref{fig:dip}, 
+right column. The 857 GHz slope is by definition unity.
+
+At 1250, 2141 and 3000 GHz, we use the SFD98-reprocessed DIRBE maps. For each
+DIRBE band, we determine $s_{i, 857}$ by performing a linear fit to DIRBE as a 
+function of \PLANCK~857 GHz, after both have been zodiacal light subtracted and
+smoothed to $1^{\circ}$ FWHM, also restricting to the low HI mask of 
+$\S$\ref{sec:relzero} (see Figure XX).
+% smoothed to 1 degree resolution
+% restricted to same low HI mask as in Sect. 3.5.2 analysis
+% sentence pointing to figure showing the regressions
+
+Including 857 GHz, we thus have nine correlation slope constraints for six 
+free parameters. Including DIRBE 140$\mu$m and 240$\mu$m is critical in making 
+this problem sufficiently constrained, and also in providing information near 
+the peak of the dust SED at $\sim$140$\mu$m, which is particularly sensitive to
+ the presence of a single versus multiple MBB components. % last sentence mentioning
 % that the large number of frequency channels and good coverage of the 
 % dust SED peak were what made FIRAS so appropriate for FDS99 analysis ??
+
+%All of the correlations are performed using 
+%$1^{\circ}$ smoothed maps
+
+% need to mention that this is all for the low HI mask !!!!
+% should have a three panel figure illustrating linear fits of
 

### 2014-07-05 ms.tex
added DIRBE vs. 857 GHz linear fit figure

@@
 smoothed to $1^{\circ}$ FWHM, also restricting to the low HI mask of 
-$\S$\ref{sec:relzero} (see Figure XX).
-% smoothed to 1 degree resolution
+$\S$\ref{sec:relzero} (see Figure \ref{fig:dirbe_slopes}).
+% re-mention nside=64 or just bag it?
 % restricted to same low HI mask as in Sect. 3.5.2 analysis
 % sentence pointing to figure showing the regressions
+
+\begin{figure*}
+\begin{center}
+\epsfig{file=dirbe_slopes.eps, width=6.5in}
+\caption{\label{fig:dirbe_slopes} DIRBE linear fits for correlation slope 
+analysis.}
+\end{center}
+\end{figure*}
 

### 2014-07-05 ms.tex
moving figures around
nearly complete first pass at correlation slope discussion

@@
 
-\begin{figure}
-\begin{center}
-\epsfig{file=sed.eps, width=3.3in}
-\caption{\label{fig:sed} Planck SED for a single nside=2048 pixel in the 
-Polaris region. Note that the two lowest-frequency data points (\PLANCK~100, 
-143 GHz) were not used in our fit, while the three lowest-frequency data
-points were not used in the \cite{planckdust} fit.}
-\end{center}
-\end{figure}
-
-% add error bars to this example SED plot
-
-\begin{figure*}
-\begin{center}
-\epsfig{file=posteriors.eps, width=7.0in}
-\caption{Gridded posterior PDFs for three nside=2048 pixels. Red crosses mark 
-the best-fit parameters based on our Markov chain sampling of the posterior. 
-The posterior distributions are in general extremely well-behaved, showing
-no multimodality or other pathological qualities. Our MCMC parameter 
-estimates coincide well with the peaks in the gridded posteriors. The 
-colorscale is linear in $log(P)$, with black representing the maximum of 
-$log(P)$ and white representing $max(log(P))-5$. Left: Low S/N pixel at 
-high-latitude in Galactic north. Center: High S/N pixel in the Polaris region. 
-Right: Low S/N pixel at high-latitude in the Galactic south.}
-\end{center}
-\end{figure*}
-
-% overplot ellipses showing 1 sigma errors in posterior grayscales
-
 \section{Dust Emission Model}
@@
 
+\begin{figure*}
+\begin{center}
+\epsfig{file=dirbe_slopes.eps, width=6.5in}
+\caption{\label{fig:dirbe_slopes} DIRBE linear fits for correlation slope 
+analysis.}
+\end{center}
+\end{figure*}
+
 While we ultimately aim to obtain \PLANCK-resolution maps of the spatially 
@@
 to be those derived from the relative zero level fits of $\S$\ref{sec:relzero},
-and are illustrated by the dashed red lines in plots of Figure \ref{fig:dip}, 
-right column. The 857 GHz slope is by definition unity.
+and are illustrated by the dashed red lines in the right-hand column plots of 
+Figure \ref{fig:dip}. The 857 GHz slope is by definition unity.
 
@@
 
-\begin{figure*}
-\begin{center}
-\epsfig{file=dirbe_slopes.eps, width=6.5in}
-\caption{\label{fig:dirbe_slopes} DIRBE linear fits for correlation slope 
-analysis.}
-\end{center}
-\end{figure*}
-
 Including 857 GHz, we thus have nine correlation slope constraints for six 
 free parameters. Including DIRBE 140$\mu$m and 240$\mu$m is critical in making 
-this problem sufficiently constrained, and also in providing information near 
-the peak of the dust SED at $\sim$140$\mu$m, which is particularly sensitive to
- the presence of a single versus multiple MBB components. % last sentence mentioning
+this problem sufficiently overconstrained, and also in providing information 
+near the peak of the dust SED at $\sim$140$\mu$m, which is particularly 
+sensitive to the presence of a single versus multiple MBB components. 
+% last sentence mentioning
 % that the large number of frequency channels and good coverage of the 
@@
 
-% hmm it's really seeming like I need to move the color correction section
-% to be before this, because I need the \tilde{I} things in this equation
-
 \begin{equation} \label{equ:chi2corr}
-\chi^2 = \sum_{i=0}^{8}\frac{\big[s_{i, 857}-n\frac{\tilde{I}_{\nu_i}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}{\tilde{I}_{857}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}\big]^2}{\sigma_{s}^2}
+\chi^2 = \sum_{i=0}^{8}\frac{\big[s_{i, 857}-n\frac{\tilde{I}_{\nu_i}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}{\tilde{I}_{857}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}\big]^2}{\sigma_{i}^2}
 \end{equation}
@@
 case, we take $f_1$=0 and hence $q_1/q_2$, $\beta_1$ and $T_1$ are immaterial, 
-but Equation \ref{equ:chi2corr} still applies.
-
-%All comparisons between %\PLANCK~and the FDS99 predictions were made after 
-%smoothing both to $1^{\circ}$, subtracting the SMICA CMB model, and ignoring 
-%SMICA inpainted pixels. For 100-857 GHz, the linearity between the FDS and 
-%\PLANCK~is excellent.
+but Equation \ref{equ:chi2corr} still applies. Note also that no `priors' have
+been included to preferentially drag our results towards agreement with those 
+of FDS99.
+
+The results of our chi-squared minimization are listed in Table 
+\ref{tab:global}. First (model 1), we fix $\beta_1$, $\beta_2$ ,$q_1/q_2$ and
+$f_1$ to the best-fit values from the FDS99 analysis based on DIRBE+FIRAS. We
+then allow $n$ and $T_2$ to vary so as to best match our 
+DIRBE+\PLANCK~spectrum. This results in a reduced chi-squared of 
+$\chi^2_{\nu}$=3.41. Reassuringly, $n$ is quite close to unity. It should be 
+noted though that our best-fit $T_2$ is $\sim$0.5 K lower than that found by 
+FDS99 for the same values of $\beta_1$, $\beta_2$ ,$q_1/q_2$ and $f_1$.
+
+Next (model 2), we consider the fully-general two-component model, allowing all
+ six model parameters to vary. In this case, the reduced chi-squared of the 
+best fit is $\chi^2_{\nu}=$1.33, signifying that our introduction of four 
+additional free parameters is justified. The best-fit $\beta_1$ and $\beta_2$ 
+are both consistent with the corresponding FDS99 values to within 5\%. 
+$q_1/q_2$=8.22 represents a $\sim$40\% lower value than found by FDS99, while
+$f_1$=0.0458 represents a $\sim$25\% increase relative to FDS99. Again, our
+best-fit high-latitude $T_2$ is $\sim$0.5 K lower than the typical value of 
+$\langle T_2 \rangle$=16.2 K from FDS99.
+
+Lastly, we calculate the optimal single-MBB fit to the \PLANCK+DIRBE 
+correlation slope spectrum. The best-fit single MBB has $\beta$=1.59, 
+$T$=19.63, and $\chi^2_{\nu}$=5.65, indicating a significantly worse fit to the
+data than our best-fit two-component model (model 2). Thus, our \PLANCK+DIRBE 
+correlation slope analysis has confirmed the basic conclusion of FDS99 and 
+others e.g. \cite{reach95}, that the FIR/submm dust SED prefers two MBBs to 
+just one, but, for the first time, independent of FIRAS. However, it is also
+apparent that the improvement in $\chi^2_{\nu}$ for single-MBB versus double
+MBB models found here is substantially less dramatic 
+($\Delta\chi^2_{\nu}$=4.32) than that found in FDS99 
+($\Delta\chi^2_{\nu}$=29.2). This is likely attributable to the exquisite 
+narrow-band frequency coverage of FIRAS, especially near the dust SED peak, 
+which makes FIRAS a better suited data set than \PLANCK~for a detailed 
+analysis of the globally best-fit dust SED model.
+
+% acknowledge that the preference for two MBBs is relatively weak when swapping
+% in Planck for FIRAS, probably due to the
 
@@
 
-\section{Fitting Procedure}
+\section{MCMC Fitting Procedure}
 \label{sec:fitting}
@@
 $f_1$ is also allowed to vary from one line of sight to another.
+
+\begin{figure}
+\begin{center}
+\epsfig{file=sed.eps, width=3.3in}
+\caption{\label{fig:sed} Planck SED for a single nside=2048 pixel in the 
+Polaris region. Note that the two lowest-frequency data points (\PLANCK~100, 
+143 GHz) were not used in our fit, while the three lowest-frequency data
+points were not used in the \cite{planckdust} fit.}
+\end{center}
+\end{figure}
+
+% add error bars to this example SED plot
+
+\begin{figure*}
+\begin{center}
+\epsfig{file=posteriors.eps, width=7.0in}
+\caption{Gridded posterior PDFs for three nside=2048 pixels. Red crosses mark 
+the best-fit parameters based on our Markov chain sampling of the posterior. 
+The posterior distributions are in general extremely well-behaved, showing
+no multimodality or other pathological qualities. Our MCMC parameter 
+estimates coincide well with the peaks in the gridded posteriors. The 
+colorscale is linear in $log(P)$, with black representing the maximum of 
+$log(P)$ and white representing $max(log(P))-5$. Left: Low S/N pixel at 
+high-latitude in Galactic north. Center: High S/N pixel in the Polaris region. 
+Right: Low S/N pixel at high-latitude in the Galactic south.}
+\end{center}
+\end{figure*}
+
+% overplot ellipses showing 1 sigma errors in posterior grayscales
 

### 2014-07-05 ms.tex
added final sentence to correlation slope discussion

@@
 data than our best-fit two-component model (model 2). Thus, our \PLANCK+DIRBE 
-correlation slope analysis has confirmed the basic conclusion of FDS99 and 
+correlation slope analysis has confirmed the main conclusion of FDS99 and 
 others e.g. \cite{reach95}, that the FIR/submm dust SED prefers two MBBs to 
-just one, but, for the first time, independent of FIRAS. However, it is also
-apparent that the improvement in $\chi^2_{\nu}$ for single-MBB versus double
-MBB models found here is substantially less dramatic 
-($\Delta\chi^2_{\nu}$=4.32) than that found in FDS99 
-($\Delta\chi^2_{\nu}$=29.2). This is likely attributable to the exquisite 
-narrow-band frequency coverage of FIRAS, especially near the dust SED peak, 
-which makes FIRAS a better suited data set than \PLANCK~for a detailed 
-analysis of the globally best-fit dust SED model.
-
-% acknowledge that the preference for two MBBs is relatively weak when swapping
-% in Planck for FIRAS, probably due to the
+just one, but, for the first time, independent of FIRAS. Still, it is apparent 
+that the improvement in $\chi^2_{\nu}$ for single-MBB versus double MBB models 
+found here is substantially less dramatic ($\Delta\chi^2_{\nu}$=4.32) than that
+found in FDS99 ($\Delta\chi^2_{\nu}$=29.2). This is likely attributable to the 
+exquisite narrow-band frequency coverage of FIRAS, especially near the dust SED
+peak, which makes FIRAS a better suited data set than \PLANCK~for a detailed 
+analysis of the globally best-fit dust SED model. In $\S$\ref{sec:hier}, we
+confirm the basic conclusions of this section via an MCMC-based approach in
+which the dust temperature is allowed to vary spatially.
 
@@
 \subsection{Global Parameters Revisited}
+\label{sec:hier}
 % discuss goodness of fit tests based on running Markov chains with different

### 2014-07-05 ms.tex
filled in caption for DIRBE correlation slope figure

@@
 \epsfig{file=dirbe_slopes.eps, width=6.5in}
-\caption{\label{fig:dirbe_slopes} DIRBE linear fits for correlation slope 
-analysis.}
+\caption{\label{fig:dirbe_slopes} Linear fits of DIRBE 240$\mu$m (left), 
+140$\mu$m (center), and 100$\mu$m (right) as a function of \PLANCK~857 GHz. The
+red lines illustrate the DIRBE correlation slopes used in our global parameter 
+analysis of $\S$\ref{sec:global}.}
 \end{center}

### 2014-07-06 ms.tex
deleted comments to self that have already been addressed, added a couple of new comments to self
writing section about using Markov chains to evaluate goodness-of-fit of various dust SED models

@@
 sensitive to the presence of a single versus multiple MBB components.
-% last sentence mentioning
-% that the large number of frequency channels and good coverage of the 
-% dust SED peak were what made FIRAS so appropriate for FDS99 analysis ??
-
-%All of the correlations are performed using 
-%$1^{\circ}$ smoothed maps
-
-% need to mention that this is all for the low HI mask !!!!
-% should have a three panel figure illustrating linear fits of
 
@@
 which the dust temperature is allowed to vary spatially.
+
+% also might be worth mentioning that the MCMC analysis involves constraints
+% where the zero level matters, whereas the correlation slope analysis here
+% renders the zero levels irrelevant
 
@@
 \label{sec:hier}
+
+The posterior sampling framework thus far described also affords us an 
+opportunity to cross-check the conclusions of the correlation slope analysis in
+$\S$\ref{sec:global}. The basic idea will be to continue sampling the posterior
+of Equation \ref{eqn:post}, but at low resolution ($N_{side}$=64), including 
+all HFI bands as well as DIRBE 100$\mu$m, 140$\mu$m and 240$\mu$m, and 
+switching to a uniform prior on $T_2$. Under these circumstances, the 
+chi-squared corresponding to the best-fit parameters for each pixel, termed 
+$\chi^2_p$, is simply $-2 \times log(P_{max})$. 
+% maybe invent a term chi^2_p or something to 
+% reduce potential confusion caused by notation
+
+\begin{figure}
+\begin{center}
+\epsfig{file=chi2_dirbe.eps, width=3.3in}
+\caption{\label{fig:chi2_dirbe} Testing }
+\end{center}
+\end{figure}
+
+Because we seek to compare the goodness-of-fit for various dust SED models in 
+the diffuse ISM, we restrict to a set of $\sim$10,800 pixels ($\sim$22\% of the
+sky), with $|b|>30^{\circ}$ and $|\beta|>10^{\circ}$. We also avoid the SMICA 
+inpainting mask, pixels with appreciable CO contamination, and compact sources.
+The goodness-of-fit `objective function' we employ to judge the quality of 
+a particular dust SED model is $\langle \chi^2_p \rangle$, where the average 
+is taken over the aforementioned set of $\sim$10,800 pixels. 
+$\langle \chi_{p}^2 \rangle$ is also equivalent to the reduced chi-squared, 
+$\chi^2_{\nu}$, when considering the total number of free parameters to be the 
+number of pixels multiplied by the number of free parameters per pixel, and 
+similarly for the total number of constraints.
+
+We calculate $\chi^2_{\nu}$ for various dust SED models, independently 
+minimizing each $\chi^2_p$ by finding pixel $p$'s best-fitting dust 
+temperature and normalization, then evaluating $\langle \chi_{p}^2 \rangle$. 
+First, we considered single-MBB models with $\beta$ spatially constant (see the
+black line in Figure \ref{fig:chi2_dirbe}). $\beta$=1.57 yields the best fit, with 
+$\chi^2_{\nu}$=2.51. This result is in excellent agreement with that of 
+$\S$\ref{sec:global}, where we found the best-fit single-MBB model to have 
+$\beta$=1.59.
+
+% mention other single MBB variants
+
+Next, we calculate $\chi^2_{\nu}$ for the two-component model with global 
+parameters from FDS99 (Table \ref{tab:global}, model 2). We find 
+$\chi^2_{\nu}$=2.33, a slight improvement relative to the $\beta$=1.59 
+single-MBB model. Finally, calculate $\chi^2_{\nu}$ for Table \ref{tab:global} 
+model 3, the two-component model favored by our \PLANCK+DIRBE correlation 
+slopes. In this case, we achieve the best goodness-of-fit out of the all the 
+models tested, with $\chi^2_{\nu}$=2.11.
+
+% could compare temperatures, but masks are different
+
 % discuss goodness of fit tests based on running Markov chains with different
 % sets of global parameters
+
+% also should emphasize that an important difference here relative to the
+% correlation slope analysis is that here, the zero levels actually do matter
 

### 2014-07-06 ms.tex
still working on goodness-of-fit discussion

@@
 \epsfig{file=chi2_dirbe.eps, width=3.3in}
-\caption{\label{fig:chi2_dirbe} Testing }
+\caption{\label{fig:chi2_dirbe} Comparison of goodness-of-fit, 
+$\chi^2_{\nu}$=$\langle \chi^2_p \rangle$ for various dust SED models.}
 \end{center}
@@
 temperature and normalization, then evaluating $\langle \chi_{p}^2 \rangle$. 
-First, we considered single-MBB models with $\beta$ spatially constant (see the
-black line in Figure \ref{fig:chi2_dirbe}). $\beta$=1.57 yields the best fit, with 
-$\chi^2_{\nu}$=2.51. This result is in excellent agreement with that of 
+First, we consider single-MBB models with $\beta$ spatially constant (see the
+black line in Figure \ref{fig:chi2_dirbe}). $\beta$=1.57 yields the best fit, 
+with $\chi^2_{\nu}$=2.51. This result is in excellent agreement with that of 
 $\S$\ref{sec:global}, where we found the best-fit single-MBB model to have 
-$\beta$=1.59.
+$\beta$=1.59. We also evaluated $chi^2_{\nu}$ for single-MBB models in which
+$\beta$ varies spatially. In these cases, we used the $\beta$ map from 
+\cite{planckdust}. We started by calculating $\chi^2_{\nu}$ using the 
+\cite{planckdust} temperature map, finding $chi^2_{\nu}$=4.68. Note that
+in this case no per-pixel chi-squared minimization was involved, as we simply 
+evaluated $\chi^2_{p}$ for each pixel based on the fully-specified 
+\cite{planckdust} model. % mention beta template but floating t, normalization
 
@@
 
+% end with a few sentences summarizing overall takeaway(s) from this 
+% goodness-of-fit analysis
+
 % could compare temperatures, but masks are different
-
-% discuss goodness of fit tests based on running Markov chains with different
-% sets of global parameters
 

### 2014-07-06 ms.tex
still working on goodness-of-fit section

@@
 The posterior sampling framework thus far described also affords us an
-opportunity to cross-check the conclusions of the correlation slope analysis in
+opportunity to evaluate the goodness-of-fit for competing dust SED models, and 
+thereby cross-check the conclusions of our correlation slope analysis in
 $\S$\ref{sec:global}. The basic idea will be to continue sampling the posterior
@@
 chi-squared corresponding to the best-fit parameters for each pixel, termed 
-$\chi^2_p$, is simply $-2 \times log(P_{max})$. 
+$\chi^2_p$, is simply $-2 \times log(P_{max})$. We will refer to the
+per-pixel chi-squared per degree of freedom as $\chi^2_{p, \nu}$
 % maybe invent a term chi^2_p or something to 
@@
 The goodness-of-fit `objective function' we employ to judge the quality of 
-a particular dust SED model is $\langle \chi^2_p \rangle$, where the average 
-is taken over the aforementioned set of $\sim$10,800 pixels. 
-$\langle \chi_{p}^2 \rangle$ is also equivalent to the reduced chi-squared, 
-$\chi^2_{\nu}$, when considering the total number of free parameters to be the 
-number of pixels multiplied by the number of free parameters per pixel, and 
-similarly for the total number of constraints.
+a particular dust SED model is $\langle \chi^2_{p, \nu} \rangle$, where the 
+average is taken over the aforementioned set of $\sim$10,800 pixels. 
+$\langle \chi_{p, \nu}^2 \rangle$ is also equivalent to the reduced 
+chi-squared, $\chi^2_{\nu}$, when considering the total number of free 
+parameters to be the number of pixels multiplied by the number of free 
+parameters per pixel (and similarly for the total number of constraints), and
+taking $\chi^2$=$\sum\chi^2_{p}$.
 
@@
 $\S$\ref{sec:global}, where we found the best-fit single-MBB model to have 
-$\beta$=1.59. We also evaluated $chi^2_{\nu}$ for single-MBB models in which
-$\beta$ varies spatially. In these cases, we used the $\beta$ map from 
-\cite{planckdust}. We started by calculating $\chi^2_{\nu}$ using the 
-\cite{planckdust} temperature map, finding $chi^2_{\nu}$=4.68. Note that
-in this case no per-pixel chi-squared minimization was involved, as we simply 
-evaluated $\chi^2_{p}$ for each pixel based on the fully-specified 
-\cite{planckdust} model. % mention beta template but floating t, normalization
-
-% mention other single MBB variants
+$\beta$=1.59.
+
+We also evaluated $\chi^2_{\nu}$ for single-MBB models in which
+$\beta$ varies spatially. In these cases, we adopted the 0.5$^{\circ}$ 
+resolution $\beta$ map from \cite{planckdust}. We started by calculating 
+$\chi^2_{\nu}$ using the \cite{planckdust} temperature map, finding 
+$\chi^2_{\nu}$=4.68. Note that in this case no per-pixel chi-squared 
+minimization was involved, as we simply evaluated $\chi^2_{p}$ for each pixel 
+based on the fully-specified \cite{planckdust} emission model. Next, we tested 
+a single-MBB model for which we adopted the \cite{planckdust} $\beta$ map, but 
+allowed the per-pixel temperature and normalization to vary so as to minimize 
+$\chi^2_p$. In this case, we found $\chi^2_{\nu}$=2.51, effectively identical 
+to the value found for the spatially constant $\beta$=1.57 single-MBB model. 
+This is perhaps unsurprising, as the average $\beta$ value from 
+\cite{planckdust} over the mask in question is $\langle\beta\rangle$=1.58. 
+This result does suggest, however, that the half-degree variations in $\beta$ 
+are not materially improving the goodness-of-fit over the full frequency range 
+100-3000 GHz relative to a model with appropriately chosen spatially constant 
+$\beta$.
+
+% mention that when t floats, we find a lower T than the Planck team?
+% mention beta template but floating t, normalization
 

### 2014-07-06 ms.tex
still writing goodness-of-fit section

@@
 $\chi^2_p$, is simply $-2 \times log(P_{max})$. We will refer to the
-per-pixel chi-squared per degree of freedom as $\chi^2_{p, \nu}$
+per-pixel chi-squared per degree of freedom as $\chi^2_{p, \nu}$.
 % maybe invent a term chi^2_p or something to 
@@
 
-% mention that when t floats, we find a lower T than the Planck team?
-% mention beta template but floating t, normalization
-
-Next, we calculate $\chi^2_{\nu}$ for the two-component model with global 
-parameters from FDS99 (Table \ref{tab:global}, model 2). We find 
-$\chi^2_{\nu}$=2.33, a slight improvement relative to the $\beta$=1.59 
-single-MBB model. Finally, calculate $\chi^2_{\nu}$ for Table \ref{tab:global} 
-model 3, the two-component model favored by our \PLANCK+DIRBE correlation 
-slopes. In this case, we achieve the best goodness-of-fit out of the all the 
-models tested, with $\chi^2_{\nu}$=2.11.
+% mention that when t floats, we find a lower T by ~ 1 degree than the Planck 
+%team?
+
+We move on to evaluate two-component models, first calculating $\chi^2_{\nu}$ 
+with the FDS99 global parameters (Table \ref{tab:global}, model 2). We find
+$\chi^2_{\nu}$=2.33, a slight improvement relative to the best-fitting
+single-MBB models. Finally, calculate $\chi^2_{\nu}$ for Table 
+\ref{tab:global} model 3, the two-component model favored by our \PLANCK+DIRBE 
+correlation slopes. In this case, we achieve the best goodness-of-fit out of 
+all the models we have tested, with $\chi^2_{\nu}$=2.11.
+
+Thus, our degree-resolution goodness-of-fit analysis has generally confirmed
+the conclusions of $\S$\ref{sec:global}. We find the single-MBB $\beta$ value 
+favored by the combination of \PLANCK~and DIRBE to be nearly identical here 
+($\beta$=1.57) versus in $\S$\ref{sec:global}. As in $\S$\ref{sec:global}, we 
+also find that the \PLANCK+FIRAS and\PLANCK+DIRBE best-fit two-component models
+from Table \ref{tab:global} outperform single-MBB alternatives, though only by 
+a relatively small margin. The agreement between our correlation slope analysis
+and the present goodness-of-fit analysis is especially encouraging for two main
+reasons: (1) in the present analysis, dust temperature was allowed to vary on 
+degree scales, whereas in $\S$\ref{sec:global} we assumed a single global dust 
+temperature (2)
 
@@
 
-% could compare temperatures, but masks are different
+% could compare temperatures from correlation slope analysis versus here, but 
+% masks are different, so i guess it's just not worth it
 

### 2014-07-06 ms.tex
think I may have finished first pass at goodness-of-fit section

@@
 favored by the combination of \PLANCK~and DIRBE to be nearly identical here 
-($\beta$=1.57) versus in $\S$\ref{sec:global}. As in $\S$\ref{sec:global}, we 
-also find that the \PLANCK+FIRAS and\PLANCK+DIRBE best-fit two-component models
-from Table \ref{tab:global} outperform single-MBB alternatives, though only by 
-a relatively small margin. The agreement between our correlation slope analysis
-and the present goodness-of-fit analysis is especially encouraging for two main
-reasons: (1) in the present analysis, dust temperature was allowed to vary on 
-degree scales, whereas in $\S$\ref{sec:global} we assumed a single global dust 
-temperature (2)
-
-% end with a few sentences summarizing overall takeaway(s) from this 
-% goodness-of-fit analysis
+($\beta$=1.57) versus in $\S$\ref{sec:global} ($\beta$=1.59). As in 
+$\S$\ref{sec:global}, we also find that the \PLANCK+FIRAS and \PLANCK+DIRBE 
+best-fit two-component models from Table \ref{tab:global} outperform single-MBB
+alternatives, though only by a relatively small margin. The agreement between 
+our correlation slope analysis and the present goodness-of-fit analysis is 
+especially encouraging for two main reasons: (1) in the present analysis, dust 
+temperature has been allowed to vary on degree scales, whereas in 
+$\S$\ref{sec:global} we assumed a single global dust temperature (2) in the
+present analysis, our zero-level offsets factor into the dust temperature,
+whereas in $\S$6 this was not the case, meaning the former and latter analyses 
+agree in spite of their potential to be affected by rather different 
+systematics.
 
@@
 % masks are different, so i guess it's just not worth it
-
-% also should emphasize that an important difference here relative to the
-% correlation slope analysis is that here, the zero levels actually do matter
 

### 2014-07-06 ms.tex
filled in goodness-of-fit figure caption

@@
 per-pixel chi-squared per degree of freedom as $\chi^2_{p, \nu}$.
-% maybe invent a term chi^2_p or something to 
-% reduce potential confusion caused by notation
 
@@
 \caption{\label{fig:chi2_dirbe} Comparison of goodness-of-fit, 
-$\chi^2_{\nu}$=$\langle \chi^2_p \rangle$ for various dust SED models.}
+$\chi^2_{\nu}$=$\langle \chi^2_{p, \nu} \rangle$ for various dust SED models. 
+For single-MBB models with spatially constant $\beta$, we varied $\beta$ 
+between 1 and 2 (x axis), achieving reduced chi-squared $\chi^2_{\nu}$ shown by
+the black line, with $\beta$=1.57 providing the best fit. Horizontal lines 
+indicate $\chi^2_{\nu}$ for other dust SED models considered, including the 
+FDS99 best-fit model and our best-fit \PLANCK+DIRBE model from 
+$\S$\ref{sec:global}. The minimum $\chi^2_{\nu}$ was achieved with
+two-componenent `model 2' from Table \ref{tab:global} (horizontal magenta 
+line).}
 \end{center}
@@
 
+% say that, becuase such little improvement for two-component versus
+% single MBB in this analysis, we include a single-MBB beta = 1.57 fit in
+% our data release ???
+
 % could compare temperatures from correlation slope analysis versus here, but 

### 2014-07-08 ms.tex
comment
starting discussion of EBV residuals, added four-panel figure showing residuals

@@
 
-% do I need to cite a reference the first time that i mention SDSS ?
-
 % maybe note the possibility in the future of calibrating to a 3D dust
@@
 % of frequency at which tau is evaluated does not matter
+
+\begin{figure*}
+\begin{center}
+\epsfig{file=ebv_resid.eps, width=6.6in}
+\caption{\label{fig:resid} $E(B-V)_{2comp}$ residuals as a function of
+SFD $E(B-V)$. The grayscale represents the conditional probability within each
+bin in SFD $E(B-V)$. The central black line shows the moving median. The upper
+and lower black lines represent the moving 75th and 25th percentiles 
+respectively.}
+\end{center}
+\end{figure*}
 
@@
 
+% need to explain SSPP acronym somewhere ?
 % cite Green appendix for details of deriving EBV_SSPP from Schlafly 11 data ?
 
-The result of this regression is shown in Figure \ref{fig:calib}. Indeed there 
-appears to be a strong linear correlation between $E(B-V)_{SSPP}$ 
-and $\tau_{545}$. The conversion factor from $\tau_{545}$ to $E(B-V)$ is 
-2.46$\times$10$^{3}$. Reassuringly, the best-fit offset is quite close to 
-zero, $\sim$0.6 mmag.
-
-Figure \ref{fig:resid} shows a two-dimensional histogram of the residuals of
-the $\tau_{545}$-based $E(B-V)$ predictions relative to the corresponding
-spectrum-based $E(B-V)$ predictions, as a function of SFD $E(B-V)$. Clearly 
-there are some systematic trends in the residuals. Still, for 
-$E(B-V)_{SFD}$$<$0.28 ($\sim$80\% of the sky), the residual median is always 
-within 10 mmag of zero. Over the entire range $E(B-V)_{SFD}$$<$0.7, the 
-residual median is always within 30 mmag of zero.
-
-\begin{figure}
-\begin{center}
-\epsfig{file=ebv_resid.eps, width=3.3in}
-\caption{\label{fig:resid} $E(B-V)_{2comp}$ residuals as a function of
-SFD $E(B-V)$. The grayscale represents the conditional probability within each
-bin in SFD $E(B-V)$. The central black line shows the moving median. The upper
-and lower black lines represent the moving 75th and 25th percentiles 
-respectively.}
-\end{center}
-\end{figure}
+This regression is illustrated in Figure \ref{fig:calib}. As expected, there 
+appears to be a strong linear correlation between $E(B-V)_{SSPP}$ and 
+$\tau_{545}$. The conversion factor from $\tau_{545}$ to $E(B-V)$ is 
+2.46$\times$10$^{3}$. Reassuringly, the best-fit offset is quite close to zero,
+$\sim$0.6 mmag.
+
+Figure \ref{fig:resid} shows the residuals of our $\tau_{545}$-based reddening 
+predictions, $E(B-V)_{2comp}$, relative to the corresponding SF11 reddening 
+measurements, $E(B-V)_{SSPP}$, as a function of SFD reddening, $E(B-V)_{SFD}$, 
+(top left panel) and as a function of hot dust temperature (bottom left panel).
+For comparison, the right panels show analogous residual plots, but with 
+respect to reddening predictions based on our calibration of the 
+\cite{planckdust} 353 GHz optical depth to $E(B-V)_{SSPP}$ , using the same 
+regression procedure employed to calibrate $E(B-V)_{2comp}$. We refer to these 
+reddening predictions based on the \cite{planckdust} single-MBB model and 
+calibrated to the SF11 measurements as $E(B-V)_{mbb}$.
+
+All four residual plots in Figure 12 show systematic problems at some level. 
+The most striking systematic trend is the `bending' behavior of the reddening
+residuals versus $E(B-V)_{SFD}$ (top panels), with the median residual 
+bottoming out near $-10$ mmag around $E(B-V)_{SFD}$=0.15 mag. This behavior is 
+common to both $E(B-V)_{2comp}$ and $E(B-V)_{mbb}$, and in fact was first noted
+in the residuals of $E(B-V)_{SFD}$ itself relative to $E(B-V)_{SSPP}$ by SF11 
+(see their Figure 6). Such a bending behavior is troubling because it could 
+indicate a nonlinearity common to many FIR reddening predictions based on
+column densities inferred from dust emission. Alternatively, because the SF11 
+stars are distributed over the sky in a highly non-uniform manner, the bend 
+could arise from aliasing of discrepancies particular to certain sky regions 
+(e.g. inner vs. outer Galaxy) on to the $E(B-V)_{SFD}$ axis.
+
+The obvious culprit for any potential nonlinearity in FIR-based reddening
+estimates is a faulty temperature correction. For this reason, we have included
+the bottom panels of Figure \ref{fig:resid}, to check for the presence of
+a dependence of the reddening residuals on dust temperature.
+
+%Clearly there are some systematic trends in the residuals.
+%Still, for $E(B-V)_{SFD}$$<$0.28 ($\sim$80\% of the sky), the residual median 
+%is always within 10 mmag of zero. Over the entire range $E(B-V)_{SFD}$$<$0.7, 
+%the residual median is always within 30 mmag of zero.
 
@@
 
+% if we're not going to be claiming to be superseding SFD in terms of 
+% reddening, then do we even want to include anything extinction-related
+% (data files and/or code) in this data release ?
+
 %at some point in this should make statements re: the fact that in terms

### 2014-07-08 ms.tex
writing about attempts to fix reddening residuals

@@
 
+% MENTION THAT THE TAU TEMPLATE IS INDEPENDENT OF FREQUENCY FOR 
+% TWO-COMPONENT MODELS WITH SPATIALLY CONSTANT BETAS, Q1/Q2 AND F1
+
 % need to explain SSPP acronym somewhere ?
@@
 
+% could add a sentence praising the two-component reddening prediction for
+% only having issues at the ~<10 mmag level for EBV_SFD ~< 0.4 mag, since
+% it could be a lot worse ...
+
 The obvious culprit for any potential nonlinearity in FIR-based reddening
@@
 the bottom panels of Figure \ref{fig:resid}, to check for the presence of
-a dependence of the reddening residuals on dust temperature.
-
-%Clearly there are some systematic trends in the residuals.
-%Still, for $E(B-V)_{SFD}$$<$0.28 ($\sim$80\% of the sky), the residual median 
-%is always within 10 mmag of zero. Over the entire range $E(B-V)_{SFD}$$<$0.7, 
-%the residual median is always within 30 mmag of zero.
+a temperature dependence of the reddening residuals. Indeed, in both the
+two-component and single-MBB cases there exists some systematic dependence of
+the reddening residuals on temperature. For $T_{mbb}$$\gtrsim$19 K, the 
+median residual is reasonably flat, but at lower temperatures (the lowest 
+temperature $\sim$20\% of the sky), the median shows trends at the $\sim$10 
+mmag level. On the other hand, the median residual in the two-component case 
+shows a clear trend of decreasing with increasing $T_2$ over the entire range
+of $T_2$ shown, with a peak-to-peak amplitude of $\sim$20 mmag.
 
 \subsection{Rectifying Reddening Residuals}
+In this section we describe our attempts to eliminate the systematic
+problems in the two-component reddening residuals shown in the left column
+of Figure \ref{fig:resid}. We employed two main strategies: (1) recompute
+the two-component $\tau_{545}$ by re-running our Markov chains after modifying 
+the input maps and/or changing the particular two-component model adopted and
+(2) making spatial cuts to isolate sky regions in which the 
+residuals are especially pristine (or especially problematic).
+
+The following is a list of dust model modifications we tested, but 
+proved to have little impact on the shape of the reddening residuals versus
+$E(B-V)_{SFD}$ and $T_2$:
+
+\begin{itemize}
+\item Varying each of the global two-component model parameters $\beta_1$, 
+$\beta_2$, $q_1/q_2$ and $f_1$ individually while holding the others fixed.
+\vspace{-3mm}
+\item Allowing $f_1$ to vary spatially as in the fits of $\S$\ref{sec:lores}.
+\vspace{-2mm}
+\item Changing the mean and/or variance of the $T_2$ prior.
+\vspace{-6mm}
+\item Varying multiple global parameters at a time e.g. both $f_1$ and 
+$q_1/q_2$, restricting to regions of parameter space favored by our 
+goodness-of-fit analyses described in $\S$\ref{sec:global} and 
+$\S$\ref{sec:hier}.
+\end{itemize}
+
+We additionally investigated spatial cuts which did not resolve the 
+dominant problems noted in the reddening residuals:
+
 % discuss changing global params and offsets, and ecl plane cut

### 2014-07-08 ms.tex
starting to describe experiments with reddening residuals

@@
 
-We additionally investigated spatial cuts which did not resolve the 
-dominant problems noted in the reddening residuals:
+We additionally investigated the following spatial cuts which did not resolve 
+the dominant problems noted in the reddening residuals:
+\begin{itemize}
+\item Separating Celestial north and south.
+\vspace{-3mm}
+\item Separating Galactic north and south.
+\vspace{-3mm}
+\item Separating inner and outer Galaxy.
+\vspace{-3mm}
+\item Combining the above two sets of cuts i.e. separating the Galaxy into
+quadrants. 
+\vspace{-3mm}
+\item Combining these spatial cuts with the dust model changes of the previous
+list.
+\end{itemize}
+
+However, we did find that changing the zero level offsets of the input maps 
+had a significant effect on the strength of the anticorrelation between
+reddening residual and $T_2$. In particular, we experimented with perturbing 
+the zero level offset of \PLANCK~857 GHz while correspondingly changing the 
+zero levels of the remaining \PLANCK~maps based on the prescription of 
+$\S$\ref{sec:relzero}. We also experimented with changing the zero level of SFD
+\verb|i100|, independent of the other zero levels. Unfortunately, completely
+flattening the reddening residual dependence on $T_2$ required unreasonably 
+large zero level changes. For example, flattening the $T_2$ residual required
+adding $\gtrsim$0.6 MJy/sr to the \verb|i100| map. Furthermore, we note that 
+even relatively large zero level modifications had virtually no effect in 
+eliminating the `bend' versus $E(B-V)_{SFD}$. Thus, simply changing the
+zero level offsets showed a bit of promise in rectifying the residual 
+temperature dependence, but of itself was not a sufficient solution.
+
+The ony solution we were able to identify that both removed the `bend' vs.
+$E(B-V)_{SFD}$ and the temperature dependence of the residual was cutting 
+out the ecliptic plane, restricting to $|\beta|>20^{\circ}$ . In this case, we 
+completely eliminated the bending behavior of the residual versus 
+$E(B-V)_{SFD}$, and significantly reduced the $T_2$ dependence (see Figure
+QQ)
+
+% but required offsets too big
+
+% but then we tried ECL cuts, and in combination with modest offsets, that 
+% worked
 

### 2014-07-08 ms.tex
still discussing reddening residuals

@@
 problems in the two-component reddening residuals shown in the left column
-of Figure \ref{fig:resid}. We employed two main strategies: (1) recompute
+of Figure \ref{fig:resid}. We employed two main strategies: (1) recomputing
 the two-component $\tau_{545}$ by re-running our Markov chains after modifying 
@@
 The following is a list of dust model modifications we tested, but 
-proved to have little impact on the shape of the reddening residuals versus
-$E(B-V)_{SFD}$ and $T_2$:
+proved to have little impact on the reddening residual trends versus either 
+$E(B-V)_{SFD}$ or $T_2$:
 
@@
 
-However, we did find that changing the zero level offsets of the input maps 
-had a significant effect on the strength of the anticorrelation between
+However, we found that changing the zero level offsets of the input maps 
+had a significant effect on the strength of the anticorrelation between median 
 reddening residual and $T_2$. In particular, we experimented with perturbing 
@@
 large zero level changes. For example, flattening the $T_2$ residual required
-adding $\gtrsim$0.6 MJy/sr to the \verb|i100| map. Furthermore, we note that 
-even relatively large zero level modifications had virtually no effect in 
-eliminating the `bend' versus $E(B-V)_{SFD}$. Thus, simply changing the
-zero level offsets showed a bit of promise in rectifying the residual 
-temperature dependence, but of itself was not a sufficient solution.
+adding $\gtrsim$0.6 MJy/sr to the \verb|i100| map. Such an offset is 
+implausible, being an order of magnitude larger than the nominal \verb|i100| 
+zero level uncertainty quoted by SFD98, and comparable to the entire 3000 GHz 
+CIB monopole signal. Furthermore, we note that even these large zero 
+level modifications had virtually no effect in eliminating the reddening 
+residual `bend' versus $E(B-V)_{SFD}$. Thus, changing the zero level 
+offsets showed hints of promise in rectifying the residual temperature 
+dependence, but cannot completely resolve the systematic trends in reddening 
+residuals.
+% last few words here are kind of bad, need better terminology
 
@@
 $E(B-V)_{SFD}$, and significantly reduced the $T_2$ dependence (see Figure
-QQ)
-
-% but required offsets too big
+\ref{fig:resid_ecl}), to a peak-to-peak amplitude of only $\sim$10 mmag. We
+still included the single-MBB plots (right column), to show that 
+the bend versus $E(B-V)_{SFD}$ is eliminated by the $|\beta|$ cut, even
+for the single-MBB model. However, the single-MBB residuals still differ
+systematically from zero for $T$$\lesssim$$19$ K. Perhaps these improvements in
+the two-component reddening residuals after restricting to high ecliptic 
+latitude should come as no surprise, given that the ecliptic plane is the most 
+obvious systematic problem with the temperature correction upon inspecting the 
+full-sky temperature map in Figure \ref{fig:results}.
+
+\begin{figure*}
+\begin{center}
+\epsfig{file=ebv_resid_ecl.eps, width=6.6in}
+\caption{\label{fig:resid_ecl} $E(B-V)_{2comp}$ residuals as a function of
+SFD $E(B-V)$, including a cut on ecliptic latitude, $|\beta|>20^{\circ}$. The 
+grayscale represents the conditional probability within each bin in SFD 
+$E(B-V)$. The central black line shows the moving median. The upper and lower 
+black lines represent the moving 75th and 25th percentiles respectively.}
+\end{center}
+\end{figure*}
 
@@
 % worked
-
-% discuss changing global params and offsets, and ecl plane cut
-
-% should eventually try re-making 2d scatterplot figure in python..
 
@@
 \epsfig{file=results.eps, width=7.0in}
-\caption{Our best-fit $T_2$, binned to 27.5$'$ resolution}
+\caption{\label{fig:results} Our best-fit $T_2$, binned to 27.5$'$ resolution}
 \end{center}

### 2014-07-08 ms.tex
added last figure to reddening residual discussion

@@
 
-The ony solution we were able to identify that both removed the `bend' vs.
-$E(B-V)_{SFD}$ and the temperature dependence of the residual was cutting 
+The ony solution we have been able to identify that both removes the `bend' vs.
+$E(B-V)_{SFD}$ and the temperature dependence of the residual is cutting 
 out the ecliptic plane, restricting to $|\beta|>20^{\circ}$ . In this case, we 
@@
 latitude should come as no surprise, given that the ecliptic plane is the most 
-obvious systematic problem with the temperature correction upon inspecting the 
-full-sky temperature map in Figure \ref{fig:results}.
+obvious systematic problem with our temperature map upon inspecting the 
+full-sky results shown in Figure \ref{fig:results}.
 
@@
 
+After cutting the ecliptic plane, we found that only small zero level
+perturbations were required to fully flatten the temperature residuals,
+while still maintaining flat residuals versus $E(B-V)_{SFD}$. The optimal
+offsets we found were $\pm$0.08 MJy/sr to \verb|i100| and 857 GHz respectively
+(see Figure \ref{fig:resid_offs}). These offsets are well within reason, 
+given the nominal zero level uncertainties quoted in Table QQ.
+
+\begin{figure}
+\begin{center}
+\epsfig{file=resid_offs.eps, width=3.3in}
+\caption{\label{fig:resid_offs} $E(B-V)_{2comp}$ residuals as a function of
+SFD $E(B-V)$, including a cut on ecliptic latitude, $|\beta|>20^{\circ}$, 
+and zero level perturbations of $\pm$0.08 MJy/sr to i100 and 
+857 GHz respectively. The grayscale represents the conditional probability 
+within each bin in SFD $E(B-V)$. The central black line shows the moving 
+median. The upper and lower black lines represent the moving 75th and 25th 
+percentiles respectively.}
+\end{center}
+\end{figure}
+
 % but then we tried ECL cuts, and in combination with modest offsets, that 

### 2014-07-09 ms.tex
a bunch of clean up in reddening residual discussion

@@
 
+% mention that this is especially true because Planck gives such a huge
+% increase in temperature resolution relative to SFD (and possibly reference
+% temperature comparison figure as well)
+
 \subsection{Reddening Calibration Procedure}
@@
 set of $\sim$10$^5$ quasars. The SFD calibration was originally tied to a 
-sample of 384 elliptical galaxies, but was later revised by \cite{schlafly11} 
-using $\sim$250,000 stars with both spectroscopy and broadband photometry 
-available from SDSS. To calibrate our $\tau_{545}$ to reddening, we make use of
-the same set of stars studied by \cite{schlafly11}.
+sample of 384 elliptical galaxies, but was later revised by 
+\citet[hereafter SF11]{schlafly11} based on $\sim$260,000 stars with both 
+spectroscopy and broadband photometry available from SDSS.
 
@@
 
-Given a library of stellar atmosphere models, the spectral lines of these stars
-can be used to predict their intrinsic optical broadband colors. The `true' 
-reddening is then simply the difference in the observed $g-r$ color and the 
-$g-r$ color predicted from the spectral lines. Applying a color transformation 
-then yields `true' $E(B-V)$ values for $\sim$260,000 lines of sight. Throughout
-our SSPP calibration analysis, we restrict to the $\sim$230,000 lines of sight 
-with $|b|$$>$20$^{\circ}$ in order to avoid stars which may not lie behind the 
-full dust column. The calibration of two-component optical depth to $E(B-V)$ is
-performed as a linear regression of $E(B-V)_{SSPP}$ versus $\tau_{545}$. 
-$\tau_{545}$ is considered to be the independent variable in this regression, 
-as we ultimately wish to predict $E(B-V)$ as a function of optical depth, and 
-$\tau_{545}$ has much higher S/N than the SSPP $E(B-V)$ estimates.
+To calibrate our two-component optical depth to reddening, we make use of the 
+stellar sample from SF11. Given a library of model stellar atmospheres, the 
+spectral lines of these stars can be used to predict their intrinsic optical 
+broadband colors. The `true' reddening is then simply the difference between 
+the observed $g-r$ color and the $g-r$ color predicted from the spectral lines.
+Applying a color transformation then yields `true' $E(B-V)$ values for 
+$\sim$260,000 lines of sight. Throughout our SSPP calibration analysis, we 
+restrict to the $\sim$230,000 lines of sight with $|b|$$>$20$^{\circ}$ in order
+to avoid stars which may not lie behind the full dust column. The calibration 
+of two-component optical depth to $E(B-V)$ is performed as a linear regression 
+of $E(B-V)_{SSPP}$ versus $\tau_{545}$. $\tau_{545}$ is considered to be the 
+independent variable in this regression, as we ultimately wish to predict 
+$E(B-V)$ as a function of optical depth, and $\tau_{545}$ has much higher S/N 
+than the SSPP $E(B-V)$ estimates.
 
@@
 This regression is illustrated in Figure \ref{fig:calib}. As expected, there 
-appears to be a strong linear correlation between $E(B-V)_{SSPP}$ and 
-$\tau_{545}$. The conversion factor from $\tau_{545}$ to $E(B-V)$ is 
-2.46$\times$10$^{3}$. Reassuringly, the best-fit offset is quite close to zero,
-$\sim$0.6 mmag.
+is a strong linear correlation between $E(B-V)_{SSPP}$ and $\tau_{545}$. The 
+conversion factor from $\tau_{545}$ to $E(B-V)$ is 2.46$\times$10$^{3}$. 
+Reassuringly, the best-fit offset is quite close to zero, $\sim$0.6 mmag.
 
@@
 residuals versus $E(B-V)_{SFD}$ (top panels), with the median residual 
-bottoming out near $-10$ mmag around $E(B-V)_{SFD}$=0.15 mag. This behavior is 
-common to both $E(B-V)_{2comp}$ and $E(B-V)_{mbb}$, and in fact was first noted
-in the residuals of $E(B-V)_{SFD}$ itself relative to $E(B-V)_{SSPP}$ by SF11 
-(see their Figure 6). Such a bending behavior is troubling because it could 
-indicate a nonlinearity common to many FIR reddening predictions based on
+bottoming out near $-10$ mmag at $E(B-V)_{SFD}$$\approx$0.15 mag. This behavior
+is common to both $E(B-V)_{2comp}$ and $E(B-V)_{mbb}$, and in fact was first 
+noted in the residuals of $E(B-V)_{SFD}$ itself relative to $E(B-V)_{SSPP}$ by 
+SF11 (see their Figure 6). Such a bending behavior is troubling because it 
+could indicate a nonlinearity common to many FIR reddening predictions based on
 column densities inferred from dust emission. Alternatively, because the SF11 
@@
 mmag level. On the other hand, the median residual in the two-component case 
-shows a clear trend of decreasing with increasing $T_2$ over the entire range
-of $T_2$ shown, with a peak-to-peak amplitude of $\sim$20 mmag.
+trends downward with increasing $T_2$ over the entire $T_2$ range shown, with a
+peak-to-peak amplitude of $\sim$20 mmag.
 
@@
 
-The following is a list of dust model modifications we tested, but 
-proved to have little impact on the reddening residual trends versus either 
-$E(B-V)_{SFD}$ or $T_2$:
+The following is a list of dust model modifications we tested, but which
+proved to have little impact on the reddening residual trends as a function 
+of either $E(B-V)_{SFD}$ or $T_2$:
 
@@
 flattening the reddening residual dependence on $T_2$ required unreasonably 
-large zero level changes. For example, flattening the $T_2$ residual required
-adding $\gtrsim$0.6 MJy/sr to the \verb|i100| map. Such an offset is 
+large zero level modifications. For example, flattening the $T_2$ residual 
+required adding $\gtrsim$0.6 MJy/sr to the \verb|i100| map. Such an offset is 
 implausible, being an order of magnitude larger than the nominal \verb|i100| 
@@
 residual `bend' versus $E(B-V)_{SFD}$. Thus, changing the zero level 
-offsets showed hints of promise in rectifying the residual temperature 
-dependence, but cannot completely resolve the systematic trends in reddening 
-residuals.
+offsets showed hints of promise in rectifying the reddening residual 
+temperature dependence, but cannot completely resolve the systematic trends in 
+reddening residuals.
 % last few words here are kind of bad, need better terminology
 
-The ony solution we have been able to identify that both removes the `bend' vs.
-$E(B-V)_{SFD}$ and the temperature dependence of the residual is cutting 
-out the ecliptic plane, restricting to $|\beta|>20^{\circ}$ . In this case, we 
-completely eliminated the bending behavior of the residual versus 
-$E(B-V)_{SFD}$, and significantly reduced the $T_2$ dependence (see Figure
-\ref{fig:resid_ecl}), to a peak-to-peak amplitude of only $\sim$10 mmag. We
-still included the single-MBB plots (right column), to show that 
-the bend versus $E(B-V)_{SFD}$ is eliminated by the $|\beta|$ cut, even
-for the single-MBB model. However, the single-MBB residuals still differ
-systematically from zero for $T$$\lesssim$$19$ K. Perhaps these improvements in
-the two-component reddening residuals after restricting to high ecliptic 
-latitude should come as no surprise, given that the ecliptic plane is the most 
-obvious systematic problem with our temperature map upon inspecting the 
-full-sky results shown in Figure \ref{fig:results}.
+The only solution we have been able to identify that both removes the `bend' 
+vs. $E(B-V)_{SFD}$ and simultaneously reduces the temperature dependence of the
+reddening residuals is cutting out the ecliptic plane by restricting to 
+$|\beta|>20^{\circ}$. In this case, we completely eliminated the bending 
+behavior of the residual versus $E(B-V)_{SFD}$, and significantly reduced the 
+$T_2$ dependence to a peak-to-peak amplitude of only $\sim$10 mmag (see Figure 
+\ref{fig:resid_ecl}). Figure \ref{fig:resid_ecl} still includes the single-MBB 
+plots (right column), to show that the bend versus $E(B-V)_{SFD}$ is eliminated
+by the $|\beta|$ cut, even for the single-MBB model. However, the single-MBB 
+residuals still differ systematically from zero for $T$$\lesssim$$19$ K. 
+Perhaps the improvements in the two-component reddening residuals after 
+restricting to high ecliptic latitude should come as no surprise, given that 
+the ecliptic plane is the most obvious systematic problem with our temperature 
+map (see the full-sky results shown in Figure \ref{fig:results}).
 
@@
 (see Figure \ref{fig:resid_offs}). These offsets are well within reason, 
-given the nominal zero level uncertainties quoted in Table QQ.
+given the nominal zero level uncertainties quoted in Table \ref{table:offs}.
 

### 2014-07-09 ms.tex
working to fix captions for reddening residual plots

@@
 have found using the LAB H\,\textsc{i} data \citep{lab} for 
-$-72$$<$$v_{LSR}$$<$$+25$ that the best-fit slope for H\,\textsc{i}$<$70 K km/s
-is a factor of $\sim$1.9 lower than the best fit slope for 110 K km/s 
+$-72$$<$$v_{LSR}$$<$$+25$ km/s that the best-fit slope for H\,\textsc{i}$<$70 K
+km/s is a factor of $\sim$1.9 lower than the best fit slope for 110 K km/s 
 $<$H\,\textsc{i}$<$200 K km/s, and as a result the implied zero-point offsets 
@@
 \epsfig{file=ebv_resid.eps, width=6.6in}
-\caption{\label{fig:resid} $E(B-V)_{2comp}$ residuals as a function of
-SFD $E(B-V)$. The grayscale represents the conditional probability within each
-bin in SFD $E(B-V)$. The central black line shows the moving median. The upper
-and lower black lines represent the moving 75th and 25th percentiles 
-respectively.}
+\caption{\label{fig:resid} (top left) Residuals of $E(B-V)_{2comp}$ relative to
+$E(B-V)_{SSPP}$ as a function of $E(B-V)_{SFD}$. The grayscale represents the 
+conditional probability within each $E(B-V)_{SFD}$ bin. The central black line 
+shows the moving median. The upper and lower black lines represent the moving 
+75th and 25th percentiles respectively. (bottom left) Residuals of 
+$E(B-V)_{2comp}$ relative to $E(B-V)_{SSPP}$ as a function of hot dust 
+temperature $T_2$. (top right) Same as top left, but illustrating the residuals
+of $E(B-V)_{mbb}$, our calibration of the \cite{planckdust} $\tau_{353}$ to 
+$E(B-V)_{SSPP}$. (bottom right)  Same as bottom left, but showing the 
+$E(B-V)_{mbb}$ residuals as a function of the single-MBB dust temperature from 
+\cite{planckdust}.}
 \end{center}
@@
 \epsfig{file=ebv_resid_ecl.eps, width=6.6in}
-\caption{\label{fig:resid_ecl} $E(B-V)_{2comp}$ residuals as a function of
-SFD $E(B-V)$, including a cut on ecliptic latitude, $|\beta|>20^{\circ}$. The 
-grayscale represents the conditional probability within each bin in SFD 
-$E(B-V)$. The central black line shows the moving median. The upper and lower 
-black lines represent the moving 75th and 25th percentiles respectively.}
+\caption{\label{fig:resid_ecl} Same as Figure \ref{fig:resid}, but 
+restricting to high ecliptic latitude, $|\beta|>20^{\circ}$. The top left and 
+top right plots both show that the bending of the reddening residuals as a 
+function of $E(B-V)_{SFD}$ as seen in Figure \ref{fig:resid} has been 
+eliminated. Further, the two-component reddening residual temperature 
+dependence (bottom left) has been significantly reduced relative to the
+corresponding trend shown in Figure \ref{fig:resid}, bottom left panel.}
 \end{center}

### 2014-07-09 ms.tex
explain temperature axis limits for reddening residual plots
caption for last reddening residual figure

@@
 $E(B-V)_{mbb}$ residuals as a function of the single-MBB dust temperature from 
-\cite{planckdust}.}
+\cite{planckdust}. The temperature axes always range from the 
+0.4$^{th}$ percentile to 99.6$^{th}$ percentile temperature values.}
 \end{center}
@@
 \epsfig{file=resid_offs.eps, width=3.3in}
-\caption{\label{fig:resid_offs} $E(B-V)_{2comp}$ residuals as a function of
-SFD $E(B-V)$, including a cut on ecliptic latitude, $|\beta|>20^{\circ}$, 
-and zero level perturbations of $\pm$0.08 MJy/sr to i100 and 
-857 GHz respectively. The grayscale represents the conditional probability 
-within each bin in SFD $E(B-V)$. The central black line shows the moving 
-median. The upper and lower black lines represent the moving 75th and 25th 
-percentiles respectively.}
+\caption{\label{fig:resid_offs} Two-component reddening residuals after 
+restricting to high ecliptic latitude ($|\beta|>20^{\circ}$) and perturbing the
+\texttt{i100} and 857 GHz zero levels by $+$0.08 MJy/sr and $-$0.08 MJy/sr 
+respectively. The bending behavior as a function of $E(B-V)_{SFD}$ has been
+eliminated, and virtually no temperature dependence remains.}
 \end{center}

### 2014-07-09 ms.tex
writing in emission prediction and conclusions sections

@@
 \section{Low-frequency Emission Predictions}
+FDS99 originally performed their two-component versus single-MBB dust SED 
+analysis for the sake of accurately forecasting low-frequency CMB foregrounds.
+The need for accurate CMB foreground predictions, especially in the 100-150 GHz
+frequency range, has been highlighted of late by the \cite{bicep2} $B$-mode 
+polarization results. In this section we show that our two-component foreground
+predictions are more accurate than those based on the single-MBB model of 
+\cite{planckdust} over the 100-217 GHz frequency range.
+
 % compare 100-217 GHz predictions using my model versus Planck Collaboration
@@
 %striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping
-An important difference between our maps and those of \cite{planckdust} is our 
-use of SFD \verb|i100| instead of IRIS 100$\mu$m \citep{IRIS}. Residual 
-\IRAS~striping at levels higher than that remaining in SFD \verb|i100| is 
-clearly visible in the \cite{planckdust} maps.
+%%%An important difference between our maps and those of \cite{planckdust} is 
+%%%our 
+%%%use of SFD \verb|i100| instead of IRIS 100$\mu$m \citep{IRIS}. Residual 
+%%%\IRAS~striping at levels higher than that remaining in SFD \verb|i100| is 
+%%%clearly visible in the \cite{planckdust} maps.
 
 %we actually have 6.1' arcminute resolution
-It is true that we have smoothed the input intensity maps for this study 
-to $6.1'$ FWHM, which is nominally lower resolution than the $5'$ 
-\cite{planckdust} maps. However, as is apparent from figure 
-\ref{fig:comparison}, the fact that \cite{planckdust} modeled $\beta$ at 
-$0.5^{\circ}$ resolution has effectively blurred their dust temperature map.
-
-%\subsection{Validation with FIRAS}
+%%%It is true that we have smoothed the input intensity maps for this study 
+%%%to $6.1'$ FWHM, which is nominally lower resolution than the $5'$ 
+%%%\cite{planckdust} maps. However, as is apparent from figure 
+%%%\ref{fig:comparison}, the fact that \cite{planckdust} modeled $\beta$ at 
+%%%$0.5^{\circ}$ resolution has effectively blurred their dust temperature map.
 
@@
 \label{sec:conclusion}
+
+\subsection{Single-MBB versus Two-component emission}
+In both the correlation slope analysis of $\S$\ref{sec:global} and the 
+goodness-of-fit analysis of $\S$\ref{sec:hier} we found that the 
+best-fit \PLANCK+DIRBE two-component model (Table \ref{tab:global}, model 2) 
+outperformed the best-fit single-MBB model, but by a lesser margin than found 
+by FDS99 using FIRAS+DIRBE. We found $\Delta \chi^2_{nu}$= and $\Delta$
+
+% sentence criticizing the half-degree beta single MBB model of Planck team
+% in terms of the imprint that leaves on low-frequency emission 
+% predictions ?
+
+\subsection{Towards a Replacement for SFD}
+%  ---> CIBA
+%   ---> do i want a figure illustrating the CIBA problem at high latitude ?
+%  ---> zodi
+%  ---> more testing needed, in any event, to prove Planck based reddening
+%       estimates outperform SFD
+
 % should mention that one definitive improvement of this work relative

### 2014-07-09 ms.tex
rewriting introduction to reddening section

@@
 optical reddening/extinction is another important application of the 
-$\tau_{545}$ map.
+$\tau_{545}$ map. Translating our two-component optical depth to reddening
+is especially valuable because our $T_2$ map has $\sim$13$\times$ better
+angular resolution than the SFD temperature correction, and thus there is 
+reason to believe our two-component reddening estimates may be superior to
+those of SFD. However, as discussed in $\S$\ref{sec:replace}, we do not yet 
+advocate for the wholesale replacement of SFD, and more detailed work is still 
+necessary to determine/quantify the extent to which \PLANCK-based dust maps
+might improve reddening estimates relative to SFD.
 
@@
 
-We calibrate to reddening empirically rather than derive
-a relationship between $\tau_{545}$ and reddening by introducing additional 
+We calibrate optical depth to reddening empirically rather than derive a 
+relationship between $\tau_{545}$ and reddening by introducing additional 
 assumptions about the dust grain physics and size distribution. To achieve this
@@
 spectroscopy and broadband photometry available from SDSS.
-
-% maybe note the possibility in the future of calibrating to a 3D dust
-% map type data product rather than directly to a set of individual 
-% stars/galaxies
 
@@
 \subsection{Towards a Replacement for SFD}
+\label{sec:replace}
 %  ---> CIBA

### 2014-07-09 ms.tex
define SSPP acronym and cite SSPP reference

@@
 \citet[hereafter SF11]{schlafly11} based on $\sim$260,000 stars with both 
-spectroscopy and broadband photometry available from SDSS.
+spectroscopy and broadband photometry available from the SEGUE Stellar 
+Parameter Pipeline \citep[SSPP,][]{sspp}.
 
@@
 
-\subsection{Rectifying Reddening Residuals}
+\subsection{Rectifying the Reddening Residuals}
 In this section we describe our attempts to eliminate the systematic

### 2014-07-10 ms.tex
writing conclusions about comparison of dust SED emission models

@@
 \subsection{Single-MBB versus Two-component emission}
+% could use an opening sentence here just reiterating that a major thrust of
+% this work was to decide whether the two-component model
+% still makes sense after swapping in Planck for FIRAS
+
+% second sentence of opening paragraph reiterating what the basic two
+% strategies were that we employed to compare dust SED models
+
 In both the correlation slope analysis of $\S$\ref{sec:global} and the 
@@
 outperformed the best-fit single-MBB model, but by a lesser margin than found 
-by FDS99 using FIRAS+DIRBE. We found $\Delta \chi^2_{nu}$= and $\Delta$
+by FDS99 using FIRAS+DIRBE. Specifically, our best-fit \PLANCK+DIRBE 
+two-component model yielded an improvement of $\Delta \chi^2_{\nu}$=3.41 
+($\S$\ref{sec:global}) and $\Delta \chi^2_{\nu}$=0.4 ($\S$\ref{sec:hier}). This
+represents a far less dramatic contrast than found by the FDS99 correlation 
+slope analysis, $\Delta \chi^2_{\nu}$=29.2. Perhaps, though, the relative lack 
+of discrimination amongst competing dust SED models when relying on 
+\PLANCK+DIRBE is not surprising, given that our constraints include only nine 
+broad frequency channels, whereas FDS99 employed $>$200 narrow bands.
 

### 2014-07-10 ms.tex
editing intro to low-frequency prediction comparison section

@@
 \section{Low-frequency Emission Predictions}
-FDS99 originally performed their two-component versus single-MBB dust SED 
-analysis for the sake of accurately forecasting low-frequency CMB foregrounds.
-The need for accurate CMB foreground predictions, especially in the 100-150 GHz
-frequency range, has been highlighted of late by the \cite{bicep2} $B$-mode 
-polarization results. In this section we show that our two-component foreground
-predictions are more accurate than those based on the single-MBB model of 
-\cite{planckdust} over the 100-217 GHz frequency range.
+FDS99 originally performed their \PLANCK+DIRBE dust SED analysis for the sake 
+of accurately forecasting low-frequency CMB foregrounds. Recently, Galactic CMB
+foregrounds, especially in the 100-150 GHz frequency range, have become a focal
+point of cosmology owing to the \cite{bicep2} $B$-mode polarization results. 
+Here we show that our two-component foreground predictions are more accurate 
+than those based on the \cite{planckdust} single-MBB model over the 100-217 GHz
+frequency range.
 
@@
 % is this the section where, potentially, plots of the residuals might go?
+
+%end section saying that the predictions accessible through our data 
+% release should be investigated/tested/swapped in by people doing
+% B-mode stuff
 

### 2014-07-10 ms.tex
intro sentences for conclusion discussion of emission model comparisons

@@
 \subsection{Single-MBB versus Two-component emission}
-% could use an opening sentence here just reiterating that a major thrust of
-% this work was to decide whether the two-component model
-% still makes sense after swapping in Planck for FIRAS
-
-% second sentence of opening paragraph reiterating what the basic two
-% strategies were that we employed to compare dust SED models
+A major aim of this work has been to determine whether the  FDS99 
+two-component dust emission model (or an FDS99-like model) remains favored over
+single-MBB models when swapping the \PLANCK~HFI maps for FIRAS at frequencies 
+below 1250 GHz. We compared dust SED models in two ways (1) by fitting a 
+100-3000 GHz spectrum composed of per-band correlation slopes versus 
+\PLANCK~857 GHz (2) by finding the best-fit dust temperature and optical depth
+per line-of-sight, with each pixel's SED comprised of 100-3000 GHz 
+\PLANCK+DIRBE data, and comparing the average goodness-of-fit under various
+emission models.
 
@@
 
+% one or two last sentence(s) saying two-component model still alive, wasn't
+% an artifact of FIRAS, and also the predictions from our data release
+% are a suitable alternative for estimating CMB foregrounds and can provide
+% a handle on foreground systematics when swapped for other
+
+% nevertheless, ...
+% in above paragraph, say which single-MBB beta(s) we find to be favored
+
 % sentence criticizing the half-degree beta single MBB model of Planck team
@@
 % the derived parameters !!!!
+
+% should there be a future work section or can the suggestions/plans of
+% future work just be a part of ``SFD replacement'' subsection
 

### 2014-07-10 ms.tex
added ending sentences to section about comparison between different dust emission models

@@
 
-% one or two last sentence(s) saying two-component model still alive, wasn't
-% an artifact of FIRAS, and also the predictions from our data release
-% are a suitable alternative for estimating CMB foregrounds and can provide
-% a handle on foreground systematics when swapped for other
-
-% nevertheless, ...
 % in above paragraph, say which single-MBB beta(s) we find to be favored
+
+Nevertheless, we have established that the two-component emission model
+remains viable in light of the \PLANCK~HFI data, and that the FIR/submm 
+dust SED's preference for two MBB components rather than just one is not
+simply an idiosyncracy of the FIRAS spectra. We recommend that those interested
+in thermal dust foregrounds in the 100-3000 GHz frequency range use our data 
+release to predict unpolarized dust emission, at the very least in order to 
+help determine the level at which the choice of dust emission model may 
+influence their conclusions.
+%last sentence needs work
 

### 2014-07-10 ms.tex
conclusion section mostly in place

@@
 \label{sec:replace}
-%  ---> CIBA
+Because of the broad frequency coverage and high angular resolution afforded
+by the \PLANCK~HFI full-sky maps, we initially speculated that a \PLANCK~based 
+extinction map might easily outperform SFD, the current industry standard data 
+product. However, at this point in time, we do not yet recommend that the 
+results presented in this work be considered a replacement for SFD in terms of 
+optical extinction/reddening estimates.
+
+% CIBA
+The CIBA remains a major imperfection that still requires further 
+investigation. The CIB anisotropies are very evident in low-dust regions of our
+maps of optical depth and predicted dust emission. As described in 
+$\S$\ref{sec:mcmc}, we have propagated the CIBA RMS amplitudes and 
+inter-frequency covariances into our uncertainty estimates through the 
+likelihood function in our MCMC procedure. However, this treatment falls far 
+short of actually removing the spatial imprint of the CIBA on our optical depth
+and temperature maps. The CIB anisotropies are more prominent in our optical 
+depth map relative to that of SFD because of the lower-frequency \PLANCK~maps 
+we rely upon to achieve a high-resolution temperature correction.
+
+Imperfect zodi corrections represent a second major limitation of our results.
+The prominence of the ecliptic plane in our 
+full-sky temperature map of Figure \ref{fig:results} suggests that zodiacal
+light subtractions performed on the input maps are not ideal. Our comparisons 
+of the maps used in this study against HI emission bear out this notion, and 
+show that the imperfect zodi corrections are not limited to \verb|i100| (the
+highest frequency for which the zodi should be most problematic), but in fact
+are noticeable in all of the HFI ZodiCorrected maps as well. We deemed it 
+infeasible to reconsider all of the \PLANCK~zodi corrections in addition to the
+3000 GHz zodi correction as a part of this study. Perhaps the forthcoming 
+\PLANCK~data release, including data from additional orbits, will effectively 
+eliminate any residual zodi problems in the \PLANCK~bands. Under these 
+circumstances it might then be worthwhile to consider revising the DIRBE 
+100$\mu$m zodi correction provided by SFD.
+
+Irrespective of the notable imperfections in our results, more detailed
+comparisons between our reddening estimates here and those of SFD are required 
+to determine/quantify which map is superior in particular applications. One 
+definitive improvement of our reddening estimates relative to those of SFD is 
+our ability to quote reddening uncertainties, which results from the 
+probabilistic framework of $\S$\ref{sec:mcmc}. The extinction estimates 
+from this work can also be employed as an alternative to those of SFD, to gauge
+the impact of dust map choice in a specific application.
+
+% perhaps zodi will just magically be fixed in the forthcoming Planck dta
+% release
+
 %   ---> do i want a figure illustrating the CIBA problem at high latitude ?
@@
 
+% and should also say that it's worth looking up extinction values here
+% to gauge whether results are dependent on choice of dust map
+
 % should there be a future work section or can the suggestions/plans of
 % future work just be a part of ``SFD replacement'' subsection
+
+% mention here the idea of getting even higher resolution by folding
+% in WISE ?
 

### 2014-07-10 ms.tex
cleaning up text in conclusions section

@@
 Imperfect zodi corrections represent a second major limitation of our results.
-The prominence of the ecliptic plane in our 
-full-sky temperature map of Figure \ref{fig:results} suggests that zodiacal
-light subtractions performed on the input maps are not ideal. Our comparisons 
-of the maps used in this study against HI emission bear out this notion, and 
-show that the imperfect zodi corrections are not limited to \verb|i100| (the
-highest frequency for which the zodi should be most problematic), but in fact
-are noticeable in all of the HFI ZodiCorrected maps as well. We deemed it 
-infeasible to reconsider all of the \PLANCK~zodi corrections in addition to the
-3000 GHz zodi correction as a part of this study. Perhaps the forthcoming 
-\PLANCK~data release, including data from additional orbits, will effectively 
-eliminate any residual zodi problems in the \PLANCK~bands. Under these 
-circumstances it might then be worthwhile to consider revising the DIRBE 
+The ecliptic plane's prominence in our full-sky temperature map (Figure 
+\ref{fig:results}) suggests that the zodiacal light subtractions performed on 
+the input maps are not ideal. Our comparisons of the FIR maps used in this 
+study against H\,\textsc{i} emission bear out this notion, further revealing 
+that the imperfect zodi corrections are not limited to \verb|i100| (the 
+map for which one would expect zodiacal contamination to be most 
+problematic), but in fact are noticeable in all of the HFI 
+\verb|R1.10_nominal_ZodiCorrected| maps as well. We deemed it infeasible to 
+reconsider all of the \PLANCK~zodi corrections in addition to the 3000 GHz zodi
+correction as a part of this study. Perhaps the forthcoming \PLANCK~data 
+release, including observations acquired during additional orbits, will 
+effectively eliminate any residual zodi problems in the \PLANCK~bands. Under 
+these circumstances it might then be worthwhile to consider revising the DIRBE 
 100$\mu$m zodi correction provided by SFD.
+
+% audit for word ``zodi'' ... is this an acceptable jargon term ?
+% could use IPD as an abbreviation at certain points, not sure if i've 
+% defined that acronym already somewhere else in the text?
 
@@
 from this work can also be employed as an alternative to those of SFD, to gauge
-the impact of dust map choice in a specific application.
+the impact of dust map choice in a specific end user's application.
 

### 2014-07-11 ms.tex
a bunch of minor clean-up throughout, moved global parameter table to appear earlier in manuscript

@@
 
-The primary FDS99 analysis considered the intrinsic grain properties, for 
-example the emissivity power law indices, to be constant over the sky, and 
-performed a correlation slope analysis to constrain these parameters with FIRAS
-and DIRBE observations. FDS99 also constructed a DIRBE 240$\mu$m/100$\mu$m 
-ratio to account for temperature variation at $\sim$1.3$^{\circ}$ resolution. 
-In this work we seek to apply FDS99-like emission models to the \PLANCK~data 
-set, which offers a dramatic enhancement in angular resolution relative to the 
-FIRAS spectra. The \PLANCK~data thereby allow us to derive an improved 
-temperature correction at near-\IRAS~resolution, re-evaluate the best-fit 
-global dust properties, and fit additional parameters of the two-component 
-model as a function of position on the sky. % in this last sentence
-% reference the relevant sections for each sub-goal mentioned
+The primary FDS99 analysis considered the intrinsic grain properties of each
+species, for example the emissivity power law indices, to be constant over the 
+sky, and performed a correlation slope analysis to constrain these parameters 
+with FIRAS and DIRBE observations. FDS99 also constructed a DIRBE 
+240$\mu$m/100$\mu$m ratio to account for temperature variation at 
+$\sim$1.3$^{\circ}$ resolution. In this work we seek to apply FDS99-like 
+emission models to the \PLANCK~data set, which offers a dramatic enhancement in
+angular resolution relative to the FIRAS spectra. The \PLANCK~data thereby 
+allow us to derive an improved temperature correction at near-\IRAS~resolution,
+re-evaluate the best-fit global dust properties, and fit additional parameters 
+of the two-component model as a function of position on the sky. 
+% in this last sentence reference the relevant sections for each sub-goal 
+% mentioned
 
@@
 dust species, while $f_1$ dictates the relative amounts of each species 
-present. Following the convention of FDS99, $\nu_0$ is chosen to be 3000 GHz.
+present. Following the convention of FDS99, we choose $\nu_0$=3000 GHz.
 
@@
 
-Fixing the four parameters of Table \ref{tab:global}, our full-resolution, 
-five-band fits have two remaining free parameters per line of sight: the hot 
-dust temperature $T_2$ determines the SED shape and the normalization of 
-$M_{\nu}$ determines the SED amplitude. In the lower-resolution fits of 
-$\S$\ref{sec:lores} which include all HFI bands, we will allow $f_1$ to be a 
-third free parameter, still holding $\beta_1$, $\beta_2$, and $q_1/q_2$ fixed.
-
-%explain that we take the ``hot'' dust temperature to be T2 rather than T1
-
-% maybe point to the SED fit summary figure as an example of what
-%
-
-% For the parameters thus far specified, the two dust temperatures are further 
-% related by:
-
-%\begin{equation}
-%T_1 = 0.352T_2^{1.18}
-%\end{equation}
-
-% more important than the details of the above equation is the notion
-% that, for any set of f1, q1/q2, beta1, beta2, the relationship between
-% T1 and T2 is a simple power law
-
-%the below statements seem like they might best be moved to a generic
-%opening of the next section, stating our philosophy of breaking sky
-%into pixels, each with 5 SED measurements, and that with this small
-%number of constraints per pixel, it makes sense to have a baseline
-% fit at full resolution that has only two free parameters
-
-%FDS99 found $T_2 \approx 16.2$K, $T_1 \approx 9.4$K to be typical at 
-%high-latitude. In the present formulation, there are only two free parameters 
-%to describe an observed SED: the hot dust temperature $T_2$ determines the SED
-%shape and the normalization of $M_{\nu}$ determines the SED amplitude. In 
-%principle, we could allow additional parameters, such as $f_1$ and the ratio 
-%$q_1/q_2$, to vary. However the number of free parameters in our baseline fit 
-%at the full $6.1'$ resolution is limited by the fact that, for each sky 
-%location, the observed SED contains only five independent intensity 
-%measurements (\verb|i100| along with the four highest-frequency 
-%\PLANCK~bands).
-
-To calculate the optical depth in the context of this model, we assume
-optically thin conditions, meaning that $\tau_{\nu}$ = $M_{\nu}/S_{\nu}$, where
-$M_{\nu}$ is the appropriately scaled two-component intensity and the source
-function is given by:
-
-\begin{equation}
-\label{eqn:source}
-S_{\nu} = \frac{f_1q_1(\nu/\nu_0)^{\beta_1}B_{\nu}(T_1) + f_2q_2(\nu/\nu_0)^{\beta_2}B_{\nu}(T_2)}{f_1q_1(\nu/\nu_0)^{\beta_1}+f_2q_2(\nu/\nu_0)^{\beta_2}}
-\end{equation}
-
-\section{Predicting the Observed SED}
-\label{sec:bpcorr}
-
-The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
-flux density per solid angle $M_{\nu}$ in e.g. MJy/sr for any single frequency 
-$\nu$. In practice, however, we wish to constrain our model using measurements 
-in the broad DIRBE/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. 
-Both the \PLANCK~and DIRBE data products quote flux density per solid 
-angle in MJy/sr under the `IRAS convention'. More precisely, each value 
-reported in the \PLANCK~maps gives the amplitude of a power-law spectrum 
-with $\alpha$=$-1$, evaluated at the nominal band center frequency, such that 
-this spectrum integrated against the transmission reproduces the 
-bolometer-measured power. Because our model spectra do not conform to the 
-$\alpha$=$-1$ convention, we have computed color correction factors to account 
-for the MBB($T$, $\beta$) spectral shape and the transmission as a function of 
-frequency:
-
-% is delta(nu)/nu conventionally (nu_off-nu_on)/nu_c or 1/2 of that ?
-
-\begin{equation} \label{equ:bpcorr}
-b_{\nu_i}(T, \beta) = \frac{\int \nu^{\beta}B_{\nu}(T)\mathcal{T}_{\nu_i}(\nu) d\nu \bigg[\int (\nu_{i,c}/\nu)\mathcal{T}_{\nu_i}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
-\end{equation}
-
-% integral limits ??? check planck paper to see what they did
-% -> planck spectral response paper just leaves the integrals indefinite
-
-Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
-$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 1249.1352, 2141.3747, 
-2997.92458\} GHz. $\mathcal{T}_{\nu_i}(\nu)$ represents the relative 
-transmission as a function of frequency for band $\nu_i$. For the HFI maps, 
-$\mathcal{T}_{\nu_i}(\nu)$ is given by the \PLANCK~transmission curves provided
-in the file \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz and
-DIRBE 140$\mu$m, 240$\mu$m, we have adopted the corresponding DIRBE 
-transmission curves. Again, since DIRBE-quoted fluxes also follow the 
-$\alpha$=$-1$ convention, Equation \ref{equ:bpcorr} remains applicable.
-
-% what is the reference for the dirbe
-
-%The color correction factors
-%of Equation \ref{equ:bpcorr} are applied in the sense that 
-%$b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ is a prediction suitable for 
-%direct comparison to the \PLANCK~data products.
-
-The two-component model prediction in band $\nu_i$ under the IRAS convention, 
-termed $\tilde{I}_{\nu_i}$, is then constructed as a linear combination of 
-color-corrected MBB terms:
-
-\begin{equation} \label{equ:iras}
-\tilde{I}_{\nu_i} \propto \sum_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k)
-\end{equation}
-
-Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. Our color correction 
-approach allows us to predict $\tilde{I}_{\nu_i}$ by computing monochromatic 
-flux densities at the central frequency $\nu_{i,c}$ and then multiplying by 
-factors $b_{\nu_i}(T, \beta)$ which are interpolated off of a set of 
-precomputed, one-dimensional lookup tables each listing $b_{\nu_i}(T, \beta)$ 
-as a function of $T$. We avoided the need to interpolate in both $\beta$ and 
-$T$ by computing only a small set of one dimensional correction factors for the
-particular set of $\beta$ values of interest (e.g. $\beta$=1.67, 2.7, 
-1.63, 2.82 ..., see Table \ref{tab:global}).
-
-% need some sort of clarification about the fact that, in the parts of the 
-% analysis where beta floats, i actually do interpolate color corrections 
-% off of a 2d grid in (T, beta)
-
-This color correction approach makes the MCMC sampling described in 
-$\S$\ref{sec:mcmc} much more computationally efficient by circumventing the 
-need to perform the integral in the numerator of Equation \ref{equ:bpcorr} 
-on-the-fly for each proposed dust temperature. We have chosen to compute the 
-color corrections on a per-MBB basis because this approach is very 
-versatile; all possible two-component (and single-MBB) models are linear 
-combinations of MBBs, so we can apply all of our color correction machinery 
-even when we allow parameters other than temperature (e.g. $f_1$) to vary and 
-thereby modify the dust spectrum shape.
-
-% We note that it is not clear which bandpass should properly be ascribed to 
-% the \IRAS/DIRBE composite 100$\mu$m maps under consideration.
-
-With these color corrections and the  formalism established in 
-$\S$\ref{sec:modeling} in hand, we can mathematically state the model we will 
-use e.g. during MCMC sampling to predict the observed SED, which we will 
-denote by \{$\tilde{I}_{\nu_i}$\}. The predicted observations are given by:
-
-\begin{equation}
-\label{eqn:inten}
-\tilde{I}_{\nu_i} = \frac{\sum\limits_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k) u_{\nu_i}^{-1}(T_k, \beta_k)}{\sum\limits_{k=1}^{2} b_{545}(T_k, \beta_k) f_k q_k (545 \textrm{GHz}/\nu_0)^{\beta_k} B_{545}(T_k)}\tilde{I}_{545}
-\end{equation}
-
-This equation is quite similar to Equation \ref{equ:iras}, but with two 
-important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
-specified by $\tilde{I}_{545}$, which represents the flux density per solid
-angle measured in the \PLANCK~545 GHz band. The denominator serves to ensure 
-that, for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. 
-Second, each term in the numerator is multiplied by a conversion factor 
-$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
-\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
-remaining maps (545-3000 GHz) have units of MJy/sr. We have adopted the 
-strategy of predicting each band in its native units, whether MJy/sr or 
-$K_{CMB}$. For this reason, we always evaluate $B_{\nu_{i,c}}$ in Equation 
-\ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for 
-$\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
-represents the conversion factor from $K_{CMB}$ to MJy/sr, given by 
-\cite{planckresponse} Equation 32.
-
-%is the old sentence below worth reinstating ?
-
-%To reiterate, for 
-%$\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ has units of 
-%(MJy/sr)/$K_{CMB}$,and therefore $\tilde{I}_{\nu_{i}}$ will have different 
-%units depending on the band $\nu_i$, though $\tilde{I}_{\nu_{i}}$ always has 
-%the same units as the native band $\nu_i$ map.
-
-% check that RIMO file i've used is actually the most up-to-date version
-
-% extremely abrupt transition here...
-\section{Global Model Parameters}
-\label{sec:global}
 %%%%
@@
 
+Fixing the four parameters of Table \ref{tab:global}, our full-resolution, 
+five-band fits have two remaining free parameters per line of sight: the hot 
+dust temperature $T_2$ determines the SED shape and the normalization of 
+$M_{\nu}$ determines the SED amplitude. In the lower-resolution fits of 
+$\S$\ref{sec:lores} which include all HFI bands, we will allow $f_1$ to be a 
+third free parameter, still holding $\beta_1$, $\beta_2$, and $q_1/q_2$ fixed.
+
+%explain that we take the ``hot'' dust temperature to be T2 rather than T1
+
+% maybe point to the SED fit summary figure as an example of what
+%
+
+% For the parameters thus far specified, the two dust temperatures are further 
+% related by:
+
+%\begin{equation}
+%T_1 = 0.352T_2^{1.18}
+%\end{equation}
+
+% more important than the details of the above equation is the notion
+% that, for any set of f1, q1/q2, beta1, beta2, the relationship between
+% T1 and T2 is a simple power law
+
+%the below statements seem like they might best be moved to a generic
+%opening of the next section, stating our philosophy of breaking sky
+%into pixels, each with 5 SED measurements, and that with this small
+%number of constraints per pixel, it makes sense to have a baseline
+% fit at full resolution that has only two free parameters
+
+%FDS99 found $T_2 \approx 16.2$K, $T_1 \approx 9.4$K to be typical at 
+%high-latitude. In the present formulation, there are only two free parameters 
+%to describe an observed SED: the hot dust temperature $T_2$ determines the SED
+%shape and the normalization of $M_{\nu}$ determines the SED amplitude. In 
+%principle, we could allow additional parameters, such as $f_1$ and the ratio 
+%$q_1/q_2$, to vary. However the number of free parameters in our baseline fit 
+%at the full $6.1'$ resolution is limited by the fact that, for each sky 
+%location, the observed SED contains only five independent intensity 
+%measurements (\verb|i100| along with the four highest-frequency 
+%\PLANCK~bands).
+
+To calculate the optical depth in the context of this model, we assume
+optically thin conditions, meaning that $\tau_{\nu}$ = $M_{\nu}/S_{\nu}$, where
+$M_{\nu}$ is the appropriately scaled two-component intensity and the source
+function is given by:
+
+\begin{equation}
+\label{eqn:source}
+S_{\nu} = \frac{f_1q_1(\nu/\nu_0)^{\beta_1}B_{\nu}(T_1) + f_2q_2(\nu/\nu_0)^{\beta_2}B_{\nu}(T_2)}{f_1q_1(\nu/\nu_0)^{\beta_1}+f_2q_2(\nu/\nu_0)^{\beta_2}}
+\end{equation}
+
+\section{Predicting the Observed SED}
+\label{sec:bpcorr}
+
+The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
+flux density per solid angle $M_{\nu}$ in e.g. MJy/sr for any single frequency 
+$\nu$. In practice, however, we wish to constrain our model using measurements 
+in the broad \PLANCK/DIRBE bandpasses, each with $\Delta\nu/\nu\sim0.3$. 
+Both the \PLANCK~and DIRBE data products quote flux density per solid 
+angle in MJy/sr under the `IRAS convention'. More precisely, each value 
+reported in the \PLANCK~maps gives the amplitude of a power-law spectrum 
+with $\alpha$=$-1$, evaluated at the nominal band center frequency, such that 
+this spectrum integrated against the transmission reproduces the 
+bolometer-measured power. Because our model spectra do not conform to the 
+$\alpha$=$-1$ convention, we have computed color correction factors to account 
+for the MBB($T$, $\beta$) spectral shape and the transmission as a function of 
+frequency:
+
+% is delta(nu)/nu conventionally (nu_off-nu_on)/nu_c or 1/2 of that ?
+
+\begin{equation} \label{equ:bpcorr}
+b_{\nu_i}(T, \beta) = \frac{\int \nu^{\beta}B_{\nu}(T)\mathcal{T}_{\nu_i}(\nu) d\nu \bigg[\int (\nu_{i,c}/\nu)\mathcal{T}_{\nu_i}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
+\end{equation}
+
+% integral limits ??? check planck paper to see what they did
+% -> planck spectral response paper just leaves the integrals indefinite
+
+Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
+$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 1249.1352, 2141.3747, 
+2997.92458\} GHz. $\mathcal{T}_{\nu_i}(\nu)$ represents the relative 
+transmission as a function of frequency for band $\nu_i$. For the HFI maps, 
+$\mathcal{T}_{\nu_i}(\nu)$ is given by the \PLANCK~transmission curves provided
+in the file \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz and
+DIRBE 140$\mu$m, 240$\mu$m, we have adopted the corresponding DIRBE 
+transmission curves. Again, since DIRBE-quoted fluxes also follow the 
+$\alpha$=$-1$ convention, Equation \ref{equ:bpcorr} remains applicable.
+
+% what is the reference for the dirbe
+
+%The color correction factors
+%of Equation \ref{equ:bpcorr} are applied in the sense that 
+%$b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ is a prediction suitable for 
+%direct comparison to the \PLANCK~data products.
+
+The two-component model prediction in band $\nu_i$ under the IRAS convention, 
+termed $\tilde{I}_{\nu_i}$, is then constructed as a linear combination of 
+color-corrected MBB terms:
+
+\begin{equation} \label{equ:iras}
+\tilde{I}_{\nu_i} \propto \sum_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k)
+\end{equation}
+
+Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. Our color correction 
+approach allows us to predict $\tilde{I}_{\nu_i}$ by computing monochromatic 
+flux densities at the central frequency $\nu_{i,c}$ and then multiplying by 
+factors $b_{\nu_i}(T, \beta)$ which are interpolated off of a set of 
+precomputed, one-dimensional lookup tables each listing $b_{\nu_i}(T, \beta)$ 
+as a function of $T$. We avoided the need to interpolate in both $\beta$ and 
+$T$ by computing only a small set of one dimensional correction factors for the
+particular set of $\beta$ values of interest (e.g. $\beta$=1.67, 2.7, 
+1.63, 2.82 ..., see Table \ref{tab:global}).
+
+% need some sort of clarification about the fact that, in the parts of the 
+% analysis where beta floats, i actually do interpolate color corrections 
+% off of a 2d grid in (T, beta)
+
+This color correction approach makes the MCMC sampling described in 
+$\S$\ref{sec:mcmc} much more computationally efficient by circumventing the 
+need to perform the integral in the numerator of Equation \ref{equ:bpcorr} 
+on-the-fly for each proposed dust temperature. We have chosen to compute the 
+color corrections on a per-MBB basis because this approach is very 
+versatile; all possible two-component (and single-MBB) models are linear 
+combinations of MBBs, so we can apply all of our color correction machinery 
+even when we allow parameters other than temperature (e.g. $f_1$) to vary and 
+thereby modify the dust spectrum shape.
+
+% We note that it is not clear which bandpass should properly be ascribed to 
+% the \IRAS/DIRBE composite 100$\mu$m maps under consideration.
+
+With these color corrections and the  formalism established in 
+$\S$\ref{sec:modeling} in hand, we can mathematically state the model we will 
+use e.g. during MCMC sampling to predict the observed SED, which we will 
+denote by \{$\tilde{I}_{\nu_i}$\}. The predicted observations are given by:
+
+\begin{equation}
+\label{eqn:inten}
+\tilde{I}_{\nu_i} = \frac{\sum\limits_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k) u_{\nu_i}^{-1}(T_k, \beta_k)}{\sum\limits_{k=1}^{2} b_{545}(T_k, \beta_k) f_k q_k (545 \textrm{GHz}/\nu_0)^{\beta_k} B_{545}(T_k)}\tilde{I}_{545}
+\end{equation}
+
+This equation is quite similar to Equation \ref{equ:iras}, but with two 
+important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
+specified by $\tilde{I}_{545}$, which represents the flux density per solid
+angle measured in the \PLANCK~545 GHz band. The denominator serves to ensure 
+that, for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. 
+Second, each term in the numerator is multiplied by a conversion factor 
+$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
+\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
+remaining maps (545-3000 GHz) have units of MJy/sr. We have adopted the 
+strategy of predicting each band in its native units, whether MJy/sr or 
+$K_{CMB}$. For this reason, we always evaluate $B_{\nu_{i,c}}$ in Equation 
+\ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for 
+$\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
+represents the conversion factor from $K_{CMB}$ to MJy/sr, given by 
+\cite{planckresponse} Equation 32.
+
+%is the old sentence below worth reinstating ?
+
+%To reiterate, for 
+%$\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ has units of 
+%(MJy/sr)/$K_{CMB}$,and therefore $\tilde{I}_{\nu_{i}}$ will have different 
+%units depending on the band $\nu_i$, though $\tilde{I}_{\nu_{i}}$ always has 
+%the same units as the native band $\nu_i$ map.
+
+% check that RIMO file i've used is actually the most up-to-date version
+
+% extremely abrupt transition here...
+\section{Global Model Parameters}
+\label{sec:global}
+
 \begin{figure*}
@@
 and are illustrated by the dashed red lines in the right-hand column plots of 
-Figure \ref{fig:dip}. The 857 GHz slope is by definition unity.
+Figure \ref{fig:dip}. The 857 GHz slope is unity by definition.
 
@@
 
-Including 857 GHz, we thus have nine correlation slope constraints for six 
+Counting 857 GHz, we thus have nine correlation slope constraints for six 
 free parameters. Including DIRBE 140$\mu$m and 240$\mu$m is critical in making 
-this problem sufficiently overconstrained, and also in providing information 
-near the peak of the dust SED at $\sim$140$\mu$m, which is particularly 
-sensitive to the presence of a single versus multiple MBB components.
+the problem at hand sufficiently overconstrained, and also in providing 
+information near the peak of the dust SED at $\sim$140$\mu$m, which is 
+particularly sensitive to the presence of a single versus multiple MBB 
+components.
 
@@
 case, we take $f_1$=0 and hence $q_1/q_2$, $\beta_1$ and $T_1$ are immaterial, 
-but Equation \ref{equ:chi2corr} still applies. Note also that no `priors' have
-been included to preferentially drag our results towards agreement with those 
-of FDS99.
+but Equation \ref{equ:chi2corr} still applies. Note also that no `priors' are
+included to preferentially drag our results towards agreement with those of 
+FDS99.
 
@@
 noted though that our best-fit $T_2$ is $\sim$0.5 K lower than that found by 
-FDS99 for the same values of $\beta_1$, $\beta_2$ ,$q_1/q_2$ and $f_1$.
+FDS99 for the same values of $\beta_1$, $\beta_2$, $q_1/q_2$ and $f_1$.
 
@@
 analysis of the globally best-fit dust SED model. In $\S$\ref{sec:hier}, we
-confirm the basic conclusions of this section via an MCMC-based approach in
-which the dust temperature is allowed to vary spatially.
+confirm the basic conclusions of this section via an approach in which we 
+allow the dust temperature to vary spatially.
 
@@
 thereby cross-check the conclusions of our correlation slope analysis in
-$\S$\ref{sec:global}. The basic idea will be to continue sampling the posterior
-of Equation \ref{eqn:post}, but at low resolution ($N_{side}$=64), including 
-all HFI bands as well as DIRBE 100$\mu$m, 140$\mu$m and 240$\mu$m, and 
-switching to a uniform prior on $T_2$. Under these circumstances, the 
+$\S$\ref{sec:global}. The basic idea will be to continue evaluating the 
+posterior of Equation \ref{eqn:post}, but at low resolution ($N_{side}$=64), 
+including all HFI bands as well as DIRBE 100$\mu$m, 140$\mu$m and 240$\mu$m, 
+and switching to a uniform prior on $T_2$. Under these circumstances, the 
 chi-squared corresponding to the best-fit parameters for each pixel, termed 
@@
 We move on to evaluate two-component models, first calculating $\chi^2_{\nu}$ 
-with the FDS99 global parameters (Table \ref{tab:global}, model 2). We find
+with the FDS99 global parameters (Table \ref{tab:global}, model 1). We find
 $\chi^2_{\nu}$=2.33, a slight improvement relative to the best-fitting
-single-MBB models. Finally, calculate $\chi^2_{\nu}$ for Table 
-\ref{tab:global} model 3, the two-component model favored by our \PLANCK+DIRBE 
+single-MBB models. Finally, we calculate $\chi^2_{\nu}$ for Table 
+\ref{tab:global} model 2, the two-component model favored by our \PLANCK+DIRBE 
 correlation slopes. In this case, we achieve the best goodness-of-fit out of 

### 2014-07-12 ms.tex
mentioning/referring to newly added sections where appropriate throughout the text

@@
 isolate thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we 
-explain the dust emission model we fit to the \PLANCK~and \IRAS~data. In 
-$\S$\ref{sec:global} we describe our constraints on this model's global 
-parameters derived from the \PLANCK~High Frequency Instrument (HFI) maps. In 
-$\S$\ref{sec:fitting} we detail the Markov chain Monte Carlo (MCMC) method with
-which we have estimated the spatially varying parameters of our model. In 
-$\S$\ref{sec:ebv} we calibrate our derived optical depth to reddening at 
-optical wavelengths. In $\S$\ref{sec:release} we present the full-sky maps of 
-dust temperature and optical depth we have obtained, and conclude in 
-$\S$\ref{sec:conclusion}.
+explain the dust emission model we apply to the \PLANCK~and \IRAS/DIRBE data. 
+In $\S$\ref{sec:bpcorr}, we discuss the details of predicting 
+\PLANCK~observations based on this dust model. In $\S$\ref{sec:global} we 
+derive constraints on our model's global parameters based on the \PLANCK~High 
+Frequency Instrument (HFI) maps. In $\S$\ref{sec:fitting} we detail the Markov 
+chain Monte Carlo (MCMC) method with which we have estimated the spatially 
+varying parameters of our model. In $\S$\ref{sec:ebv} we calibrate our derived 
+optical depth to reddening at optical wavelengths. In $\S$\ref{sec:release} we 
+present the full-sky maps of dust temperature and optical depth we have 
+obtained, and conclude in $\S$\ref{sec:conclusion}.
 
@@
 
-% mention that the two different emissivity power laws allow 
-% the model to simultaneously explain narrow SED peak, and flattening
-% of SED toward the millimeter
 At sufficiently high frequencies, Galactic thermal dust emission can be 
@@
 angular resolution relative to the FIRAS spectra. The \PLANCK~data thereby 
-allow us to derive an improved temperature correction at near-\IRAS~resolution,
-re-evaluate the best-fit global dust properties, and fit additional parameters 
-of the two-component model as a function of position on the sky. 
+allow us to derive an improved temperature correction at near-\IRAS~resolution
+($\S$\ref{sec:mcmc}), re-evaluate the best-fit global dust properties 
+($\S$\ref{sec:global}, $\S$\ref{sec:hier}), and fit additional parameters 
+of the two-component model as a function of position on the sky 
+($\S$\ref{sec:lores}). 
 % in this last sentence reference the relevant sections for each sub-goal 

### 2014-07-12 ms.tex
mention emission predictions section at end of intro, other minor clean-up

@@
 
-% might be more appropriate to cite the 2D dust map Eddie is making rather
-% than the `methods' paper
-
 In $\S$\ref{sec:data} we introduce the data used throughout this study. In 
@@
 varying parameters of our model. In $\S$\ref{sec:ebv} we calibrate our derived 
-optical depth to reddening at optical wavelengths. In $\S$\ref{sec:release} we 
-present the full-sky maps of dust temperature and optical depth we have 
-obtained, and conclude in $\S$\ref{sec:conclusion}.
+optical depth to reddening at optical wavelengths. In $\S$\ref{sec:lofreq} we
+evaluate the accuracy of our two-component thermal dust emission predictions 
+from 100-217 GHz. In $\S$\ref{sec:release} we present the full-sky maps of dust
+temperature and optical depth we have obtained, and conclude in 
+$\S$\ref{sec:conclusion}.
 
@@
 rms of the per-quadrant offsets was 0.0586 MJy/sr.
-
-% in previous sentence, think it might be better to only quote rms, and
-% omit the ranges of values for each parameter ?
 
@@
 \section{Low-frequency Emission Predictions}
+\label{sec:lofreq}
 FDS99 originally performed their \PLANCK+DIRBE dust SED analysis for the sake 

### 2014-07-12 ms.tex
explain meaning of q1, q2, f1, f2

@@
 \begin{equation}
-M_{\nu} \propto f_{1}q_{1}\Big(\frac{\nu}{\nu_{0}}\Big)^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}\Big(\frac{\nu}{\nu_0}\Big)^{\beta_2}B_{\nu}(T_2)
+M_{\nu} \propto f_{1}q_{1}\Big(\frac{\nu}{\nu_{0}}\Big)^{\beta_1}B_{\nu}(T_1) + f_{2}q_{2}\Big(\frac{\nu}{\nu_0}\Big)^{\beta_2}B_{\nu}(T_2)
 \end{equation}
@@
 emissivity power-law indices of the cold and hot components respectively. 
-$q_1/q_2$ encodes the relative emission/absorption cross-sections of the two 
-dust species, while $f_1$ dictates the relative amounts of each species 
-present. Following the convention of FDS99, we choose $\nu_0$=3000 GHz.
+$q_1$ represents the ratio of FIR emission cross section to optical absorption 
+cross section for species 1, and similarly $q_2$ for species 2. $f_1$ and 
+$f_2$ dictate the relative contributions of the two MBB components to the
+combined SED, and can be thought of as encoding the mass fraction of each 
+species, although technically $f_1$ ($f_2$) is the optical absorption 
+cross-section weighted mass fraction for species 1 (2). Following the 
+convention of FDS99, we choose $\nu_0$=3000 GHz and take $f_2$=(1$-$$f_1$).
 
@@
 
-Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. Our color correction 
-approach allows us to predict $\tilde{I}_{\nu_i}$ by computing monochromatic 
-flux densities at the central frequency $\nu_{i,c}$ and then multiplying by 
-factors $b_{\nu_i}(T, \beta)$ which are interpolated off of a set of 
-precomputed, one-dimensional lookup tables each listing $b_{\nu_i}(T, \beta)$ 
-as a function of $T$. We avoided the need to interpolate in both $\beta$ and 
-$T$ by computing only a small set of one dimensional correction factors for the
-particular set of $\beta$ values of interest (e.g. $\beta$=1.67, 2.7, 
-1.63, 2.82 ..., see Table \ref{tab:global}).
+%Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. 
+Our color correction approach allows us to predict $\tilde{I}_{\nu_i}$ by 
+computing monochromatic flux densities at the central frequency $\nu_{i,c}$ and
+then multiplying by factors $b_{\nu_i}(T, \beta)$ which are interpolated off of
+a set of precomputed, one-dimensional lookup tables each listing 
+$b_{\nu_i}(T, \beta)$ as a function of $T$. We avoided the need to interpolate 
+in both $\beta$ and $T$ by computing only a small set of one dimensional 
+correction factors for the particular set of $\beta$ values of interest (e.g. 
+$\beta$=1.67, 2.7, 1.63, 2.82 ..., see Table \ref{tab:global}).
 

### 2014-07-13 ms.tex
removed f1 Lambert figure, added 100-217 GHz emission prediction figure and wrote corresponding discussion text

@@
 
-\begin{figure}
-\begin{center}
-\epsfig{file=f1_lambert.eps, width=3.3in}
-\caption{\label{fig:f1lambert} The results of our low-resolution fit with $f_1$
-allowed to vary, shown in Lambert projection to highlight the salient features 
-near the north Galactic pole.}
-\end{center}
-\end{figure}
+%%%\begin{figure}
+%%%\begin{center}
+%%%\epsfig{file=f1_lambert.eps, width=3.3in}
+%%%\caption{\label{fig:f1lambert} The results of our low-resolution fit with $f_1$
+%%%allowed to vary, shown in Lambert projection to highlight the salient features 
+%%%near the north Galactic pole.}
+%%%\end{center}
+%%%\end{figure}
 
@@
 highlight these regions of unusually high $f_1$, we display the northern
-Galactic hemisphere in Lambert projection in Figure \ref{fig:f1lambert}.
+Galactic hemisphere in Lambert projection in Figure \ref{fig:f1}.
 
@@
 
-% compare 100-217 GHz predictions using my model versus Planck Collaboration
-% single-MBB model
+\begin{figure*}
+\begin{center}
+\epsfig{file=compare_lofreq.eps, width=6.6in}
+\caption{\label{fig:lofreq} Comparison of low-frequency thermal dust emission 
+predictions.}
+\end{center}
+\end{figure*}
+
+To assess the accuracy of low-frequency emission predictions, we compare
+the \PLANCK~HFI map at each of 100, 143, 217 GHz to the corresponding 
+single-MBB and two-component predictions, with all maps smoothed to 
+$1^{\circ}$ FWHM and binned down to $N_{side}=64$. We restrict to the 
+same set of pixels used for the goodness-of-fit analysis of 
+$\S$\ref{sec:hier}, with $|b|>30^{\circ}$ and $|\beta|>30^{\circ}$, also 
+avoiding molecular emission, the SMICA inpainting mask, and compact sources. We
+then perform a linear fit between the \PLANCK~observed emission and the 
+predicted emission at each frequency and for each emission model. For these
+fits, we consider the predicted emission to be the independent variable, 
+since it has higher S/N than the observations, especially at 100 and 143 GHz.
+We also assign pixel weights proportional to the predicted emission, so that
+the best-fit lines faithfully capture the linear trend exhibited 
+without being biased by the large number of very low S/N pixels with minimal 
+emission. Scatter plots between the predicted and observed emission are shown 
+in Figure \ref{fig:lofreq}. The best-fit lines are overplotted and their 
+equations are given in the top left corner of each subplot.
+
+All of the best-fit offsets, in both the single-MBB and two-component cases,
+are within the uncertainties quoted in Table \ref{table:offs}. On the other 
+hand, Figure \ref{fig:lofreq} shows that the \cite{planckdust} single-MBB 
+predictions yield slopes substantially different from unity: 1.079 at 217 GHz, 
+1.126 at 143 GHz, and 1.188 at 100 GHz. The fact that the slopes are larger 
+than unity indicates that the \cite{planckdust} predictions are systematically 
+low. The systematic underprediction evidently become gradually more severe as 
+lower frequencies are considered, with a 7.9\% underprediction at 217 GHz, a 
+12.6\% underprediction at 143 GHz and an 18.8\% underprediction at 100 GHz.
+
+For the case of the two-component model, we perform full-resolution 217-3000 
+GHz fits using the \PLANCK+DIRBE favored global parameters (Table 
+\ref{tab:global}, model 2), then smooth to $1^{\circ}$ FWHM and bin down to 
+$N_{side}=64$ before predicting the 100-217 GHz emission. The bottom row of
+Figure 14 shows that each of the best-fit lines is very similar to the 
+corresponding red line which represents a perfect match between predicted and 
+observed emission. More quantitatively, the two-component slopes are all within
+2.2\% of unity: 0.978 at 217 GHz, 0.986 at 143 GHz and 1.022 at 100 GHz. 
+We note that at 217 GHz, the good agreement is in some sense predetermined by 
+the fact that \PLANCK~217 GHz has been included in our two-component MCMC fits.
+On the other hand, the 143 and 100 GHz predictions are truly based on 
+extrapolation.
+
+% mention imprint of Planck team's half-degree on low-freq extrapolation ?
 
@@
 
-%end section saying that the predictions accessible through our data 
-% release should be investigated/tested/swapped in by people doing
-% B-mode stuff
-
-%striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping
-%%%An important difference between our maps and those of \cite{planckdust} is 
-%%%our 
-%%%use of SFD \verb|i100| instead of IRIS 100$\mu$m \citep{IRIS}. Residual 
-%%%\IRAS~striping at levels higher than that remaining in SFD \verb|i100| is 
-%%%clearly visible in the \cite{planckdust} maps.
-
-%we actually have 6.1' arcminute resolution
 %%%It is true that we have smoothed the input intensity maps for this study 

### 2014-07-13 ms.tex
clean-up of low-frequency predictions section, added sentence about superiority of two-component emission predicts to conclusions section

@@
 
-All of the best-fit offsets, in both the single-MBB and two-component cases,
+In both the single-MBB and two-component cases, all of the best fit offsets
 are within the uncertainties quoted in Table \ref{table:offs}. On the other 
-hand, Figure \ref{fig:lofreq} shows that the \cite{planckdust} single-MBB 
-predictions yield slopes substantially different from unity: 1.079 at 217 GHz, 
-1.126 at 143 GHz, and 1.188 at 100 GHz. The fact that the slopes are larger 
-than unity indicates that the \cite{planckdust} predictions are systematically 
-low. The systematic underprediction evidently become gradually more severe as 
-lower frequencies are considered, with a 7.9\% underprediction at 217 GHz, a 
-12.6\% underprediction at 143 GHz and an 18.8\% underprediction at 100 GHz.
+hand, the top row of Figure \ref{fig:lofreq} shows that the \cite{planckdust} 
+single-MBB predictions yield slopes substantially different from unity: 1.079 
+at 217 GHz, 1.126 at 143 GHz, and 1.188 at 100 GHz. The fact that the slopes 
+are larger than unity indicates that the \cite{planckdust} predictions are 
+systematically low. The systematic underprediction evidently become gradually 
+more severe as lower frequencies are considered, with a 7.9\% underprediction 
+at 217 GHz, a 12.6\% underprediction at 143 GHz and an 18.8\% underprediction 
+at 100 GHz.
 
@@
 the fact that \PLANCK~217 GHz has been included in our two-component MCMC fits.
-On the other hand, the 143 and 100 GHz predictions are truly based on 
-extrapolation.
+On the other hand, the 143 and 100 GHz predictions are based on extrapolation.
+
+We conclude from our predicted versus observed emission comparison that our 
+two-component model outperforms the \cite{planckdust} single-MBB model at 
+predicting Galactic thermal dust emission in diffuse regions from 100-217 GHz.
+
+% could add a last sentence trying to soften this, acknowledging that 
+% planck team warned about their model below 353 GHz
 
@@
 dust SED's preference for two MBB components rather than just one is not
-simply an idiosyncracy of the FIRAS spectra. We recommend that those interested
-in thermal dust foregrounds in the 100-3000 GHz frequency range use our data 
-release to predict unpolarized dust emission, at the very least in order to 
-help determine the level at which the choice of dust emission model may 
-influence their conclusions.
+simply an idiosyncracy of the FIRAS spectra. Furthermore, we showed in 
+$\S$\ref{sec:lofreq} that our 100-217 GHz two-component emission predictions
+are more accurate than those of \cite{planckdust} by margins of $\sim$5-15\%.
+We therefore recommend that those interested in thermal dust foregrounds in 
+the 100-3000 GHz frequency range use our data release to predict unpolarized 
+dust emission, at the very least in order to help determine the level at which 
+the choice of dust emission model may influence their conclusions.
 %last sentence needs work

### 2014-07-14 ms.tex
starting to edit/re-write MCMC sampling description/discussion

@@
 two-component dust emission model parameters which are permitted to vary
-spatially. We perform two types of fits: (1) full-resolution 
-$6.1'$ fits, in which just two parameters, the SED normalization and the hot 
-dust temperature $T_2$, vary spatially and (2) lower-resolution fits in which 
-$f_1$ is also allowed to vary from one line of sight to another.
+spatially. We use the MCMC procedure described to perform two types of fits: 
+(1) full-resolution $6.1'$ fits, in which only  the SED normalization and dust 
+temperatures vary spatially, and (2) lower-resolution fits in which $f_1$ is 
+also allowed to vary from one line of sight to another.
 
@@
 \label{sec:pix}
-For the purpose of fitting, we break the sky into $\sim$50 million pixels of 
+For the purpose of fitting, we divide the sky into $\sim$50 million pixels of 
 angular size $\sim$1.72$'$, defined by the HEALPix pixelization in Galactic 
@@
 consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
- fixed, while the dust spectrum normalization and dust temperature vary for
-each line-of-sight. In order to predict the dust SED for a given pixel, we are 
-therefore left with two remaining degrees of freedom, and must choose an 
-appropriate set of two parameters to sample and thereby constrain via MCMC. To 
-determine the SED normalization in each pixel, we draw samples in 
-$\tilde{I}_{545}$, the broadband intensity in the 545 GHz bandpass, as defined 
-in Equation \ref{eqn:inten}. With the four aforementioned global parameters 
-fixed, the dust spectrum shape is determined entirely by the two dust 
-temperatures, which are coupled. To constrain the dust temperatures,
+fixed, while the dust spectrum normalization and dust temperatures are allowed 
+to vary for each line-of-sight. In order to predict the dust SED for a given 
+pixel, we are thus left with two remaining degrees of freedom, and must 
+choose an appropriate set of two parameters to sample and thereby constrain via
+MCMC. To determine the SED normalization in each pixel, we draw samples in 
+$\tilde{I}_{545}$, the `IRAS convention' intensity in the 545 GHz bandpass, 
+as defined in Equation \ref{eqn:inten}. With the four aforementioned global 
+parameters fixed, the dust spectrum shape is determined entirely by the two 
+dust temperatures, which are coupled. To constrain the dust temperatures,
  we sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we 
-compute the corresponding value of $T_1$, thereby specifying ($\beta$, $T$) for
-both MBB components and thus fully specifying the SED shape. In principle,
-we could sample in either $T_1$ or $T_2$, but have chosen to sample in $T_2$ 
-because emission from this component dominates in the relatively high frequency
-bands which most strongly constrain the dust temperatures.
+compute the corresponding value of $T_1$, thereby determining the temperature
+and emissivity power law index for both MBB components and thus fully 
+specifying the SED shape. In principle, we could sample in either $T_1$ or 
+$T_2$, but have chosen to sample in $T_2$ because emission from this component 
+dominates in the relatively high frequency bands which most strongly constrain 
+the dust temperatures.
 
@@
 
-Here \{$I$\} denotes the set of observed broadband intensities, $I_{217}$, 
-$I_{353}$, etc. The likelihood function is given by:
+Here \{$I$\} denotes the set of observed intensities quoted under
+the `IRAS convention': $I_{217}$, $I_{353}$, ... The likelihood function is 
+given by:
 
@@
 
-In order to obtain reasonable fitting results at high latitude where the data 
-is noisy, we include the prior on $T_2$:
-
-%what about the offset uncertainty for 217 GHz
+In order to ensure reasonable fit results at high latitude where the intensity 
+constraints are noisy, we include a prior on $T_2$:
 
@@
 
-% maybe have a section justifying the T2 prior value of 16.2K, presumably using
-% FIRAS as a cross-check?
-
-With $\bar{T}_2$ = 16.2 K and $\sigma_{\bar{T}_2}$ = 1.4 K. In principle, there
+% justification for T2 prior standard deviation
+With $\bar{T}_2$ = 15.7 K and $\sigma_{\bar{T}_2}$ = 1.4 K. The $T_2$ prior 
+mean is chosen based on the typical high-latitude $T_2$ value derived from
+the correlation slope analysis from $\S$\ref{sec:global}. In principle, there 
 can also be an informative prior on $\tilde{I}_{545}$. However, we have chosen 
@@
 \begin{center}
-\epsfig{file=compare_lofreq.eps, width=6.6in}
+\epsfig{file=compare_lofreq.eps, width=6.8in}
 \caption{\label{fig:lofreq} Comparison of low-frequency thermal dust emission 

### 2014-07-14 ms.tex
added caption for low-frequency emission prediction comparison figure, auditing for nside formatting

@@
 
-With $p$ denoting a single nside=64 HEALPix pixel \citep{healpix} in the maps 
-$\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
+With $p$ denoting a single $N_{side}$=64 HEALPix pixel \citep{healpix} in the 
+maps $\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
 $\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
@@
 \epsfig{file=sed.eps, width=3.3in}
-\caption{\label{fig:sed} Planck SED for a single nside=2048 pixel in the 
+\caption{\label{fig:sed} Planck SED for a single $N_{side}$=2048 pixel in the 
 Polaris region. Note that the two lowest-frequency data points (\PLANCK~100, 
@@
 \epsfig{file=posteriors.eps, width=7.0in}
-\caption{Gridded posterior PDFs for three nside=2048 pixels. Red crosses mark 
-the best-fit parameters based on our Markov chain sampling of the posterior. 
-The posterior distributions are in general extremely well-behaved, showing
-no multimodality or other pathological qualities. Our MCMC parameter 
+\caption{Gridded posterior PDFs for three $N_{side}$=2048 pixels. Red crosses 
+mark the best-fit parameters based on our Markov chain sampling of the 
+posterior. The posterior distributions are in general extremely well-behaved, 
+showing no multimodality or other pathological qualities. Our MCMC parameter 
 estimates coincide well with the peaks in the gridded posteriors. The 
@@
 $log(P)$ and white representing $max(log(P))-5$. Left: Low S/N pixel at 
-high-latitude in Galactic north. Center: High S/N pixel in the Polaris region. 
-Right: Low S/N pixel at high-latitude in the Galactic south.}
+high latitude in the Galactic north. Center: High S/N pixel in the Polaris 
+region. Right: Low S/N pixel at high latitude in the Galactic south.}
 \end{center}
@@
 \epsfig{file=compare_lofreq.eps, width=6.8in}
-\caption{\label{fig:lofreq} Comparison of low-frequency thermal dust emission 
-predictions.}
+\caption{\label{fig:lofreq} Comparison between low-frequency thermal dust 
+emission predictions from our best-fit two-component model (Table 
+\ref{tab:global}, model 2) and those of \cite{planckdust}. The top row shows
+scatterplots of the \cite{planckdust} predictions versus observed \PLANCK~100 
+GHz (left), \PLANCK~143 GHz (center) and \PLANCK~217 GHz (right). The bottom 
+row shows scatterplots of the corresponding two-component predictions versus
+\PLANCK~observations. In all cases, the blue line indicates the best-fit linear
+relationship, while the red line represents a perfect match between predictions
+and observations. The lines of best-fit illustrate that the single-MBB model 
+systematically underpredicts emission (in the multiplicative sense) by 18.8\%, 
+12.6\% and 7.9\% at 100, 143 and 217 GHz respectively. On the other hand, by 
+the same metric, the two-component model predictions at 100-217 GHz are always 
+accurate to within $\le$2.2\%.}
 \end{center}
@@
 
+% could add a sentence noting that similar zodi corrections are evident
+% in all existing, comparable temperature map data products : Planck 2013a,
+% SFD98 and FDS99
+
 % audit for word ``zodi'' ... is this an acceptable jargon term ?

### 2014-07-14 ms.tex
caption for full-sky results figure

@@
 \epsfig{file=results.eps, width=7.0in}
-\caption{\label{fig:results} Our best-fit $T_2$, binned to 27.5$'$ resolution}
+\caption{\label{fig:results} (top) Hot dust temperature derived from our 
+full-resolution two-component model fits of \PLANCK~217-857 GHz and SFD 
+\texttt{i100}, downbinned to 27.5$'$ resolution. (bottom) Corresponding
+full-sky map of best-fit 545 GHz optical depth.}
 \end{center}
@@
 likelihood function in our MCMC procedure. However, this treatment falls far 
-short of actually removing the spatial imprint of the CIBA on our optical depth
-and temperature maps. The CIB anisotropies are more prominent in our optical 
-depth map relative to that of SFD because of the lower-frequency \PLANCK~maps 
-we rely upon to achieve a high-resolution temperature correction.
+short of actually removing the spatial imprint of the CIBA on our derived 
+parameters. The CIB anisotropies are more prominent in our optical depth map 
+relative to that of SFD because of the lower-frequency \PLANCK~maps we rely 
+upon to achieve a high-resolution temperature correction.
 

### 2014-07-14 ms.tex
f1 map figure caption
clarify that we use the Planck+DIRBE revised global parameters by default in full-resolution fits

@@
 consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
-fixed, while the dust spectrum normalization and dust temperatures are allowed 
-to vary for each line-of-sight. In order to predict the dust SED for a given 
-pixel, we are thus left with two remaining degrees of freedom, and must 
-choose an appropriate set of two parameters to sample and thereby constrain via
-MCMC. To determine the SED normalization in each pixel, we draw samples in 
-$\tilde{I}_{545}$, the `IRAS convention' intensity in the 545 GHz bandpass, 
-as defined in Equation \ref{eqn:inten}. With the four aforementioned global 
+fixed. By default, we employ the best-fit \PLANCK+DIRBE global parameters of 
+Table \ref{tab:global}, model 2, although our data release 
+($\S$\ref{sec:release}) includes fits with the FDS99 global parameters as well.
+Still,  the dust spectrum normalization and dust temperatures are allowed to 
+vary for each line-of-sight. In order to predict the dust SED for a given 
+pixel, we are thus left with two remaining degrees of freedom, and must choose 
+an appropriate set of two parameters to sample and thereby constrain via MCMC. 
+To determine the SED normalization in each pixel, we draw samples in 
+$\tilde{I}_{545}$, the `IRAS convention' intensity in the 545 GHz bandpass, as 
+defined in Equation \ref{eqn:inten}. With the four aforementioned global 
 parameters fixed, the dust spectrum shape is determined entirely by the two 
-dust temperatures, which are coupled. To constrain the dust temperatures,
- we sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we 
-compute the corresponding value of $T_1$, thereby determining the temperature
-and emissivity power law index for both MBB components and thus fully 
-specifying the SED shape. In principle, we could sample in either $T_1$ or 
-$T_2$, but have chosen to sample in $T_2$ because emission from this component 
-dominates in the relatively high frequency bands which most strongly constrain 
-the dust temperatures.
+dust temperatures, which are coupled. To constrain the dust temperatures, we 
+sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we compute
+the corresponding value of $T_1$, thereby determining the temperature and 
+emissivity power law index for both MBB components and thus fully specifying 
+the SED shape. In principle, we could sample in either $T_1$ or $T_2$, but have
+chosen to sample in $T_2$ because emission from this component dominates in the
+relatively high frequency bands which most strongly constrain the dust 
+temperatures.
 
@@
 \epsfig{file=f1_1deg.eps, width=3.3in}
-\caption{\label{fig:f1} The results of our low-resolution fit with $f_1$
-allowed to vary.}
+\caption{\label{fig:f1} The $1^{\circ}$ FWHM map of $f_1$ derived from our 
+low-resolution fit in which $f_1$ is allowed to vary spatially.}
 \end{center}

### 2014-07-14 ms.tex
rewrite of T2 prior explanation

@@
 parameters $\tilde{I}_{545}$ and $T_2$. For each pixel, we run a 
-Metropolis-Hastings Markov chain sampling the posterior probability as a 
-function of the two parameters $\tilde{I}_{545}$ and $T_2$. More specifically, 
-we are sampling the posterior given by:
+Metropolis-Hastings Markov chain sampling the posterior probability of
+reproducing the observed 217-3000 GHz SED as a function of the two parameters 
+$\tilde{I}_{545}$ and $T_2$. More specifically, we are sampling the posterior 
+given by:
 
@@
 
-In order to ensure reasonable fit results at high latitude where the intensity 
-constraints are noisy, we include a prior on $T_2$:
+We include the following prior on the hot dust temperature:
 
@@
 mean is chosen based on the typical high-latitude $T_2$ value derived from
-the correlation slope analysis from $\S$\ref{sec:global}. In principle, there 
-can also be an informative prior on $\tilde{I}_{545}$. However, we have chosen 
-to assume a uniform prior on the SED normalization and, as a matter of 
-notation, will omit $P(\tilde{I}_{545})$ henceforward. In practice we always 
-perform computations using logarithms of the relevant probabilities.
+the correlation slope analysis from $\S$\ref{sec:global}. We find, as 
+desired, that this relatively broad $T_2$ prior has little influence on the 
+derived temperatures, other than to regularize the rare pixels with one or more
+defective intensities which might otherwise yield unreasonable parameter
+estimates. In principle, there can also be an informative prior on 
+$\tilde{I}_{545}$. However, we have chosen to assume a uniform prior on the SED
+normalization and, as a matter of notation, will omit $P(\tilde{I}_{545})$ 
+henceforward. In practice we always perform computations using logarithms of 
+the relevant probabilities.
 %mention something about the proposal distribution at some point?

### 2014-07-15 ms.tex
discussing proposal distribution

@@
 parameters $\tilde{I}_{545}$ and $T_2$. For each pixel, we run a 
-Metropolis-Hastings Markov chain sampling the posterior probability of
+Metropolis-Hastings (MH) Markov chain sampling the posterior probability of
 reproducing the observed 217-3000 GHz SED as a function of the two parameters 
@@
 
-% justification for T2 prior standard deviation
 With $\bar{T}_2$ = 15.7 K and $\sigma_{\bar{T}_2}$ = 1.4 K. The $T_2$ prior 
@@
 $\tilde{I}_{545}$ = $I_{545}$ and $T_2$ consistent with the FDS99 
-DIRBE 100$\mu$m/240$\mu$m ratio map $\mathscr{R}$. We run 500 steps of burn-in 
-and then 2000 steps during which we keep track of the proposed $T_{2, j}$ and 
-$\tilde{I}_{545, j}$ values at the $j^{th}$ step since the end of burn-in. From
- these 2000 samples, we compute estimates of each parameter, 
-$T_2$ = $\langle T_{2, j} \rangle$, $\tilde{I}_{545}$ = 
-$\langle \tilde{I}_{545, j} \rangle$, and of each parameter's variance, 
+DIRBE 100$\mu$m/240$\mu$m ratio map $\mathscr{R}$. The initial proposal 
+distribution is a two-dimensional normal distribution, with 
+$\sigma_{T_2}$=0.25 K and 
+$\sigma_{\tilde{I}_{545}}$=max(0.01$\times$$I_{545}$, 0.05 MJy/sr). We run 5 
+iterations of burn-in, each consisting of 500 MH steps. After each burn-in 
+iteration, we rescale the proposal distribution so as to ultimately attain an 
+acceptance fraction $f_{acc}$ as close as possible to the optimal value 
+$f_{opt}=0.234$. This is accomplished by multiplying the proposal distribution 
+standard deviations by $f_{acc}$/$f_{opt}$.
+
+We then estimate the parameters and their covariances by performing 10000 steps
+during which we keep track of the proposed $T_{2, j}$ and $\tilde{I}_{545, j}$ 
+values at the $j^{th}$ step since the end of burn-in. From these 2000 samples, 
+we compute estimates of each parameter, $T_2$ = $\langle T_{2, j} \rangle$, 
+$\tilde{I}_{545}$ = $\langle \tilde{I}_{545, j} \rangle$, and of each 
+parameter's variance, 
 $\sigma^2_{T_2}$ = $\langle T^2_{2, j} \rangle-\langle T_{2, j} \rangle ^2$ and
@@
 \rangle-\langle \tilde{I}_{545, j} \rangle ^2$. We also compute the 
- corresponding estimate of the monochromatic two-component intensity at 545 
-GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
+corresponding estimate of the monochromatic two-component intensity at 545 GHz,
+$M_{545}$ = $\langle M_{545, j} \rangle$ = 
 $\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$  and its variance. 

### 2014-07-15 ms.tex
still fixing up explanation/details of MCMC procedure

@@
 
-We then estimate the parameters and their covariances by performing 10000 steps
-during which we keep track of the proposed $T_{2, j}$ and $\tilde{I}_{545, j}$ 
-values at the $j^{th}$ step since the end of burn-in. From these 2000 samples, 
-we compute estimates of each parameter, $T_2$ = $\langle T_{2, j} \rangle$, 
-$\tilde{I}_{545}$ = $\langle \tilde{I}_{545, j} \rangle$, and of each 
-parameter's variance, 
-$\sigma^2_{T_2}$ = $\langle T^2_{2, j} \rangle-\langle T_{2, j} \rangle ^2$ and
+We then estimate the parameters and their uncertainties by performing 10,000 
+sampling steps, with $T_{2, j}$ and $\tilde{I}_{545, j}$ denoting the proposed 
+parameter values at the $j^{th}$ step since the end of burn-in. From these 
+10,000 samples, we compute estimates of each parameter's mean, 
+$\langle T_2 \rangle$ = $\langle T_{2, j} \rangle$, 
+$\langle \tilde{I}_{545} \rangle$ = $\langle \tilde{I}_{545, j} \rangle$, of 
+each parameter's variance, 
+$\sigma^2_{T_2}$ = $\langle T^2_{2, j} \rangle-\langle T_{2, j} \rangle ^2$, 
 $\sigma^2_{\tilde{I}_{545}}$=$\langle \tilde{I}^2_{545, j} 
-\rangle-\langle \tilde{I}_{545, j} \rangle ^2$. We also compute the 
-corresponding estimate of the monochromatic two-component intensity at 545 GHz,
-$M_{545}$ = $\langle M_{545, j} \rangle$ = 
+\rangle-\langle \tilde{I}_{545, j} \rangle ^2$ and of the covariance 
+$\sigma_{T_2}\sigma_{\tilde{I}_{545}}$=$\langle T_{2,j}-\langle T_2 \rangle 
+\rangle \langle \tilde{I}_{545, j} - \langle \tilde{I}_{545} \rangle \rangle$.
+
+We also compute the corresponding estimate of the monochromatic two-component 
+intensity at 545 GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
 $\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$  and its variance. 

### 2014-07-15 ms.tex
minor clean-up of MCMC sampling procedure description

@@
 distribution is a two-dimensional normal distribution, with 
-$\sigma_{T_2}$=0.25 K and 
-$\sigma_{\tilde{I}_{545}}$=max(0.01$\times$$I_{545}$, 0.05 MJy/sr). We run 5 
-iterations of burn-in, each consisting of 500 MH steps. After each burn-in 
-iteration, we rescale the proposal distribution so as to ultimately attain an 
-acceptance fraction $f_{acc}$ as close as possible to the optimal value 
-$f_{opt}=0.234$. This is accomplished by multiplying the proposal distribution 
-standard deviations by $f_{acc}$/$f_{opt}$.
-
-We then estimate the parameters and their uncertainties by performing 10,000 
-sampling steps, with $T_{2, j}$ and $\tilde{I}_{545, j}$ denoting the proposed 
-parameter values at the $j^{th}$ step since the end of burn-in. From these 
-10,000 samples, we compute estimates of each parameter's mean, 
+$\sigma_{T_2}$=0.25 K, 
+$\sigma_{\tilde{I}_{545}}$=max(0.01$\times$$I_{545}$, 0.05 MJy/sr) and
+$\sigma_{T_2}\sigma_{\tilde{I}_{545}}$=0. We run 5 iterations of burn-in, each 
+consisting of 500 MH steps. After each burn-in iteration, we rescale the 
+proposal distribution so as to ultimately attain an acceptance fraction 
+$f_{acc}$ as close as possible to the optimal value $f_{opt}=0.234$. This is 
+accomplished by multiplying the proposal distribution standard deviations by 
+$f_{acc}$/$f_{opt}$.
+
+After burn-in, we estimate the parameters and their uncertainties by performing
+10,000 sampling steps, with $T_{2, j}$ and $\tilde{I}_{545, j}$ denoting the 
+proposed parameter values at the $j^{th}$ step since the end of burn-in. From 
+these 10,000 samples, we compute estimates of each parameter's mean, 
 $\langle T_2 \rangle$ = $\langle T_{2, j} \rangle$, 
@@
 function $S_{545}$ calculated according to Equation \ref{eqn:source}.
-
-%in the above need to mention/introduce the use of ``j'' to denothe the j'th
-%step of the MH sampling **after** burn-in has finished
-
-% actually we I think we want to keep track of $\tilde{I}_{545}$/b_{545}
-% which is the monochromatic value, since that is most useful downstream
-% when making foreground predictions that typically won't have anything
-% to do with Planck bandpasses
 

### 2014-07-15 ms.tex
finish explaining MCMC procedure, and mention validation of MCMC results with gridded posteriors

@@
 
+After obtaining this initial estimate of the covariance matrix for each
+pixel, we re-run the entire MCMC procedure, starting from the first burn-in 
+iteration, but this time beginning with a proposal distribution that is a 
+two-dimensional normal distribution with covariance equal to the first-pass
+covariance estimate. This gives the proposal distribution for each pixel
+ approximately the ``right shape'', whereas on the first pass we had to start
+by making ad hoc assumptions about the relative widths of the proposal 
+distribution in $\tilde{I}_{545}$ and $T_2$, and also assumed that the 
+$\sigma_{T_2}\sigma_{\tilde{I}_{545}}$=0 for the proposal distribution. We
+validated the recovered parameters and uncertainties from our MCMC procedure
+by comparing with results based on gridded posterior calculations. These 
+comparisons verified that the proposal distribution rescaling and reshaping 
+steps that we employ do improve the accuracy of the recovered 
+parameters/uncertainties, and that the parameters/uncertainties ultimately 
+derived are highly reliable.
+
 We also compute the corresponding estimate of the monochromatic two-component 

### 2014-07-15 ms.tex
re-wrote paragraph about 545 GHz optical depth and 545 GHz monochromatic intensity estimates

@@
 
-We also compute the corresponding estimate of the monochromatic two-component 
-intensity at 545 GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
-$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$  and its variance. 
-$M_{545}$ is of more general utility in making foreground predictions because 
-it provides the normalization for the two-component spectrum $M_{\nu}$, 
-independent of the \PLANCK~545 GHz bandpass. Lastly, we compute the 545 GHz
-optical depth as $\tau_{545}$ = $\langle \tau_{545, j} \rangle$ = 
-$\langle M_{545, j}/S_{545, j} \rangle$ and its variance, with the source 
-function $S_{545}$ calculated according to Equation \ref{eqn:source}.
+Lastly, during post burn-in sampling, we also estimate the monochromatic 
+two-component intensity at 545 GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
+$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$, its variance, and
+the 545 GHz optical depth $\langle \tau_{545, j} \rangle$ = 
+$\langle M_{545, j}/S_{545, j} \rangle$ and its variance. $\tau_{545}$ and 
+$M_{545}$ are more readily useful than the sampling parameters themselves for 
+translating our fit results into predicted reddening ($\S$\ref{sec:ebv}) and 
+thermal dust emission ($\S$\ref{sec:lofreq}), respectively.
+
+%$M_{545}$ is of more general utility in making foreground predictions because 
+%it provides the normalization for the two-component spectrum $M_{\nu}$, 
+%independent of the \PLANCK~545 GHz bandpass. Finally, we acompute the 545 GHz
+%optical depth as $\tau_{545}$ = and its variance, with the source 
+%function $S_{545}$ calculated according to Equation \ref{eqn:source}.
 

### 2014-07-15 ms.tex
start switching to vector notation for intensities in MCMC discussion, move second EBV residual figure

@@
 \label{eqn:post}
-P(\tilde{I}_{545}, T_2|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2)P(T_2)P(\tilde{I}_{545})
+P(\tilde{I}_{545}, T_2|\vec{I}~) \propto \mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2)P(T_2)P(\tilde{I}_{545})
 \end{equation}
@@
 
-Here \{$I$\} denotes the set of observed intensities quoted under
-the `IRAS convention': $I_{217}$, $I_{353}$, ... The likelihood function is 
-given by:
+Here $\vec{I}$ denotes the vector of observed intensities quoted under
+the `IRAS convention': $\vec{I}$ = ($I_{217}$, $I_{353}$, ..., $I_{3000}$). The
+likelihood function is given by:
 
 \begin{equation} \label{equ:like}
-\mathcal{L}(\{I\}|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(\tilde{I}_{\nu_{i}}|I_{\nu_{i}}, \sigma_{\nu_i})
+\mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(\tilde{I}_{\nu_{i}}|I_{\nu_{i}}, \sigma_{\nu_i})
 \end{equation}
@@
 
-Where the product runs over $\nu_i$ in $\{217,\ 353,\ 545,\ 857,\ 3000\}$ GHz
+Where the product runs over $\nu_i$$\in$$\{217,\ 353,\ 545,\ 857,\ 3000\}$ GHz
 and $\tilde{I}_{\nu_i}$ is a function of $\tilde{I}_{545}$ and $T_2$ as 
-specified by Equation \ref{eqn:inten}. For each pixel, the errors on each 
-intensity measurement $\sigma_{\nu_i}$ are given by:
+specified by Equation \ref{eqn:inten}. For each pixel, the uncertainty on each 
+intensity measurement $\sigma_{\nu_i}$ is given by:
 
@@
 
+\begin{figure*}
+\begin{center}
+\epsfig{file=ebv_resid_ecl.eps, width=6.6in}
+\caption{\label{fig:resid_ecl} Same as Figure \ref{fig:resid}, but 
+restricting to high ecliptic latitude, $|\beta|>20^{\circ}$. The top left and 
+top right plots both show that the bending of the reddening residuals as a 
+function of $E(B-V)_{SFD}$ as seen in Figure \ref{fig:resid} has been 
+eliminated. Further, the two-component reddening residual temperature 
+dependence (bottom left) has been significantly reduced relative to the
+corresponding trend shown in Figure \ref{fig:resid}, bottom left panel.}
+\end{center}
+\end{figure*}
+
 The only solution we have been able to identify that both removes the `bend' 
@@
 map (see the full-sky results shown in Figure \ref{fig:results}).
-
-\begin{figure*}
-\begin{center}
-\epsfig{file=ebv_resid_ecl.eps, width=6.6in}
-\caption{\label{fig:resid_ecl} Same as Figure \ref{fig:resid}, but 
-restricting to high ecliptic latitude, $|\beta|>20^{\circ}$. The top left and 
-top right plots both show that the bending of the reddening residuals as a 
-function of $E(B-V)_{SFD}$ as seen in Figure \ref{fig:resid} has been 
-eliminated. Further, the two-component reddening residual temperature 
-dependence (bottom left) has been significantly reduced relative to the
-corresponding trend shown in Figure \ref{fig:resid}, bottom left panel.}
-\end{center}
-\end{figure*}
 

### 2014-07-15 ms.tex
starting to re-write discussion of fits with f_1 allowed to vary

@@
 
-Here $\vec{I}$ denotes the vector of observed intensities quoted under
-the `IRAS convention': $\vec{I}$ = ($I_{217}$, $I_{353}$, ..., $I_{3000}$). The
-likelihood function is given by:
+Here $\vec{I}$ denotes the vector of observed thermal dust intensities quoted 
+under the `IRAS convention': $\vec{I}$ = ($I_{217}$, $I_{353}$, ..., 
+$I_{3000}$). The likelihood function is given by:
 
@@
 
-As explained in $\S$\ref{sec:modeling} and $\S$\ref{sec:samp}, our 
-full-resolution fits fix the parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ 
-globally so that only the dust temperatures and SED normalization vary on a 
-per-pixel basis. The reason for fixing so many parameters is that, at $6.1'$
-FWHM, only five SED measurements are available per pixel.
+%As explained in $\S$\ref{sec:modeling} and $\S$\ref{sec:samp}, our 
+%full-resolution fits fix the parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ 
+%globally so that only the dust temperatures and SED normalization vary on a 
+%per-pixel basis. The reason for fixing so many parameters is that, at $6.1'$
+%FWHM, only five SED measurements are available per pixel.
 
@@
 % to the effect of ``staying in overconstrained regime''
-
-However, sacrificing angular resolution in order to incorporate 
-the \PLANCK~100, 143 GHz bands can allow us to introduce an additional free 
-parameter and run our Markov chains in three-dimensional parameter space.
-
-We ran the Markov chains in three dimensions by allowing 
-$f_1$ to be a third free parameter. In these chains, we sampled the posterior
-given by:
-
-\begin{equation}
-\label{eqn:f1post}
-P(\tilde{I}_{545}, T_2, f_1|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2, f_1)P(T_2)P(f_1)
-\end{equation}
-
-We still employ the likelihood function of Equation \ref{equ:like}, the only
-difference being that $f_1$ can vary from proposal to proposal within each 
-individual pixel when predicting \{$\tilde{I}_{\nu_i}$\} with Equation 
-\ref{eqn:inten}. The prior $P(T_2)$ from Equation \ref{equ:t2prior} remains 
-unchanged. The prior on $f_1$ is:
-
-\begin{equation} \label{equ:f1prior}
-P(f_1) = \mathcal{N}(f_1|\bar{f}_1, \sigma_{\bar{f}_1})
-\end{equation}
-
-With $\bar{f}_1$=0.0363 and $\sigma_{\bar{f}_1}$=0.003. This is a fairly
-stringent prior, but we must restrict the fit from wandering with too much
-freedom, as we are attempting to constrain three parameters using an SED
-with only seven intensity measurements. To boost S/N, we have performed
-the fits using maps smoothed to $1^{\circ}$ resolution.
 
@@
 \end{figure}
+
+As mentioned in $\S$\ref{sec:modeling}, the combination of high S/N and high 
+angular resolution afforded by the \PLANCK~HFI maps provides us with the 
+opportunity to allow additional parameters of the two-component model, 
+previously fixed by FDS99, to vary spatially. Specifically, we consider
+allowing $f_1$ to vary, while maintaining $\beta_1$, $\beta_2$, and $q_1/q_2$
+spatially constant. In such fits, there will therefore be three free 
+parameters.
+
+% sentence or two about why f_1 is natural parameter to try varying 
+% rather than q1/q2 or beta1 or beta2 !!!!!~~!!!
+
+In order for such fits to remain sufficiently constrained with an additional 
+free parameter, we consider \PLANCK~maps smoothed to $1^{\circ}$ FWHM to 
+boost per-pixel S/N, and pixelize at $N_{side}=64$. We also include DIRBE 
+140$\mu$m and 240$\mu$m at degree resolution in the fits with free-$f_1$ fits.
+
+% also we're adding in 100 GHz and 143 GHz, which is something not
+% done in full-resolution fits
+
+We run the Markov chains in three dimensions sampling in all three of $f_1$,
+$\tilde{I}_{545}$ and $T_2$. We are now sampling the posterior given by:
+
+\begin{equation}
+\label{eqn:f1post}
+P(\tilde{I}_{545}, T_2, f_1|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2, f_1)P(T_2)P(f_1)
+\end{equation}
+
+This posterior still employs the likelihood function of Equation 
+\ref{equ:like}, the only difference being that $f_1$ can vary from proposal to 
+proposal within each individual pixel when predicting \{$\tilde{I}_{\nu_i}$\} 
+with Equation \ref{eqn:inten}. The prior $P(T_2)$ from Equation 
+\ref{equ:t2prior} remains unchanged. The prior on $f_1$ is:
+
+\begin{equation} \label{equ:f1prior}
+P(f_1) = \mathcal{N}(f_1|\bar{f}_1, \sigma_{\bar{f}_1})
+\end{equation}
+
+With $\bar{f}_1$=0.0363 and $\sigma_{\bar{f}_1}$=0.003. This is a fairly
+stringent prior, but we must restrict the fit from wandering with too much
+freedom, as we are attempting to constrain three parameters using an SED
+with only nine intensity measurements, several of which are quite noisy. 
+%To boost S/N, we have performed
+%the fits using maps smoothed to $1^{\circ}$ resolution.
 
@@
 
-The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. Some of 
-the most striking features occur near the north Galactic pole, and to 
-highlight these regions of unusually high $f_1$, we display the northern
-Galactic hemisphere in Lambert projection in Figure \ref{fig:f1}.
+The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. A 
+general trend of increasing $f_1$ towards lower Galactic latitudes is 
+apparent. The other most salient features are the relatively low
+values of $f_1$ in the Polaris flare, and the relatively high $f_1$ values
+near the north Galactic pole.
+
+%Some of 
+%the most striking features occur near the north Galactic pole, and to 
+%highlight these regions of unusually high $f_1$, we display the northern
+%Galactic hemisphere in Lambert projection in Figure \ref{fig:f1}.
 

### 2014-07-15 ms.tex
reiterate that 100, 143 GHz two-component predictions shown are indeed extrapolations

@@
 \label{sec:lofreq}
-FDS99 originally performed their \PLANCK+DIRBE dust SED analysis for the sake 
-of accurately forecasting low-frequency CMB foregrounds. Recently, Galactic CMB
+FDS99 originally performed their FIRAS+DIRBE dust SED analysis for the sake of
+accurately forecasting low-frequency CMB foregrounds. Recently, Galactic CMB
 foregrounds, especially in the 100-150 GHz frequency range, have become a focal
@@
 the same metric, the two-component model predictions at 100-217 GHz are always 
-accurate to within $\le$2.2\%.}
+accurate to within $\le$2.2\%. The two-component fit results shown are based on
+217-3000 GHz observations, meaning that the 100 GHz and 143 GHz predictions are
+truly extrapolations, while the 217 GHz agreement is enforced by the fitting 
+process itself to some extent.}
 \end{center}

### 2014-07-17 ms.tex
fixed spelling typo
still re-writing discussion of fits with variable f1

@@
 considered in this study are of high angular resolution, the broad 
-\PLANCK~bandpasses do not allow us to adopt the same appraoch as FDS99 in 
+\PLANCK~bandpasses do not allow us to adopt the same approach as FDS99 in 
 dealing with line emission. Instead, we must subtract estimates of the 
@@
 consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
-fixed. By default, we employ the best-fit \PLANCK+DIRBE global parameters of 
-Table \ref{tab:global}, model 2, although our data release 
+spatially constant. By default, we employ the best-fit \PLANCK+DIRBE global 
+parameters of Table \ref{tab:global}, model 2, although our data release 
 ($\S$\ref{sec:release}) includes fits with the FDS99 global parameters as well.
-Still,  the dust spectrum normalization and dust temperatures are allowed to 
-vary for each line-of-sight. In order to predict the dust SED for a given 
+For each line of sight, only the dust spectrum normalization and dust 
+temperatures are allowed to vary. In order to predict the dust SED for a given 
 pixel, we are thus left with two remaining degrees of freedom, and must choose 
@@
 To determine the SED normalization in each pixel, we draw samples in 
-$\tilde{I}_{545}$, the `IRAS convention' intensity in the 545 GHz bandpass, as 
-defined in Equation \ref{eqn:inten}. With the four aforementioned global 
-parameters fixed, the dust spectrum shape is determined entirely by the two 
-dust temperatures, which are coupled. To constrain the dust temperatures, we 
-sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we compute
-the corresponding value of $T_1$, thereby determining the temperature and 
-emissivity power law index for both MBB components and thus fully specifying 
-the SED shape. In principle, we could sample in either $T_1$ or $T_2$, but have
-chosen to sample in $T_2$ because emission from this component dominates in the
-relatively high frequency bands which most strongly constrain the dust 
-temperatures.
+$\tilde{I}_{545}$, the `IRAS convention' intensity in the \PLANCK~545 GHz 
+bandpass, as defined in Equation \ref{eqn:inten}. With the four aforementioned 
+global parameters fixed, the dust spectrum shape is determined entirely by the 
+two dust temperatures, which are coupled. To constrain the dust temperatures, 
+we sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we 
+compute the corresponding value of $T_1$, thereby determining the temperature 
+and emissivity power law index for both MBB components and thus fully 
+specifying the SED shape. In principle, we could sample in either $T_1$ or 
+$T_2$, but have chosen to sample in $T_2$ because emission from this component 
+dominates in the relatively high frequency bands which most strongly constrain 
+the dust temperatures.
 
@@
 \epsfig{file=f1_1deg.eps, width=3.3in}
-\caption{\label{fig:f1} The $1^{\circ}$ FWHM map of $f_1$ derived from our 
+\caption{\label{fig:f1} $1^{\circ}$ FWHM map of $f_1$ derived from our 
 low-resolution fit in which $f_1$ is allowed to vary spatially.}
@@
 allowing $f_1$ to vary, while maintaining $\beta_1$, $\beta_2$, and $q_1/q_2$
-spatially constant. In such fits, there will therefore be three free 
-parameters.
+spatially constant. In principle, we could alternatively introduce a third free
+ parameter by allowing $q_1/q_2$, $\beta_1$ or $\beta_2$ to vary while holding 
+$f_1$ fixed. However, a model in which $f_1$ varies continuously from one line 
+of sight to another is the most natural three-parameter scenario, in that $f_1$
+variation can be attributed to continuous variation of the dust species' mass
+fractions, whereas continuous variations in the other global parameters, which 
+represent grain emission/absoprtion properties, seem less plausible.
 
@@
 
-In order for such fits to remain sufficiently constrained with an additional 
-free parameter, we consider \PLANCK~maps smoothed to $1^{\circ}$ FWHM to 
-boost per-pixel S/N, and pixelize at $N_{side}=64$. We also include DIRBE 
-140$\mu$m and 240$\mu$m at degree resolution in the fits with free-$f_1$ fits.
-
-% also we're adding in 100 GHz and 143 GHz, which is something not
-% done in full-resolution fits
+In order for our variable $f_1$ fits to remain sufficiently constrained with 
+the addition of another free parameter, we consider \PLANCK~maps smoothed to 
+$1^{\circ}$ FWHM for increased S/N, and pixelize at $N_{side}=64$. To best
+constrain the model parameters in each pixel, we also include \PLANCK~100 GHz 
+and 143 GHz, and DIRBE 140$\mu$m and 240$\mu$m, all at $1^{\circ}$ resolution.
 
@@
 \label{eqn:f1post}
-P(\tilde{I}_{545}, T_2, f_1|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2, f_1)P(T_2)P(f_1)
+P(\tilde{I}_{545}, T_2, f_1|\vec{I}~) \propto \mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2, f_1)P(T_2)P(f_1)
 \end{equation}
@@
 with Equation \ref{eqn:inten}. The prior $P(T_2)$ from Equation 
-\ref{equ:t2prior} remains unchanged. The prior on $f_1$ is:
+\ref{equ:t2prior} remains unchanged. We adopt the following prior on $f_1$:
 

### 2014-07-17 ms.tex
still cleaning up discussion of fits with variable f1

@@
 spatially constant. In principle, we could alternatively introduce a third free
- parameter by allowing $q_1/q_2$, $\beta_1$ or $\beta_2$ to vary while holding 
+parameter by permitting $\beta_1$, $\beta_2$ or $q_1/q_2$ to vary while holding
 $f_1$ fixed. However, a model in which $f_1$ varies continuously from one line 
 of sight to another is the most natural three-parameter scenario, in that $f_1$
-variation can be attributed to continuous variation of the dust species' mass
+variation can be attributed to continuous changes in the dust species' mass
 fractions, whereas continuous variations in the other global parameters, which 
@@
 
-% sentence or two about why f_1 is natural parameter to try varying 
-% rather than q1/q2 or beta1 or beta2 !!!!!~~!!!
-
-In order for our variable $f_1$ fits to remain sufficiently constrained with 
-the addition of another free parameter, we consider \PLANCK~maps smoothed to 
-$1^{\circ}$ FWHM for increased S/N, and pixelize at $N_{side}=64$. To best
-constrain the model parameters in each pixel, we also include \PLANCK~100 GHz 
-and 143 GHz, and DIRBE 140$\mu$m and 240$\mu$m, all at $1^{\circ}$ resolution.
-
-We run the Markov chains in three dimensions sampling in all three of $f_1$,
-$\tilde{I}_{545}$ and $T_2$. We are now sampling the posterior given by:
+In order for our variable $f_1$ fits to remain sufficiently constrained 
+following the introduction of a third free parameter, we enhance per-pixel S/N 
+by smoothing the input maps $1^{\circ}$ FWHM, and pixelize at $N_{side}=64$. To
+best constrain the model parameters in each pixel, we also include \PLANCK~100 
+GHz and 143 GHz, and DIRBE 140$\mu$m and 240$\mu$m, all at $1^{\circ}$ 
+resolution.
+
+We now run Markov chains sampling in all three of $f_1$, $\tilde{I}_{545}$ and 
+$T_2$, with the posterior given by:
 
@@
 with only nine intensity measurements, several of which are quite noisy.
-%To boost S/N, we have performed
-%the fits using maps smoothed to $1^{\circ}$ resolution.
 

### 2014-07-17 ms.tex
added NSF GRF grant number
mask CO emission in f1 map figure, and explain this in the caption

@@
 \subsection{Molecular Emission}
+\label{sec:mole}
 Because the FIRAS spectra consist of many narrow frequency bins, FDS99 were
@@
 \caption{\label{fig:f1} $1^{\circ}$ FWHM map of $f_1$ derived from our 
-low-resolution fit in which $f_1$ is allowed to vary spatially.}
+low-resolution fit in which $f_1$ is allowed to vary spatially. Red coloring
+masks pixels with appreciable molecular emission, as defined in 
+$\S$\ref{sec:mole}. Such pixels should not be trusted in this analysis, which 
+is sensitive to the SED shape at low frequencies that are contaminated by CO 
+line emission.}
 \end{center}
@@
 This material is based upon work supported by the National Science Foundation 
-Graduate Research Fellowship under Grant No. We acknowledge support of NASA 
-grant NNX12AE08G for this research. Based on observations obtained with Planck 
-(http://www.esa.int/Planck), an ESA science mission with instruments and 
+Graduate Research Fellowship under Grant No. DGE1144152. We acknowledge support
+of NASA grant NNX12AE08G for this research. Based on observations obtained with
+Planck (http://www.esa.int/Planck), an ESA science mission with instruments and
 contributions directly funded by ESA Member States, NASA, and Canada. This 

### 2014-07-17 ms.tex
finished first pass at re-write of variable f1 discussion

@@
 
-% check whether I545 normalization parameter is the monochromatic
-% 545 GHz intensity, or if it is for the Planck bandpass
-% i think it should eventually be monochromatic, since that will be
-% more useful to people who want SED predictions
-
 \begin{equation}
@@
 Here $\vec{I}$ denotes the vector of observed thermal dust intensities quoted 
-under the `IRAS convention': $\vec{I}$ = ($I_{217}$, $I_{353}$, ..., 
-$I_{3000}$). The likelihood function is given by:
+under the `IRAS convention': $\vec{I}$ = ($I_{217}$, $I_{353}$, $I_{545}$, 
+$I_{857}$, $I_{3000}$). The likelihood function is given by:
 
@@
 following the introduction of a third free parameter, we enhance per-pixel S/N 
-by smoothing the input maps $1^{\circ}$ FWHM, and pixelize at $N_{side}=64$. To
-best constrain the model parameters in each pixel, we also include \PLANCK~100 
-GHz and 143 GHz, and DIRBE 140$\mu$m and 240$\mu$m, all at $1^{\circ}$ 
-resolution.
+by smoothing the input maps to $1^{\circ}$ FWHM, and pixelize at $N_{side}=64$.
+To best constrain the model parameters in each pixel, we also include 
+\PLANCK~100 GHz and 143 GHz, and DIRBE 140$\mu$m and 240$\mu$m, all at 
+$1^{\circ}$ resolution.
 
@@
 
-This posterior still employs the likelihood function of Equation 
-\ref{equ:like}, the only difference being that $f_1$ can vary from proposal to 
-proposal within each individual pixel when predicting \{$\tilde{I}_{\nu_i}$\} 
-with Equation \ref{eqn:inten}. The prior $P(T_2)$ from Equation 
-\ref{equ:t2prior} remains unchanged. We adopt the following prior on $f_1$:
+The likelihood here is conceptually the same as that of Equation 
+\ref{equ:like}, but now depends on $f_1$, which can vary from proposal to 
+proposal within each individual pixel. The other difference is that 
+$\vec{\mathbf{I}}$ and $\underline{\mathbf{\tilde{I}}}$ now include 100 GHz, 
+143 GHz, 140$\mu$m and 240$\mu$m, in addition to the five bands used for the 
+full-resolution fits.
+
+The prior $P(T_2)$ from Equation \ref{equ:t2prior} 
+remains unchanged. We adopt the following prior on $f_1$:
 
@@
 
-With $\bar{f}_1$=0.0363 and $\sigma_{\bar{f}_1}$=0.003. This is a fairly
-stringent prior, but we must restrict the fit from wandering with too much
-freedom, as we are attempting to constrain three parameters using an SED
-with only nine intensity measurements, several of which are quite noisy.
+With $\bar{f}_1$=0.0485 (from Table \ref{tab:global}, model 2) and 
+$\sigma_{\bar{f}_1}$=0.003. This is a fairly stringent prior, but we must 
+restrict the fit from wandering with too much freedom, as we are attempting to 
+constrain three parameters using an SED with only nine intensity measurements, 
+several of which are quite noisy.
 
@@
 \end{itemize}
+
+\begin{figure*}
+\begin{center}
+\epsfig{file=ebv_resid_ecl.eps, width=6.6in}
+\caption{\label{fig:resid_ecl} Same as Figure \ref{fig:resid}, but 
+restricting to high ecliptic latitude, $|\beta|>20^{\circ}$. The top left and 
+top right plots both show that the bending of the reddening residuals as a 
+function of $E(B-V)_{SFD}$ as seen in Figure \ref{fig:resid} has been 
+eliminated. Further, the two-component reddening residual temperature 
+dependence (bottom left) has been significantly reduced relative to the
+corresponding trend shown in Figure \ref{fig:resid}, bottom left panel.}
+\end{center}
+\end{figure*}
 
@@
 % last few words here are kind of bad, need better terminology
-
-\begin{figure*}
-\begin{center}
-\epsfig{file=ebv_resid_ecl.eps, width=6.6in}
-\caption{\label{fig:resid_ecl} Same as Figure \ref{fig:resid}, but 
-restricting to high ecliptic latitude, $|\beta|>20^{\circ}$. The top left and 
-top right plots both show that the bending of the reddening residuals as a 
-function of $E(B-V)_{SFD}$ as seen in Figure \ref{fig:resid} has been 
-eliminated. Further, the two-component reddening residual temperature 
-dependence (bottom left) has been significantly reduced relative to the
-corresponding trend shown in Figure \ref{fig:resid}, bottom left panel.}
-\end{center}
-\end{figure*}
 

### 2014-07-18 ms.tex
beginning re-write of likelihood and uncertainty budget explanations

@@
 \usepackage{mathrsfs}
+\usepackage{amsmath}
 
@@
 $\S$\ref{sec:modeling} in hand, we can mathematically state the model we will 
-use e.g. during MCMC sampling to predict the observed SED, which we will 
-denote by \{$\tilde{I}_{\nu_i}$\}. The predicted observations are given by:
+use e.g. during MCMC sampling to predict the observed SED. The predicted 
+observation in band $\nu_i$ is given by:
 
@@
 Metropolis-Hastings (MH) Markov chain sampling the posterior probability of
-reproducing the observed 217-3000 GHz SED as a function of the two parameters 
+the observed 217-3000 GHz thermal dust SED as a function of the two parameters 
 $\tilde{I}_{545}$ and $T_2$. More specifically, we are sampling the posterior 
@@
 \label{eqn:post}
-P(\tilde{I}_{545}, T_2|\vec{I}~) \propto \mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2)P(T_2)P(\tilde{I}_{545})
+P(\tilde{I}_{545}, T_2|\vec{\mathbf{I}}~) \propto \mathcal{L}(\vec{\mathbf{I}}~|\tilde{I}_{545}, T_2)P(T_2)P(\tilde{I}_{545})
 \end{equation}
@@
 
-Here $\vec{I}$ denotes the vector of observed thermal dust intensities quoted 
-under the `IRAS convention': $\vec{I}$ = ($I_{217}$, $I_{353}$, $I_{545}$, 
+Here $\vec{\mathbf{I}}$ denotes the vector of observed thermal dust intensities quoted 
+under the `IRAS convention': $\vec{\mathbf{I}}$ = ($I_{217}$, $I_{353}$, $I_{545}$, 
 $I_{857}$, $I_{3000}$). The likelihood function is given by:
 
+%\begin{equation} \label{equ:like}
+%\mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(\tilde{I}_{\nu_{i}}|I_{\nu_{i}}, \sigma_{\nu_i})
+%\end{equation}
+
 \begin{equation} \label{equ:like}
-\mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(\tilde{I}_{\nu_{i}}|I_{\nu_{i}}, \sigma_{\nu_i})
+\mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2) = \textrm{exp}\Big[-\frac{1}{2}(\vec{\mathbf{I}}-\underline{\mathbf{\tilde{I}}})\Sigma^{-1}(\vec{\mathbf{I}}-\underline{\mathbf{\tilde{I}}})^T\Big]
 \end{equation}
@@
 
-Where the product runs over $\nu_i$$\in$$\{217,\ 353,\ 545,\ 857,\ 3000\}$ GHz
-and $\tilde{I}_{\nu_i}$ is a function of $\tilde{I}_{545}$ and $T_2$ as 
-specified by Equation \ref{eqn:inten}. For each pixel, the uncertainty on each 
-intensity measurement $\sigma_{\nu_i}$ is given by:
+Here $\underline{\mathbf{\tilde{I}}}$ is the vector of predicted observations 
+based on Equation \ref{eqn:inten} and the proposed values of $\tilde{I}_{545}$ 
+and $T_2$: $\underline{\mathbf{\tilde{I}}} = $($\tilde{I}_{217}$, 
+$\tilde{I}_{353}$, $\tilde{I}_{545}$, $\tilde{I}_{857}$, $\tilde{I}_{3000}$). 
+$\Sigma$ is the covariance matrix constructed based on the uncertainties in the
+observed intensities:
 
 \begin{equation}
-\sigma_{\nu_i}(p) = \sqrt{c^2_{\nu_i}I_{\nu_i}(p)^2 + c^2_{\nu_i}CMB(p)^2 + (\delta O_{\nu_i})^2 + n_{\nu_i}(p)^2}
+\Sigma = \begin{pmatrix} \sigma^2_{217}                           & \ldots  & \rho_{217,3000}\sigma_{217}\sigma_{3000} \\ 
+                         \vdots                                   & \ddots  & \vdots                                   \\
+                         \rho_{3000,217}\sigma_{3000}\sigma_{217} & \ldots  & \sigma^2_{3000}
+\end{pmatrix}
+\end{equation}
+
+For each pixel $p$ and band $\nu_i$, the variance of the measured value 
+$I_{\nu_i}(p)$ is taken to be:
+
+\begin{equation}
+\sigma_{\nu_i}(p) = c^2_{\nu_i}I_{\nu_i}(p)^2 + c^2_{\nu_i}CMB(p)^2 + (\delta O_{\nu_i})^2 + n_{\nu_i}(p)^2
 \end{equation}

### 2014-07-18 ms.tex
use bold without any arrows or underlining to denote vector quantities

@@
 \label{eqn:post}
-P(\tilde{I}_{545}, T_2|\vec{\mathbf{I}}~) \propto \mathcal{L}(\vec{\mathbf{I}}~|\tilde{I}_{545}, T_2)P(T_2)P(\tilde{I}_{545})
+P(\tilde{I}_{545}, T_2|\mathbf{I}) \propto \mathcal{L}(\mathbf{I}|\tilde{I}_{545}, T_2)P(T_2)P(\tilde{I}_{545})
 \end{equation}
@@
 
-Here $\vec{\mathbf{I}}$ denotes the vector of observed thermal dust intensities quoted 
-under the `IRAS convention': $\vec{\mathbf{I}}$ = ($I_{217}$, $I_{353}$, $I_{545}$, 
-$I_{857}$, $I_{3000}$). The likelihood function is given by:
+Here $\mathbf{I}$ denotes the vector of observed thermal dust intensities 
+quoted under the `IRAS convention': $\mathbf{I}$ = ($I_{217}$, $I_{353}$,
+$I_{545}$, $I_{857}$, $I_{3000}$). The likelihood function is given by:
 
@@
 \begin{equation} \label{equ:like}
-\mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2) = \textrm{exp}\Big[-\frac{1}{2}(\vec{\mathbf{I}}-\underline{\mathbf{\tilde{I}}})\Sigma^{-1}(\vec{\mathbf{I}}-\underline{\mathbf{\tilde{I}}})^T\Big]
+\mathcal{L}(\mathbf{I}|\tilde{I}_{545}, T_2) = \textrm{exp}\Big[-\frac{1}{2}(\mathbf{I}-\mathbf{\tilde{I}})\Sigma^{-1}(\mathbf{I}-\mathbf{\tilde{I}})^T\Big]
 \end{equation}
@@
 
-Here $\underline{\mathbf{\tilde{I}}}$ is the vector of predicted observations 
+Here $\mathbf{\tilde{I}}$ is the vector of predicted observations 
 based on Equation \ref{eqn:inten} and the proposed values of $\tilde{I}_{545}$ 
-and $T_2$: $\underline{\mathbf{\tilde{I}}} = $($\tilde{I}_{217}$, 
+and $T_2$: $\mathbf{\tilde{I}} = $($\tilde{I}_{217}$, 
 $\tilde{I}_{353}$, $\tilde{I}_{545}$, $\tilde{I}_{857}$, $\tilde{I}_{3000}$). 
@@
 \label{eqn:f1post}
-P(\tilde{I}_{545}, T_2, f_1|\vec{I}~) \propto \mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2, f_1)P(T_2)P(f_1)
+P(\tilde{I}_{545}, T_2, f_1|\mathbf{I}) \propto \mathcal{L}(\mathbf{I}|\tilde{I}_{545}, T_2, f_1)P(T_2)P(f_1)
 \end{equation}
@@
 proposal within each individual pixel. The other difference is that 
-$\vec{\mathbf{I}}$ and $\underline{\mathbf{\tilde{I}}}$ now include 100 GHz, 
+$\mathbf{I}$ and $\mathbf{\tilde{I}}$ now include 100 GHz, 
 143 GHz, 140$\mu$m and 240$\mu$m, in addition to the five bands used for the 

### 2014-07-18 ms.tex
still overhauling MCMC section(s)

@@
 
-For each pixel $p$ and band $\nu_i$, the variance of the measured value 
+For each pixel $p$ in band $\nu_i$, the variance of the measured value 
 $I_{\nu_i}(p)$ is taken to be:
 
-\begin{equation}
-\sigma_{\nu_i}(p) = c^2_{\nu_i}I_{\nu_i}(p)^2 + c^2_{\nu_i}CMB(p)^2 + (\delta O_{\nu_i})^2 + n_{\nu_i}(p)^2
-\end{equation}
+\begin{multline}
+\sigma^2_{\nu_i}(p) = c^2_{\nu_i}I_{\nu_i}(p)^2 + c^2_{\nu_i}\sigma_{CMB}^2 + (\delta O_{\nu_i})^2 \\
++ n_{\nu_i}^2 + \sigma^2_{\nu_i, CIBA} + \sigma^2_{CO}(p)
+\end{multline}
 
@@
 mean is chosen based on the typical high-latitude $T_2$ value derived from
-the correlation slope analysis from $\S$\ref{sec:global}. We find, as 
+the correlation slope analysis of $\S$\ref{sec:global}. We find, as 
 desired, that this relatively broad $T_2$ prior has little influence on the 
@@
 the relevant probabilities.
-%mention something about the proposal distribution at some point?
 
@@
 $\sigma_{\tilde{I}_{545}}$=max(0.01$\times$$I_{545}$, 0.05 MJy/sr) and
-$\sigma_{T_2}\sigma_{\tilde{I}_{545}}$=0. We run 5 iterations of burn-in, each 
+$\rho_{T_2, \tilde{I}_{545}}$=0. We run 5 iterations of burn-in, each 
 consisting of 500 MH steps. After each burn-in iteration, we rescale the 
@@
 
-After obtaining this initial estimate of the covariance matrix for each
-pixel, we re-run the entire MCMC procedure, starting from the first burn-in 
-iteration, but this time beginning with a proposal distribution that is a 
-two-dimensional normal distribution with covariance equal to the first-pass
-covariance estimate. This gives the proposal distribution for each pixel
- approximately the ``right shape'', whereas on the first pass we had to start
-by making ad hoc assumptions about the relative widths of the proposal 
-distribution in $\tilde{I}_{545}$ and $T_2$, and also assumed that the 
-$\sigma_{T_2}\sigma_{\tilde{I}_{545}}$=0 for the proposal distribution. We
-validated the recovered parameters and uncertainties from our MCMC procedure
+After obtaining this initial estimate of the covariance matrix for each pixel, 
+we re-run a second iteration of the entire MCMC procedure, starting from the 
+first burn-in period. On this iteration, for each pixel, we begin with a 
+proposal distribution that is a two-dimensional Gaussian with covariance equal 
+to the first-pass covariance estimate. This gives the each pixel's proposal 
+distribution approximately the `right shape', whereas on the first pass we 
+started by simply guessing the relative widths of the proposal distribution in 
+$\tilde{I}_{545}$, $T_2$, and also assumed that the 
+$\rho_{T_2, \tilde{I}_{545}}$=0.
+
+We validated the recovered parameters and uncertainties from our MCMC procedure
 by comparing with results based on gridded posterior calculations. These 
@@
 two-component intensity at 545 GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
-$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$, its variance, and
-the 545 GHz optical depth $\langle \tau_{545, j} \rangle$ = 
+$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$, its variance, and the 
+545 GHz optical depth $\tau_{545}$=$\langle \tau_{545, j} \rangle$ = 
 $\langle M_{545, j}/S_{545, j} \rangle$ and its variance. $\tau_{545}$ and 
 $M_{545}$ are more readily useful than the sampling parameters themselves for 
-translating our fit results into predicted reddening ($\S$\ref{sec:ebv}) and 
-thermal dust emission ($\S$\ref{sec:lofreq}), respectively.
-
-%$M_{545}$ is of more general utility in making foreground predictions because 
-%it provides the normalization for the two-component spectrum $M_{\nu}$, 
-%independent of the \PLANCK~545 GHz bandpass. Finally, we acompute the 545 GHz
-%optical depth as $\tau_{545}$ = and its variance, with the source 
-%function $S_{545}$ calculated according to Equation \ref{eqn:source}.
+translating our fit results into predictions of reddening ($\S$\ref{sec:ebv}) 
+and thermal dust emission ($\S$\ref{sec:lofreq}), respectively.
 
@@
 \label{sec:lores}
-%mention that the pixelization changes ---> to lower HEALpix nside
-%mention that over some region of the sky with high signal and high
-%S/N we try fitting t2, normalization and one of q1/q2, f_1
-%using more bands (including 143, and maybe 100 GHz)
-
-%As explained in $\S$\ref{sec:modeling} and $\S$\ref{sec:samp}, our 
-%full-resolution fits fix the parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ 
-%globally so that only the dust temperatures and SED normalization vary on a 
-%per-pixel basis. The reason for fixing so many parameters is that, at $6.1'$
-%FWHM, only five SED measurements are available per pixel.
-
-% need some sort of add on to last sentence or another sentence entirely
-% to the effect of ``staying in overconstrained regime''
 

### 2014-07-18 ms.tex
error budget explanation partially re-written

@@
 \begin{multline}
-\sigma^2_{\nu_i}(p) = c^2_{\nu_i}I_{\nu_i}(p)^2 + c^2_{\nu_i}\sigma_{CMB}^2 + (\delta O_{\nu_i})^2 \\
-+ n_{\nu_i}^2 + \sigma^2_{\nu_i, CIBA} + \sigma^2_{CO}(p)
+\sigma^2_{\nu_i}(p) = c^2_{\nu_i}I_{\nu_i}^2(p) + c^2_{\nu_i}\sigma_{CMB, \nu_i}^2 + (\delta O_{\nu_i})^2 \\
++ n_{\nu_i}^2 + \sigma^2_{CIBA, \nu_i} + \sigma^2_{CO, \nu_i}(p)
 \end{multline}
@@
 
-This error budget is the same as that of \cite{planckdust} Equation 7. 
-$c_{\nu_i}$ is the multiplicative calibration uncertainty for the intensity in 
-each band. We have adopted the $c_{\nu_i}$ values listed in \cite{planckdust} 
-Table 1. For the 217 GHz band, we have assigned $c_{217 GHz}$ = 0.54, from 
-Table 11 of \cite{planckcalib}. $CMB$ represents the CMB intensity 
-subtracted at the relevant pixel. $\delta O_{\nu_i}$ represents the uncertainty
-in the offset used to tie \PLANCK~intensity to H\,\textsc{i}. We have adopted 
-the  $\delta O_{\nu_i}$ values of \cite{planckdust} Table 1. $n_{\nu_i}$ 
-represents the instrumental noise in the pixel of interest, and is taken to be 
-the square root of the \verb|ii_cov| parameter that accompanies each 
-\PLANCK~intensity map.
+% need to make sure to cite planckcalib paper
+
+This error budget is modeled after \cite{planckdust} Equation 7, but with some 
+modifications and additions. The first term accounts for the multiplicative 
+uncertainty on the input maps. Table \ref{table:offs} lists the multiplicative 
+calibration uncertainty $c_{\nu}$ for each band. These values are taken from 
+Table 11 of \cite{planckcalib}. The second term is intended to represent a 
+typical uncertainty due to the subtraction of the \verb|SMICA| CMB model. The 
+analogous term in \cite{planckdust} Equation 7 is 
+($c_{\nu}$$\times$\verb|SMICA|($p$))$^2$, i.e. a term proportional to CMB model
+amplitude. Because this error term's spatial dependence has the potential to 
+imprint the CMB anisotropies on the derived parameters, we have chosen to 
+replace \verb|SMICA|($p$) with a spatially constant, RMS value for the CMB 
+amplitude, $\sigma_{CMB}$. Table \ref{table:offs} lists the adopted values of 
+$\sigma_{CMB}$. $\delta O_{\nu_i}$ represents the uncertainty in the band 
+$\nu_i$ zero level offset, and the values of $\delta O_{\nu_i}$ can be read 
+off from the second column of Table \ref{table:offs}. $n_{\nu_i}$ represents 
+the instrumental noise in the pixel of interest, and is taken to be the square 
+root of the \verb|ii_cov| parameter that accompanies each \PLANCK~intensity 
+map.
+
+% still need to explain off-diagonal terms in covariance ...
 

### 2014-07-19 ms.tex
still working on describing uncertainty model, also mention DIRBE 140um/240um in data section

@@
 
+In some of our FIR dust SED analyses which do not require high angular 
+resolution, specifically those of $\S$\ref{sec:global}, $\S$\ref{sec:lores}, 
+and $\S$\ref{sec:hier}, we also make use of the SFD reprocessings of DIRBE 
+140$\mu$m (2141 GHz) and 240$\mu$m (1250 GHz).
+
 \section{Preprocessing}
@@
 
-\begin{equation}
+\begin{equation} \label{equ:molcorr}
 I_{CO, \nu_i} = \sum\limits_{N} I_{CO, \nu_i, N, N-1}
@@
 \sigma^2_{\nu_i}(p) = c^2_{\nu_i}I_{\nu_i}^2(p) + c^2_{\nu_i}\sigma_{CMB, \nu_i}^2 + (\delta O_{\nu_i})^2 \\
-+ n_{\nu_i}^2 + \sigma^2_{CIBA, \nu_i} + \sigma^2_{CO, \nu_i}(p)
++ n_{\nu_i}^2 + \sigma^2_{CO, \nu_i}(p)  + \sigma^2_{CIBA, \nu_i}
 \end{multline}
@@
 analogous term in \cite{planckdust} Equation 7 is 
-($c_{\nu}$$\times$\verb|SMICA|($p$))$^2$, i.e. a term proportional to CMB model
-amplitude. Because this error term's spatial dependence has the potential to 
-imprint the CMB anisotropies on the derived parameters, we have chosen to 
-replace \verb|SMICA|($p$) with a spatially constant, RMS value for the CMB 
-amplitude, $\sigma_{CMB}$. Table \ref{table:offs} lists the adopted values of 
-$\sigma_{CMB}$. $\delta O_{\nu_i}$ represents the uncertainty in the band 
-$\nu_i$ zero level offset, and the values of $\delta O_{\nu_i}$ can be read 
-off from the second column of Table \ref{table:offs}. $n_{\nu_i}$ represents 
-the instrumental noise in the pixel of interest, and is taken to be the square 
-root of the \verb|ii_cov| parameter that accompanies each \PLANCK~intensity 
-map.
+($c_{\nu}$$\times$\verb|SMICA|($p$))$^2$, i.e. an uncertainty proportional to 
+the CMB model amplitude in each pixel. Because this term's spatial dependence 
+has the potential to imprint the CMB anisotropies on the derived parameters, we
+have chosen to replace \verb|SMICA|($p$) with a spatially constant, RMS value 
+for the CMB amplitude, $\sigma_{CMB}$. Table \ref{table:offs} lists the adopted
+values of $\sigma_{CMB}$. $\delta O_{\nu_i}$ represents the uncertainty in the 
+band $\nu_i$ zero level offset, and the values of $\delta O_{\nu_i}$ can be 
+read off from the second column of Table \ref{table:offs}. $n_{\nu_i}$ 
+represents the instrumental noise in the pixel of interest, and is taken to be 
+the square root of the \verb|ii_cov| parameter that accompanies each 
+\PLANCK~intensity map. The next term accounts for the uncertainty on the 
+CO emission correction, with $\sigma_{CO, \nu_i}$=0.15$\times$$I_{CO, \nu_i}$
+(see $\S$\ref{sec:mole}, specifically Equation \ref{equ:molcorr}).
 

### 2014-07-19 ms.tex
still describing error budget

@@
 rms of the per-quadrant offsets was 0.0586 MJy/sr.
-
-% mention that all of this assumes that residual CMB dipole
-% and other low order-corrections are negligible at 857 GHz
 
@@
 calibration uncertainty $c_{\nu}$ for each band. These values are taken from 
-Table 11 of \cite{planckcalib}. The second term is intended to represent a 
-typical uncertainty due to the subtraction of the \verb|SMICA| CMB model. The 
-analogous term in \cite{planckdust} Equation 7 is 
-($c_{\nu}$$\times$\verb|SMICA|($p$))$^2$, i.e. an uncertainty proportional to 
-the CMB model amplitude in each pixel. Because this term's spatial dependence 
-has the potential to imprint the CMB anisotropies on the derived parameters, we
-have chosen to replace \verb|SMICA|($p$) with a spatially constant, RMS value 
-for the CMB amplitude, $\sigma_{CMB}$. Table \ref{table:offs} lists the adopted
-values of $\sigma_{CMB}$. $\delta O_{\nu_i}$ represents the uncertainty in the 
-band $\nu_i$ zero level offset, and the values of $\delta O_{\nu_i}$ can be 
-read off from the second column of Table \ref{table:offs}. $n_{\nu_i}$ 
-represents the instrumental noise in the pixel of interest, and is taken to be 
-the square root of the \verb|ii_cov| parameter that accompanies each 
-\PLANCK~intensity map. The next term accounts for the uncertainty on the 
-CO emission correction, with $\sigma_{CO, \nu_i}$=0.15$\times$$I_{CO, \nu_i}$
+Table 11 of \cite{planckcalib}. The second term represents an uncertainty due 
+to our subtraction of the \verb|SMICA| CMB model. The analogous term in 
+\cite{planckdust} Equation 7 is ($c_{\nu}$$\times$\verb|SMICA|($p$))$^2$, i.e. 
+an uncertainty proportional to the CMB model amplitude in each pixel. Because 
+this term's spatial dependence can imprint the CMB anisotropies on the derived 
+parameters, we have chosen to replace \verb|SMICA|($p$) with a spatially 
+constant, RMS value for the CMB amplitude, $\sigma_{CMB}$. Table 
+\ref{table:offs} lists the adopted values of $\sigma_{CMB}$. $\delta O_{\nu_i}$
+represents the uncertainty in the band $\nu_i$ zero level offset, and the 
+values of $\delta O_{\nu_i}$ can be read off from the second column of Table 
+\ref{table:offs}. $n_{\nu_i}$ represents the instrumental noise in band 
+$\nu_i$. Because using per-pixel noise estimates based on the \verb|ii_cov| 
+parameter can imprint sharp-edged features of the survey pattern onto the 
+derived parameters, we have adopted a conservative, spatially constant value of
+$n_{\nu_i}$ for each band. Table \ref{table:offs} lists the values of 
+$n_{\nu_i}$ adopted. The next term accounts for the uncertainty on the CO 
+emission correction, taking $\sigma_{CO, \nu_i}$=0.15$\times$$I_{CO, \nu_i}$ 
 (see $\S$\ref{sec:mole}, specifically Equation \ref{equ:molcorr}).
@@
 % still need to explain off-diagonal terms in covariance ...
+
+% mention that each of the error terms is always rescaled properly according
+% to smoothing/rebinning and relevant power spectrum
 

### 2014-07-19 ms.tex
added column for per-band nominal detector noise to table of basic map parameters

@@
 
-\begin{deluxetable*}{rrrrrr} 
+\begin{deluxetable*}{cccccc} 
 \tabletypesize{\scriptsize}
-\tablecolumns{5} 
+\tablecolumns{6} 
 \tablewidth{0pc} 
@@
 \colhead{Dipole ($K_{CMB}$)} & 
+\colhead{$n_{\nu}$} ($K_{CMB}$) &
 \colhead{$c_{\nu}$} &
@@
 \startdata
-100 & 1.69$\times$10$^{-5}$$\pm$3.61$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ &  0.0054 & 9.66 \\
-143 & 3.58$\times$10$^{-5}$$\pm$7.58$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & 0.0054 &  7.27 \\
-217 & 7.79$\times$10$^{-5}$$\pm$2.60$\times$10$^{-6}$ & $-$1.40$\times$10$^{-5}$ & 0.0054 &  5.01 \\
-353 & 2.76$\times$10$^{-4}$$\pm$1.95$\times$10$^{-5}$ & $-$3.08$\times$10$^{-5}$ & 0.012 & 4.86 \\
-    & Offset (MJy/sr) & Dipole (MJy/sr) & & \\ \cline{2-3} \\ [-2ex]
-545 & 7.27$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ & 1.63$\times$10$^{-2}$ & 0.10 & 4.84 \\
-857 & 1.82$\times$10$^{-2}$$\pm$6.02$\times$10$^{-2}$ &  - & 0.10 & 4.63 \\
-3000 & 0.0$\pm$4.3$\times$10$^{-2}$ & - & 0.10 & 6.1
+100  & 1.69$\times$10$^{-5}$$\pm$3.61$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & 7.77$\times$10$^{-5}$ & 0.0054 & 9.66 \\
+143  & 3.58$\times$10$^{-5}$$\pm$7.58$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & 3.25$\times$10$^{-5}$ & 0.0054 & 7.27 \\
+217  & 7.79$\times$10$^{-5}$$\pm$2.60$\times$10$^{-6}$ & $-$1.40$\times$10$^{-5}$ & 4.51$\times$10$^{-5}$ & 0.0054 & 5.01 \\
+353  & 2.76$\times$10$^{-4}$$\pm$1.95$\times$10$^{-5}$ & $-$3.08$\times$10$^{-5}$ & 1.51$\times$10$^{-4}$ & 0.012  & 4.86 \\
+     & Offset (MJy/sr)                                 & Dipole (MJy/sr)          & $n_{\nu}$ (MJy/sr)    &        &      \\ \cline{2-4} \\ [-2ex]
+545  & 7.27$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ & 1.63$\times$10$^{-2}$    & 0.046                 & 0.10   & 4.84 \\
+857  & 1.82$\times$10$^{-2}$$\pm$6.02$\times$10$^{-2}$ & -                        & 0.046                 & 0.10   & 4.63 \\
+3000 & 0.0$\pm$4.3$\times$10$^{-2}$                    & -                        & 0.06                  & 0.10   & 6.1
 \enddata

### 2014-07-19 ms.tex
cleaning up description of uncertainties

@@
 parameters, we have chosen to replace \verb|SMICA|($p$) with a spatially 
-constant, RMS value for the CMB amplitude, $\sigma_{CMB}$. Table 
-\ref{table:offs} lists the adopted values of $\sigma_{CMB}$. $\delta O_{\nu_i}$
-represents the uncertainty in the band $\nu_i$ zero level offset, and the 
-values of $\delta O_{\nu_i}$ can be read off from the second column of Table 
-\ref{table:offs}. $n_{\nu_i}$ represents the instrumental noise in band 
-$\nu_i$. Because using per-pixel noise estimates based on the \verb|ii_cov| 
-parameter can imprint sharp-edged features of the survey pattern onto the 
+constant, RMS value for the CMB amplitude, $\sigma_{CMB, \nu_i}$. 
+$\delta O_{\nu_i}$ represents the uncertainty in the band $\nu_i$ zero level 
+offset, and the values of $\delta O_{\nu_i}$ can be read off from the second 
+column of Table \ref{table:offs}. $n_{\nu_i}$ represents the instrumental noise
+in band $\nu_i$. Because using per-pixel noise estimates based on the \PLANCK~
+\verb|ii_cov| parameter can imprint features of the survey pattern onto the 
 derived parameters, we have adopted a conservative, spatially constant value of
-$n_{\nu_i}$ for each band. Table \ref{table:offs} lists the values of 
-$n_{\nu_i}$ adopted. The next term accounts for the uncertainty on the CO 
-emission correction, taking $\sigma_{CO, \nu_i}$=0.15$\times$$I_{CO, \nu_i}$ 
-(see $\S$\ref{sec:mole}, specifically Equation \ref{equ:molcorr}).
+$n_{\nu_i}$ for each band. These values of $n_{\nu_i}$ are listed in Table 
+\ref{table:offs}. The next term accounts for the uncertainty on the CO emission
+correction, taking $\sigma_{CO, \nu_i}$=0.15$\times$$I_{CO, \nu_i}$ (see 
+$\S$\ref{sec:mole}, specifically Equation \ref{equ:molcorr}).
 

### 2014-07-19 ms.tex
may have finished first pass at full description of noise model

@@
 
-\begin{equation}
+\begin{equation} \label{equ:covariance}
 \Sigma = \begin{pmatrix} \sigma^2_{217}                           & \ldots  & \rho_{217,3000}\sigma_{217}\sigma_{3000} \\ 
@@
 
-% still need to explain off-diagonal terms in covariance ...
+Finally, we include a term to account for the RMS amplitude of the CIBA in
+band $\nu_i$, $\sigma_{CIBA, \nu_i}$. The values for the CIBA RMS amplitudes 
+are obtained by assuming a $T$=18.3 K, $\beta$=1.0 MBB spectrum for the CIB, 
+with 857 GHz normalization from \cite{ciba}. The CIBA not only contributes to 
+the per-band variance $\sigma^2_{\nu_i}$, but also to the inter-frequency 
+covariances; this is why we have included the off-diagonal terms in the
+covariance matrix of Equation \ref{equ:covariance}. In our noise model, the 
+CIBA is the only source of inter-frequency covariance. Thus, the off-diagonal 
+covariance matrix element between bands $\nu_i$ and $\nu_j$ is given by:
+
+\begin{equation}
+\Sigma_{ij} = \rho_{\nu_i, \nu_j}\sigma_{\nu_i}\sigma_{\nu_j} = \rho_{CIBA, \nu_i, \nu_j}\sigma_{CIBA, \nu_i}\sigma_{CIBA, \nu_j}
+\end{equation}
+
+With values for $\rho_{CIBA, \nu_i, \nu_j}$ from \cite{covarciba}. The approach
+we have taken in accounting for the CIBA is similar to that of 
+\cite{planckdust}, Appendix B, in that we treat the CIBA amplitude in each 
+pixel as a Gaussian random draw. However, instead of performing a separate 
+analysis to gauge the uncertainty on derived dust parameters due to the CIBA, 
+we allow the CIBA covariance to propagate naturally into our uncertainties via 
+the likelihood function. Still, our treatment of the CIBA is a major 
+oversimplification relative to the ideal situation in which the detailed 
+spatial structure of the CIBA would be thoroughly accounted for or even removed
+by subtraction.
 
@@
 
+\begin{figure*}
+\begin{center}
+\epsfig{file=ebv_resid_ecl.eps, width=6.6in}
+\caption{\label{fig:resid_ecl} Same as Figure \ref{fig:resid}, but 
+restricting to high ecliptic latitude, $|\beta|>20^{\circ}$. The top left and 
+top right plots both show that the bending of the reddening residuals as a 
+function of $E(B-V)_{SFD}$ as seen in Figure \ref{fig:resid} has been 
+eliminated. Further, the two-component reddening residual temperature 
+dependence (bottom left) has been significantly reduced relative to the
+corresponding trend shown in Figure \ref{fig:resid}, bottom left panel.}
+\end{center}
+\end{figure*}
+
 The obvious culprit for any potential nonlinearity in FIR-based reddening
@@
 \subsection{Rectifying the Reddening Residuals}
+
 In this section we describe our attempts to eliminate the systematic
@@
 \end{itemize}
-
-\begin{figure*}
-\begin{center}
-\epsfig{file=ebv_resid_ecl.eps, width=6.6in}
-\caption{\label{fig:resid_ecl} Same as Figure \ref{fig:resid}, but 
-restricting to high ecliptic latitude, $|\beta|>20^{\circ}$. The top left and 
-top right plots both show that the bending of the reddening residuals as a 
-function of $E(B-V)_{SFD}$ as seen in Figure \ref{fig:resid} has been 
-eliminated. Further, the two-component reddening residual temperature 
-dependence (bottom left) has been significantly reduced relative to the
-corresponding trend shown in Figure \ref{fig:resid}, bottom left panel.}
-\end{center}
-\end{figure*}
 

### 2014-07-19 ms.tex
various edits

@@
 \ref{equ:harm} did not improve the correlations at higher frequencies 
-sufficiently to warrant replacing the dipole-only correction in those cases.
+enough to warrant replacing the dipole-only correction in those cases.
 
@@
 
-% also might be worth mentioning that the MCMC analysis involves constraints
-% where the zero level matters, whereas the correlation slope analysis here
-% renders the zero levels irrelevant
-
 % maybe a table listing the correlation slopes and their uncertainties
@@
 
-% scatterplot figure showing linear regression of EBV vs. tau
 \begin{figure}
@@
 \caption{\label{fig:calib} Linear fit of $E(B-V)_{SSPP}$ as function of
-$\tau_{545}$.}
+$\tau_{545}$, restricting to $|b|$$>$20$^{\circ}$ and 
+$|\beta|$$>$20$^{\circ}$.}
 \end{center}
@@
 % TWO-COMPONENT MODELS WITH SPATIALLY CONSTANT BETAS, Q1/Q2 AND F1
-
-% need to explain SSPP acronym somewhere ?
-% cite Green appendix for details of deriving EBV_SSPP from Schlafly 11 data ?
 
@@
 We are releasing $N_{side}$=2048 HEALPix maps in Galactic coordinates 
-summarizing the results of of our two-component dust fits.
+summarizing the results of our full-resolution two-component dust fits. 
+Refer to the data release documentation and FITS file headers for further 
+details.
+
+% will we release software for making thermal dust predictions (i suppose
+% we can just release a reddening map, and there doesn't need to be 
+% any software released in that regard?)
 
@@
 % (data files and/or code) in this data release ?
-
-%at some point in this should make statements re: the fact that in terms
-%of predicting *emission* the conversion to tau is unnecessary and
-%and actually the raw uncertainty on Ghz 545 amplitude is the relevant quantity
 

### 2014-07-20 ms.tex
several minor edits

@@
  $10.5^{\circ}\times8.3^{\circ}$  region centered about 
-$(l,b) = (111.6^{\circ}, 20.3^{\circ})$. Note the differing colorscales. Both 
+$(l,b) = (111.6^{\circ}, 18.3^{\circ})$. Note the differing colorscales. Both 
 models incorporating \PLANCK~data clearly show a major improvement in angular 
@@
 translating our fit results into predictions of reddening ($\S$\ref{sec:ebv}) 
-and thermal dust emission ($\S$\ref{sec:lofreq}), respectively.
+and thermal dust emission ($\S$\ref{sec:lofreq}), respectively. At high
+Galactic latitude, we find a typical $T_2$ uncertainty of 0.45 K, and
+typical $\tilde{I}_{545}$ fractional uncertainty of 13\%.
 
@@
 With $\bar{f}_1$=0.0485 (from Table \ref{tab:global}, model 2) and 
-$\sigma_{\bar{f}_1}$=0.003. This is a fairly stringent prior, but we must 
+$\sigma_{\bar{f}_1}$=0.005. This is a fairly stringent prior, but we must 
 restrict the fit from wandering with too much freedom, as we are attempting to 
@@
 
-% perhaps zodi will just magically be fixed in the forthcoming Planck dta
-% release
-
+% perhaps zodi will just magically be fixed in the forthcoming Planck
 %   ---> do i want a figure illustrating the CIBA problem at high latitude ?
@@
 % the derived parameters !!!!
-
-% and should also say that it's worth looking up extinction values here
-% to gauge whether results are dependent on choice of dust map
 

### 2014-07-20 ms.tex
fixing up a couple of figure captions

@@
 \epsfig{file=posteriors.eps, width=7.0in}
-\caption{Gridded posterior PDFs for three $N_{side}$=2048 pixels. Red crosses 
-mark the best-fit parameters based on our Markov chain sampling of the 
-posterior. The posterior distributions are in general extremely well-behaved, 
-showing no multimodality or other pathological qualities. Our MCMC parameter 
-estimates coincide well with the peaks in the gridded posteriors. The 
-colorscale is linear in $log(P)$, with black representing the maximum of 
-$log(P)$ and white representing $max(log(P))-5$. Left: Low S/N pixel at 
-high latitude in the Galactic north. Center: High S/N pixel in the Polaris 
-region. Right: Low S/N pixel at high latitude in the Galactic south.}
+\caption{Gridded posterior PDFs for three $N_{side}$=2048 pixels. Light green
+crosses and ellipses mark the best-fit parameters and $1\sigma$ uncertainties 
+based on our MCMC sampling of the posterior. The posterior distributions are in
+general extremely well-behaved, showing no multimodality or other pathological 
+qualities. Our MCMC parameter and uncertainty estimates are in good agreement 
+with the gridded posteriors. The colorscale is linear in $log(P)$, with black 
+representing the maximum of $log(P)$ and white representing $max(log(P))-5$. 
+Left: Low S/N pixel at high latitude in the Galactic north. Center: High S/N 
+pixel in the Polaris region. Right: Low S/N pixel at high latitude in the 
+Galactic south.}
 \end{center}
@@
 \epsfig{file=calib_ebv.eps, width=3.3in}
-\caption{\label{fig:calib} Linear fit of $E(B-V)_{SSPP}$ as function of
-$\tau_{545}$, restricting to $|b|$$>$20$^{\circ}$ and 
-$|\beta|$$>$20$^{\circ}$.}
+\caption{\label{fig:calib} Linear fit of $E(B-V)_{SSPP}$ as a function of
+two-component $\tau_{545}$, restricting to $|b|$$>$20$^{\circ}$.}
 \end{center}

### 2014-07-21 ms.tex
fixing up captions and other minor edits

@@
 \epsfig{file=zp_857.eps, width=3.4in}
-\caption{\label{fig:fdsref} Scatterplot of $\mathcal{F}_{857}$ versus 
-$\mathcal{I}_{857}$, illustrating our absolute zero point determination by
-comparison to the FDS99 prediction for \PLANCK~857 GHz.}
+\caption{\label{fig:fdsref} Scatter plot of FDS99-predicted 857 GHz thermal
+dust emission versus \PLANCK~857 GHz observations, illustrating our absolute 
+zero level determination described in $\S$\ref{sec:zp_abs}.}
 \end{center}
@@
 \caption{\label{fig:dip}  Scatter plots of \PLANCK~100, 143, 217, 353, and 545 
-GHz versus \PLANCK~857 GHz. Left: before applying zero-level offsets and 
-additional low-order corrections. Right: after correcting for the best-fit 
-offset and residual Solar dipole (143-545 GHz). 100 GHz is shown after applying
-the spherical harmonic correction of Equation \ref{equ:harm}. The dashed red 
-line shows the best-fit linear relationship in all cases.}
+GHz versus \PLANCK~857 GHz. Left: before applying our best-fit zero level 
+offsets and additional low-order corrections. Right, top four panels: 
+\PLANCK~143-545 GHz after correcting for the best-fit offset and residual Solar
+dipole. Bottom right: \PLANCK~100 GHz after applying the spherical harmonic 
+corrections of Equation \ref{equ:harm}. The dashed red line shows the best-fit 
+linear relationship in all cases.}
 \end{center}
@@
 \caption{\label{fig:harm} Summary of low-order corrections at 100 GHz. Left: 
-prior to our low-order corrections, a $\sim$17$\mu$K zero-level offset is 
+prior to our low-order corrections, a $\sim$17$\mu$K zero level offset is 
 present and strong low-order problems reduce the linearity of the 100 GHz 
-scatter versus 857 GHz. Center: scatter plot versus 857 GHz after applying the 
-best-fit offset and residual Solar dipole corrections derived with Equation 
-\ref{equ:dip} to \PLANCK~100 GHz. The correlation is strengthened, but remains
-far less tight than for 143-545 GHz (see Figure \ref{fig:dip}, top four rows, 
-right column). Right: after applying the spherical harmonic correction of
-Equation \ref{equ:harm} to \PLANCK~100 GHz, the correlation versus 857 GHz is 
-far more tightly linear than following the dipole correction.}
+trend versus 857 GHz. Center: scatter plot of \PLANCK~100 GHz versus 857 GHz 
+after applying the best-fit offset and residual Solar dipole corrections 
+derived with Equation \ref{equ:dip} to \PLANCK~100 GHz. The correlation is 
+strengthened, but remains far less tight than for 143-545 GHz (see right 
+column of Figure \ref{fig:dip}, top four rows). Right: after applying the 
+spherical harmonic corrections of Equation \ref{equ:harm} to \PLANCK~100 GHz, 
+the correlation versus 857 GHz is far more tightly linear than following the 
+dipole correction.}
 \end{center}
@@
 \epsfig{file=dirbe_slopes.eps, width=6.5in}
-\caption{\label{fig:dirbe_slopes} Linear fits of DIRBE 240$\mu$m (left), 
-140$\mu$m (center), and 100$\mu$m (right) as a function of \PLANCK~857 GHz. The
-red lines illustrate the DIRBE correlation slopes used in our global parameter 
-analysis of $\S$\ref{sec:global}.}
+\caption{\label{fig:dirbe_slopes} Linear fits of SFD-reprocessed DIRBE 
+240$\mu$m (left), 140$\mu$m (center), and 100$\mu$m (right) as a function of 
+\PLANCK~857 GHz. The red lines illustrate the DIRBE correlation slopes used in 
+our dust emission model optimization of $\S$\ref{sec:global}.}
 \end{center}
@@
 
-In the case of the two-component model, based on a spectrum of \PLANCK~and 
+In the two-component model case, based on a spectrum of \PLANCK~and 
 DIRBE correlations slopes, we wish to obtain estimates for six free parameters:
@@
 
-At 1250, 2141 and 3000 GHz, we use the SFD98-reprocessed DIRBE maps. For each
+At 1250, 2141 and 3000 GHz, we use the SFD-reprocessed DIRBE maps. For each
 DIRBE band, we determine $s_{i, 857}$ by performing a linear fit to DIRBE as a 
@@
 crosses and ellipses mark the best-fit parameters and $1\sigma$ uncertainties 
-based on our MCMC sampling of the posterior. The posterior distributions are in
-general extremely well-behaved, showing no multimodality or other pathological 
-qualities. Our MCMC parameter and uncertainty estimates are in good agreement 
-with the gridded posteriors. The colorscale is linear in $log(P)$, with black 
-representing the maximum of $log(P)$ and white representing $max(log(P))-5$. 
-Left: Low S/N pixel at high latitude in the Galactic north. Center: High S/N 
-pixel in the Polaris region. Right: Low S/N pixel at high latitude in the 
-Galactic south.}
+based on our MCMC sampling of the posteriors. The posterior distributions are 
+in general extremely well-behaved, showing no multimodality or other 
+pathological qualities. Our MCMC parameter and uncertainty estimates are in 
+good agreement with the gridded posteriors. The colorscale is linear in 
+$log(P)$, with black representing the maximum of $log(P)$ and white 
+representing $max(log(P))-5$. Left: Low S/N pixel at high latitude in the 
+Galactic north. Center: High S/N pixel in the Polaris region. Right: Low S/N 
+pixel at high latitude in the Galactic south.}
 \end{center}
@@
 implausible, being an order of magnitude larger than the nominal \verb|i100| 
-zero level uncertainty quoted by SFD98, and comparable to the entire 3000 GHz 
-CIB monopole signal. Furthermore, we note that even these large zero 
-level modifications had virtually no effect in eliminating the reddening 
-residual `bend' versus $E(B-V)_{SFD}$. Thus, changing the zero level 
-offsets showed hints of promise in rectifying the reddening residual 
-temperature dependence, but cannot completely resolve the systematic trends in 
-reddening residuals.
+zero level uncertainty quoted by SFD, and comparable to the entire 3000 GHz CIB
+monopole signal. Furthermore, we note that even these large zero level 
+modifications had virtually no effect in eliminating the reddening residual 
+`bend' versus $E(B-V)_{SFD}$. Thus, changing the zero level offsets showed 
+hints of promise in rectifying the reddening residual temperature dependence, 
+but cannot completely resolve the systematic trends in reddening residuals.
 % last few words here are kind of bad, need better terminology

### 2014-07-21 ms.tex
more clean-up, still focused on figure captions

@@
 \epsfig{file=sed.eps, width=3.3in}
-\caption{\label{fig:sed} Planck SED for a single $N_{side}$=2048 pixel in the 
-Polaris region. Note that the two lowest-frequency data points (\PLANCK~100, 
-143 GHz) were not used in our fit, while the three lowest-frequency data
-points were not used in the \cite{planckdust} fit.}
+\caption{\label{fig:sed} Observed SED (black points and error bars) and 
+best-fit thermal dust emission models for a single $N_{side}$=2048 pixel in the
+Polaris flare region. The best-fit two-component model (black line) is derived 
+based on \PLANCK~217-857 GHz and SFD 100$\mu$m at full $6.1'$ resolution. Note 
+that the two lowest-frequency data points were not used in the two-component 
+fit shown, while the three lowest-frequency data points were not used in the 
+\cite{planckdust} single-MBB fit shown (cyan).}
 \end{center}
@@
 \epsfig{file=posteriors.eps, width=7.0in}
-\caption{Gridded posterior PDFs for three $N_{side}$=2048 pixels. Light green
+\caption{\label{fig:post} Gridded posterior PDFs for three $N_{side}$=2048 
+pixels, based on \PLANCK~217-857 GHz and SFD 100$\mu$m at full $6.1'$ 
+resolution. The colorscale is linear in $log(P)$, with black corresponding to 
+the maximum of $log(P)$ and white representing $max[log(P)]-5$. Light green 
 crosses and ellipses mark the best-fit parameters and $1\sigma$ uncertainties 
-based on our MCMC sampling of the posteriors. The posterior distributions are 
-in general extremely well-behaved, showing no multimodality or other 
-pathological qualities. Our MCMC parameter and uncertainty estimates are in 
-good agreement with the gridded posteriors. The colorscale is linear in 
-$log(P)$, with black representing the maximum of $log(P)$ and white 
-representing $max(log(P))-5$. Left: Low S/N pixel at high latitude in the 
-Galactic north. Center: High S/N pixel in the Polaris region. Right: Low S/N 
-pixel at high latitude in the Galactic south.}
+based on our MCMC sampling of the posteriors. Our MCMC parameter and 
+uncertainty estimates are in good agreement with those based on gridded 
+posteriors. These three pixels are also representative in that we find the 
+posterior distributions from Equation \ref{eqn:post} are in general extremely 
+well-behaved, showing no multimodality or other pathological qualities. Left: 
+Low S/N pixel at high latitude in the Galactic north. Center: High S/N pixel in
+the Polaris flare region. Right: Low S/N pixel at high latitude in the Galactic
+south.}
 \end{center}
@@
 the likelihood function. Still, our treatment of the CIBA is a major 
-oversimplification relative to the ideal situation in which the detailed 
-spatial structure of the CIBA would be thoroughly accounted for or even removed
-by subtraction.
+oversimplification; a more sophisticated approach that accounts for the 
+detailed CIBA spatial structure, or even removes the CIBA by subtraction would
+be preferable.
 
@@
 \epsfig{file=tcomparison.eps, width=3.3in}
-\caption{\label{fig:comparison} Comparison of SFD temperature, two-component 
-model $T_2$, and \cite{planckdust} temperature (labeled $T_{R1.20}$) for a
- $10.5^{\circ}\times8.3^{\circ}$  region centered about 
-$(l,b) = (111.6^{\circ}, 18.3^{\circ})$. Note the differing colorscales. Both 
-models incorporating \PLANCK~data clearly show a major improvement in angular 
+\caption{\label{fig:comparison} Comparison of temperature maps based on FIR 
+dust emission over a $10.5^{\circ}\times8.3^{\circ}$ region centered about 
+$(l,b) = (111.6^{\circ}, 18.3^{\circ})$. Top: SFD temperature map based on 
+DIRBE $100\mu$m and $240\mu$m, with $\sim$1.3$^{\circ}$ resolution. Center: 
+$6.1'$ resolution two-component temperature based on \PLANCK~217-857 GHz and 
+SFD 100$\mu$m. Bottom: \cite{planckdust} single-MBB temperature map based on 
+\PLANCK~353-857 GHz and 100$\mu$m data, with $5.1'$ FWHM. Both temperature maps
+incorporating \PLANCK~observations clearly show a major improvement in angular 
 resolution relative to SFD.}
@@
 Galactic latitude, we find a typical $T_2$ uncertainty of 0.45 K, and
-typical $\tilde{I}_{545}$ fractional uncertainty of 13\%.
+typical $\tilde{I}_{545}$ fractional uncertainty of 13\%. Figure \ref{fig:sed}
+shows a summary of the observed SED and resulting best-fit two-component
+model for a single $N_{side}$=2048 pixel, and Figure \ref{fig:post} 
+shows posterior PDFs for three pixels.
 
@@
 \caption{\label{fig:chi2_dirbe} Comparison of goodness-of-fit, 
-$\chi^2_{\nu}$=$\langle \chi^2_{p, \nu} \rangle$ for various dust SED models. 
-For single-MBB models with spatially constant $\beta$, we varied $\beta$ 
-between 1 and 2 (x axis), achieving reduced chi-squared $\chi^2_{\nu}$ shown by
-the black line, with $\beta$=1.57 providing the best fit. Horizontal lines 
-indicate $\chi^2_{\nu}$ for other dust SED models considered, including the 
-FDS99 best-fit model and our best-fit \PLANCK+DIRBE model from 
-$\S$\ref{sec:global}. The minimum $\chi^2_{\nu}$ was achieved with
-two-componenent `model 2' from Table \ref{tab:global} (horizontal magenta 
-line).}
+$\chi^2_{\nu}$=$\langle \chi^2_{p, \nu} \rangle$, for various dust SED models,
+as described in $\S$\ref{sec:hier}. For single-MBB models with spatially 
+constant $\beta$, we varied $\beta$ between 1 and 2 (horizontal axis), 
+achieving reduced chi-squared $\chi^2_{\nu}$ shown by the black line, with 
+$\beta$=1.57 providing the best fit. Horizontal lines indicate $\chi^2_{\nu}$ 
+for other dust emission models considered, including the FDS99 best-fit 
+two-component model (Table \ref{tab:global}, model 1, red) and the 
+\cite{planckdust} single-MBB model (green). The minimum $\chi^2_{\nu}$ is 
+achieved with two-componenent `model 2' from Table \ref{tab:global} (magenta).}
 \end{center}
@@
 $E(B-V)_{mbb}$ residuals as a function of the single-MBB dust temperature from 
-\cite{planckdust}. The temperature axes always range from the 
-0.4$^{th}$ percentile to 99.6$^{th}$ percentile temperature values.}
+\cite{planckdust}. The temperature axes always range from the 0.4$^{th}$ 
+percentile temperature value to the 99.6$^{th}$ percentile temperature value.}
 \end{center}
@@
 full-resolution two-component model fits of \PLANCK~217-857 GHz and SFD 
-\texttt{i100}, downbinned to 27.5$'$ resolution. (bottom) Corresponding
-full-sky map of best-fit 545 GHz optical depth.}
+100$\mu$m, downbinned to 27.5$'$ resolution. (bottom) Corresponding full-sky 
+map of best-fit 545 GHz optical depth.}
 \end{center}

### 2014-07-22 ms.tex
still working on captions, other minor edits

@@
 offsets and additional low-order corrections. Right, top four panels: 
-\PLANCK~143-545 GHz after correcting for the best-fit offset and residual Solar
-dipole. Bottom right: \PLANCK~100 GHz after applying the spherical harmonic 
-corrections of Equation \ref{equ:harm}. The dashed red line shows the best-fit 
-linear relationship in all cases.}
+\PLANCK~143-545 GHz after correcting for each band's best-fit offset and 
+residual Solar dipole. Bottom right: \PLANCK~100 GHz after applying the 
+spherical harmonic corrections of Equation \ref{equ:harm}. The dashed red line 
+shows the best-fit linear relationship in all cases.}
 \end{center}
@@
 resolution has very high S/N, we can safely perform such a cut on 
-$\mathcal{I}_{857}$. Figure \ref{fig:fdsref} shows a scatterplot of 
+$\mathcal{I}_{857}$. Figure \ref{fig:fdsref} shows a scatter plot of 
 $\mathcal{I}_{857}$ versus $\mathcal{F}_{857}$, with a moving median and linear
@@
 least squares fit with uniform weights and iterative outlier rejection. Figure 
-\ref{fig:dip} shows scatterplots of the band $\nu_i$ versus 857 GHz correlation
- before and after correcting for the best-fit offset and residual dipole, for 
-each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only are the tightened 
-correlations striking in these scatterplots, but the residual dipole 
+\ref{fig:dip} shows scatter plots of the band $\nu_i$ versus 857 GHz 
+correlation before and after correcting for the best-fit offset and residual 
+dipole, for each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only are the 
+tightened correlations striking in these scatter plots, but the residual dipole
 subtractions appear very successful in the two-dimensional band $\nu_i$ maps 
@@
 model for a single $N_{side}$=2048 pixel, and Figure \ref{fig:post} 
-shows posterior PDFs for three pixels.
+shows posterior PDFs for three pixels. Figure \ref{fig:comparison} shows
+a map of our derived hot dust temperature at full-resolution, for a patch
+of sky in the Polaris flare region.
 
@@
 \caption{\label{fig:calib} Linear fit of $E(B-V)_{SSPP}$ as a function of
-two-component $\tau_{545}$, restricting to $|b|$$>$20$^{\circ}$.}
+two-component $\tau_{545}$, illustrating our procedure for calibrating optical 
+depth to reddening.}
 \end{center}
@@
 \caption{\label{fig:resid_ecl} Same as Figure \ref{fig:resid}, but 
-restricting to high ecliptic latitude, $|\beta|>20^{\circ}$. The top left and 
-top right plots both show that the bending of the reddening residuals as a 
-function of $E(B-V)_{SFD}$ as seen in Figure \ref{fig:resid} has been 
-eliminated. Further, the two-component reddening residual temperature 
-dependence (bottom left) has been significantly reduced relative to the
-corresponding trend shown in Figure \ref{fig:resid}, bottom left panel.}
+restricting to high ecliptic latitude, $|\beta|>20^{\circ}$. In both the top 
+left and top right plots, the bending of the reddening residuals as a function 
+of $E(B-V)_{SFD}$ seen in Figure \ref{fig:resid} has been eliminated. Further, 
+the two-component reddening residual temperature dependence (bottom left) has 
+been significantly reduced relative to the corresponding trend shown in Figure 
+\ref{fig:resid}.}
 \end{center}
@@
 \ref{tab:global}, model 2) and those of \cite{planckdust}. The top row shows
-scatterplots of the \cite{planckdust} predictions versus observed \PLANCK~100 
+scatter plots of the \cite{planckdust} predictions versus observed \PLANCK~100 
 GHz (left), \PLANCK~143 GHz (center) and \PLANCK~217 GHz (right). The bottom 
-row shows scatterplots of the corresponding two-component predictions versus
+row shows scatter plots of the corresponding two-component predictions versus
 \PLANCK~observations. In all cases, the blue line indicates the best-fit linear

### 2014-07-22 ms.tex
finished caption for f1 figure

@@
 \caption{\label{fig:f1} $1^{\circ}$ FWHM map of $f_1$ derived from our 
-low-resolution fit in which $f_1$ is allowed to vary spatially. Red coloring
-masks pixels with appreciable molecular emission, as defined in 
-$\S$\ref{sec:mole}. Such pixels should not be trusted in this analysis, which 
-is sensitive to the SED shape at low frequencies that are contaminated by CO 
-line emission.}
+low-resolution fits described in $\S$\ref{sec:lores}. Red coloring masks pixels
+with appreciable molecular emission, as defined in $\S$\ref{sec:mole}. Such 
+pixels should not be trusted in this analysis, which is sensitive to the SED 
+shape at low frequencies affected by CO line emission. Variations in $f_1$
+along the ecliptic plane are spurious results of imperfect zodiacal light
+subtractions. However, interesting astrophysical variations of $f_1$ 
+are evident, particularly the trend of increasing $f_1$ with decreasing
+Galactic latitude, the relatively low $f_1$ values in the Polaris flare region,
+and the clouds with relatively high $f_1$ near the north Galactic pole.}
 \end{center}

### 2014-07-22 ms.tex
complete rewrite of abstract, other minor edits

@@
 \begin{abstract}
-We present full-sky, $6.1'$ resolution maps of dust optical depth and 
-temperature derived by fitting the \cite{FDS99} two-component dust emission 
-model to the \PLANCK~217, 353, 545, and 857 GHz maps along with  
-\IRAS~100$\mu$m data. This parametrization of the far-infrared thermal dust 
-spectrum as the sum of two modified blackbodies serves as an important 
-alternative to the commonly adopted single modified blackbody dust emission 
-model. Because our two-component model matches the dust spectrum near its 
-peak, accounts for the flattening of the dust spectrum at millimeter 
-wavelengths, and specifies dust temperature at 6.1$'$ FWHM, our model 
-provides accurate, high-resolution thermal dust emission foreground predictions
-from 100 GHz to 3000 GHz. We also calibrate the derived optical depth to 
-reddening at visible wavelengths, and compare the resulting reddening estimates
-with those based on stellar spectra, as well as those of \cite{SFD} and 
-\cite{planckdust} based on infrared emission.
+
+We apply the \cite{FDS99} two-component thermal dust emission model to the
+\PLANCK~HFI maps. This parametrization of the far-infrared dust spectrum as the
+sum of two modified blackbodies serves as an important alternative to the 
+commonly adopted single modified blackbody (MBB) dust emission model. Analyzing
+the joint \PLANCK/DIRBE dust spectrum, we show that two-component models 
+provide a better fit to the 100-3000 GHz emission than do single-MBB models, 
+though by a lesser margin than found by \cite{FDS99} based on FIRAS and DIRBE. 
+We also derive full-sky $6.1'$ resolution maps of dust optical depth and 
+temperature by fitting the two-component model to the \PLANCK~217, 353, 545, 
+and 857 GHz maps along with  DIRBE/\IRAS~100$\mu$m data. Because our 
+two-component model matches the dust spectrum near its peak, accounts for the 
+flattening of the dust spectrum at millimeter wavelengths, and specifies dust 
+temperature at 6.1$'$ FWHM, our model provides reliable, high-resolution 
+thermal dust emission foreground predictions from 100 GHz to 3000 GHz. We find 
+that, in diffuse sky regions, our two-component 100-217 GHz thermal dust 
+emission predictions are on average accurate to within $\le$2.2\%, which 
+represents an improvement of 5-15\% relative to predictions based on the 
+\cite{planckdust} single-MBB model. We calibrate our two-component optical 
+depth to reddening at visible wavelengths, and compare the resulting reddening 
+estimates with those based on stellar spectra. We find that imperfect zodiacal 
+light subtraction is the dominant large-scale systematic problem in our 
+two-component temperature map and reddening estimates.
 
@@
 range of frequencies. \cite{planckdust} has recently conducted a study modeling
-\PLANCK~353 GHz, 545 GHz, 857 GHz and \IRAS~100$\mu$m emission with a single
-MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
-as an alernative parametrization for the dust spectral energy distribution 
-(SED) composed  of \PLANCK~and \IRAS~data. In doing so, we obtain maps of dust 
-temperature and optical depth, both at $6.1'$ resolution. Because we employ a 
-model that has been validated with FIRAS data down to sub-mm wavelengths, we 
-expect our best-fit parameters to be useful in constructing high-resolution 
+\PLANCK~353 GHz, 545 GHz, 857 GHz and DIRBE/\IRAS~100$\mu$m emission with a 
+single-MBB spectrum. Here we investigate the FDS99 two-component dust emission 
+model as an alernative parametrization for the dust spectral energy 
+distribution (SED) composed  of \PLANCK High Frequency Instrument (HFI), DIRBE 
+and \IRAS~data. In doing so, we obtain maps of dust temperature and optical 
+depth, both at $6.1'$ resolution. Because we employ a model that has been 
+validated with FIRAS data down to submillimeter (submm) wavelengths, we expect 
+our best-fit parameters to be useful in constructing high-resolution 
 predictions of dust emission over a very broad range of wavelengths. This 
@@
 SED, for example \AKARI~140-160$\mu$m \citep{akari}. We also anticipate our 
-derived optical depth map will serve as a useful cross-check for extinction 
+derived optical depth map will serve as a valuable cross-check for extinction 
 estimates based directly upon optical observations of stars 
@@
 isolate thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we 
-explain the dust emission model we apply to the \PLANCK~and \IRAS/DIRBE data. 
-In $\S$\ref{sec:bpcorr}, we discuss the details of predicting 
+explain the two-component emission model we apply to the \PLANCK-based dust 
+SED. In $\S$\ref{sec:bpcorr}, we discuss the details of predicting 
 \PLANCK~observations based on this dust model. In $\S$\ref{sec:global} we 
-derive constraints on our model's global parameters based on the \PLANCK~High 
-Frequency Instrument (HFI) maps. In $\S$\ref{sec:fitting} we detail the Markov 
-chain Monte Carlo (MCMC) method with which we have estimated the spatially 
-varying parameters of our model. In $\S$\ref{sec:ebv} we calibrate our derived 
-optical depth to reddening at optical wavelengths. In $\S$\ref{sec:lofreq} we
-evaluate the accuracy of our two-component thermal dust emission predictions 
-from 100-217 GHz. In $\S$\ref{sec:release} we present the full-sky maps of dust
-temperature and optical depth we have obtained, and conclude in 
-$\S$\ref{sec:conclusion}.
+derive constraints on our model's global parameters in light of the \PLANCK~HFI
+maps. In $\S$\ref{sec:fitting} we detail the Markov chain Monte Carlo (MCMC) 
+method with which we have estimated the spatially varying parameters of our 
+model. In $\S$\ref{sec:ebv} we calibrate our derived optical depth to reddening
+at optical wavelengths. In $\S$\ref{sec:lofreq} we evaluate the accuracy of our
+two-component thermal dust emission predictions from 100-217 GHz. In 
+$\S$\ref{sec:release} we present the full-sky maps of dust temperature and 
+optical depth we have obtained, and conclude in $\S$\ref{sec:conclusion}.
 
@@
 The following subsections detail the processing steps we have applied to 
-isolate Galactic dust emission in the \PLANCK~maps in preparation for our joint
-\PLANCK/\IRAS~SED fits. % reference fitting section at end of this sentence ?
+isolate Galactic dust emission in the \PLANCK~maps in preparation for SED
+fitting. % reference fitting section at end of this sentence ?
 
@@
 \tablewidth{0pc} 
-\tablecaption{\label{table:offs} Planck/IRAS Map Properties \& Pre-processing} 
+\tablecaption{\label{table:offs} Input Map Properties \& Pre-processing} 
 \tablehead{

### 2014-07-22 ms.tex
audited for FDS99-like versus FDS99

@@
 
-\title{Two-component thermal dust emission model: application to the 
+\title{Modeling thermal dust emission with two components: application to the 
 {\it PLANCK} HFI maps}
@@
 that, in diffuse sky regions, our two-component 100-217 GHz thermal dust 
-emission predictions are on average accurate to within $\le$2.2\%, which 
-represents an improvement of 5-15\% relative to predictions based on the 
-\cite{planckdust} single-MBB model. We calibrate our two-component optical 
-depth to reddening at visible wavelengths, and compare the resulting reddening 
-estimates with those based on stellar spectra. We find that imperfect zodiacal 
-light subtraction is the dominant large-scale systematic problem in our 
-two-component temperature map and reddening estimates.
+emission predictions are on average accurate to within 2.2\%, which represents 
+an improvement of 5-15\% relative to predictions based on the \cite{planckdust}
+single-MBB model. We calibrate our two-component optical depth to reddening at 
+visible wavelengths, and compare the resulting reddening estimates with those 
+based on stellar spectra. We find imperfect zodiacal light subtraction in both 
+DIRBE/\IRAS~and \PLANCK~to be the dominant large-scale systematic problem 
+in our two-component temperature map and reddening estimates.
 
@@
 240$\mu$m/100$\mu$m ratio to account for temperature variation at 
-$\sim$1.3$^{\circ}$ resolution. In this work we seek to apply FDS99-like 
-emission models to the \PLANCK~data set, which offers a dramatic enhancement in
+$\sim$1.3$^{\circ}$ resolution. In this work we seek to apply the FDS99 
+emission model to the \PLANCK~data set, which offers a dramatic enhancement in
 angular resolution relative to the FIRAS spectra. The \PLANCK~data thereby 
@@
 ($\S$\ref{sec:mcmc}), re-evaluate the best-fit global dust properties 
-($\S$\ref{sec:global}, $\S$\ref{sec:hier}), and fit additional parameters 
-of the two-component model as a function of position on the sky 
+($\S$\ref{sec:global}, $\S$\ref{sec:hier}), and fit additional 
+two-component model parameters as a function of position on the sky 
 ($\S$\ref{sec:lores}).
-% in this last sentence reference the relevant sections for each sub-goal 
-% mentioned
 
@@
 A major aim of this work has been to determine whether the  FDS99 
-two-component dust emission model (or an FDS99-like model) remains favored over
-single-MBB models when swapping the \PLANCK~HFI maps for FIRAS at frequencies 
-below 1250 GHz. We compared dust SED models in two ways (1) by fitting a 
-100-3000 GHz spectrum composed of per-band correlation slopes versus 
-\PLANCK~857 GHz (2) by finding the best-fit dust temperature and optical depth
-per line-of-sight, with each pixel's SED comprised of 100-3000 GHz 
-\PLANCK+DIRBE data, and comparing the average goodness-of-fit under various
-emission models.
+two-component dust emission model remains favored over single-MBB models when 
+swapping the \PLANCK~HFI maps for FIRAS at frequencies below 1250 GHz. We 
+compared dust SED models in two ways (1) by fitting a 100-3000 GHz spectrum 
+composed of per-band correlation slopes versus \PLANCK~857 GHz (2) by finding 
+the best-fit dust temperature and optical depth per line-of-sight, with each 
+pixel's SED comprised of 100-3000 GHz \PLANCK+DIRBE data, and comparing the 
+average goodness-of-fit under various emission models.
 

### 2014-07-24 ms.tex
abstract rewrite, this is the version sent around for feedback/comments

@@
 We also derive full-sky $6.1'$ resolution maps of dust optical depth and 
-temperature by fitting the two-component model to the \PLANCK~217, 353, 545, 
-and 857 GHz maps along with  DIRBE/\IRAS~100$\mu$m data. Because our 
-two-component model matches the dust spectrum near its peak, accounts for the 
-flattening of the dust spectrum at millimeter wavelengths, and specifies dust 
-temperature at 6.1$'$ FWHM, our model provides reliable, high-resolution 
-thermal dust emission foreground predictions from 100 GHz to 3000 GHz. We find 
-that, in diffuse sky regions, our two-component 100-217 GHz thermal dust 
-emission predictions are on average accurate to within 2.2\%, which represents 
-an improvement of 5-15\% relative to predictions based on the \cite{planckdust}
-single-MBB model. We calibrate our two-component optical depth to reddening at 
-visible wavelengths, and compare the resulting reddening estimates with those 
-based on stellar spectra. We find imperfect zodiacal light subtraction in both 
-DIRBE/\IRAS~and \PLANCK~to be the dominant large-scale systematic problem 
+temperature by fitting the two-component model to \PLANCK~217, 353, 545, and 
+857 GHz along with  DIRBE/\IRAS~100$\mu$m data. Because our two-component model
+matches the dust spectrum near its peak, accounts for the flattening of the 
+dust spectrum at millimeter wavelengths, and specifies dust temperature at 
+6.1$'$ FWHM, our model provides reliable, high-resolution thermal dust emission
+foreground predictions from 100 GHz to 3000 GHz. We find that, in diffuse sky 
+regions, our two-component 100-217 GHz thermal dust emission predictions are on
+average accurate to within 2.2\%, while the \cite{planckdust} single-MBB model 
+systematically underpredicts emission by 18.8\% at 100 GHz, 12.6\% at 143 GHz 
+and 7.9\% at 217 GHz. We calibrate our two-component optical depth to reddening
+at visible wavelengths, and compare the resulting reddening estimates with 
+those based on stellar spectra. We find imperfect zodiacal light subtraction in
+both DIRBE/\IRAS~and \PLANCK~to be the dominant large-scale systematic problem 
 in our two-component temperature map and reddening estimates.
@@
 best-fit two-component models from Table \ref{tab:global} outperform single-MBB
-alternatives, though only by a relatively small margin. The agreement between 
-our correlation slope analysis and the present goodness-of-fit analysis is 
-especially encouraging for two main reasons: (1) in the present analysis, dust 
-temperature has been allowed to vary on degree scales, whereas in 
-$\S$\ref{sec:global} we assumed a single global dust temperature (2) in the
-present analysis, our zero-level offsets factor into the dust temperature,
-whereas in $\S$6 this was not the case, meaning the former and latter analyses 
-agree in spite of their potential to be affected by rather different 
-systematics.
+alternatives, though only by a relatively small margin in $\chi^2_{\nu}$. 
+Still, because our present analysis has $\sim$75,500 degrees-of-freedom, 
+$\Delta \chi^2_{\nu}$=0.4 formally corresponds to an enormously significant
+improvement in $\chi^2$. The agreement between our correlation slope analysis 
+and the present goodness-of-fit analysis is especially encouraging for two main
+reasons: (1) in the present analysis, dust temperature has been allowed to vary
+on degree scales, whereas in $\S$\ref{sec:global} we assumed a single global 
+dust temperature and (2) in the present analysis, our zero-level offsets factor
+into the dust temperature, whereas in $\S$6 this was not the case, meaning the 
+former and latter analyses agree in spite of their potential to be affected by 
+rather different systematics.
 
@@
 best-fit \PLANCK+DIRBE two-component model (Table \ref{tab:global}, model 2) 
-outperformed the best-fit single-MBB model, but by a lesser margin than found 
-by FDS99 using FIRAS+DIRBE. Specifically, our best-fit \PLANCK+DIRBE 
-two-component model yielded an improvement of $\Delta \chi^2_{\nu}$=3.41 
-($\S$\ref{sec:global}) and $\Delta \chi^2_{\nu}$=0.4 ($\S$\ref{sec:hier}). This
-represents a far less dramatic contrast than found by the FDS99 correlation 
-slope analysis, $\Delta \chi^2_{\nu}$=29.2. Perhaps, though, the relative lack 
-of discrimination amongst competing dust SED models when relying on 
-\PLANCK+DIRBE is not surprising, given that our constraints include only nine 
-broad frequency channels, whereas FDS99 employed $>$200 narrow bands.
+outperformed the best-fit single-MBB model, but by a lesser margin in 
+$\chi^2_{\nu}$ than found by FDS99 using FIRAS+DIRBE. Specifically, our 
+best-fit \PLANCK+DIRBE two-component model yielded an improvement of 
+$\Delta \chi^2_{\nu}$=3.41 ($\S$\ref{sec:global}) and $\Delta \chi^2_{\nu}$=0.4
+($\S$\ref{sec:hier}). This represents a far less dramatic contrast in 
+$\chi^2_{\nu}$ than found by the FDS99 correlation slope analysis, 
+$\Delta \chi^2_{\nu}$=29.2. Perhaps a relative lack of discrimination amongst 
+competing dust SED models when relying on \PLANCK+DIRBE is to be expected, 
+given that our constraints include only nine broad frequency channels, whereas 
+FDS99 employed $>$200 narrow bands. Still, $\Delta \chi^2_{\nu}$=0.4 from 
+$\S$\ref{sec:hier} is formally of enormous significance, given the 
+$\sim$75,000 degrees of freedom in that analysis.
 
@@
 $\S$\ref{sec:lofreq} that our 100-217 GHz two-component emission predictions
-are more accurate than those of \cite{planckdust} by margins of $\sim$5-15\%.
-We therefore recommend that those interested in thermal dust foregrounds in 
-the 100-3000 GHz frequency range use our data release to predict unpolarized 
-dust emission, at the very least in order to help determine the level at which 
-the choice of dust emission model may influence their conclusions.
+are on average accurate to within 2.2\%, whereas the \cite{planckdust} 
+single-MBB model systematically understimates low-frequency dust emission by 
+18.8\% at 100 GHz, 12.6\% at 143 GHz and 7.9\% at 217 GHz. We therefore 
+recommend that those interested in thermal dust foregrounds in the 100-3000 GHz
+frequency range use our data release to predict unpolarized dust emission, at 
+the very least in order to help determine the level at which the choice of dust
+emission model may influence their conclusions.
 %last sentence needs work

### 2014-08-07 ms.tex
minor revisions after soliciting comments

@@
 model as an alernative parametrization for the dust spectral energy 
-distribution (SED) composed  of \PLANCK High Frequency Instrument (HFI), DIRBE 
+distribution (SED) composed  of \PLANCK~High Frequency Instrument (HFI), DIRBE 
 and \IRAS~data. In doing so, we obtain maps of dust temperature and optical 
@@
 \epsfig{file=f1_1deg.eps, width=3.3in}
-\caption{\label{fig:f1} $1^{\circ}$ FWHM map of $f_1$ derived from our 
+\caption{\label{fig:f1} $1^{\circ}$ FWHM full-sky map of $f_1$ derived from our
 low-resolution fits described in $\S$\ref{sec:lores}. Red coloring masks pixels
@@
 \epsfig{file=ebv_resid_ecl.eps, width=6.6in}
-\caption{\label{fig:resid_ecl} Same as Figure \ref{fig:resid}, but 
-restricting to high ecliptic latitude, $|\beta|>20^{\circ}$. In both the top 
-left and top right plots, the bending of the reddening residuals as a function 
-of $E(B-V)_{SFD}$ seen in Figure \ref{fig:resid} has been eliminated. Further, 
-the two-component reddening residual temperature dependence (bottom left) has 
-been significantly reduced relative to the corresponding trend shown in Figure 
-\ref{fig:resid}.}
+\caption{\label{fig:resid_ecl} Same as Figure \ref{fig:resid}, but restricting 
+to high ecliptic latitude, $|\beta|>20^{\circ}$. In both the top left and top 
+right plots, the bending of the reddening residuals as a function of 
+$E(B-V)_{SFD}$ seen in Figure \ref{fig:resid} has been eliminated. Further, the
+two-component reddening residual temperature dependence (bottom left) has been 
+significantly reduced relative to the corresponding trend shown in Figure 
+\ref{fig:resid}. For $E(B-V)_{SFD}$$\gtrsim$0.3 mag, the top row plots appear 
+noisy because there are an insufficient number of remaining SSPP points of 
+comparison.}
 \end{center}

### 2014-08-09 ms.tex
short title
starting last pass of revisions before submitting to journal

@@
 
-\shorttitle{\PLANCK~Dust Model}
+\shorttitle{\PLANCK~Two-component Dust Model}
 
@@
 those based on stellar spectra. We find imperfect zodiacal light subtraction in
-both DIRBE/\IRAS~and \PLANCK~to be the dominant large-scale systematic problem 
-in our two-component temperature map and reddening estimates.
+both DIRBE/\IRAS~and \PLANCK~to be the dominant large angular scale systematic 
+problem in our two-component temperature map and reddening estimates.
 
@@
 to the total observed sky intensity. At optical and ultraviolet (UV) 
-wavelengths, extinction by foreground dust grains attenuates the signal from 
-extragalactic sources over the entire sky. Observations of interstellar dust 
-emission/absorption can improve our understanding of the composition and 
-physical conditions that prevail in the interstellar medium (ISM), an 
+wavelengths, dust grains absorb and scatter starlight. Observations of 
+interstellar dust emission/absorption can improve our understanding of the 
+physical conditions and composition of the interstellar medium (ISM), an 
 environment which plays a crucial role in Galactic evolution and star 
@@
 combining this best-fit two-component model with a custom reprocessing of 
-\IRAS~100$\mu$m, FDS99 provided widely used foreground predictions with $6.1'$ 
-FHWM, limited largely by their $1.3^{\circ}$ resolution DIRBE-based temperature
-correction.
+DIRBE and \IRAS~100$\mu$m data, FDS99 provided widely used foreground 
+predictions with $6.1'$ FHWM, limited largely by their $1.3^{\circ}$ resolution
+DIRBE-based temperature correction.
 
@@
 we include 100$\mu$m data in our SED fits. In particular, we use the 
-\citet[henceforth SFD]{SFD} reprocessing of \IRAS~100$\mu$m, which we will 
-refer to as \verb|i100|, and at times by frequency as 3000 GHz. The \verb|i100|
- map has angular resolution of $6.1'$, and was constructed so as to contain 
-only thermal emission from Galactic dust, with compact sources and zodiacal 
-light removed, and its zero level tied to H\,\textsc{i}. We use the \verb|i100|
-map as is, without any custom modifications.
+\citet[henceforth SFD]{SFD} reprocessing of DIRBE/\IRAS~100$\mu$m, which we 
+will refer to as \verb|i100|, and at times by frequency as 3000 GHz. The 
+\verb|i100| map has angular resolution of $6.1'$, and was constructed so as to 
+contain only thermal emission from Galactic dust, with compact sources and 
+zodiacal light removed, and its zero level tied to H\,\textsc{i}. We use the 
+\verb|i100| map as is, without any custom modifications.
 
@@
 applying appropriate unit conversions for the 545 and 857 GHz maps with native 
-units of MJy/sr. Low-order corrections, particularly removal of the residual 
-Solar dipole, are discussed in $\S$\ref{sec:zp}.
+units of MJy/sr. Low-order corrections, particularly our removal of  Solar 
+dipole residuals, are discussed in $\S$\ref{sec:zp}.
 
@@
 zero, assuming a linear correlation between these two measurements at low 
-column density. However, this approach is somewhat unsatisfying in that there 
-appear to be different slopes of \PLANCK~857 GHz versus H\,\textsc{i} for 
-different ranges of H\,\textsc{i} intensity. In particular, \PLANCK~857 GHz 
-appears to ``flatten out'' at very low H\,\textsc{i}. More quantitavely, we 
-have found using the LAB H\,\textsc{i} data \citep{lab} for 
-$-72$$<$$v_{LSR}$$<$$+25$ km/s that the best-fit slope for H\,\textsc{i}$<$70 K
-km/s is a factor of $\sim$1.9 lower than the best fit slope for 110 K km/s 
-$<$H\,\textsc{i}$<$200 K km/s, and as a result the implied zero-point offsets 
-for \PLANCK~857 GHz differ by $\sim$0.37 MJy/sr.
+column density. However, this approach is less than completely satsifying in 
+that there appear to be different slopes of \PLANCK~857 GHz versus 
+H\,\textsc{i} for different ranges of H\,\textsc{i} intensity. In particular, 
+\PLANCK~857 GHz appears to ``flatten out'' at very low H\,\textsc{i}, as shown
+in Figure 5 of \cite{planckdust}. More quantitavely, we have found using the 
+LAB H\,\textsc{i} data \citep{lab} for $-72$$<$$v_{LSR}$$<$$+25$ km/s that the 
+best-fit slope for H\,\textsc{i}$<$70 K km/s is a factor of $\sim$1.9 lower 
+than the best fit slope for 110 K km/s $<$H\,\textsc{i}$<$200 K km/s, and as a 
+result the implied zero level offsets for \PLANCK~857 GHz differ by $\sim$0.37 
+MJy/sr.
 
@@
 H\,\textsc{i} emission, we decided to instead constrain the 857 GHz zero level 
-by comparison to the FDS99 857 GHz prediction. This renders the \PLANCK~857 GHz
+by comparison to the FDS99 857 GHz prediction. This renders our \PLANCK~857 GHz
 absolute zero level tied indirectly to H\,\textsc{i} through the FDS99 
-100$\mu$m and 240$\mu$m zero points.
+100$\mu$m and 240$\mu$m zero levels.
 
@@
 of $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine the dust 
-spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels with 
+spectrum shape. We rebin to $N_{side}$=64 and restrict to pixels with 
 $\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to degree 
@@
 iterative outlier rejection. The best-fit linear model is given by 
-$\mathcal{F}_{857}$=0.991$\mathcal{I}_{857}$$-$0.018. It is encouraging that 
-the slope is quite close to unity, and the offset near zero.
+$\mathcal{F}_{857}$=0.991$\mathcal{I}_{857}$$-$0.018 MJy/sr. It is encouraging 
+that the slope is quite close to unity.
 
@@
 In doing so, we assume \PLANCK~857 GHz contains no appreciable Solar dipole 
-residual or other low-order problems. % grammar?
+residual.
 
@@
 \begin{equation}
-M_{\nu} \propto f_{1}q_{1}\Big(\frac{\nu}{\nu_{0}}\Big)^{\beta_1}B_{\nu}(T_1) + f_{2}q_{2}\Big(\frac{\nu}{\nu_0}\Big)^{\beta_2}B_{\nu}(T_2)
+M_{\nu} \propto \Big[f_{1}q_{1}\Big(\frac{\nu}{\nu_{0}}\Big)^{\beta_1}B_{\nu}(T_1) + f_{2}q_{2}\Big(\frac{\nu}{\nu_0}\Big)^{\beta_2}B_{\nu}(T_2)\Big]
 \end{equation}
@@
 $T_2$ is the `hot' dust temperature, and $\beta_1$ and $\beta_2$ are the
-emissivity power-law indices of the cold and hot components respectively. 
+emissivity power-law indices of the cold and hot dust components respectively. 
 $q_1$ represents the ratio of FIR emission cross section to optical absorption 
@@
 
-Fixing the four parameters of Table \ref{tab:global}, our full-resolution, 
+Fixing the aforementioned four global parameters, our full-resolution, 
 five-band fits have two remaining free parameters per line of sight: the hot 
@@
 
-% For the parameters thus far specified, the two dust temperatures are further 
-% related by:
-
-%\begin{equation}
-%T_1 = 0.352T_2^{1.18}
-%\end{equation}
-
-% more important than the details of the above equation is the notion
-% that, for any set of f1, q1/q2, beta1, beta2, the relationship between
-% T1 and T2 is a simple power law
-
-%the below statements seem like they might best be moved to a generic
-%opening of the next section, stating our philosophy of breaking sky
-%into pixels, each with 5 SED measurements, and that with this small
-%number of constraints per pixel, it makes sense to have a baseline
-% fit at full resolution that has only two free parameters
-
-%FDS99 found $T_2 \approx 16.2$K, $T_1 \approx 9.4$K to be typical at 
-%high-latitude. In the present formulation, there are only two free parameters 
-%to describe an observed SED: the hot dust temperature $T_2$ determines the SED
-%shape and the normalization of $M_{\nu}$ determines the SED amplitude. In 
-%principle, we could allow additional parameters, such as $f_1$ and the ratio 
-%$q_1/q_2$, to vary. However the number of free parameters in our baseline fit 
-%at the full $6.1'$ resolution is limited by the fact that, for each sky 
-%location, the observed SED contains only five independent intensity 
-%measurements (\verb|i100| along with the four highest-frequency 
-%\PLANCK~bands).
-
 To calculate the optical depth in the context of this model, we assume
 optically thin conditions, meaning that $\tau_{\nu}$ = $M_{\nu}/S_{\nu}$, where
-$M_{\nu}$ is the appropriately scaled two-component intensity and the source
-function is given by:
+$M_{\nu}$ is the appropriately scaled two-component model intensity and the 
+source function is given by:
 
@@
 $\mathcal{T}_{\nu_i}(\nu)$ is given by the \PLANCK~transmission curves provided
-in the file \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz and
-DIRBE 140$\mu$m, 240$\mu$m, we have adopted the corresponding DIRBE 
-transmission curves. Again, since DIRBE-quoted fluxes also follow the 
-$\alpha$=$-1$ convention, Equation \ref{equ:bpcorr} remains applicable.
+in the file \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For \verb|i100| 
+and DIRBE 140$\mu$m, 240$\mu$m, we have adopted the corresponding DIRBE 
+transmission curves.
+
+%Again, since DIRBE-quoted fluxes also follow the 
+%$\alpha$=$-1$ convention, Equation \ref{equ:bpcorr} remains applicable.
 
@@
 %Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. 
-Our color correction approach allows us to predict $\tilde{I}_{\nu_i}$ by 
-computing monochromatic flux densities at the central frequency $\nu_{i,c}$ and
-then multiplying by factors $b_{\nu_i}(T, \beta)$ which are interpolated off of
-a set of precomputed, one-dimensional lookup tables each listing 
+The color correction of Equation \ref{equ:bpcorr} therefore allows us to 
+predict $\tilde{I}_{\nu_i}$ by computing monochromatic flux densities at the 
+central frequency $\nu_{i,c}$ and then multiplying by factors 
+$b_{\nu_i}(T, \beta)$. In practice, we interpolated the color corrections off 
+of a set of precomputed, one-dimensional lookup tables each listing 
 $b_{\nu_i}(T, \beta)$ as a function of $T$. We avoided the need to interpolate 
@@
 correction factors for the particular set of $\beta$ values of interest (e.g. 
-$\beta$=1.67, 2.7, 1.63, 2.82 ..., see Table \ref{tab:global}).
+$\beta$=1.67, 2.7, 1.63, 2.82 ..., see Table \ref{tab:global}). This color 
+correction approach makes the MCMC sampling described in $\S$\ref{sec:mcmc} 
+much more computationally efficient by circumventing the need to perform the 
+integral in the numerator of Equation \ref{equ:bpcorr} on-the-fly for each 
+proposed dust temperature. We have chosen to compute the color corrections on a
+per-MBB basis because this approach is very versatile; all possible 
+two-component (and single-MBB) models are linear combinations of MBBs, so we 
+can apply all of our color correction machinery even when we allow parameters 
+other than temperature (e.g. $f_1$) to vary and thereby modify the dust 
+spectrum shape.
 
@@
 % off of a 2d grid in (T, beta)
-
-This color correction approach makes the MCMC sampling described in 
-$\S$\ref{sec:mcmc} much more computationally efficient by circumventing the 
-need to perform the integral in the numerator of Equation \ref{equ:bpcorr} 
-on-the-fly for each proposed dust temperature. We have chosen to compute the 
-color corrections on a per-MBB basis because this approach is very 
-versatile; all possible two-component (and single-MBB) models are linear 
-combinations of MBBs, so we can apply all of our color correction machinery 
-even when we allow parameters other than temperature (e.g. $f_1$) to vary and 
-thereby modify the dust spectrum shape.
 
@@
 important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
-specified by $\tilde{I}_{545}$, which represents the flux density per solid
-angle measured in the \PLANCK~545 GHz band. The denominator serves to ensure 
-that, for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. 
-Second, each term in the numerator is multiplied by a conversion factor 
+specified by $\tilde{I}_{545}$, which represents the IRAS convention 
+\PLANCK~545 GHz intensity. The denominator serves to ensure that, for the case 
+of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. Second, each term in 
+the numerator is multiplied by a unit conversion factor 
 $u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
@@
 the problem at hand sufficiently overconstrained, and also in providing 
-information near the peak of the dust SED at $\sim$140$\mu$m, which is 
+information near the peak of the dust SED at $\sim$160$\mu$m, which is 
 particularly sensitive to the presence of a single versus multiple MBB 
@@
 \begin{equation} \label{equ:chi2corr}
-\chi^2 = \sum_{i=0}^{8}\frac{\big[s_{i, 857}-n\frac{\tilde{I}_{\nu_i}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}{\tilde{I}_{857}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}\big]^2}{\sigma_{i}^2}
+\chi^2 = \sum_{i=0}^{8}\frac{\big[s_{i, 857}-n\frac{\tilde{I}_{\nu_i}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}{\tilde{I}_{857}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}\big]^2}{\sigma_{s_i}^2}
 \end{equation}
@@
 Where $\nu_i$$\in$\{100, 143, 217, 353, 545, 857, 1250, 2141, 3000\} GHz. Note 
-that this formula encompasses the general two-component case. In the single-MBB
+that this formula encompasses the general two-component case; in the single-MBB
 case, we take $f_1$=0 and hence $q_1/q_2$, $\beta_1$ and $T_1$ are immaterial, 
@@
 Next (model 2), we consider the fully-general two-component model, allowing all
- six model parameters to vary. In this case, the reduced chi-squared of the 
-best fit is $\chi^2_{\nu}=$1.33, signifying that our introduction of four 
+six model parameters to vary. In this case, the reduced chi-squared of the best
+fit parameters is $\chi^2_{\nu}=$1.33, signifying that our introduction of four
 additional free parameters is justified. The best-fit $\beta_1$ and $\beta_2$ 
@@
 confirm the basic conclusions of this section via an approach in which we 
-allow the dust temperature to vary spatially.
+allow the dust temperature to vary spatially. The analysis of $\S$7.5 also
+allows us to confirm the conclusions of this section while including a 
+fully detailed uncertainty model; our assumption of 2\% per-band uncertainties
+on the correlation slopes is largely a statement that we seek a model
+accurate to 2\% from 100-3000 GHz, although the fact that our $\chi^2_{\nu}$ 
+values are order unity shows that the assumed uncertainties are not grossly 
+over or underestimated.
 
@@
 coordinates, with $N_{side}$=2048. This pixelization is convenient because it 
-is the same format in which the \PLANCK~HFI maps were released, and because it 
+is the format in which the \PLANCK~HFI maps were released, and because it 
 adequately samples the $6.1'$ FWHM maps under consideration in our 
@@
 consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
-spatially constant. By default, we employ the best-fit \PLANCK+DIRBE global 
-parameters of Table \ref{tab:global}, model 2, although our data release 
-($\S$\ref{sec:release}) includes fits with the FDS99 global parameters as well.
-For each line of sight, only the dust spectrum normalization and dust 
-temperatures are allowed to vary. In order to predict the dust SED for a given 
-pixel, we are thus left with two remaining degrees of freedom, and must choose 
-an appropriate set of two parameters to sample and thereby constrain via MCMC. 
-To determine the SED normalization in each pixel, we draw samples in 
-$\tilde{I}_{545}$, the `IRAS convention' intensity in the \PLANCK~545 GHz 
-bandpass, as defined in Equation \ref{eqn:inten}. With the four aforementioned 
-global parameters fixed, the dust spectrum shape is determined entirely by the 
-two dust temperatures, which are coupled. To constrain the dust temperatures, 
-we sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we 
-compute the corresponding value of $T_1$, thereby determining the temperature 
-and emissivity power law index for both MBB components and thus fully 
-specifying the SED shape. In principle, we could sample in either $T_1$ or 
-$T_2$, but have chosen to sample in $T_2$ because emission from this component 
-dominates in the relatively high frequency bands which most strongly constrain 
-the dust temperatures.
+spatially constant. We employ the best-fit \PLANCK+DIRBE global parameters of 
+Table \ref{tab:global}, model 2. For each line of sight, only the dust spectrum
+normalization and dust temperatures are allowed to vary. In order to predict 
+the dust SED for a given pixel, we are thus left with two remaining degrees of 
+freedom, and must choose an appropriate set of two parameters to sample and 
+thereby constrain via MCMC. To determine the SED normalization in each pixel, 
+we draw samples in $\tilde{I}_{545}$, the `IRAS convention' intensity in the 
+\PLANCK~545 GHz bandpass, as defined in Equation \ref{eqn:inten}. With the four
+aforementioned global parameters fixed, the dust spectrum shape is determined 
+entirely by the two dust temperatures, which are coupled. To constrain the dust
+temperatures, we sample in $T_2$, the hot dust temperature. For each sample in 
+$T_2$, we compute the corresponding value of $T_1$, thereby determining the 
+temperature and emissivity power law index for both MBB components and thus 
+fully specifying the SED shape. In principle, we could sample in either $T_1$ 
+or $T_2$, but have chosen to sample in $T_2$ because emission from this 
+component dominates in the relatively high frequency bands which most strongly 
+constrain the dust temperatures.
 
@@
 the observed 217-3000 GHz thermal dust SED as a function of the two parameters 
-$\tilde{I}_{545}$ and $T_2$. More specifically, we are sampling the posterior 
-given by:
+$\tilde{I}_{545}$ and $T_2$. More specifically, for each pixel, we are sampling
+the posterior given by:
 
@@
 \label{sec:release}
-We are releasing $N_{side}$=2048 HEALPix maps in Galactic coordinates 
-summarizing the results of our full-resolution two-component dust fits. 
-Refer to the data release documentation and FITS file headers for further 
-details.
-
-% will we release software for making thermal dust predictions (i suppose
-% we can just release a reddening map, and there doesn't need to be 
-% any software released in that regard?)
+We are releasing a set of $N_{side}$=2048 HEALPix maps in Galactic coordinates 
+which summarize the results of our full-resolution two-component dust fits. 
+Low-resolution renderings of our full-sky dust temperature and optical depth 
+maps are shown in Figure \ref{fig:results}. Our data release also includes
+software utilities for obtaining emission and reddening predictions from our 
+\PLANCK-based two-component fits. Refer to the data release documentation and 
+FITS file headers for further details.\footnote{\texttt{http://faun.rc.fas.harvard.edu/ameisner/planckdust}}
+
+% mention that DR includes software to obtain emission and extinction 
+% predictions
 

### 2014-08-09 ms.tex
more pre-submission edits

@@
 residuals of the Solar dipole remain at low frequencies. We will address these 
-issues by separately solving two sub-problems: first, fixing the absolute zero 
-level of \PLANCK~857 GHz relative to external data, and second fitting 
+issues by separately solving two sub-problems: first, we set the absolute zero 
+level of \PLANCK~857 GHz relative to external data, and second we fit the 
 100-545 GHz offsets and low order corrections by correlating these 
@@
 
-Because of these ambiguities in the relationship between 857 GHz and 
-H\,\textsc{i} emission, we decided to instead constrain the 857 GHz zero level 
-by comparison to the FDS99 857 GHz prediction. This renders our \PLANCK~857 GHz
-absolute zero level tied indirectly to H\,\textsc{i} through the FDS99 
-100$\mu$m and 240$\mu$m zero levels.
+Because of this ambiguity in the relationship between 857 GHz and H\,\textsc{i}
+emission, we decided to instead constrain the \PLANCK~857 GHz zero level by 
+comparison to the FDS99-predicted 857 GHz thermal dust emission. This renders 
+our \PLANCK~857 GHz absolute zero level tied indirectly to H\,\textsc{i} 
+through the FDS99 100$\mu$m and 240$\mu$m zero levels.
 
@@
 assume no offset need be applied to \verb|i100|, which already has its zero 
-level tied to H\,\textsc{i}.
+level tied to H\,\textsc{i} by SFD.
 
@@
 \ref{fig:dip} shows scatter plots of the band $\nu_i$ versus 857 GHz 
-correlation before and after correcting for the best-fit offset and residual 
-dipole, for each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only are the 
-tightened correlations striking in these scatter plots, but the residual dipole
-subtractions appear very successful in the two-dimensional band $\nu_i$ maps 
-themselves. Before performing thermal dust fits, we therefore subtract the 
-best-fit $b$ and $d\mathcal{D}$ from each band $\nu_i$ map. The best-fit 
-offsets and residual dipole amplitudes are listed in Table \ref{table:offs},
-along with other important per-band parameters, such as the fractional 
-multiplicative calibration uncertainty $c_{\nu}$.
+correlation before (left) and after (right) correcting for the best-fit offset 
+and residual dipole, for each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only 
+are the tightened correlations striking in these scatter plots, but the 
+residual dipole subtractions appear very successful in the two-dimensional band
+$\nu_i$ maps themselves. Before performing thermal dust fits, we therefore 
+subtract the best-fit $b$ and $d\mathcal{D}$ from each 143-545 GHz map. The 
+best-fit offsets and residual dipole amplitudes are listed in Table 
+\ref{table:offs}, along with other important per-band parameters, such as the 
+fractional multiplicative calibration uncertainty $c_{\nu}$.
 
@@
 the millimeter in a manner which is not consistent with a simple extrapolation 
-of the single-MBB model to low frequencies. In the diffuse ISM, \cite{reach95} 
+of single-MBB models to low frequencies. In the diffuse ISM, \cite{reach95} 
 found an improved fit to the FIRAS data using an empirically motivated 
@@
 $f_2$ dictate the relative contributions of the two MBB components to the
-combined SED, and can be thought of as encoding the mass fraction of each 
-species, although technically $f_1$ ($f_2$) is the optical absorption 
-cross-section weighted mass fraction for species 1 (2). Following the 
-convention of FDS99, we choose $\nu_0$=3000 GHz and take $f_2$=(1$-$$f_1$).
+combined SED. Thus, $f_1$ and $f_2$ can be thought of as encoding the mass 
+fraction of each species, although technically $f_1$ ($f_2$) is the optical 
+absorption cross-section weighted mass fraction for species 1 (2). Following 
+the convention of FDS99, we choose $\nu_0$=3000 GHz and take $f_2$=(1$-$$f_1$).
 
@@
 of a set of precomputed, one-dimensional lookup tables each listing 
-$b_{\nu_i}(T, \beta)$ as a function of $T$. We avoided the need to interpolate 
-in both $\beta$ and $T$ by computing only a small set of one dimensional 
-correction factors for the particular set of $\beta$ values of interest (e.g. 
-$\beta$=1.67, 2.7, 1.63, 2.82 ..., see Table \ref{tab:global}). This color 
-correction approach makes the MCMC sampling described in $\S$\ref{sec:mcmc} 
-much more computationally efficient by circumventing the need to perform the 
-integral in the numerator of Equation \ref{equ:bpcorr} on-the-fly for each 
-proposed dust temperature. We have chosen to compute the color corrections on a
-per-MBB basis because this approach is very versatile; all possible 
-two-component (and single-MBB) models are linear combinations of MBBs, so we 
-can apply all of our color correction machinery even when we allow parameters 
-other than temperature (e.g. $f_1$) to vary and thereby modify the dust 
-spectrum shape.
+$b_{\nu_i}(T, \beta)$ for a single $\beta$ value as a function of $T$. We thus
+avoided the need to interpolate in both $\beta$ and $T$ by computing only a 
+small set of one dimensional correction factors for the particular set of 
+$\beta$ values of interest (e.g. $\beta$=1.67, 2.7, 1.63, 2.82 ..., see Table 
+\ref{tab:global}). This color correction approach makes the MCMC sampling 
+described in $\S$\ref{sec:mcmc} much more computationally efficient by 
+circumventing the need to perform the integral in the numerator of Equation 
+\ref{equ:bpcorr} on-the-fly for each proposed dust temperature. We have chosen 
+to compute the color corrections on a per-MBB basis because this approach is 
+very versatile; all possible two-component (and single-MBB) models are linear 
+combinations of MBBs, so we can apply all of our color correction machinery 
+even when we allow parameters other than temperature (e.g. $f_1$) to vary and 
+thereby modify the dust spectrum shape.
 
@@
 accurate to 2\% from 100-3000 GHz, although the fact that our $\chi^2_{\nu}$ 
-values are order unity shows that the assumed uncertainties are not grossly 
+values are order unity suggests that the assumed uncertainties are not grossly 
 over or underestimated.
@@
 temperatures, we sample in $T_2$, the hot dust temperature. For each sample in 
-$T_2$, we compute the corresponding value of $T_1$, thereby determining the 
-temperature and emissivity power law index for both MBB components and thus 
-fully specifying the SED shape. In principle, we could sample in either $T_1$ 
-or $T_2$, but have chosen to sample in $T_2$ because emission from this 
-component dominates in the relatively high frequency bands which most strongly 
-constrain the dust temperatures.
+$T_2$, we compute the corresponding value of $T_1$, thereby fully specifying 
+the SED shape. In principle, we could sample in either $T_1$ or $T_2$, but have
+chosen to sample in $T_2$ because emission from this component dominates in the
+relatively high frequency bands which most strongly constrain the dust 
+temperatures.
 
@@
 \begin{equation} \label{equ:like}
-\mathcal{L}(\mathbf{I}|\tilde{I}_{545}, T_2) = \textrm{exp}\Big[-\frac{1}{2}(\mathbf{I}-\mathbf{\tilde{I}})\Sigma^{-1}(\mathbf{I}-\mathbf{\tilde{I}})^T\Big]
+\mathcal{L}(\mathbf{I}|\tilde{I}_{545}, T_2) = \textrm{exp}\Big[-\frac{1}{2}(\mathbf{I}-\mathbf{\tilde{I}})^T\Sigma^{-1}(\mathbf{I}-\mathbf{\tilde{I}})\Big]
 \end{equation}
@@
 $\tilde{I}_{353}$, $\tilde{I}_{545}$, $\tilde{I}_{857}$, $\tilde{I}_{3000}$). 
-$\Sigma$ is the covariance matrix constructed based on the uncertainties in the
-observed intensities:
+$\Sigma$ is the per-pixel covariance matrix constructed based on the 
+uncertainties in the observed intensities:
 
@@
 \ref{table:offs}. The next term accounts for the uncertainty on the CO emission
-correction, taking $\sigma_{CO, \nu_i}$=0.15$\times$$I_{CO, \nu_i}$ (see 
+correction, taking $\sigma_{CO, \nu_i}(p)$=0.15$\times$$I_{CO, \nu_i}(p)$ (see 
 $\S$\ref{sec:mole}, specifically Equation \ref{equ:molcorr}).
@@
 two-component intensity at 545 GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
-$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$, its variance, and the 
-545 GHz optical depth $\tau_{545}$=$\langle \tau_{545, j} \rangle$ = 
+$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}, \beta_2) \rangle$, its variance, 
+and the 545 GHz optical depth $\tau_{545}$=$\langle \tau_{545, j} \rangle$ = 
 $\langle M_{545, j}/S_{545, j} \rangle$ and its variance. $\tau_{545}$ and 
@@
 and thermal dust emission ($\S$\ref{sec:lofreq}), respectively. At high 
-Galactic latitude, we find a typical $T_2$ uncertainty of 0.45 K, and
-typical $\tilde{I}_{545}$ fractional uncertainty of 13\%. Figure \ref{fig:sed}
-shows a summary of the observed SED and resulting best-fit two-component
-model for a single $N_{side}$=2048 pixel, and Figure \ref{fig:post} 
-shows posterior PDFs for three pixels. Figure \ref{fig:comparison} shows
-a map of our derived hot dust temperature at full-resolution, for a patch
-of sky in the Polaris flare region.
+Galactic latitude, we find a typical $T_2$ uncertainty of 0.45 K, and typical 
+$\tilde{I}_{545}$ fractional uncertainty of 13\%. Figure \ref{fig:sed} shows a 
+summary of the observed SED and resulting best-fit two-component model for a 
+single $N_{side}$=2048 pixel, and Figure \ref{fig:post} shows posterior PDFs 
+for three pixels. Figure \ref{fig:comparison} shows a map of our derived hot 
+dust temperature at full-resolution, for a patch of sky in the Polaris flare 
+region.
 
@@
 Galactic latitude, the relatively low $f_1$ values in the Polaris flare region,
-and the clouds with relatively high $f_1$ near the north Galactic pole.}
+and the clouds with relatively high $f_1$ values the north Galactic pole.}
 \end{center}
@@
 
-%%%\begin{figure}
-%%%\begin{center}
-%%%\epsfig{file=f1_lambert.eps, width=3.3in}
-%%%\caption{\label{fig:f1lambert} The results of our low-resolution fit with $f_1$
-%%%allowed to vary, shown in Lambert projection to highlight the salient features 
-%%%near the north Galactic pole.}
-%%%\end{center}
-%%%\end{figure}
-
 The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. A 
@@
 apparent. The other most salient features are the relatively low
-values of $f_1$ in the Polaris flare, and the relatively high $f_1$ values
+values of $f_1$ in the Polaris flare, and the relatively high $f_1$ clouds
 near the north Galactic pole.
@@
 %Galactic hemisphere in Lambert projection in Figure \ref{fig:f1}.
-
-% add comment about high f_1 regions near NGP
-% also add sentences referring reader to the two f_1 figures
 
@@
 and switching to a uniform prior on $T_2$. Under these circumstances, the 
-chi-squared corresponding to the best-fit parameters for each pixel, termed 
+chi-squared corresponding to the best-fit parameters for pixel $p$, termed 
 $\chi^2_p$, is simply $-2 \times log(P_{max})$. We will refer to the
@@
 minimizing each $\chi^2_p$ by finding pixel $p$'s best-fitting dust 
-temperature and normalization, then evaluating $\langle \chi_{p}^2 \rangle$. 
-First, we consider single-MBB models with $\beta$ spatially constant (see the
-black line in Figure \ref{fig:chi2_dirbe}). $\beta$=1.57 yields the best fit, 
-with $\chi^2_{\nu}$=2.51. This result is in excellent agreement with that of 
-$\S$\ref{sec:global}, where we found the best-fit single-MBB model to have 
-$\beta$=1.59.
-
-We also evaluated $\chi^2_{\nu}$ for single-MBB models in which
-$\beta$ varies spatially. In these cases, we adopted the 0.5$^{\circ}$ 
-resolution $\beta$ map from \cite{planckdust}. We started by calculating 
-$\chi^2_{\nu}$ using the \cite{planckdust} temperature map, finding 
-$\chi^2_{\nu}$=4.68. Note that in this case no per-pixel chi-squared 
-minimization was involved, as we simply evaluated $\chi^2_{p}$ for each pixel 
-based on the fully-specified \cite{planckdust} emission model. Next, we tested 
-a single-MBB model for which we adopted the \cite{planckdust} $\beta$ map, but 
-allowed the per-pixel temperature and normalization to vary so as to minimize 
-$\chi^2_p$. In this case, we found $\chi^2_{\nu}$=2.51, effectively identical 
-to the value found for the spatially constant $\beta$=1.57 single-MBB model. 
-This is perhaps unsurprising, as the average $\beta$ value from 
-\cite{planckdust} over the mask in question is $\langle\beta\rangle$=1.58. 
-This result does suggest, however, that the half-degree variations in $\beta$ 
-are not materially improving the goodness-of-fit over the full frequency range 
-100-3000 GHz relative to a model with appropriately chosen spatially constant 
-$\beta$.
+temperature and normalization, then evaluating 
+$\langle \chi_{p, \nu}^2 \rangle$. First, we consider single-MBB models with 
+$\beta$ spatially constant (see the black line in Figure \ref{fig:chi2_dirbe}).
+$\beta$=1.57 yields the best fit, with $\chi^2_{\nu}$=2.51. This result is in 
+excellent agreement with that of $\S$\ref{sec:global}, where we found the 
+best-fit single-MBB model to have $\beta$=1.59.
+
+We also evaluated $\chi^2_{\nu}$ for single-MBB models in which $\beta$ varies 
+spatially. In these cases, we adopted the 0.5$^{\circ}$ resolution $\beta$ map 
+from \cite{planckdust}. We started by calculating $\chi^2_{\nu}$ using the 
+\cite{planckdust} temperature map, finding $\chi^2_{\nu}$=4.68. Note that in 
+this case no per-pixel chi-squared minimization was involved, as we simply 
+evaluated $\chi^2_{p}$ for each pixel based on the fully-specified 
+\cite{planckdust} emission model. Next, we tested a single-MBB model for which 
+we adopted the \cite{planckdust} $\beta$ map, but allowed the per-pixel 
+temperature and normalization to vary so as to minimize $\chi^2_p$. In this 
+case, we found $\chi^2_{\nu}$=2.51, effectively identical to the value found 
+for the spatially constant $\beta$=1.57 single-MBB model. This is perhaps 
+unsurprising, as the average $\beta$ value from \cite{planckdust} over the mask
+in question is $\langle\beta\rangle$=1.58. This result does suggest, however, 
+that in diffuse regions the half-degree variations in $\beta$ are not 
+materially improving the goodness-of-fit over the full frequency range 100-3000
+GHz relative to a model with appropriately chosen spatially constant $\beta$.
 
@@
 improvement in $\chi^2$. The agreement between our correlation slope analysis 
-and the present goodness-of-fit analysis is especially encouraging for two main
-reasons: (1) in the present analysis, dust temperature has been allowed to vary
-on degree scales, whereas in $\S$\ref{sec:global} we assumed a single global 
-dust temperature and (2) in the present analysis, our zero-level offsets factor
-into the dust temperature, whereas in $\S$6 this was not the case, meaning the 
-former and latter analyses agree in spite of their potential to be affected by 
-rather different systematics.
-
-% say that, becuase such little improvement for two-component versus
-% single MBB in this analysis, we include a single-MBB beta = 1.57 fit in
-% our data release ???
+and the present goodness-of-fit analysis is especially encouraging for three 
+main reasons: (1) in the present analysis, dust temperature has been allowed to
+vary on degree scales, whereas in $\S$\ref{sec:global} we assumed a single 
+global dust temperature (2) the present analysis employs a fully detailed, 
+per-pixel uncertainty model and (3) in the present analysis, our zero-level 
+offsets factor into the dust temperature, whereas in $\S$6 this was not the 
+case, meaning the former and latter analyses agree in spite of their potential 
+to be affected by rather different systematics.
 
@@
 
-While the temperature and optical depth maps thus far derived are
-useful for making thermal dust emission foreground predictions, estimating 
-optical reddening/extinction is another important application of the 
-$\tau_{545}$ map. Translating our two-component optical depth to reddening
-is especially valuable because our $T_2$ map has $\sim$13$\times$ better
-angular resolution than the SFD temperature correction, and thus there is 
-reason to believe our two-component reddening estimates may be superior to
-those of SFD. However, as discussed in $\S$\ref{sec:replace}, we do not yet 
-advocate for the wholesale replacement of SFD, and more detailed work is still 
-necessary to determine/quantify the extent to which \PLANCK-based dust maps
-might improve reddening estimates relative to SFD.
+While the temperature and optical depth maps thus far derived are useful for 
+making thermal dust emission foreground predictions, estimating optical 
+reddening/extinction is another important application of the $\tau_{545}$ map. 
+Translating our two-component optical depth to reddening is especially valuable
+because our $T_2$ map has $\sim$13$\times$ better angular resolution than the 
+SFD temperature correction, and thus there is reason to believe our 
+two-component reddening estimates may be superior to those of SFD. However, as 
+discussed in $\S$\ref{sec:replace}, we do not yet advocate for the wholesale 
+replacement of SFD, and more detailed work is still necessary to 
+determine/quantify the extent to which \PLANCK-based dust maps might improve 
+reddening estimates relative to SFD.
 
@@
 is a strong linear correlation between $E(B-V)_{SSPP}$ and $\tau_{545}$. The 
-conversion factor from $\tau_{545}$ to $E(B-V)$ is 2.46$\times$10$^{3}$. 
-Reassuringly, the best-fit offset is quite close to zero, $\sim$0.6 mmag.
+conversion factor from $\tau_{545}$ to $E(B-V)$ is 2.62$\times$10$^{3}$. 
+Reassuringly, the best-fit offset is close to zero, $\sim$2.6 mmag.
 
@@
 estimates is a faulty temperature correction. For this reason, we have included
-the bottom panels of Figure \ref{fig:resid}, to check for the presence of
-a temperature dependence of the reddening residuals. Indeed, in both the
+the bottom panels of Figure \ref{fig:resid}, to check for the presence of a 
+temperature dependence of the reddening residuals. Indeed, in both the
 two-component and single-MBB cases there exists some systematic dependence of
-the reddening residuals on temperature. For $T_{mbb}$$\gtrsim$19 K, the 
-median residual is reasonably flat, but at lower temperatures (the lowest 
-temperature $\sim$20\% of the sky), the median shows trends at the $\sim$10 
-mmag level. On the other hand, the median residual in the two-component case 
-trends downward with increasing $T_2$ over the entire $T_2$ range shown, with a
+the reddening residuals on temperature. For $T_{mbb}$$\gtrsim$19 K, the median 
+residual is reasonably flat, but at lower temperatures (the lowest temperature 
+$\sim$20\% of SSPP sight lines), the median shows trends at the $\sim$10 mmag 
+level. On the other hand, the median residual in the two-component case trends 
+downward with increasing $T_2$ over the entire $T_2$ range shown, with a 
 peak-to-peak amplitude of $\sim$20 mmag.
@@
 
-In this section we describe our attempts to eliminate the systematic
-problems in the two-component reddening residuals shown in the left column
-of Figure \ref{fig:resid}. We employed two main strategies: (1) recomputing
-the two-component $\tau_{545}$ by re-running our Markov chains after modifying 
-the input maps and/or changing the particular two-component model adopted and
-(2) making spatial cuts to isolate sky regions in which the 
-residuals are especially pristine (or especially problematic).
-
-The following is a list of dust model modifications we tested, but which
-proved to have little impact on the reddening residual trends as a function 
-of either $E(B-V)_{SFD}$ or $T_2$:
+In this section we describe our attempts to eliminate the systematic problems 
+in the two-component reddening residuals shown in the left column of Figure 
+\ref{fig:resid}. We employed two main strategies: (1) recomputing the 
+two-component $\tau_{545}$ by re-running our Markov chains after modifying the 
+input maps and/or changing the particular two-component model paramters adopted
+and (2) making spatial cuts to isolate sky regions in which the residuals are 
+especially pristine (or especially problematic).
+
+The following is a list of dust model modifications we tested, but which proved
+to have little impact on the reddening residual trends as a function of either 
+$E(B-V)_{SFD}$ or $T_2$:
 
@@
 hints of promise in rectifying the reddening residual temperature dependence, 
-but cannot completely resolve the systematic trends in reddening residuals.
+but could not by itself completely resolve the systematic trends in reddening 
+residuals.
 % last few words here are kind of bad, need better terminology
@@
 After cutting the ecliptic plane, we found that only small zero level
-perturbations were required to fully flatten the temperature residuals,
-while still maintaining flat residuals versus $E(B-V)_{SFD}$. The optimal
-offsets we found were $\pm$0.08 MJy/sr to \verb|i100| and 857 GHz respectively
-(see Figure \ref{fig:resid_offs}). These offsets are well within reason, 
-given the nominal zero level uncertainties quoted in Table \ref{table:offs}.
+perturbations were required to fully flatten the temperature residuals, while 
+still maintaining flat residuals versus $E(B-V)_{SFD}$. The optimal offsets we 
+found were $\pm$0.08 MJy/sr to \verb|i100| and 857 GHz respectively (see Figure
+\ref{fig:resid_offs}). These offsets are well within reason, given the nominal 
+zero level uncertainties quoted in Table \ref{table:offs}.
 
@@
 \end{figure}
-
-% but then we tried ECL cuts, and in combination with modest offsets, that 
-% worked
 
@@
 
-To assess the accuracy of low-frequency emission predictions, we compare
-the \PLANCK~HFI map at each of 100, 143, 217 GHz to the corresponding 
-single-MBB and two-component predictions, with all maps smoothed to 
-$1^{\circ}$ FWHM and binned down to $N_{side}=64$. We restrict to the 
-same set of pixels used for the goodness-of-fit analysis of 
-$\S$\ref{sec:hier}, with $|b|>30^{\circ}$ and $|\beta|>30^{\circ}$, also 
-avoiding molecular emission, the SMICA inpainting mask, and compact sources. We
-then perform a linear fit between the \PLANCK~observed emission and the 
-predicted emission at each frequency and for each emission model. For these
-fits, we consider the predicted emission to be the independent variable, 
-since it has higher S/N than the observations, especially at 100 and 143 GHz.
-We also assign pixel weights proportional to the predicted emission, so that
-the best-fit lines faithfully capture the linear trend exhibited 
-without being biased by the large number of very low S/N pixels with minimal 
-emission. Scatter plots between the predicted and observed emission are shown 
-in Figure \ref{fig:lofreq}. The best-fit lines are overplotted and their 
-equations are given in the top left corner of each subplot.
-
-In both the single-MBB and two-component cases, all of the best fit offsets
-are within the uncertainties quoted in Table \ref{table:offs}. On the other 
-hand, the top row of Figure \ref{fig:lofreq} shows that the \cite{planckdust} 
+To assess the accuracy of low-frequency emission predictions, we compare the 
+observed \PLANCK~HFI map at each of 100, 143, 217 GHz to the corresponding 
+single-MBB and two-component predictions, with all maps smoothed to $1^{\circ}$
+FWHM and binned down to $N_{side}$=$64$. We restrict to the same set of pixels 
+used for the goodness-of-fit analysis of $\S$\ref{sec:hier}, with 
+$|b|>30^{\circ}$ and $|\beta|>30^{\circ}$, also avoiding molecular emission, 
+the SMICA inpainting mask, and compact sources. We then perform a linear fit 
+between the \PLANCK~observed emission and the predicted emission at each 
+frequency and for each emission model. For these fits, we consider the 
+predicted emission to be the independent variable, since it has higher S/N than
+the observations, especially at 100 and 143 GHz. We also assign pixel weights 
+proportional to the predicted emission, so that the best-fit lines faithfully 
+capture the linear trend exhibited without being biased by the large number of 
+very low S/N pixels with minimal emission. Scatter plots between the predicted 
+and observed emission are shown in Figure \ref{fig:lofreq}. The best-fit lines 
+are overplotted and their equations are given in the top left corner of each 
+subplot.
+
+In both the single-MBB and two-component cases, all of the best fit offsets are
+within the uncertainties quoted in Table \ref{table:offs}. On the other hand, 
+the top row of Figure \ref{fig:lofreq} shows that the \cite{planckdust} 
 single-MBB predictions yield slopes substantially different from unity: 1.079 
@@
 are larger than unity indicates that the \cite{planckdust} predictions are 
-systematically low. The systematic underprediction evidently become gradually 
-more severe as lower frequencies are considered, with a 7.9\% underprediction 
-at 217 GHz, a 12.6\% underprediction at 143 GHz and an 18.8\% underprediction 
-at 100 GHz.
+systematically low. The systematic underprediction evidently becomes gradually 
+more pronounced as lower frequencies are considered, with a 7.9\% 
+underprediction at 217 GHz, a 12.6\% underprediction at 143 GHz and an 18.8\% 
+underprediction at 100 GHz.
 
@@
 observed emission. More quantitatively, the two-component slopes are all within
-2.2\% of unity: 0.978 at 217 GHz, 0.986 at 143 GHz and 1.022 at 100 GHz. 
-We note that at 217 GHz, the good agreement is in some sense predetermined by 
-the fact that \PLANCK~217 GHz has been included in our two-component MCMC fits.
-On the other hand, the 143 and 100 GHz predictions are based on extrapolation.
-
-We conclude from our predicted versus observed emission comparison that our 
+2.2\% of unity: 0.978 at 217 GHz, 0.986 at 143 GHz and 1.022 at 100 GHz. We 
+note that at 217 GHz, the good agreement is in some sense predetermined by the 
+fact that \PLANCK~217 GHz has been included in our two-component MCMC fits. On 
+the other hand, the 143 and 100 GHz predictions are based on extrapolation.
+
+We conclude from these predicted versus observed emission comparisons that our 
 two-component model outperforms the \cite{planckdust} single-MBB model at 
 predicting Galactic thermal dust emission in diffuse regions from 100-217 GHz.
+It should be noted, though, that \cite{planckdust} did not intend for their 
+single-MBB model to be extrapolated to frequencies below 350 GHz (see their
+$\S$7.2.1), whereas we optimized our two-component model to be valid over the 
+entire 100-3000 GHz frequency range.
 
@@
 
-% mention that DR includes software to obtain emission and extinction 
-% predictions
-
 % if we're not going to be claiming to be superseding SFD in terms of 
@@
 % (data files and/or code) in this data release ?
-
-%software utilities
-%provide maps at multiple different nsides ?
-%   -> if so, actually smooth the maps before rebinning, or leave 
-%      undersampled?
-% provide uncertainty maps for tau and T2 ??
 
@@
 \subsection{Single-MBB versus Two-component emission}
-A major aim of this work has been to determine whether the  FDS99 
-two-component dust emission model remains favored over single-MBB models when 
-swapping the \PLANCK~HFI maps for FIRAS at frequencies below 1250 GHz. We 
-compared dust SED models in two ways (1) by fitting a 100-3000 GHz spectrum 
-composed of per-band correlation slopes versus \PLANCK~857 GHz (2) by finding 
-the best-fit dust temperature and optical depth per line-of-sight, with each 
-pixel's SED comprised of 100-3000 GHz \PLANCK+DIRBE data, and comparing the 
-average goodness-of-fit under various emission models.
+A major aim of this work has been to determine whether the  FDS99 two-component
+dust emission model remains favored over single-MBB models when swapping the 
+\PLANCK~HFI maps for FIRAS at frequencies below 1250 GHz. We compared dust SED 
+models in two ways (1) by fitting a 100-3000 GHz spectrum composed of per-band 
+correlation slopes versus \PLANCK~857 GHz (2) by finding the best-fit dust 
+temperature and optical depth per line-of-sight, with each pixel's SED 
+comprised of 100-3000 GHz \PLANCK+DIRBE data, and comparing the average 
+goodness-of-fit under various emission models.
 
 In both the correlation slope analysis of $\S$\ref{sec:global} and the 
-goodness-of-fit analysis of $\S$\ref{sec:hier} we found that the 
-best-fit \PLANCK+DIRBE two-component model (Table \ref{tab:global}, model 2) 
+goodness-of-fit analysis of $\S$\ref{sec:hier} we found that the best-fit 
+\PLANCK+DIRBE two-component model (Table \ref{tab:global}, model 2) 
 outperformed the best-fit single-MBB model, but by a lesser margin in 
@@
 FDS99 employed $>$200 narrow bands. Still, $\Delta \chi^2_{\nu}$=0.4 from 
-$\S$\ref{sec:hier} is formally of enormous significance, given the 
-$\sim$75,000 degrees of freedom in that analysis.
-
-% in above paragraph, say which single-MBB beta(s) we find to be favored
-
-Nevertheless, we have established that the two-component emission model
-remains viable in light of the \PLANCK~HFI data, and that the FIR/submm 
-dust SED's preference for two MBB components rather than just one is not
-simply an idiosyncracy of the FIRAS spectra. Furthermore, we showed in 
+$\S$\ref{sec:hier} is formally of enormous significance, given the $\sim$75,000
+degrees of freedom in that analysis.
+
+% in above paragraph, say which single-MBB beta(s) we find to be favored ?
+
+Nevertheless, we have established that the two-component emission model remains
+viable in light of the \PLANCK~HFI data, and that the FIR/submm dust SED's 
+preference for two MBB components rather than just one is not simply an 
+idiosyncracy of the FIRAS spectra. Furthermore, we showed in 
 $\S$\ref{sec:lofreq} that our 100-217 GHz two-component emission predictions 
 are on average accurate to within 2.2\%, whereas the \cite{planckdust} 
-single-MBB model systematically understimates low-frequency dust emission by 
+single-MBB model systematically underestimates low-frequency dust emission by 
 18.8\% at 100 GHz, 12.6\% at 143 GHz and 7.9\% at 217 GHz. We therefore 
@@
 emission model may influence their conclusions.
-%last sentence needs work
 
@@
 study against H\,\textsc{i} emission bear out this notion, further revealing 
-that the imperfect zodi corrections are not limited to \verb|i100| (the 
-map for which one would expect zodiacal contamination to be most 
-problematic), but in fact are noticeable in all of the HFI 
-\verb|R1.10_nominal_ZodiCorrected| maps as well. We deemed it infeasible to 
-reconsider all of the \PLANCK~zodi corrections in addition to the 3000 GHz zodi
-correction as a part of this study. Perhaps the forthcoming \PLANCK~data 
-release, including observations acquired during additional orbits, will 
-effectively eliminate any residual zodi problems in the \PLANCK~bands. Under 
-these circumstances it might then be worthwhile to consider revising the DIRBE 
-100$\mu$m zodi correction provided by SFD.
+that the imperfect zodi corrections are not limited to \verb|i100| (the map for
+which one would expect zodiacal contamination to be most problematic), but in 
+fact are noticeable in all of the HFI \verb|R1.10_nominal_ZodiCorrected| maps 
+as well. We deemed it infeasible to reconsider all of the \PLANCK~zodi 
+corrections in addition to the 3000 GHz zodi correction as a part of this 
+study. Perhaps the forthcoming \PLANCK~data release, including observations 
+acquired during additional orbits, will effectively eliminate any residual zodi
+problems in the \PLANCK~bands. Under these circumstances it might then be 
+worthwhile to consider revising the DIRBE 100$\mu$m zodi correction provided by
+SFD.
 
@@
 our ability to quote reddening uncertainties, which results from the 
-probabilistic framework of $\S$\ref{sec:mcmc}. The extinction estimates 
-from this work can also be employed as an alternative to those of SFD, to gauge
-the impact of dust map choice in a specific end user's application.
+probabilistic framework of $\S$\ref{sec:mcmc}. The extinction estimates from 
+this work can also be employed as an alternative to those of SFD, to gauge the 
+impact of dust map choice in a specific end user's application.
 

### 2014-08-09 ms.tex
define 'zodi' jargon

@@
 
-Imperfect zodi corrections represent a second major limitation of our results.
-The ecliptic plane's prominence in our full-sky temperature map (Figure 
-\ref{fig:results}) suggests that the zodiacal light subtractions performed on 
-the input maps are not ideal. Our comparisons of the FIR maps used in this 
-study against H\,\textsc{i} emission bear out this notion, further revealing 
-that the imperfect zodi corrections are not limited to \verb|i100| (the map for
-which one would expect zodiacal contamination to be most problematic), but in 
-fact are noticeable in all of the HFI \verb|R1.10_nominal_ZodiCorrected| maps 
-as well. We deemed it infeasible to reconsider all of the \PLANCK~zodi 
-corrections in addition to the 3000 GHz zodi correction as a part of this 
-study. Perhaps the forthcoming \PLANCK~data release, including observations 
-acquired during additional orbits, will effectively eliminate any residual zodi
-problems in the \PLANCK~bands. Under these circumstances it might then be 
-worthwhile to consider revising the DIRBE 100$\mu$m zodi correction provided by
-SFD.
+Imperfect zodiacal light (zodi) corrections represent a second major limitation
+of our results. The ecliptic plane's prominence in our full-sky temperature map
+(Figure \ref{fig:results}) suggests that the zodiacal light subtractions 
+performed on the input maps are not ideal. Our comparisons of the FIR maps used
+in this study against H\,\textsc{i} emission bear out this notion, further 
+revealing that the imperfect zodi corrections are not limited to \verb|i100| 
+(the map for which one would expect zodiacal contamination to be most 
+problematic), but in fact are noticeable in all of the HFI 
+\verb|R1.10_nominal_ZodiCorrected| maps as well. We deemed it infeasible to 
+reconsider all of the \PLANCK~zodi corrections in addition to the 3000 GHz zodi
+correction as a part of this study. Perhaps the forthcoming \PLANCK~data 
+release, including observations acquired during additional orbits, will 
+effectively eliminate any residual zodi problems in the \PLANCK~bands. Under 
+these circumstances it might then be worthwhile to consider revising the DIRBE 
+100$\mu$m zodi correction provided by SFD.
 

### 2014-08-09 ms.tex
more minor editing/clean-up prior to submission

@@
 respectively. The bending behavior as a function of $E(B-V)_{SFD}$ has been
-eliminated, and virtually no temperature dependence remains.}
+eliminated, and virtually no temperature dependence remains. For 
+$E(B-V)_{SFD}$$\gtrsim$0.3 mag, the top plot appears noisy because there are an
+insufficient number of remaining SSPP points of comparison following our cut on
+ecliptic latitude..}
 \end{center}
@@
 
-% could add a last sentence trying to soften this, acknowledging that 
-% planck team warned about their model below 353 GHz
+% do i want to caution people not to extrapolate our 2comp model to higher
+% frequencies, similar to what planck team did in their sec. 7.2.1 ??
 

### 2014-08-09 ms.tex
improvements to several figure captions

@@
 \caption{\label{fig:post} Gridded posterior PDFs for three $N_{side}$=2048 
-pixels, based on \PLANCK~217-857 GHz and SFD 100$\mu$m at full $6.1'$ 
+HEALPix pixels, based on \PLANCK~217-857 GHz and SFD 100$\mu$m at full $6.1'$ 
 resolution. The colorscale is linear in $log(P)$, with black corresponding to 
@@
 are evident, particularly the trend of increasing $f_1$ with decreasing 
-Galactic latitude, the relatively low $f_1$ values in the Polaris flare region,
-and the clouds with relatively high $f_1$ values the north Galactic pole.}
+absolute Galactic latitude, the relatively low $f_1$ values in the Polaris 
+flare region, and the clouds with relatively high $f_1$ values near the north 
+Galactic pole.}
 \end{center}
@@
 The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. A 
-general trend of increasing $f_1$ towards lower Galactic latitudes is 
+general trend of increasing $f_1$ towards lower absolute Galactic latitudes is 
 apparent. The other most salient features are the relatively low
@@
 achieving reduced chi-squared $\chi^2_{\nu}$ shown by the black line, with 
-$\beta$=1.57 providing the best fit. Horizontal lines indicate $\chi^2_{\nu}$ 
-for other dust emission models considered, including the FDS99 best-fit 
-two-component model (Table \ref{tab:global}, model 1, red) and the 
+$\beta$=1.57 providing the best single-MBB fit. Horizontal lines indicate 
+$\chi^2_{\nu}$ for other dust emission models considered, including the FDS99 
+best-fit two-component model (Table \ref{tab:global}, model 1, red) and the 
 \cite{planckdust} single-MBB model (green). The minimum $\chi^2_{\nu}$ is 
@@
 \subsection{Reddening Calibration Procedure}
+\label{sec:calib_ebv}
 
@@
 \caption{\label{fig:calib} Linear fit of $E(B-V)_{SSPP}$ as a function of
-two-component $\tau_{545}$, illustrating our procedure for calibrating optical 
-depth to reddening.}
+two-component 545 GHz optical depth, illustrating our procedure for 
+calibrating optical depth to reddening, as described in 
+$\S$\ref{sec:calib_ebv}.}
 \end{center}
@@
 100$\mu$m, downbinned to 27.5$'$ resolution. (bottom) Corresponding full-sky 
-map of best-fit 545 GHz optical depth.}
+map of best-fit two-component 545 GHz optical depth.}
 \end{center}

### 2014-08-09 ms.tex
tweak single-pixel spectrum example figure caption

@@
 Polaris flare region. The best-fit two-component model (black line) is derived 
-based on \PLANCK~217-857 GHz and SFD 100$\mu$m at full $6.1'$ resolution. Note 
-that the two lowest-frequency data points were not used in the two-component 
-fit shown, while the three lowest-frequency data points were not used in the 
-\cite{planckdust} single-MBB fit shown (cyan).}
+via the MCMC procedure of $\S$\ref{sec:mcmc}, based on \PLANCK~217-857 GHz and 
+SFD 100$\mu$m at full $6.1'$ resolution. Note that the two lowest-frequency 
+data points were not used in the two-component fit shown, while the three 
+lowest-frequency data points were not used in the \cite{planckdust} single-MBB 
+fit shown (cyan).}
 \end{center}

### 2014-08-09 ms.tex
last pre-submission edits to introduction

@@
 relatively artifact-free broadband data covering the entire sky and a wide 
-range of frequencies. \cite{planckdust} has recently conducted a study modeling
-\PLANCK~353 GHz, 545 GHz, 857 GHz and DIRBE/\IRAS~100$\mu$m emission with a 
-single-MBB spectrum. Here we investigate the FDS99 two-component dust emission 
-model as an alernative parametrization for the dust spectral energy 
-distribution (SED) composed  of \PLANCK~High Frequency Instrument (HFI), DIRBE 
-and \IRAS~data. In doing so, we obtain maps of dust temperature and optical 
-depth, both at $6.1'$ resolution. Because we employ a model that has been 
-validated with FIRAS data down to submillimeter (submm) wavelengths, we expect 
-our best-fit parameters to be useful in constructing high-resolution 
-predictions of dust emission over a very broad range of wavelengths. This 
-includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
-model may not adequately fit, and also measurements near the peak of the dust 
-SED, for example \AKARI~140-160$\mu$m \citep{akari}. We also anticipate our 
-derived optical depth map will serve as a valuable cross-check for extinction 
-estimates based directly upon optical observations of stars 
-\citep[e.g.][]{schlafly14} and as a baseline for next-generation dust 
-extinction maps incorporating high-resolution, full-sky infrared data sets such
-as \WISE~\citep{wright10, meisner14} and \AKARI.
+range of frequencies. Towards this end, \cite{planckdust} has recently 
+conducted a study modeling \PLANCK~353 GHz, 545 GHz, 857 GHz and 
+DIRBE/\IRAS~100$\mu$m emission with a single-MBB spectrum. Here we investigate 
+the FDS99 two-component dust emission model as an alernative parametrization 
+for the 100-3000 GHz dust spectral energy distribution (SED) composed  of 
+\PLANCK~High Frequency Instrument (HFI), DIRBE and \IRAS~data. In doing so, we 
+obtain \PLANCK-based maps of dust temperature and optical depth, both at $6.1'$
+resolution. Because we employ a model that has been validated with FIRAS down 
+to millimeter wavelengths and optimized for \PLANCK, our derived parameters are
+useful in constructing high-resolution predictions of dust emission over a very
+broad range of wavelengths. This includes low frequencies (100-350 GHz), which 
+\cite{planckdust} caution their model may not adequately fit, and also 
+wavelengths near the peak of the dust SED, relevant to e.g. 
+\AKARI~140-160$\mu$m \citep{akari}. We also anticipate our derived optical 
+depth map will serve as a valuable cross-check for extinction estimates based 
+directly upon optical observations of stars \citep[e.g.][]{schlafly14} and as a
+baseline for next-generation dust extinction maps incorporating 
+high-resolution, full-sky infrared data sets such as 
+\WISE~\citep{wright10, meisner14} and \AKARI.
 

### 2014-08-10 ms.tex
removed all comments

@@
 
-% might consider changing the word `specifies' in penultimate sentence
-
-% specify early on that this is 'Galactic dust', 'dust' is kind of a vague
-% term ... on the other hand the Planck dust paper is pretty lax about this
-
-% mention more explicitly the enhanced temperature resolution relative to SFD??
-
 \end{abstract}
@@
 
-% mention re-radiation somewhere ?
-
 Over the past decades, satellite observations have dramatically enhanced our
@@
 resolution in 213 narrow frequency bins between 30 GHz and 2850 GHz.
-
-% DIRBE beam solid angles:
-% http://lambda.gsfc.nasa.gov/product/cobe/dirbe_products.cfm
 
@@
 DIRBE-based temperature correction.
-
-% additional sentence suggested by doug : 
-% The fact that the range of optical
-% properties of small silicate particles measured in the lab (Agladze et
-% al. 1996) spans the range needed by the FDS99 model makes plausible
-% that the distinct species are real.
 
@@
 100 and 143 GHz, as these have FWHM of 9.66$'$ and 7.27$'$ respectively.
-% in last sentence, reference Table 1 ?
 
@@
 isolate Galactic dust emission in the \PLANCK~maps in preparation for SED
-fitting. % reference fitting section at end of this sentence ?
+fitting.
 
@@
 
-% NEED TO MENTION SMOOTHING OF THE SMICA MAP TO 6.1 ARMCIN !!!!!!
-
 \subsection{Compact Sources}
 \label{sec:ptsrc}
-% this compact source section still needs a lot of work
 After subtracting the SMICA CMB model, we interpolate over compact sources, 
@@
 Given our pixelization (see $\S$\ref{sec:pix}), 1.56\% of pixels are masked 
-at 217-857 GHz (1.05\%, 1.02\% at 100, 143 GHz)
-
-% best to refer to an appendix for details of the point source masking ?
+at 217-857 GHz (1.05\%, 1.02\% at 100, 143 GHz).
 
@@
 
-% might consider quoting rounder values in text, most precise values are:
-% 100 GHz, J=1->0 : 1.478e-5, 217 GHz, J=2->1 : 4.585e-5, 
-% 353 GHz, J=3->2 : 1.751e-4
-
 \begin{equation} \label{equ:molcorr}
@@
 
-% maybe a final sentence or two warning that, to whatever extent
-% CO line ratios vary over the sky and/or other molecules make a substantial
-% contribution to the observed Planck intensities, our molecular emission
-% correction will be insufficient
-
-% for CO line list see ~/wise/pro/planck_co_lines.pro
-
 \subsection{Zero Level}
 \label{sec:zp}
-
-% for quantitative assessment of the zero-point difference due to
-% flattening of 857 GHz vs. HI, see 
-% ~/Desktop/dust/planck_hi/piecewise.pdf (on my Mac)
-
-% -> at low HI, slope decreases by a factor of 1.88
-%    the resulting difference in 857 GHz zero points is 0.373 MJy/sr
 
@@
 MJy/sr.
-
-% maybe state approximately what 0.37 MJy/sr at 857 GHz equates to in EBV
-% --> did a quick calculation and it's only ~0.0118 mags ... thought it
-%     would be more ??
 
@@
 
-% i evaluated the `formal statistical error' using the covar keyword in
-% hogg_iter_linfit
-
 The formal statistical error on the best-fit 857 GHz offset is quite small, 
@@
 rms of the per-quadrant offsets was 0.0586 MJy/sr.
-
-% what HI intensity does the 2.15 MJy/sr 857 GHz correspond to ?
-%  ---> pretty high actually
 
@@
 
-% mention how offset/dipole values compare to those derived in the Planck
-% team paper ?
-
 \section{Dust Emission Model}
 \label{sec:modeling}
-
-% maybe a sentence to transition from preprocessing -> modeling
-% e.g. With pre-processing completed, we turned to modeling the 
-% thermal dust emission.
 
@@
 
-% kind of feel like i'm re-writing the introduction here ??
-
-% could add a last sentence 'ultimately this allows us to make high-resolution
-% foreground and extinction predictions' and/or even find a way to mention
-% other predictions, such as polarization/R_v
-
-% in the above paragraph, should I mention the Planck collaboration result
-% of beta_mm vs. beta_fir being different, with (beta_fir-beta_mm) > 0
-
-% should i also try to justify why it's worth doing this fit even
-% if it's possible to just claim different beta's at different frequencies?
-
 The shape of the two-component model spectrum we will consider is given by:
@@
 \end{equation}
-
-% With $f_{1}$ = 0.0363, $\beta_1$ = 1.67, $\beta_2$ = 2.70, and $q_1/q_2$ = 
-% 13.0.
-
-% re: following paragraph --- in the code nu_0 is actually 2997.92458
-% because this is the frequency with respect to which DIRBE color correction
-% K_100 (and my color correction as well) is referenced
-
-% not sure if `Planck function' is the correct jargon
 
@@
 Equation 14).
-
-% Importantly, the emissivity power law indices $\beta$ of the two species 
-% differ.
 
@@
 second row of Table \ref{tab:global}.
-
-%%%%
 
@@
 
-% would be great to have uncertainties on each parameter as well (in the
-% Planck case at least...) !!!!!!!!!!!!!!!
-
-%%%%
-
 Fixing the aforementioned four global parameters, our full-resolution, 
@@
 third free parameter, still holding $\beta_1$, $\beta_2$, and $q_1/q_2$ fixed.
-
-%explain that we take the ``hot'' dust temperature to be T2 rather than T1
-
-% maybe point to the SED fit summary figure as an example of what
-%
 
@@
 
-% is delta(nu)/nu conventionally (nu_off-nu_on)/nu_c or 1/2 of that ?
-
 \begin{equation} \label{equ:bpcorr}
@@
 \end{equation}
-
-% integral limits ??? check planck paper to see what they did
-% -> planck spectral response paper just leaves the integrals indefinite
 
@@
 
-%Again, since DIRBE-quoted fluxes also follow the 
-%$\alpha$=$-1$ convention, Equation \ref{equ:bpcorr} remains applicable.
-
-% what is the reference for the dirbe
-
-%The color correction factors
-%of Equation \ref{equ:bpcorr} are applied in the sense that 
-%$b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ is a prediction suitable for 
-%direct comparison to the \PLANCK~data products.
-
 The two-component model prediction in band $\nu_i$ under the IRAS convention, 
@@
 
-%Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. 
 The color correction of Equation \ref{equ:bpcorr} therefore allows us to 
@@
 
-% need some sort of clarification about the fact that, in the parts of the 
-% analysis where beta floats, i actually do interpolate color corrections 
-% off of a 2d grid in (T, beta)
-
-% We note that it is not clear which bandpass should properly be ascribed to 
-% the \IRAS/DIRBE composite 100$\mu$m maps under consideration.
-
 With these color corrections and the  formalism established in 
@@
 
-%is the old sentence below worth reinstating ?
-
-%To reiterate, for 
-%$\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ has units of 
-%(MJy/sr)/$K_{CMB}$,and therefore $\tilde{I}_{\nu_{i}}$ will have different 
-%units depending on the band $\nu_i$, though $\tilde{I}_{\nu_{i}}$ always has 
-%the same units as the native band $\nu_i$ map.
-
-% check that RIMO file i've used is actually the most up-to-date version
-
-% extremely abrupt transition here...
 \section{Global Model Parameters}
@@
 $\S$\ref{sec:relzero} (see Figure \ref{fig:dirbe_slopes}).
-% re-mention nside=64 or just bag it?
-% restricted to same low HI mask as in Sect. 3.5.2 analysis
-% sentence pointing to figure showing the regressions
 
@@
 
-% maybe a table listing the correlation slopes and their uncertainties
-% would be useful here
-
 \section{MCMC Fitting Procedure}
@@
 \end{figure}
-
-% add error bars to this example SED plot
 
@@
 \end{figure*}
-
-% overplot ellipses showing 1 sigma errors in posterior grayscales
 
@@
 
-% sentence or two mentioning reduced resolution fits where we sample in
-% three dimensions (f_1, T_2, tilde{I}_{545})
-
 \subsection{Markov Chains}
@@
 
-% be careful about notational consistency with e.g. tildes, etc.. in this sect
-
 Here $\mathbf{I}$ denotes the vector of observed thermal dust intensities 
@@
 
-%\begin{equation} \label{equ:like}
-%\mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(\tilde{I}_{\nu_{i}}|I_{\nu_{i}}, \sigma_{\nu_i})
-%\end{equation}
-
 \begin{equation} \label{equ:like}
@@
 \end{equation}
-
-%be more careful about notation re: color corrections
 
@@
 \end{multline}
-
-% is I_nu on RHS inclusive of offsets or is it the ``pure'' thermal dust
-% intensity
-
-% need to make sure to cite planckcalib paper
 
@@
 
-% mention that each of the error terms is always rescaled properly according
-% to smoothing/rebinning and relevant power spectrum
-
 We include the following prior on the hot dust temperature:
@@
 
-%Some of 
-%the most striking features occur near the north Galactic pole, and to 
-%highlight these regions of unusually high $f_1$, we display the northern
-%Galactic hemisphere in Lambert projection in Figure \ref{fig:f1}.
-
 \subsection{Global Parameters Revisited}
@@
 GHz relative to a model with appropriately chosen spatially constant $\beta$.
-
-% mention that when t floats, we find a lower T by ~ 1 degree than the Planck 
-%team?
 
@@
 
-% could compare temperatures from correlation slope analysis versus here, but 
-% masks are different, so i guess it's just not worth it
-
 \section{Optical Reddening}
@@
 reddening estimates relative to SFD.
-
-% mention that this is especially true because Planck gives such a huge
-% increase in temperature resolution relative to SFD (and possibly reference
-% temperature comparison figure as well)
 
@@
 Parameter Pipeline \citep[SSPP,][]{sspp}.
-
-% make argument that, in models with f1 and the beta's constant, the choice
-% of frequency at which tau is evaluated does not matter
 
@@
 
-% MENTION THAT THE TAU TEMPLATE IS INDEPENDENT OF FREQUENCY FOR 
-% TWO-COMPONENT MODELS WITH SPATIALLY CONSTANT BETAS, Q1/Q2 AND F1
-
 This regression is illustrated in Figure \ref{fig:calib}. As expected, there 
@@
 (e.g. inner vs. outer Galaxy) on to the $E(B-V)_{SFD}$ axis.
-
-% could add a sentence praising the two-component reddening prediction for
-% only having issues at the ~<10 mmag level for EBV_SFD ~< 0.4 mag, since
-% it could be a lot worse ...
 
@@
 residuals.
-% last few words here are kind of bad, need better terminology
 
@@
 \end{figure}
-
-%%\section{Systematics}
-%%
-%%\subsection{CIBA}
-%%Perhaps the dominant limitation of our fits is the presence of cosmic
-%%infrared background anisotropies (CIBA) bleeding through into our maps of 
-%%Galactic dust temperature and optical depth in high-latitude regions 
-%%\citep{ciba}.
-%%\subsubsection{Simulations}
-
-%%\subsubsection{Optimizing Relative Weights}
-
-%%\subsection{Zero Point}
-%%Simulate the effect of getting zero points wrong to quantiy this
-%%systematic a bit.
-
-%%\subsection{$T_{2}$ Prior}
-%%Use FIRAS data to justify $T_2$ prior. Could I use the DIRBE 100/240 micron
-%%ratio to get a $1.3^{\circ}$ resolution prior on $T_2$?
-
-%%\subsection{Other Limitations}
-%%\IRAS~is missing in some parts of sky which will therefore not truly have 
-%%6.1' resolution.
-%%any other miscellaneous issues?
 
@@
 
-% do i want to caution people not to extrapolate our 2comp model to higher
-% frequencies, similar to what planck team did in their sec. 7.2.1 ??
-
-% mention imprint of Planck team's half-degree on low-freq extrapolation ?
-
-% is this the section where, potentially, plots of the residuals might go?
-
-%%%It is true that we have smoothed the input intensity maps for this study 
-%%%to $6.1'$ FWHM, which is nominally lower resolution than the $5'$ 
-%%%\cite{planckdust} maps. However, as is apparent from figure 
-%%%\ref{fig:comparison}, the fact that \cite{planckdust} modeled $\beta$ at 
-%%%$0.5^{\circ}$ resolution has effectively blurred their dust temperature map.
-
 \section{Data Release}
@@
 FITS file headers for further details.\footnote{\texttt{http://faun.rc.fas.harvard.edu/ameisner/planckdust}}
-
-% if we're not going to be claiming to be superseding SFD in terms of 
-% reddening, then do we even want to include anything extinction-related
-% (data files and/or code) in this data release ?
 
@@
 
-% in above paragraph, say which single-MBB beta(s) we find to be favored ?
-
 Nevertheless, we have established that the two-component emission model remains
@@
 
-% sentence criticizing the half-degree beta single MBB model of Planck team
-% in terms of the imprint that leaves on low-frequency emission 
-% predictions ?
-
 \subsection{Towards a Replacement for SFD}
@@
 
-% CIBA
 The CIBA remains a major imperfection that still requires further 
@@
 
-% could add a sentence noting that similar zodi corrections are evident
-% in all existing, comparable temperature map data products : Planck 2013a,
-% SFD98 and FDS99
-
-% audit for word ``zodi'' ... is this an acceptable jargon term ?
-% could use IPD as an abbreviation at certain points, not sure if i've 
-% defined that acronym already somewhere else in the text?
-
 Irrespective of the notable imperfections in our results, more detailed
@@
 
-% perhaps zodi will just magically be fixed in the forthcoming Planck
-%   ---> do i want a figure illustrating the CIBA problem at high latitude ?
-%  ---> zodi
-%  ---> more testing needed, in any event, to prove Planck based reddening
-%       estimates outperform SFD
-
-% should mention that one definitive improvement of this work relative
-% to FDS99 is that there are uncertainty/covariances provided for
-% the derived parameters !!!!
-
-% should there be a future work section or can the suggestions/plans of
-% future work just be a part of ``SFD replacement'' subsection
-
-% mention here the idea of getting even higher resolution by folding
-% in WISE ?
-
 This material is based upon work supported by the National Science Foundation 

### 2014-09-13 ms.tex
version that was actually submitted

@@
 We also derive full-sky $6.1'$ resolution maps of dust optical depth and 
-temperature by fitting the two-component model to \PLANCK~217, 353, 545, and 
-857 GHz along with  DIRBE/\IRAS~100$\mu$m data. Because our two-component model
+temperature by fitting the two-component model to \PLANCK~217-857 GHz along 
+with  DIRBE/\IRAS~100$\mu$m data. Because our two-component model
 matches the dust spectrum near its peak, accounts for the flattening of the 
@@
 6.1$'$ FWHM, our model provides reliable, high-resolution thermal dust emission
-foreground predictions from 100 GHz to 3000 GHz. We find that, in diffuse sky 
-regions, our two-component 100-217 GHz thermal dust emission predictions are on
+foreground predictions from 100 to 3000 GHz. We find that, in diffuse sky 
+regions, our two-component 100-217 GHz predictions are on
 average accurate to within 2.2\%, while the \cite{planckdust} single-MBB model 
 systematically underpredicts emission by 18.8\% at 100 GHz, 12.6\% at 143 GHz 
-and 7.9\% at 217 GHz. We calibrate our two-component optical depth to reddening
-at visible wavelengths, and compare the resulting reddening estimates with 
+and 7.9\% at 217 GHz. We calibrate our two-component optical depth to 
+reddening, and compare the resulting reddening estimates with 
 those based on stellar spectra. We find imperfect zodiacal light subtraction in

### 2014-09-14 ms.tex
less optimism about revised Planck zodi corrections

@@
 reconsider all of the \PLANCK~zodi corrections in addition to the 3000 GHz zodi
-correction as a part of this study. Perhaps the forthcoming \PLANCK~data 
-release, including observations acquired during additional orbits, will 
-effectively eliminate any residual zodi problems in the \PLANCK~bands. Under 
-these circumstances it might then be worthwhile to consider revising the DIRBE 
-100$\mu$m zodi correction provided by SFD.
+correction as a part of this study, especially considering that the forthcoming
+\PLANCK~2014 release is expected to include a revised/improved zodi 
+subtraction.
+
+%Perhaps the forthcoming \PLANCK~data 
+%release, including observations acquired during additional orbits, will 
+%effectively eliminate any residual zodi problems in the \PLANCK~bands. Under 
+%these circumstances it might then be worthwhile to consider revising the DIRBE
+%100$\mu$m zodi correction provided by SFD.
 

### 2014-09-14 ms.tex
per referee suggestion, mention Figure 7 of 2011 Planck team dust paper
thank refere
corrected typo in beta threshold in section 9

@@
 used for the goodness-of-fit analysis of $\S$\ref{sec:hier}, with 
-$|b|>30^{\circ}$ and $|\beta|>30^{\circ}$, also avoiding molecular emission, 
+$|b|>30^{\circ}$ and $|\beta|>10^{\circ}$, also avoiding molecular emission, 
 the SMICA inpainting mask, and compact sources. We then perform a linear fit 
@@
 underprediction at 217 GHz, a 12.6\% underprediction at 143 GHz and an 18.8\% 
-underprediction at 100 GHz.
+underprediction at 100 GHz. A deficit in single-MBB predictions relative to
+the observed \PLANCK~100-217 GHz emission was also noted in 
+\cite{planckdust2011}, e.g. their Figure 7.
 
@@
 
+We would like to thank the anonymous referee for their helpful suggestions. 
 This material is based upon work supported by the National Science Foundation 

### 2015-01-18 ms.tex
capitalize AKARI as per referee suggestion
more about 143 GHz CO to placate referee
clean up

--- 2014-09-13 ms.tex
@@
 We also derive full-sky $6.1'$ resolution maps of dust optical depth and 
-temperature by fitting the two-component model to \PLANCK~217-857 GHz along 
-with  DIRBE/\IRAS~100$\mu$m data. Because our two-component model
+temperature by fitting the two-component model to \PLANCK~217, 353, 545, and 
+857 GHz along with  DIRBE/\IRAS~100$\mu$m data. Because our two-component model
 matches the dust spectrum near its peak, accounts for the flattening of the 
@@
 6.1$'$ FWHM, our model provides reliable, high-resolution thermal dust emission
-foreground predictions from 100 to 3000 GHz. We find that, in diffuse sky 
-regions, our two-component 100-217 GHz predictions are on
+foreground predictions from 100 GHz to 3000 GHz. We find that, in diffuse sky 
+regions, our two-component 100-217 GHz thermal dust emission predictions are on
 average accurate to within 2.2\%, while the \cite{planckdust} single-MBB model 
 systematically underpredicts emission by 18.8\% at 100 GHz, 12.6\% at 143 GHz 
-and 7.9\% at 217 GHz. We calibrate our two-component optical depth to 
-reddening, and compare the resulting reddening estimates with 
+and 7.9\% at 217 GHz. We calibrate our two-component optical depth to reddening
+at visible wavelengths, and compare the resulting reddening estimates with 
 those based on stellar spectra. We find imperfect zodiacal light subtraction in
@@
 (CMB). 
-
 Over the past decades, satellite observations have dramatically enhanced our
@@
 Given our pixelization (see $\S$\ref{sec:pix}), 1.56\% of pixels are masked 
-at 217-857 GHz (1.05\%, 1.02\% at 100, 143 GHz).
+at 217-857 GHz (1.05\%, 1.02\% at 100, 143 GHz)
 
